---
title: "alternate_cues_analysis_updated"
author: "Neha"
date: "2026-02-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(readr)
#AlternateCues <- read_csv("~/Desktop/Mayr_lab/Data_analysis_project/AlternateCues/AlternateCues.csv")

AlternateCues <- read_csv("AlternateCues.csv")
View(AlternateCues)

library(tidyverse)
tibble_summary<- AlternateCues %>% 
  summary() %>% 
  tibble()
  


```

 have to remove practice blocks + the 5 unusable subjects (901, 959, 201, 975, 902) : 

Note: subject 4 can have duplicate trials removed 


```{r}

library(tidyverse)
d_use <- data %>%
  filter(!id %in% c(901, 959, 201, 975, 902)) %>% 
  droplevels()


unique(d_use$id) ## 73 subjects 

d_use <- d_use %>% 
  filter(block != 0) %>% 
  droplevels()

unique(d_use$block)

```


```{r}


id_4_clean <- d_use %>%
  filter(id == 4) %>% 
  group_by(id, block, trial) %>%
  slice(1) %>%   # keep first occurrence
  ungroup() %>% 
  droplevels()
```


```{r}
data_fixed <- d_use %>%
  filter(id != 4) %>%   # keep everyone else untouched
  bind_rows(id_4_clean) %>% 
  droplevels()

```

Sanity checks

After removing duplication-- should return back 0 for n>1

```{r}


data_fixed %>%
  count(id, block, trial) %>%
  filter(n > 1) %>% 
  droplevels()

unique(data_fixed$id) ## 73 subjects 

usable_subjects <- c(9  ,    12  ,   15  ,   10    , 11  ,   16    , 13  ,   17   ,  14 ,    8  ,    7 ,     3  ,    5  ,    99 ,    202  ,  203 ,   204  ,  401 ,   402 ,   403  ,  404,    405 ,   406 ,   501 ,   502 ,   503  ,  504 ,   505 ,   701  ,  702 ,   703  ,  704  ,  705 ,   706  ,  707  ,  708  ,  752 ,   750445, 75033,  800 ,   903,    904 ,   905 ,   906 ,   907 ,   908 ,   909 ,   910  ,  911  ,  912  ,  913 ,   914 ,   915,    916 ,   917  ,  918 ,   919  ,  953  ,  954 ,   958 ,   961422, 962,    963  ,  964,    965  ,  966,    967   , 968  ,  969 ,   970 ,   971  ,  974,    4    )
length(usable_subjects) # 73 subjects 


```

removing subjects below accuracy level of 80% 

```{r}


d_f <- data_fixed %>%
  mutate(error = as.numeric(as.character(error)))

str(d_f$error)

table(d_f$error) # 0 with 40814 trials and 1 with 2986 trials 

accuracy_per_subject <- d_f %>%
  group_by(id) %>%
  summarise(accuracy = 1 - mean(error, na.rm = TRUE))

# 2. See who falls below 80% accuracy:
accuracy_per_subject %>%
  filter(accuracy < 0.80) ## ids 202 and 914 have accuracy less than 80% 

# IDs below 80% accuracy
low_acc_ids <- accuracy_per_subject %>%
  filter(accuracy < 0.8) %>%
  pull(id)
low_acc_ids

d_final <- d_f %>% 
   filter(!id %in% c(202, 914)) %>% 
  droplevels()

unique(d_final$id) ## 71 subjects that are usable ## so overall- had to remove 8 subjects. 

```

###################################### Making new variables ############################################################################################################


A. making the valence of each group 

valence of current group has levels 1 and 2
valence of previous group has levels 1 and 2

- each group consists of three trials with the cycle variable as 1,2, and 3 (so first trials has cycle as 1 and the third trial has cycle as 3)
-valence of current group is 1 if dim 1 or dim 2 has the value of 4 
- valence of previous group is also 1 if dim 1 and dim 2 has the value of 4 
- if dim 1 and dim 2 have any values from 1-3, then the valence of current and previous group will be assigned as 2 

1- valence of current group


```{r}
library(dplyr)


d_final <- d_final %>%
  group_by(id, block) %>% 
  # valence of current group
  mutate(valence_current_group = if_else(dim1 == 4 | dim2 == 4, 1, 2)) # univalent is coded as 1 and bivalent is coded as 2 

names(d_final)
levels(d_final$valence_current_group) ## have to convert this to factor before analysis 

#unique(d_final$id)

```

2- valence_previous_group 
Lag by 3 trials within each subject (each group = 3 trials)

```{r}
d_final <- d_final %>%
  group_by(id, block) %>%       # only by subject
  #arrange(block, trial) %>%   
  mutate(valence_previous_group = lag(valence_current_group, 3)) %>%
  ungroup()


names(d_final)

# lag 1 
# turn all but first trial as NA
# fill will prapagate first value

```

3- switch variable 

```{r}

library(dplyr)

d_final <- d_final %>%
  group_by(id, block) %>%        
  mutate(
    switch = if_else(task != lag(task), 1, 0)  # 1 if task changed from previous trial
  ) %>%
  ungroup()

names(d_final)

```
I should also make prev_error variable before removing the first group of trials 

```{r}

library(tidyverse)

d_final <- d_final %>%
  group_by(id, block) %>%     # IMPORTANT
  mutate(prev_error = lag(error)) %>%
  ungroup()



```


have to first remove trials below the third trial of every block as they may not be in a group of three 

```{r}



d_final <- d_final %>%
  group_by(id, block) %>%          
  filter( trial>3) %>%   ## removes all the trials on each block that are less than the third trial 
  ungroup() %>%
  droplevels()


# trial != min(trial) &

##note: trial 4 of some blocks for some subjects (203,402,405,502,503,504) are being removed for d_final_analysis- is this due to trial != min(trial) & trial>3: because min trial is now 4??  so, removed trial != min(trial) and now i do have trial 4 for all the subjects. 
  
#   checking if all ids have trial 4: 

# num_id <- d_final_analysis %>% 
#  group_by(id, block) %>% 
#   filter( trial ==4)
# 
# unique(num_id$id) ## so all ids have trial == 4 for all blocks 

```


making trial variable that does not reset with each block 

```{r}
library(dplyr)

d_final <- d_final %>%
  group_by(id) %>%
  mutate(trial_num = row_number()) %>%
  ungroup()

```


```{r}

# library(dplyr)
# 
# d_c <- data_use %>%
#   
#   # 2. Compute z-scores for reaction time
#   mutate(rt_z = scale(time)) %>%
#   
#   # 3. Remove extreme reaction times (|z| > 3)
#   filter(abs(rt_z) <= 3) %>% 
#   droplevels()




## remove first trial from eaxh bloxk after making the new variables cause it is only used for analysis 
## have not run this yet
# d_c_analysis <- data_c %>%
#   # 1. Remove the first trial of each block
#   group_by(id, block) %>%
#   filter(trial != min(trial, na.rm = TRUE)) %>%
#   ungroup() %>%


d_final_rt <- d_final

# d_final_rt %>%
#   group_by(subject) %>%   
#   filter(!(error == 1 | lead(error) == 1)) %>%
#   ungroup()

rt_estimation <- d_final_rt %>%
  filter(error == 0, prev_error == 0)

rt_stats <- rt_estimation %>%
  group_by(
    id,
    valence_current_group,
    valence_previous_group,
    cycle
  ) %>%
  summarise(
    mean_rt = mean(time, na.rm = TRUE),
    sd_rt   = sd(time, na.rm = TRUE),
    .groups = "drop"
  )

d_final_rt <- d_final_rt %>%
  left_join(
    rt_stats,
    by = c(
      "id",
      "valence_current_group",
      "valence_previous_group",
      "cycle"
    )
  )

d_final_rt <- d_final_rt %>%
  mutate(rt_z = (time - mean_rt) / sd_rt)

d_final_rt <- d_final_rt %>%
  filter(abs(rt_z) < 3)


## checking for NAs: 

sum(is.na(d_final_rt$rt_z)) # 0 

sum(is.na(d_final_rt$prev_error)) # 0 

d_final_analysis <- d_final_rt

```


No, after removing outlier trials based on rt cutoff, I have 40,454 observations of 23 variables 


```{r}

getwd()
write.csv(d_final_analysis, "/Users/nehanagarkar/Desktop/Mayr_lab/Data_analysis_project/AlternateCues/d_final_analysis.csv", row.names = FALSE)

```

######################################################################### Analysis #######################################################################

Note: 
(i)For the RT models, error trials, and trials before errors should also be removed
(ii) - using the Valence_current_group variable --> make new variable val_c_g with levels -0.5 for (Valence_current_group == 1) and + 0.5 for (Valence_current_group == 2) 
     - using the Valence_previous_group variable --> make new variable val_p_g with levels -0.5 for (Valence_previous_group == 1) and + 0.5 for Valence_previous_group == 2) 
     

Coding: 

- Switch (0 - no switch; 1 - switch) 

- Valence_current_group (-0.5 - univalent; 0.5 bivalent) - so make new variable with this 

- Valence_previous_group (-0.5 - univalent; 0.5 bivalent) - so make new variable with this 

Models: 

lmer(RT ~ Valence_current_group * Valence_previous_group*Switch + (Valence_current_group + Valence_previous_group + Switch|Subject)) 

glmer(Error ~ Valence_current_group * Valence_previous_group*Switch + (Valence_current_group + Valence_previous_group + Switch|Subject), family = “binomial”, control = glmerControl(optimizer = “bobyqa”)) 


A. New variables for valence of current and previous group according to -0.5 and +0.5 coding 


```{r}


class(d_final_analysis)

d_final_analysis$val_c_g <- ifelse(d_final_analysis$valence_current_group == 1, -0.5,
                     ifelse(d_final_analysis$valence_current_group == 2,  0.5, NA))

d_final_analysis$val_p_g <- ifelse(d_final_analysis$valence_previous_group == 1, -0.5,
                     ifelse(d_final_analysis$valence_previous_group == 2,  0.5, NA))




```

```{r}

df_models <- d_final_analysis

### DO NOT CONVERT VARIABLES THAT THE MODEL SHOULD TREAT AS FACTORS MANUALLY INTO AS FACTORS!! BECAUSE IT WILL TREAT THE VARIABLES AS DDUMMY CODING!!! 

# df_models$id <- factor(df_models$id)
# df_models$val_c_g <- factor(df_models$val_c_g)
# df_models$val_p_g <- factor(df_models$val_p_g)
# df_models$switch <- factor(df_models$switch)
# df_models$error <- factor(df_models$error)
# df_models$prev_error <- factor(df_models$prev_error)
# 
# 
# levels(df_models$id)
# levels(df_models$val_c_g)
# levels(df_models$val_p_g)
# levels(df_models$switch)
# levels(df_models$error)
# levels(df_models$prev_error)

```

c. Models 


1. lmer model

-For the RT models, error trials, and trials before errors should also be removed
Q: should it be block wise? or across all trials? 

remove  error == 0 and prev_error == 0 for the d_final_analysis inside lmer model filter()

```{r}

library(lme4)

df_models_rt <- df_models 

library(tidyverse)

df_models_rt <- df_models_rt %>%
  filter(error == 0, prev_error == 0)
  

  m_rt<- lmer(log(time) ~  val_c_g * val_p_g* switch + (val_c_g + val_p_g + switch ||  id),
                 data = df_models_rt,
                  na.action = na.exclude)
              
                # control = lmerControl(optimizer = "bobyqa"))


 
 summary(m_rt)
 
 
#library(sjPlot)
 tab_model(m_rt,show.est=T,auto.label=F,show.stat=T)
 
 
 names(df_models)
```


2. glmer model

```{r}


df_models$error <- as.factor(df_models$error)
levels(df_models$error)

  m_error<- glmer(error ~  val_c_g * val_p_g * switch + ( val_c_g +  val_p_g + switch| id),
                 data = df_models, 
                 family = "binomial",
                  na.action = na.exclude, 
                 control = glmerControl(optimizer = "bobyqa"))

 
 summary(m_error)
 
 tab_model(m_error,show.est=T,auto.label=F,show.stat=T)
```

################################################################################################################################
                                                   DDM 
#| include: false
#first putting in some pre-made functions that will go into the ezDDM analysis: 

```{r}

normWS <- function(d ,s, dv, between = NULL) { #within subject normalization
  eval(substitute(d %>%
                    dplyr::group_by(s) %>%
                    dplyr::mutate(sAV = mean(dv, na.rm = TRUE)) %>%
                    dplyr::group_by_at(between) %>% #this is grouping by between subjects variables
                    dplyr::mutate(gAV = mean(dv, na.rm = TRUE)) %>%
                    dplyr::mutate(DV_n = dv - sAV + gAV), list(s = as.name(s), dv = as.name(dv))))
}


get_ci <- function(var, mean){
  sd <- sd(var, na.rm = TRUE)
  n <- length(var)
  se <- sd/sqrt(n)
  ci <- abs(qt(0.025, n-1, lower.tail = FALSE))*se
  return(c(mean + ci, mean - ci, sd, se, n))
}

convert_extremes <- function(value){
  
  if(value == 1){
    
    value = value - 1e-5
    
  } else if (value == 0 ){
    
    value = value + 1e-5
    
  }
  
  return(value)
  
}#making sure error is either .99 or .001
```


## Aggregation and data processing

--hausekeep 

install.packages("cli")
packageVersion("cli") -- should show ≥ 3.6.5-- it is 3.6.5 
install.packages("devtools")
devtools::install_github("hauselin/hausekeep")
library(hausekeep)

```{r}
library(devtools)
library(rio)
library(hausekeep)


library(tidyverse)
alt_cue_agg_ID_ddm <- d_final_analysis %>%
  mutate(RT_s = time/1000) %>%
  group_by(id, val_c_g, val_p_g, switch, cycle) %>%
  summarize(RT_s_m = mean(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            Error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>%
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  
  unnest(ezddm)



alt_cue_agg_ddm <- alt_cue_agg_ID_ddm %>%
  group_by(id, val_c_g, val_p_g, switch, cycle) %>%
  normWS(s = "id", dv = "a") %>%
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>%
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>%
  mutate(Ter = DV_n) %>%
  group_by(val_c_g, val_p_g, switch, cycle) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[1],
            a_ci_upper = get_ci(a, a_m)[2],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[1],
            v_ci_upper = get_ci(v, v_m)[2],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[1],
            Ter_ci_upper = get_ci(Ter, Ter_m)[2],)

#make a separate object that is averaging across the no-switch 2,3 and 4 average within those and then average within those variances
alt_cue_agg_ID_ddm_collapsed <- alt_cue_agg_ID_ddm %>% 
  filter(switch == 0, cycle %in% c(2, 3)) %>%
  group_by(id, val_c_g, val_p_g) %>% 
  summarize( # average the DDM parameters across cycles 2&3 
    a = mean(a, na.rm = TRUE), 
    v = mean(v, na.rm = TRUE), #average within those 
    Ter = mean(Ter, na.rm = TRUE), 
    a_var = mean(a^2, na.rm = TRUE), #average within those variances
    v_var = mean(v^2, na.rm = TRUE), 
    Ter_var = mean(Ter^2, na.rm = TRUE), 
    .groups = "drop" )

alt_cue_agg_ID_ddm_collapsed

alt_cue_agg_ID_ddm %>% filter(switch == 0, cycle %in% c(2,3)) %>% count(id, val_c_g, val_p_g)
```



```{r}

# alt_cue_agg_ddm$is_bivalent <- ifelse(alt_cue_agg_ddm$valence_current_group == 1 , 1,
#                      ifelse(d_final_analysis$valence_current_group == 2,  2, NA))
# 
# alt_cue_agg_ddm$prev_bivalent <- ifelse(alt_cue_agg_ddm$valence_previous_group == 1, 1,
#                      ifelse(d_final_analysis$valence_previous_group == 2,  2, NA))
# 
# 
# alt_cue_agg_ID_ddm$is_bivalent <- ifelse(alt_cue_agg_ID_ddm$valence_current_group == 1 , 1,
#                      ifelse(d_final_analysis$valence_current_group == 2,  2, NA))
# 
# alt_cue_agg_ID_ddm$prev_bivalent <- ifelse(alt_cue_agg_ID_ddm$valence_previous_group == 1, 1,
#                      ifelse(d_final_analysis$valence_previous_group == 2,  2, NA))


```


## Plots

```{r}
pos <- position_dodge(width = 0.1)

alt_cue_agg_ddm$val_c_g <- as.factor(alt_cue_agg_ddm$val_c_g)
alt_cue_agg_ddm$val_p_g <- as.factor(alt_cue_agg_ddm$val_p_g)

plt_ddm_a <- ggplot(alt_cue_agg_ddm, aes(x = cycle, y = a_m, color = val_c_g, linetype = val_p_g, group = interaction(val_c_g, val_p_g)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper), width = 0.1, position = pos)+
  theme_classic()

plt_ddm_v <- ggplot(alt_cue_agg_ddm, aes(x = cycle, y = v_m, color = val_c_g, linetype = val_p_g, group = interaction(val_c_g, val_p_g)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper), width = 0.1, position = pos)+
  theme_classic()


plt_ddm_Ter <- ggplot(alt_cue_agg_ddm, aes(x = cycle, y = Ter_m, color = val_c_g, linetype = val_p_g, group = interaction(val_c_g, val_p_g)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper), width = 0.1, position = pos)+
  theme_classic()

ggpubr::ggarrange(plt_ddm_a, plt_ddm_v, plt_ddm_Ter, common.legend = TRUE, nrow = 1)  
  

```

## Statistical Models

### First prep data so that it's ignoring cycle

```{r}
alt_cue_agg_ID_ddm_nocycle <- d_final_analysis %>%
  mutate(RT_s = time/1000) %>%
  group_by(id, valence_current_group, valence_previous_group, val_c_g, val_p_g, switch) %>%
  summarize(RT_s_m = mean(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            Error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>%
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  unnest(ezddm)
```

### Models

```{r}

library(sjPlot)
 library(lme4)


### all these models show singular 
## can remove random effect of previous bivalance as it's effect may be very similar across subjects with less variance on rt and the ddm parameters based on previous bivalance across subjects 

## Ulrich: remove the random effects and only keep intercept 


# 
# alt_cue_a <- lmer(a ~ val_c_g * val_p_g * switch + (val_c_g + val_p_g + switch| id), 
#      alt_cue_agg_ID_ddm_nocycle)

alt_cue_a <- lmer(a ~ val_c_g * val_p_g * switch + (1 | id), alt_cue_agg_ID_ddm_nocycle)


summary(alt_cue_a)

tab_model(alt_cue_a)

alt_cue_v <- lmer(v ~  val_c_g * val_p_g * switch + (1 |id), 
     alt_cue_agg_ID_ddm_nocycle)

summary(alt_cue_v)

tab_model(alt_cue_v)


alt_cue_Ter <- lmer(Ter ~  val_c_g * val_p_g * switch + (1 |id), 
     alt_cue_agg_ID_ddm_nocycle)

summary(alt_cue_Ter)

tab_model(alt_cue_Ter)
```

descriptive plots 

1. rt
```{r}

library(dplyr)
library(ggplot2)

rt_plot_df <- d_final_analysis %>%
  filter(error == 0, prev_error == 0) %>%
  group_by(valence_current_group,
           valence_previous_group,
           cycle) %>%
  summarise(
    mean_rt = mean(time, na.rm = TRUE),
    se_rt   = sd(time, na.rm = TRUE)/sqrt(n()),
    .groups = "drop"
  )
rt_plot_df <- rt_plot_df %>%
  mutate(
    cycle = factor(cycle, levels = c(1,2,3)),
    valence_current_group = factor(valence_current_group,
                                   labels = c("Current: Univalent",
                                              "Current: Bivalent")),
    valence_previous_group = factor(valence_previous_group,
                                    labels = c("Previous: Univalent",
                                               "Previous: Bivalent"))
  )

ggplot(rt_plot_df,
       aes(x = cycle,
           y = mean_rt,
           color = valence_current_group,
           linetype = valence_previous_group,
           group = interaction(valence_current_group,
                               valence_previous_group))) +
  
  geom_line(size = 1) +
  geom_point(size = 3) +
  
  geom_errorbar(aes(ymin = mean_rt - se_rt,
                    ymax = mean_rt + se_rt),
                width = .1) +
  
  labs(
    x = "Cycle",
    y = "Mean RT (ms)",
    color = "Current Group",
    linetype = "Previous Group"
  ) +
  
  theme_classic(base_size = 14)


```

2. error 

```{r}
library(dplyr)
library(ggplot2)

err_plot_df <- d_final_analysis %>%
  group_by(valence_current_group,
           valence_previous_group,
           cycle) %>%
  summarise(
    error_rate = mean(error, na.rm = TRUE),
    se_error   = sd(error, na.rm = TRUE)/sqrt(n()),
    .groups = "drop"
  )
err_plot_df <- err_plot_df %>%
  mutate(
    cycle = factor(cycle, levels = c(1,2,3)),
    
    valence_current_group = factor(
      valence_current_group,
      labels = c("Current: Univalent",
                 "Current: Bivalent")
    ),
    
    valence_previous_group = factor(
      valence_previous_group,
      labels = c("Previous: Univalent",
                 "Previous: Bivalent")
    )
  )
ggplot(err_plot_df,
       aes(x = cycle,
           y = error_rate,
           color = valence_current_group,
           linetype = valence_previous_group,
           group = interaction(valence_current_group,
                               valence_previous_group))) +
  
  geom_line(size = 1) +
  geom_point(size = 3) +
  
  geom_errorbar(aes(ymin = error_rate - se_error,
                    ymax = error_rate + se_error),
                width = .1) +
  
  labs(
    x = "Cycle",
    y = "Error Rate",
    color = "Current Group",
    linetype = "Previous Group"
  ) +
  
  theme_classic(base_size = 14)




```


#################################################################################################################################################

Within-subjects level 

Time-series analysis 

1. first- should make the residuals: 

model_RT_trial <- lmer(log(time) ~ poly(trial_num, 2) + (poly(trial_num, 2)|id),  # poly function is for generating a polynomial and it gives two functions: one for linear and one for polynomial 
                       control = lmerControl(optimizer = "bobyqa"),
                       df_models %>%  filter(error == 0 , prev_error == 0))


trial num [1st degree]	-2.59	-4.02 – -1.17	<0.001 --> 1st degree corresponds to the linear curve and it has a negative slope 
trial num [2nd degree]	1.16	0.16 – 2.15	0.022 --> 2nd degree corresponds to the quadratic curve and it has a positive slope (meaning it is an upward U shaped curve)
```{r}


##sticking to the trial level to get to the polynomial function 
# we are NOT removing within-block trends, but we are removing overall trial trends? 
df_models_rt <- df_models_rt %>%
  filter(error == 0, prev_error == 0)

model_RT_trial <- lmer(log(time) ~ poly(trial_num, 2) + (poly(trial_num, 2)|id),  # poly function is for generating a polynomial and it gives two functions: one for linear and one for polynomial 
                       control = lmerControl(optimizer = "bobyqa"),
                       df_models %>%  filter(error == 0 , prev_error == 0))


# model_RT_trial %>%
#   make_model_table()


library(sjPlot)
tab_model(model_RT_trial)

summary(model_RT_trial)

df_models <- df_models %>%
  ungroup() %>%
  mutate(time_log_pred = predict(model_RT_trial, .)) #%>%
  
subs <- df_models$id %>% unique() %>% head(5) ## sanity check with just 5 subjects 


## checking for 5 subjects 
ggplot(df_models %>% filter(id %in% subs), aes(x = trial_num, y = log(time), color = block, group = interaction(id, block)))+
  geom_line(alpha = 0.5, lwd = 0.3)+
  geom_smooth(se = FALSE)+
  geom_line(aes(y = time_log_pred), color = "green")+
  facet_grid(~id)+
  theme_classic()+
  theme(legend.position = "none")


df_models$filter_correct <- as.integer(df_models$error != 0 | df_models$prev_error != 0)

df_models$time_log_res <- NA
df_models$time_log_res[df_models$filter_correct == 0] <- residuals(model_RT_trial)


df_models <- df_models %>%
  group_by(id, block) %>%
  mutate(lag1_time_log_res = lag(time_log_res, 1))



```


# RT residual analysis

-- now, adding the residual obtained from the previous model and will put that as an additional continuous predictor to our lmer model 

```{r}

library(lme4)

alt_cue_rt_log_resrt <- lmer(time_log_res ~ val_c_g * val_p_g * switch * lag1_time_log_res + (val_c_g + val_p_g + switch + lag1_time_log_res ||id), control = lmerControl(optimizer = "bobyqa"),
     df_models %>% 
       filter(filter_correct == 0)) #warning isSignular but the model converged 


library(sjPlot)

tab_model(alt_cue_rt_log_resrt)

summary(alt_cue_rt_log_resrt)

# preds <- emmeans::emmeans(time, ~ val_c_g * val_p_g * switch * lag1_time_log_res, type = "response",
#                  at = list(val_c_g = c(-0.5, 0.5),
#                            val_p_g = c(-0.5, 0.5),
#                            switch = c(0, 1),
#                            lag1_time_log_res = c(6.5, 10.5))) %>% ## choosing random two values to denote a fast rt and a slow rt (can also use quantile function here to get it for three or more quantiles of)
  
library(tidyverse)

  preds <- emmeans::emmeans(alt_cue_rt_log_resrt, ~ val_c_g * val_p_g * switch * lag1_time_log_res, type = "response",
                 at = list(val_c_g = c(-0.5, 0.5),
                           val_p_g = c(-0.5, 0.5),
                           switch = c(0, 1),
                           lag1_time_log_res = c(-1.5, 1.5))) %>% ## choosing random two values to denote a fast rt and a slow rt (can also use quantile function here to get it for three or more quantiles of)
  
  
  as.data.frame() %>%
  mutate(prev_bivalent = case_when(val_p_g == -0.5 ~ 0, 
                                   val_p_g ==  0.5 ~ 1) %>% factor(),
         is_bivalent = case_when(val_c_g == -0.5 ~ 0,
                                   val_c_g ==  0.5 ~ 1) %>% factor(),
         switch = factor(switch),
         speed = case_when(lag1_time_log_res == min(lag1_time_log_res) ~ "fast",
                           lag1_time_log_res == max(lag1_time_log_res) ~ "slow") %>% factor()) 
  
  summary(preds)

names(preds)

ggplot(preds, aes(x = switch, y = emmean, color = is_bivalent, linetype = prev_bivalent, group = interaction(is_bivalent, prev_bivalent)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast")))+
  labs(title = "Model predictions for log RTs",
       y = "log(RT) prediction")+
  theme_classic()

```
################ Changes to coding

position factor as helmert coding (position of trial in previous group) 

cycle: 1--> coded as -2/3
if cycle variable is greater or equal to 2 -> coded as 1/3 ?



1. step 1: Throw out lag error for current trial but not to compute lag RTs- residual rt should be based on only trials that are currently not an error-- so do not exclude lag 1 rt 

Time-series analysis 

1. first- should make the residuals: 

model_RT_trial <- lmer(log(time) ~ poly(trial_num, 2) + (poly(trial_num, 2)|id),  # poly function is for generating a polynomial and it gives two functions: one for linear and one for polynomial 
                       control = lmerControl(optimizer = "bobyqa"),
                       df_models %>%  filter(error == 0 , prev_error == 0))


trial num [1st degree]	-2.59	-4.02 – -1.17	<0.001 --> 1st degree corresponds to the linear curve and it has a negative slope 
trial num [2nd degree]	1.16	0.16 – 2.15	0.022 --> 2nd degree corresponds to the quadratic curve and it has a positive slope (meaning it is an upward U shaped curve)
```{r}
library(tidyverse)

##sticking to the trial level to get to the polynomial function 
# we are NOT removing within-block trends, but we are removing overall trial trends? 
df_models_rt <- df_models_rt %>%
  filter(error == 0) ## not filtering by prev_error == 0 

library(lme4)
model_RT_trial <- lmer(log(time) ~ poly(trial_num, 2) + (poly(trial_num, 2)|id),  # poly function is for generating a polynomial and it gives two functions: one for linear and one for polynomial 
                       control = lmerControl(optimizer = "bobyqa"),
                       df_models %>%  filter(error == 0)) ## not filtering by prev_error == 0 


# model_RT_trial %>%
#   make_model_table()


library(sjPlot)
tab_model(model_RT_trial)

summary(model_RT_trial)

df_models <- df_models %>%
  ungroup() %>%
  mutate(time_log_pred = predict(model_RT_trial, .)) #%>%
  
subs <- df_models$id %>% unique() %>% head(5) ## sanity check with just 5 subjects 


## checking for 5 subjects 
ggplot(df_models %>% filter(id %in% subs), aes(x = trial_num, y = log(time), color = block, group = interaction(id, block)))+
  geom_line(alpha = 0.5, lwd = 0.3)+
  geom_smooth(se = FALSE)+
  geom_line(aes(y = time_log_pred), color = "green")+
  facet_grid(~id)+
  theme_classic()+
  theme(legend.position = "none")


df_models$filter_correct <- as.integer(df_models$error != 0 | df_models$prev_error != 0)

df_models$time_log_res <- NA
df_models$time_log_res[df_models$error == 0] <- residuals(model_RT_trial)


df_models <- df_models %>%
  group_by(id, block) %>%
  mutate(lag1_time_log_res = lag(time_log_res, 1))



```
## step 2: helmert contrast 

a. create a new cycle variable (duplicate of cycle but with different name) and assign the coding of that version of the cycle variable 

```{r}

df_models <- df_models %>% 
  mutate(cycle_helmert = cycle)

names(df_models)


```
b. 

```{r}
m <- contr.helmert(3) # 3 because cycle has 3 levels 

m[,1] <- rev(m[,1])
m[,2] <- rev(m[,2])

m

#m: 
#[,1] [,2]
#1    0    2
#2    1   -1
#3   -1   -1
```




c. naming the contrast levels: 

```{r}

colnames(m) <- c("cycle_2_v_3" , "cycle_1_v_23")

m
```

d. 

```{r}
contrasts(df_models$cycle_helmert) <- m  

df_models$cycle_helmert
```
e. RT residual analysis

-- now, adding the residual obtained from the previous model and will put that as an additional continuous predictor to our lmer model 

```{r}

library(lme4)

alt_cue_rt_log_resrt <- lmer(time_log_res ~ val_c_g * val_p_g * cycle_helmert * lag1_time_log_res + (val_c_g + val_p_g + cycle_helmert + lag1_time_log_res ||id), control = lmerControl(optimizer = "bobyqa"),
     df_models %>% 
       filter(filter_correct == 0)) #warning isSignular but the model converged 


library(sjPlot)

tab_model(alt_cue_rt_log_resrt)

summary(alt_cue_rt_log_resrt)

# preds <- emmeans::emmeans(time, ~ val_c_g * val_p_g * switch * lag1_time_log_res, type = "response",
#                  at = list(val_c_g = c(-0.5, 0.5),
#                            val_p_g = c(-0.5, 0.5),
#                            switch = c(0, 1),
#                            lag1_time_log_res = c(6.5, 10.5))) %>% ## choosing random two values to denote a fast rt and a slow rt (can also use quantile function here to get it for three or more quantiles of)
  
library(tidyverse)

  preds <- emmeans::emmeans(alt_cue_rt_log_resrt, ~ val_c_g * val_p_g * cycle_helmert * lag1_time_log_res, type = "response",
                 at = list(val_c_g = c(-0.5, 0.5),
                           val_p_g = c(-0.5, 0.5),
                           switch = c(0, 1),
                           lag1_time_log_res = c(-1.5, 1.5))) %>% ## choosing random two values to denote a fast rt and a slow rt (can also use quantile function here to get it for three or more quantiles of)
  
  
  as.data.frame() %>%
  mutate(prev_bivalent = case_when(val_p_g == -0.5 ~ 0, 
                                   val_p_g ==  0.5 ~ 1) %>% factor(),
         is_bivalent = case_when(val_c_g == -0.5 ~ 0,
                                   val_c_g ==  0.5 ~ 1) %>% factor(),
         switch = factor(cycle_helmert),
         speed = case_when(lag1_time_log_res == min(lag1_time_log_res) ~ "fast",
                           lag1_time_log_res == max(lag1_time_log_res) ~ "slow") %>% factor()) 
  
  summary(preds)

names(preds)

ggplot(preds, aes(x = cycle_helmert, y = emmean, color = is_bivalent, linetype = prev_bivalent, group = interaction(is_bivalent, prev_bivalent)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = pos)+
  #scale_x_discrete(limits = c("1", "0"))+
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast")))+
  labs(title = "Model predictions for log RTs",
       y = "log(RT) prediction")+
  theme_classic()

```


#######################################################################################################################
############################ now, coding valence and current and previous group as 0 and 1 instead of -0.5 and +0.5 and re-running the level 1 and within-subject analysis ####################################################

A. level 1



a. checking 

1. lmer model

-For the RT models, error trials, and trials before errors should also be removed
Q: should it be block wise? or across all trials? 

remove  error == 0 and prev_error == 0 for the d_final_analysis inside lmer model filter()

```{r}

library(lme4)

df_models_rt <- df_models 

library(tidyverse)

df_models_rt <- df_models_rt %>%
  filter(error == 0, prev_error == 0)
  
levels(df_models_rt$val_c_g_new) ## the valence should not be a factor if it is -0.5 and +0.5 sonce the model wil treat it as -0.5 is level 0 and 0.5 and level 1 and NOT the average of -0.5 as 0? but it shouldn't matter if it is a factor or not when it is coded as 0 and 1

## but switch is numeric for now and the model converged -- Dominik's model did NOT converge when switch was also  factor 
## but when all the three are factors AND I added bobyquoa optimizer- the model converged. without bobyqua it seemed to be using another optimizer or multiple?? and it showed convergence OK for one optimizer but then at the last sentence, it also showed that the model failed to converge 

## but when i re-ram the model with all of them as numeric, it converges, and does not give issingular warning 

df_models_rt$switch <- as.factor(df_models_rt$switch)

levels(df_models_rt$val_c_g_new)
levels(df_models_rt$val_p_g_new)
levels(df_models_rt$switch)

df_models_rt$val_c_g_new <- as.factor(df_models_rt$val_c_g_new)
df_models_rt$val_p_g_new <- as.factor(df_models_rt$val_p_g_new)
df_models_rt$switch <- as.factor(df_models_rt$switch)

  m_rt_new<- lme4::lmer(log(time) ~  val_c_g_new * val_p_g_new* switch + (val_c_g_new + val_p_g_new + switch ||  id),
                 data = df_models_rt,
                  na.action = na.exclude,
              
               control = lmerControl(optimizer = "bobyqa"))


 
 summary(m_rt_new)
 
 
#library(sjPlot)
 tab_model(m_rt_new,show.est=T,auto.label=F,show.stat=T) # tab_model uses another way of specifying (Wald's test) degrees of freedom
  tab_model(m_rt_new,show.est=T,auto.label=F,show.stat=T, df.method = "satterthwaite") ## when i use this when using lme4, the model not not converge anymore as the degress of freedom is being calculated using a different method 
 
 names(df_models)
 

 
```

```{r}
library(lmerTest) #lmerTest seems to give wrong warning that the model did not converge, even though it did converge? because the same model that was run using lme4 gave convergence 0 is OK? 
## but lmerTest lmer moel is giving both a warning of failed convergence AND convergence 0 is OK-- THAT is why the warning of failed convergence is a bug??

#### BUT-- lme4's lmer runs models, but checks convergence lineantly (does not check convergnece well). and then lmertest coems in and checks the convergence striclty-- so, we should rely on lmertest?? that is why the output for lme4 showed convergence 0 is OK at the bottom of the summary() output and then at the top of the summary output- the warning about the failed convergence is from the lmertest 

levels(df_models_rt$val_c_g_new)
levels(df_models_rt$val_p_g_new)
levels(df_models_rt$switch)

df_models_rt$val_c_g_new <- as.factor(df_models_rt$val_c_g_new)
df_models_rt$val_p_g_new <- as.factor(df_models_rt$val_p_g_new)
df_models_rt$switch <- as.factor(df_models_rt$switch)


df_models_rt$val_c_g_new <- as.numeric(as.character(df_models_rt$val_c_g_new))
df_models_rt$val_p_g_new <- as.numeric(as.character(df_models_rt$val_p_g_new))
df_models_rt$switch <-  as.numeric(as.character(df_models_rt$switch))


levels(df_models_rt$val_c_g_new)
levels(df_models_rt$val_p_g_new)
levels(df_models_rt$switch)


#### use this version!!!! 

 m_rt_new<- lmerTest::lmer(log(time) ~  val_c_g_new * val_p_g_new* switch + (val_c_g_new + val_p_g_new + switch ||  id),
                 data = df_models_rt,
                  na.action = na.exclude,
              
               control = lmerControl(optimizer = "bobyqa"))


 
 summary(m_rt_new)
 
 
#library(sjPlot)
# tab_model(m_rt_new,show.est=T,auto.label=F,show.stat=T)
 tab_model(m_rt_new,show.est=T,auto.label=F,show.stat=T, df.method = "satterthwaite") ## lmertest uses Satterthwaite's method by default 
 
 
 
```
Note: if you convrrt a numeric (valeus of 0 and 1)  to factor- it will assign levls of 1 and 2
but when conveting factor back to numeric, you should first convert factor to as.character so that it reassigns the 0 and 1 levels and then convert it to numeric 



2. glmer model

```{r}


df_models$error <- as.factor(df_models$error)

df_models$val_c_g_new <- as.factor(df_models$val_c_g_new)
df_models$val_p_g_new <- as.factor(df_models$val_p_g_new)
df_models$switch <- as.factor(df_models$switch)


df_models$val_c_g_new <- as.numeric(as.character(df_models$val_c_g_new))
df_models$val_p_g_new <- as.numeric(as.character(df_models$val_p_g_new))
df_models$switch <-  as.numeric(as.character(df_models$switch))


levels(df_models$val_c_g_new)
levels(df_models$val_p_g_new)
levels(df_models$switch)

levels(df_models$error)

  m_error_new<- lmerTest::glmer(error ~  val_c_g_new * val_p_g_new * switch + ( val_c_g_new +  val_p_g_new + switch| id),
                 data = df_models, 
                 family = "binomial",
                  na.action = na.exclude, 
                 control = glmerControl(optimizer = "bobyqa"))

 
 summary(m_error_new)
 
 tab_model(m_error_new,show.est=T,auto.label=F,show.stat=T)
```

b. running the lmer and glmer models with constrast coding of valence (0 and 1 levels) and treating everything as a factor 

1. lmer

```{r}
######## use this 
library(lmerTest)
df_models_rt <- df_models 

library(tidyverse)

df_models_rt <- df_models_rt %>%
  filter(error == 0, prev_error == 0)
  
df_models_rt$val_c_g_new <- as.factor(df_models_rt$val_c_g_new)
df_models_rt$val_p_g_new <- as.factor(df_models_rt$val_p_g_new)
df_models_rt$switch <- as.factor(df_models_rt$switch)

levels(df_models_rt$val_c_g_new)
levels(df_models_rt$val_p_g_new)
levels(df_models_rt$switch)

 m_rt_contrast<- lmer(log(time) ~  val_c_g_new * val_p_g_new* switch + (val_c_g_new + switch |  id),
                 data = df_models_rt,
                  na.action = na.exclude,
              
               control = lmerControl(optimizer = "bobyqa"))


 
 summary(m_rt_contrast)
 
 
library(sjPlot)
# tab_model(m_rt_new,show.est=T,auto.label=F,show.stat=T)
 tab_model(m_rt_contrast,show.est=T,auto.label=F,show.stat=T, df.method = "satterthwaite") ## lmertest uses Satterthwaite's method by default 




```



2. glmer 

```{r}

#### use this 

df_models$error <- as.factor(df_models$error)

m_error_contrast<- glmer(error ~  val_c_g_new * val_p_g_new * switch + ( val_c_g_new + switch| id),
                 data = df_models, 
                 family = "binomial",
                  na.action = na.exclude, 
                 control = glmerControl(optimizer = "bobyqa"))

 
 summary(m_error_contrast)
 
 tab_model(m_error_contrast,show.est=T,auto.label=F,show.stat=T)


```

3. DDM analysis using contrast coding of val_c_g and val_p_g 


#| include: false
#first putting in some pre-made functions that will go into the ezDDM analysis: 

```{r}

normWS <- function(d ,s, dv, between = NULL) { #within subject normalization
  eval(substitute(d %>%
                    dplyr::group_by(s) %>%
                    dplyr::mutate(sAV = mean(dv, na.rm = TRUE)) %>%
                    dplyr::group_by_at(between) %>% #this is grouping by between subjects variables
                    dplyr::mutate(gAV = mean(dv, na.rm = TRUE)) %>%
                    dplyr::mutate(DV_n = dv - sAV + gAV), list(s = as.name(s), dv = as.name(dv))))
}


get_ci <- function(var, mean){
  sd <- sd(var, na.rm = TRUE)
  n <- length(var)
  se <- sd/sqrt(n)
  ci <- abs(qt(0.025, n-1, lower.tail = FALSE))*se
  return(c(mean + ci, mean - ci, sd, se, n))
}

convert_extremes <- function(value){
  
  if(value == 1){
    
    value = value - 1e-5
    
  } else if (value == 0 ){
    
    value = value + 1e-5
    
  }
  
  return(value)
  
}#making sure error is either .99 or .001
```


## Aggregation and data processing

--hausekeep 

install.packages("cli")
packageVersion("cli") -- should show ≥ 3.6.5-- it is 3.6.5 
install.packages("devtools")
devtools::install_github("hauselin/hausekeep")
library(hausekeep)

```{r}
# library(devtools)
# library(rio)
# library(hausekeep)
# 
# 
# library(tidyverse)
alt_cue_agg_ID_ddm <- d_final_analysis %>%
  mutate(RT_s = time/1000) %>%
  group_by(id, val_c_g_new, val_p_g_new, switch, cycle) %>%
  summarize(RT_s_m = mean(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            Error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>%
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  
  unnest(ezddm)



alt_cue_agg_ddm <- alt_cue_agg_ID_ddm %>%
  group_by(id, val_c_g_new, val_p_g_new, switch, cycle) %>%
  normWS(s = "id", dv = "a") %>%
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>%
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>%
  mutate(Ter = DV_n) %>%
  group_by(val_c_g_new, val_p_g_new, switch, cycle) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[1],
            a_ci_upper = get_ci(a, a_m)[2],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[1],
            v_ci_upper = get_ci(v, v_m)[2],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[1],
            Ter_ci_upper = get_ci(Ter, Ter_m)[2],)

#make a separate object that is averaging across the no-switch 2,3 and 4 average within those and then average within those variances
alt_cue_agg_ID_ddm_collapsed <- alt_cue_agg_ID_ddm %>% 
  filter(switch == 0, cycle %in% c(2, 3)) %>%
  group_by(id, val_c_g_new, val_p_g_new) %>% 
  summarize( # average the DDM parameters across cycles 2&3 
    a = mean(a, na.rm = TRUE), 
    v = mean(v, na.rm = TRUE), #average within those 
    Ter = mean(Ter, na.rm = TRUE), 
    a_var = mean(a^2, na.rm = TRUE), #average within those variances
    v_var = mean(v^2, na.rm = TRUE), 
    Ter_var = mean(Ter^2, na.rm = TRUE), 
    .groups = "drop" )

alt_cue_agg_ID_ddm_collapsed

alt_cue_agg_ID_ddm %>% filter(switch == 0, cycle %in% c(2,3)) %>% count(id, val_c_g_new, val_p_g_new)
```


## Statistical Models

### First prep data so that it's ignoring cycle

```{r}
# alt_cue_agg_ID_ddm_nocycle <- d_final_analysis %>%
#   mutate(RT_s = time/1000) %>%
#   group_by(id, valence_current_group, valence_previous_group, val_c_g_new, val_p_g_new, switch) %>%
#   summarize(RT_s_m = mean(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
#             RT_s_var = var(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
#             Error = mean(error, na.rm = TRUE),
#             N_trials = n()) %>%
#   rowwise() %>%
#   mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
#                             rtCorrectVariance_seconds = RT_s_var, 
#                             rtCorrectMean_seconds = RT_s_m, 
#                             nTrials = N_trials))) %>%
#   unnest(ezddm)


alt_cue_agg_ID_ddm_nocycle <- d_final_analysis %>%
  mutate(RT_s = time/1000) %>%
  group_by(id, val_c_g, val_c_g_new, val_p_g, val_p_g_new, switch) %>%
  summarize(RT_s_m = mean(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            Error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>%
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  unnest(ezddm)


alt_cue_agg_ddm_nocycle <- alt_cue_agg_ID_ddm_nocycle %>%
  group_by(id, val_c_g_new, val_p_g_new, switch) %>%
  normWS(s = "id", dv = "a") %>%
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>%
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>%
  mutate(Ter = DV_n) %>%
  group_by(val_c_g_new, val_p_g_new, switch) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[1],
            a_ci_upper = get_ci(a, a_m)[2],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[1],
            v_ci_upper = get_ci(v, v_m)[2],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[1],
            Ter_ci_upper = get_ci(Ter, Ter_m)[2],)

```



### Plots

```{r}

alt_cue_agg_ddm$switch <- as.factor(alt_cue_agg_ddm$switch)
alt_cue_agg_ddm_nocycle$switch <- as.factor(alt_cue_agg_ddm_nocycle$switch)
alt_cue_agg_ddm_nocycle$val_c_g_new <- as.factor(alt_cue_agg_ddm_nocycle$val_c_g_new)
alt_cue_agg_ddm_nocycle$val_p_g_new <- as.factor(alt_cue_agg_ddm_nocycle$val_p_g_new)

plt_ddm_a <- ggplot(alt_cue_agg_ddm, aes(x = cycle, y = a_m, color = val_c_g_new, linetype = val_p_g_new, group = interaction(val_c_g_new, val_p_g_new)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper), width = 0.1, position = pos)+
  theme_classic()

plt_ddm_v <- ggplot(alt_cue_agg_ddm, aes(x = cycle, y = v_m, color = val_c_g_new, linetype = val_p_g_new, group = interaction(val_c_g_new, val_p_g_new)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper), width = 0.1, position = pos)+
  theme_classic()


plt_ddm_Ter <- ggplot(alt_cue_agg_ddm, aes(x = cycle, y = Ter_m, color = val_c_g_new, linetype = val_p_g_new, group = interaction(val_c_g_new, val_p_g_new)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper), width = 0.1, position = pos)+
  theme_classic()

#########
plt_ddm_a_nocycle <- ggplot(alt_cue_agg_ddm_nocycle, aes(x = switch, y = a_m, color = val_c_g_new , linetype = val_p_g_new, group = interaction(val_c_g_new, val_p_g_new)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper), width = 0.1, position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
  theme_classic()

plt_ddm_v_nocycle <- ggplot(alt_cue_agg_ddm_nocycle, aes(x = switch, y = v_m, color = val_c_g_new, linetype = val_p_g_new, group = interaction(val_c_g_new, val_p_g_new)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper), width = 0.1, position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
  theme_classic()


plt_ddm_Ter_nocycle <- ggplot(alt_cue_agg_ddm_nocycle, aes(x = switch, y = Ter_m, color = val_c_g_new, linetype = val_p_g_new, group = interaction(val_c_g_new, val_p_g_new)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper), width = 0.1, position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
  theme_classic()

ggpubr::ggarrange(plt_ddm_a, plt_ddm_a_nocycle,
                  plt_ddm_v, plt_ddm_v_nocycle,
                  plt_ddm_Ter, plt_ddm_Ter_nocycle, common.legend = TRUE, nrow = 3, ncol = 2)  


```


### Models

1. effect coding (-0.5, 0.5)

```{r}

library(sjPlot)
 library(lmerTest)


### all these models show singular 
## can remove random effect of previous bivalance as it's effect may be very similar across subjects with less variance on rt and the ddm parameters based on previous bivalance across subjects 

## Ulrich: remove the random effects and only keep intercept 


# 
# alt_cue_a <- lmer(a ~ val_c_g * val_p_g * switch + (val_c_g + val_p_g + switch| id), 
#      alt_cue_agg_ID_ddm_nocycle)

alt_cue_a <- lmer(a ~ val_c_g * val_p_g * switch + (val_c_g + switch | id), alt_cue_agg_ID_ddm_nocycle)


summary(alt_cue_a)

tab_model(alt_cue_a)

alt_cue_v <- lmer(v ~  val_c_g * val_p_g * switch + (val_c_g + switch |id), 
     alt_cue_agg_ID_ddm_nocycle)

summary(alt_cue_v)

tab_model(alt_cue_v)


alt_cue_Ter <- lmer(Ter ~  val_c_g * val_p_g * switch + (val_c_g + switch |id), 
     alt_cue_agg_ID_ddm_nocycle)

summary(alt_cue_Ter)

tab_model(alt_cue_Ter)
```



2. contrast coding 

```{r}


alt_cue_a_contrast <- lmerTest::lmer(a ~ val_c_g_new * val_p_g_new * switch + (val_c_g_new + switch | id), alt_cue_agg_ID_ddm_nocycle)


summary(alt_cue_a_contrast)

tab_model(alt_cue_a_contrast, df.method = "satterthwaite" )

alt_cue_v_contrast <- lmer(v ~  val_c_g_new * val_p_g_new * switch + (val_c_g_new + switch |id), 
     alt_cue_agg_ID_ddm_nocycle)

summary(alt_cue_v_contrast)

tab_model(alt_cue_v_contrast, df.method = "satterthwaite")


alt_cue_Ter_contrast <- lmer(Ter ~  val_c_g_new * val_p_g_new * switch + (val_c_g_new + switch |id), 
     alt_cue_agg_ID_ddm_nocycle)

summary(alt_cue_Ter_contrast)

tab_model(alt_cue_Ter_contrast, df.method = "satterthwaite")
```

descriptive plots 

1. rt
```{r}

library(dplyr)
library(ggplot2)

rt_plot_df <- d_final_analysis %>%
  filter(error == 0, prev_error == 0) %>%
  group_by(valence_current_group,
           valence_previous_group,
           cycle) %>%
  summarise(
    mean_rt = mean(time, na.rm = TRUE),
    se_rt   = sd(time, na.rm = TRUE)/sqrt(n()),
    .groups = "drop"
  )
rt_plot_df <- rt_plot_df %>%
  mutate(
    cycle = factor(cycle, levels = c(1,2,3)),
    valence_current_group = factor(valence_current_group,
                                   labels = c("Current: Univalent",
                                              "Current: Bivalent")),
    valence_previous_group = factor(valence_previous_group,
                                    labels = c("Previous: Univalent",
                                               "Previous: Bivalent"))
  )

ggplot(rt_plot_df,
       aes(x = cycle,
           y = mean_rt,
           color = valence_current_group,
           linetype = valence_previous_group,
           group = interaction(valence_current_group,
                               valence_previous_group))) +
  
  geom_line(size = 1) +
  geom_point(size = 3) +
  
  geom_errorbar(aes(ymin = mean_rt - se_rt,
                    ymax = mean_rt + se_rt),
                width = .1) +
  
  labs(
    x = "Cycle",
    y = "Mean RT (ms)",
    color = "Current Group",
    linetype = "Previous Group"
  ) +
  
  theme_classic(base_size = 14)


```

2. error 

```{r}
library(dplyr)
library(ggplot2)

err_plot_df <- d_final_analysis %>%
  group_by(valence_current_group,
           valence_previous_group,
           cycle) %>%
  summarise(
    error_rate = mean(error, na.rm = TRUE),
    se_error   = sd(error, na.rm = TRUE)/sqrt(n()),
    .groups = "drop"
  )
err_plot_df <- err_plot_df %>%
  mutate(
    cycle = factor(cycle, levels = c(1,2,3)),
    
    valence_current_group = factor(
      valence_current_group,
      labels = c("Current: Univalent",
                 "Current: Bivalent")
    ),
    
    valence_previous_group = factor(
      valence_previous_group,
      labels = c("Previous: Univalent",
                 "Previous: Bivalent")
    )
  )
ggplot(err_plot_df,
       aes(x = cycle,
           y = error_rate,
           color = valence_current_group,
           linetype = valence_previous_group,
           group = interaction(valence_current_group,
                               valence_previous_group))) +
  
  geom_line(size = 1) +
  geom_point(size = 3) +
  
  geom_errorbar(aes(ymin = error_rate - se_error,
                    ymax = error_rate + se_error),
                width = .1) +
  
  labs(
    x = "Cycle",
    y = "Error Rate",
    color = "Current Group",
    linetype = "Previous Group"
  ) +
  
  theme_classic(base_size = 14)




```



###########################################
B. within-subject analysis with val_c_g_new and val_p_g_new 


```{r}


df_models$val_c_g_new <- ifelse(df_models$valence_current_group == 1, 0,
                     ifelse(d_final_analysis$valence_current_group == 2,  1, NA))

df_models$val_p_g_new <- ifelse(df_models$valence_previous_group == 1, 0,
                     ifelse(d_final_analysis$valence_previous_group == 2,  1, NA))
```

```{r}

library(lmerTest)

model_RT_trial <- lmer(log(time) ~ poly(trial_num, 2) + (poly(trial_num, 2)|id),  # poly function is for generating a polynomial and it gives two functions: one for linear and one for polynomial 
                       control = lmerControl(optimizer = "bobyqa"),
                       df_models %>%  filter(error == 0)) ## not filtering by prev_error == 0 


# model_RT_trial %>%
#   make_model_table()


library(sjPlot)
tab_model(model_RT_trial)

summary(model_RT_trial)

df_models <- df_models %>%
  ungroup() %>%
  mutate(time_log_pred = predict(model_RT_trial, .)) #%>%
  
subs <- df_models$id %>% unique() %>% head(5) ## sanity check with just 5 subjects 


## checking for 5 subjects 
ggplot(df_models %>% filter(id %in% subs), aes(x = trial_num, y = log(time), color = block, group = interaction(id, block)))+
  geom_line(alpha = 0.5, lwd = 0.3)+
  geom_smooth(se = FALSE)+
  geom_line(aes(y = time_log_pred), color = "green")+
  facet_grid(~id)+
  theme_classic()+
  theme(legend.position = "none")


df_models$filter_correct <- as.integer(df_models$error != 0 | df_models$prev_error != 0)

df_models$time_log_res <- NA
df_models$time_log_res[df_models$error == 0] <- residuals(model_RT_trial)


df_models <- df_models %>%
  group_by(id, block) %>%
  mutate(lag1_time_log_res = lag(time_log_res, 1))



```
## step 2: helmert contrast 

a. create a new cycle variable (duplicate of cycle but with different name) and assign the coding of that version of the cycle variable 

```{r}

df_models <- df_models %>% 
  mutate(cycle_helmert = cycle)

names(df_models)

df_models <- df_models %>%
  mutate(cycle_helmert = factor(cycle))

str(df_models$cycle_helmert)


```


b. 

```{r}
m <- contr.helmert(3) # 3 because cycle has 3 levels 

m[,1] <- rev(m[,1])
m[,2] <- rev(m[,2])

m

#m: 
#[,1] [,2]
#1    0    2
#2    1   -1
#3   -1   -1
```


c. naming the contrast levels: 

```{r}

colnames(m) <- c("cycle_2_v_3" , "cycle_1_v_23")

m
```

d. 

d. 

```{r}
contrasts(df_models$cycle_helmert) <- m  

df_models$cycle_helmert
```
e. RT residual analysis

-- now, adding the residual obtained from the previous model and will put that as an additional continuous predictor to our lmer model 

```{r}


# 
# df_models$val_c_g_new <- as.factor(df_models$val_c_g_new)
# df_models$val_p_g_new <- as.factor(df_models$val_p_g_new)
# df_models$cycle_helmert <- as.factor(df_models$cycle_helmert)


alt_cue_rt_log_resrt <- lmer(time_log_res ~ val_c_g_new * val_p_g_new * cycle_helmert * lag1_time_log_res + (val_c_g_new + val_p_g_new + cycle_helmert + lag1_time_log_res |id), control = lmerControl(optimizer = "bobyqa"),
     df_models %>% 
       filter(filter_correct == 0)) #warning isSignular but the model converged 


#library(sjPlot)

tab_model(alt_cue_rt_log_resrt)

summary(alt_cue_rt_log_resrt)

# preds <- emmeans::emmeans(time, ~ val_c_g * val_p_g * switch * lag1_time_log_res, type = "response",
#                  at = list(val_c_g = c(-0.5, 0.5),
#                            val_p_g = c(-0.5, 0.5),
#                            switch = c(0, 1),
#                            lag1_time_log_res = c(6.5, 10.5))) %>% ## choosing random two values to denote a fast rt and a slow rt (can also use quantile function here to get it for three or more quantiles of)
  
library(tidyverse)



  preds <- emmeans::emmeans(alt_cue_rt_log_resrt, ~ val_c_g_new * val_p_g_new * cycle_helmert * lag1_time_log_res, type = "response",
                 at = list(val_c_g_new = c(0, 1),
                           val_p_g_new = c(0, 1),
                          # switch = c(0, 1),
                          cycle_helmert = factor(c(1,2,3)),
                           lag1_time_log_res = c(-1.5, 1.5))) %>% ## choosing random two values to denote a fast rt and a slow rt (can also use quantile function here to get it for three or more quantiles of)
  
  
  as.data.frame() %>%
  mutate(prev_bivalent = case_when(val_p_g_new == 0 ~ 0, 
                                   val_p_g_new ==  1 ~ 1) %>% factor(),
         is_bivalent = case_when(val_c_g_new == 0 ~ 0,
                                   val_c_g_new ==  1 ~ 1) %>% factor(),
         switch = factor(cycle_helmert),
         speed = case_when(lag1_time_log_res == min(lag1_time_log_res) ~ "fast",
                           lag1_time_log_res == max(lag1_time_log_res) ~ "slow") %>% factor()) 
  
  summary(preds)

names(preds)

ggplot(preds, aes(x = cycle_helmert, y = emmean, color = is_bivalent, linetype = prev_bivalent, group = interaction(is_bivalent, prev_bivalent)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = pos)+
  #scale_x_discrete(limits = c("1", "0"))+
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast")))+
  labs(title = "Model predictions for log RTs",
       y = "log(RT) prediction")+
  theme_classic()

```
######### Lag RT based on previous trial group

One concern Dominik has with the analysis above is that the lag1 residual log RT is problematic for no-switch trials. In trial 2 of a trialgroup for instance, lag1 RT corresponds to the switch RT trial (trial 1 in a trialgroup). However, for trials 3 and 4 of a trialgroup, lag 1 RT corresponds to a no-switch trial. Therefore, in the graph above, the 0 switch is hard to interpret. This is especially problematic for the Alternate Runs experiment, because there are three no switch trials, one of which has the problematic lag 1 RT corresponding to the switch trial. In the Alternate Cues experiment, at least the no switch trials are averaged (trials 2 and 3, one of which is biased, so it's a balanced average). 

Therefore, here, instead of a lag 1 RT, a new variable which calculates the mean of the *previous group RTs of no switch trials*. So again, not previous trial, but previous group averaged no switch trial RTs. That might be a better indicated for previous group stability.

## Effect coded valence (-0.5, 0.5)

```{r}


df_models <- df_models %>%
  group_by(id, block, trialgroup) %>%
  mutate(avg_ns_rt_res_log = mean(time_log_res[switch == 0], na.rm = TRUE)) %>%
  group_by(id, block) %>%
  mutate(prev_avg_ns_rt_res_log = lag(avg_ns_rt_res_log, 1),
         cycle = as.numeric(as.character(cycle))) %>%
  group_by(id, block, trialgroup) %>%
  mutate(prev_avg_ns_rt_res_log = prev_avg_ns_rt_res_log[1]) 




alt_cue_rt_log_resrt_prev_eff <- lmer(time_log_res ~ is_bivalent_eff * prev_bivalent_eff * switch_contr * prev_avg_ns_rt_res_log + (is_bivalent_eff + prev_bivalent_eff + switch_contr + prev_avg_ns_rt_res_log|id), control = lmerControl(optimizer = "bobyqa"),
                                  alt_cue %>% 
                                    filter(filter_correct == 0))

make_model_table(alt_cue_rt_log_resrt_prev_eff)

preds <- emmeans::emmeans(alt_cue_rt_log_resrt_prev_eff, ~ is_bivalent_eff * prev_bivalent_eff * switch_contr * prev_avg_ns_rt_res_log, type = "response",
                          at = list(is_bivalent_eff = factor(c(0, 1)),
                                    prev_bivalent_eff = factor(c(0, 1)),
                                    switch_contr = factor(c(0, 1)),
                                    prev_avg_ns_rt_res_log = c(-1.5, 1.5))) %>%
  as.data.frame() %>%
  mutate(speed = case_when(prev_avg_ns_rt_res_log == min(prev_avg_ns_rt_res_log) ~ "fast",
                           prev_avg_ns_rt_res_log == max(prev_avg_ns_rt_res_log) ~ "slow") %>% factor()) 



ggplot(preds, aes(x = switch_contr, y = emmean, color = is_bivalent_eff, linetype = prev_bivalent_eff, group = interaction(is_bivalent_eff, prev_bivalent_eff)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast")))+
  labs(title = "Model predictions for residual log RTs",
       y = "log(RT) prediction")+
  theme_classic()


```



## Contrast coded (0, 1)

```{r}




alt_cue_rt_log_resrt_prev_contr <- lmer(time_log_res ~ is_bivalent_contr * prev_bivalent_contr * switch_contr * prev_avg_ns_rt_res_log + (is_bivalent_contr + prev_bivalent_contr + switch_contr + prev_avg_ns_rt_res_log|id), control = lmerControl(optimizer = "bobyqa"),
                                  alt_cue %>% 
                                    filter(filter_correct == 0))

make_model_table(alt_cue_rt_log_resrt_prev_contr)

preds <- emmeans::emmeans(alt_cue_rt_log_resrt_prev_contr, ~ is_bivalent_contr * prev_bivalent_contr * switch_contr * prev_avg_ns_rt_res_log, type = "response",
                          at = list(is_bivalent_contr = factor(c(0, 1)),
                                    prev_bivalent_contr = factor(c(0, 1)),
                                    switch_contr = factor(c(0, 1)),
                                    prev_avg_ns_rt_res_log = c(-1.5, 1.5))) %>%
  as.data.frame() %>%
  mutate(speed = case_when(prev_avg_ns_rt_res_log == min(prev_avg_ns_rt_res_log) ~ "fast",
                           prev_avg_ns_rt_res_log == max(prev_avg_ns_rt_res_log) ~ "slow") %>% factor()) 



ggplot(preds, aes(x = switch_contr, y = emmean, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast")))+
  labs(title = "Model predictions for residual log RTs",
       y = "log(RT) prediction")+
  theme_classic()


```

