---
title: "alternate_cues_new"
author: "Neha"
date: "2026-02-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("theme.R")
```

```{r}
library(readr)
library(tidyverse)
library(lmerTest)
library(dplyr)
library(sjPlot)
library(devtools)
library(rio)
library(hausekeep)
library(ggplot2)

```


```{r}


## Dominik's version: 

library(ggplot2)
design <- list()
design$curr_val$color$bi <- "#E69F00"
design$curr_val$color$uni <- "#56B4E9"
design$prev_val$color$bi <- "#E69F00"
design$prev_val$color$uni <- "#56B4E9"

design$curr_val$linetype$bi <- "solid"
design$curr_val$linetype$uni <- "41" #dashed
design$prev_val$linetype$bi <- "solid"
design$prev_val$linetype$uni <- "41" #dashed

design$lines$linewidth <- 1.1

design$errorbar$width <- 0
design$errorbar$linewidth <- 0.8

apa_theming <- function(base_size = 12,
                        base_family = "sans",
                        blue = "#56B4E9",
                        orange = "#E69F00") {
  
    # based off how others strucutre their apa figure themes but adding the specifications we talked about
    theme_bw(base_size = base_size, base_family = base_family) %+replace%
      theme(
        text = element_text(family = base_family, color = "black"),
        plot.title = element_text(size = base_size * 1.4, face = "bold"),
        plot.subtitle = element_text(size = base_size * 1.1),
        plot.caption = element_text(size = base_size * 0.9),
        
        axis.title = element_text(size = base_size * 1.1),
        axis.text = element_text(size = base_size),
        axis.line = element_line(color = "black", linewidth = 0.5),
        axis.ticks = element_line(color = "black"),
        
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        
        legend.position = "right",
        legend.title = element_text(size = base_size * 1.1),
        legend.text = element_text(size = base_size),
        
        strip.background = element_rect(fill = "gray90", color = "black"),
        strip.text = element_text(size = base_size * 1.1, face = "bold", margin = margin(t = 4, b = 4))
      )#,
    
    #assigning colors specified in specfifc order
    #scale_color_manual(values = c(blue, orange)) #this will not work, as it may assign different labels dependent on how factors are ordered between experiments
}


theme_set(apa_theming())
```

```{r}
AlternateCues <- read_csv("AlternateCues.csv")
View(AlternateCues)

tibble_summary<- AlternateCues %>% 
  summary() %>% 
  tibble()

```
################################## DATA CLEANING ##################################################

have to remove practice blocks + the 5 unusable subjects (901, 959, 201, 975, 902) : 

Note: subject 4 can have duplicate trials removed 
```{r}
d_clean <- data %>%
  filter(!id %in% c(901, 959, 201, 975, 902)) %>% 
  droplevels()


unique(d_clean$id) ## 73 subjects 

d_clean <- d_clean %>% 
  filter(block != 0) %>% 
  droplevels()

unique(d_clean$block)

sort(unique((d_clean$id))) # 3, 4, 5, 7 ,8, 9 , 10, 11, 12, 13, 14, 15, 16, 17, 99, 202 , 203    204, 401 , 402 , 403, 404, 405 , 406, 501,  502,  503, 504, 505, 701, 702, 703 , 704 ,705 ,706, 707, 708 , 752, 800, 903, 904, 905, 906, 907, 908, 909 , 910, 911, 912, 913, 914, 915, 916 ,   917 ,918, 919, 953, 954, 958, 962 ,963, 964 ,965 ,966 , 967 , 968 , 969 , 970,971, 974, 75033, 750445, 961422

```

```{r}


id_4_clean <- d_clean %>%
  filter(id == 4) %>% 
  group_by(id, block, trial) %>%
  slice(1) %>%   # keep first occurrence
  ungroup() %>% 
  droplevels()
```


```{r}
data_clean <- d_clean %>%
  filter(id != 4) %>%   # keep everyone else untouched
  bind_rows(id_4_clean) %>% 
  droplevels()

```

Sanity checks

After removing duplication-- should return back 0 for n>1

```{r}


data_clean %>%
  count(id, block, trial) %>%
  filter(n > 1) %>% 
  droplevels()

unique(data_clean$id) ## 73 subjects 

temp_subjects <- c(9  ,    12  ,   15  ,   10    , 11  ,   16    , 13  ,   17   ,  14 ,    8  ,    7 ,     3  ,    5  ,    99 ,    202  ,  203 ,   204  ,  401 ,   402 ,   403  ,  404,    405 ,   406 ,   501 ,   502 ,   503  ,  504 ,   505 ,   701  ,  702 ,   703  ,  704  ,  705 ,   706  ,  707  ,  708  ,  752 ,   750445, 75033,  800 ,   903,    904 ,   905 ,   906 ,   907 ,   908 ,   909 ,   910  ,  911  ,  912  ,  913 ,   914 ,   915,    916 ,   917  ,  918 ,   919  ,  953  ,  954 ,   958 ,   961422, 962,    963  ,  964,    965  ,  966,    967   , 968  ,  969 ,   970 ,   971  ,  974,    4    )
length(temp_subjects) # 73 subjects 



```

removing subjects below accuracy level of 80% 

```{r}


data_clean <- data_clean %>%
  mutate(error = as.numeric(as.character(error)))

str(data_clean$error)

table(data_clean$error) # 0 with 40814 trials and 1 with 2986 trials 

accuracy_per_subject <- data_clean %>%
  group_by(id) %>%
  summarise(accuracy = 1 - mean(error, na.rm = TRUE))

# 2. See who falls below 80% accuracy:
accuracy_per_subject %>%
  filter(accuracy < 0.80) ## ids 202 and 914 have accuracy less than 80% 

# IDs below 80% accuracy
low_acc_ids <- accuracy_per_subject %>%
  filter(accuracy < 0.8) %>%
  pull(id)
low_acc_ids

data_clean <- data_clean %>% 
   filter(!id %in% c(202, 914)) %>% 
  droplevels()

unique(data_clean$id) ## 71 subjects that are usable ## so overall- had to remove 8 subjects. 

```

######################### making new variables #####################################################


A. making the valence of each group 

valence of current group has levels 1 and 2
valence of previous group has levels 1 and 2

- each group consists of three trials with the cycle variable as 1,2, and 3 (so first trials has cycle as 1 and the third trial has cycle as 3)
-valence of current group is 1 if dim 1 or dim 2 has the value of 4 
- valence of previous group is also 1 if dim 1 and dim 2 has the value of 4 
- if dim 1 and dim 2 have any values from 1-3, then the valence of current and previous group will be assigned as 2 

1- valence of current group


```{r}



data_clean <- data_clean %>%
  group_by(id, block) %>% 
  # valence of current group
  mutate(valence_current_group = if_else(dim1 == 4 | dim2 == 4, 1, 2)) # univalent is coded as 1 and bivalent is coded as 2 

names(data_clean)
levels(data_clean$valence_current_group) ## have to convert this to factor before analysis 

#unique(d_final$id)

```

2- valence_previous_group 
Lag by 3 trials within each subject (each group = 3 trials)

```{r}
data_clean <- data_clean %>%
  group_by(id, block) %>%       # only by subject
  #arrange(block, trial) %>%   
  mutate(valence_previous_group = lag(valence_current_group, 3)) %>%
  ungroup()


names(data_clean)

# lag 1 
# turn all but first trial as NA
# fill will prapagate first value

```

3- switch variable 

```{r}


data_clean <- data_clean %>%
  group_by(id, block) %>%        
  mutate(
    switch = if_else(task != lag(task), 1, 0)  # 1 if task changed from previous trial
  ) %>%
  ungroup()

names(data_clean)

```

prev_error variable before removing the first group of trials 

```{r}



data_clean <- data_clean %>%
  group_by(id, block) %>%     # IMPORTANT
  mutate(prev_error = lag(error)) %>%
  ungroup()



```

have to first remove trials below the third trial of every block as they may not be in a group of three 

```{r}



data_clean <- data_clean %>%
  group_by(id, block) %>%          
  filter( trial>3) %>%   ## removes all the trials on each block that are less than the third trial 
  ungroup() %>%
  droplevels()


# trial != min(trial) &

##note: trial 4 of some blocks for some subjects (203,402,405,502,503,504) are being removed for d_final_analysis- is this due to trial != min(trial) & trial>3: because min trial is now 4??  so, removed trial != min(trial) and now i do have trial 4 for all the subjects. 
  
#   checking if all ids have trial 4: 

# num_id <- d_final_analysis %>% 
#  group_by(id, block) %>% 
#   filter( trial ==4)
# 
# unique(num_id$id) ## so all ids have trial == 4 for all blocks 

```

making trial variable that does not reset with each block 

```{r}


data_clean <- data_clean %>%
  group_by(id) %>%
  mutate(trial_num = row_number()) %>%
  ungroup()

```

removing rt outlier trials 

```{r}



# d_final_rt %>%
#   group_by(subject) %>%   
#   filter(!(error == 1 | lead(error) == 1)) %>%
#   ungroup()

rt_estimation <- data_clean %>%
  filter(error == 0, prev_error == 0)

rt_stats <- rt_estimation %>%
  group_by(
    id,
    valence_current_group,
    valence_previous_group,
    cycle
  ) %>%
  summarise(
    mean_rt = mean(time, na.rm = TRUE),
    sd_rt   = sd(time, na.rm = TRUE),
    .groups = "drop"
  )

data_clean <- data_clean %>%
  left_join(
    rt_stats,
    by = c(
      "id",
      "valence_current_group",
      "valence_previous_group",
      "cycle"
    )
  )

data_clean <- data_clean %>%
  mutate(rt_z = (time - mean_rt) / sd_rt)

data_clean <- data_clean %>%
  filter(abs(rt_z) < 3)


## checking for NAs (should return 0) : 

sum(is.na(data_clean$rt_z)) # 0 

sum(is.na(data_clean$prev_error)) # 0 


```
data_clean has 40.454 observations and 24 variables at this stage 



saving this version of the df to be used: 
```{r}

# getwd()
write.csv(data_clean, "data_clean_use.csv", row.names = FALSE)

```


######################################################################################################
                                            ANALYSIS        
######################################################################################################


```{r}
d_clean_backup <- data_clean 

d_analysis <- data_clean
```

Note: 
(i)For the RT models, error trials, and trials before errors should also be removed
(ii) - using the Valence_current_group variable --> make new variable val_c_g with levels -0.5 for (Valence_current_group == 1) and + 0.5 for (Valence_current_group == 2) 
     - using the Valence_previous_group variable --> make new variable val_p_g with levels -0.5 for (Valence_previous_group == 1) and + 0.5 for Valence_previous_group == 2) 
     

Coding: 

- Switch (0 - no switch; 1 - switch) 

- Valence_current_group (-0.5 - univalent; 0.5 bivalent) - so make new variable with this 

- Valence_previous_group (-0.5 - univalent; 0.5 bivalent) - so make new variable with this 

Models: 

lmer(RT ~ Valence_current_group * Valence_previous_group*Switch + (Valence_current_group + Valence_previous_group + Switch|Subject)) 

glmer(Error ~ Valence_current_group * Valence_previous_group*Switch + (Valence_current_group + Valence_previous_group + Switch|Subject), family = “binomial”, control = glmerControl(optimizer = “bobyqa”)) 


A. New variables for valence of current and previous group according to -0.5 and +0.5 coding 

```{r}


# class(d_analysis)

d_analysis$val_c_g <- ifelse(d_analysis$valence_current_group == 1, -0.5,
                     ifelse(d_analysis$valence_current_group == 2,  0.5, NA))

d_analysis$val_p_g <- ifelse(d_analysis$valence_previous_group == 1, -0.5,
                     ifelse(d_analysis$valence_previous_group == 2,  0.5, NA))




```

B. make new valence variable for contrast coding 

```{r}
d_analysis$val_c_g_contrast <- ifelse(d_analysis$valence_current_group == 1, 0,
                     ifelse(d_analysis$valence_current_group == 2,  1, NA))

d_analysis$val_p_g_contrast <- ifelse(d_analysis$valence_previous_group == 1, 0,
                     ifelse(d_analysis$valence_previous_group == 2,  1, NA))


```


c. Models 

```{r}
#d_analysis$filter_correct <- as.integer(d_arrange$error != 0 | d_arrange$prev_error != 0)

d_analysis$filter_correct <- as.integer(d_analysis$error != 0 | d_analysis$prev_error != 0)
```


1. lmer

a. effect coding 

```{r}
######## use this 

d_analysis$val_c_g <- as.factor(d_analysis$val_c_g)
d_analysis$val_p_g <- as.factor(d_analysis$val_p_g)
d_analysis$switch <- as.factor(d_analysis$switch)

levels(d_analysis$val_c_g)
levels(d_analysis$val_p_g)
levels(d_analysis$switch)

contrasts(d_analysis$val_c_g) <- c(-0.5,0.5)
contrasts(d_analysis$val_c_g)

contrasts(d_analysis$val_p_g) <- c(-0.5,0.5)
contrasts(d_analysis$val_p_g)

levels(d_analysis$val_c_g)
levels(d_analysis$val_p_g)
levels(d_analysis$switch)

```



```{r}
saveRDS(d_analysis, "d_analysis.rds")
```


```{r}

 m_rt_effect<- lmer(log(time) ~  val_c_g * val_p_g * switch + (val_c_g + switch |  id),
                 data = d_analysis %>% filter(filter_correct == 0),
                  na.action = na.exclude,
              
               control = lmerControl(optimizer = "bobyqa"))


 summary(m_rt_effect)
 
 
 
 m_rt_effectBase<- lmer(log(time) ~  val_c_g * val_p_g * switch + (1 |  id),
                 data = d_analysis %>% filter(filter_correct == 0),
                  na.action = na.exclude,
              
               control = lmerControl(optimizer = "bobyqa"))

  summary(m_rt_effectBase)
  
  m_rt_effect1<- lmer(log(time) ~  val_c_g * val_p_g * switch + (1+switch  |  id),
                 data = d_analysis %>% filter(filter_correct == 0),
                  na.action = na.exclude,
              
               control = lmerControl(optimizer = "bobyqa"))

  summary(m_rt_effect1)
  
  anova(m_rt_effect1,m_rt_effectBase)
 
  
  
 
 
 
 
 
#library(sjPlot)
# tab_model(m_rt_new,show.est=T,auto.label=F,show.stat=T)
 tab_model(m_rt_effect,show.est=T,auto.label=F,show.stat=T, df.method = "satterthwaite") ## lmertest uses Satterthwaite's method by default 



  m_rt_effect_try<- lmer(log(time) ~  val_c_g * val_p_g * switch + (val_c_g + val_p_g+ switch |  id),
                 data = d_analysis %>% filter(filter_correct == 0),
                 # na.action = na.exclude,
              
               control = lmerControl(optimizer = "bobyqa"))


 
 summary(m_rt_effect_try)
 
 
#library(sjPlot)
# tab_model(m_rt_new,show.est=T,auto.label=F,show.stat=T)
 tab_model(m_rt_effect_try,show.est=T,auto.label=F,show.stat=T, df.method = "satterthwaite")
 


```

```{r}


d_rt_analysis <- d_analysis %>%
  filter(filter_correct == 0) %>%
  mutate(log_time = log(time)) 

m_rt_effect_use<- lmer(log_time ~  val_c_g * val_p_g * switch + (val_c_g + val_p_g+ switch |  id),
                 data = d_rt_analysis %>% filter(filter_correct == 0),
                 # na.action = na.exclude,
              
               control = lmerControl(optimizer = "bobyqa"))


 
 summary(m_rt_effect_use)
 
 
#library(sjPlot)
# tab_model(m_rt_new,show.est=T,auto.label=F,show.stat=T)
 tab_model(m_rt_effect_use,show.est=T,auto.label=F,show.stat=T, df.method = "satterthwaite")
 

```

b. contrast coding 

```{r}


d_rt_analysis$val_c_g_contrast <- as.factor(d_rt_analysis$val_c_g_contrast)
d_rt_analysis$val_p_g_contrast <- as.factor(d_rt_analysis$val_p_g_contrast)
d_rt_analysis$switch <- as.factor(d_rt_analysis$switch)

levels(d_rt_analysis$val_c_g_contrast)
levels(d_rt_analysis$val_p_g_contrast)
levels(d_rt_analysis$switch)

 m_rt_contrast<- lmer(log(time) ~  val_c_g_contrast * val_p_g_contrast * switch + (val_c_g_contrast + switch |  id),
                 data = d_rt_analysis %>% filter(filter_correct == 0),
                  na.action = na.exclude,
              
               control = lmerControl(optimizer = "bobyqa"))


 
 summary(m_rt_contrast)
 
 
#library(sjPlot)
# tab_model(m_rt_new,show.est=T,auto.label=F,show.stat=T)
 tab_model(m_rt_contrast,show.est=T,auto.label=F,show.stat=T, df.method = "satterthwaite") ## lmertest uses Satterthwaite's method by default 

```


2. glmer 

a. effect coding 

```{r}

d_analysis$error <- as.factor(d_analysis$error)
levels(d_analysis$error)

m_error_effect<- glmer(error ~  val_c_g * val_p_g * switch + ( val_c_g + val_p_g + switch| id),
                 data = d_analysis, 
                 family = "binomial",
                  na.action = na.exclude, 
                 control = glmerControl(optimizer = "bobyqa"))

 
 summary(m_error_effect)
 
 tab_model(m_error_effect,show.est=T,auto.label=F,show.stat=T)

```


b. contrast coding 

```{r}
# d_arrange$error <- as.factor(d_arrange$error)

m_error_contrast<- glmer(error ~  val_c_g_contrast * val_p_g_contrast * switch + ( val_c_g_contrast + switch| id),
                 data = d_analysis, 
                 family = "binomial",
                  na.action = na.exclude, 
                 control = glmerControl(optimizer = "bobyqa"))

 
 summary(m_error_contrast)
 
 tab_model(m_error_contrast,show.est=T,auto.label=F,show.stat=T)
```


3. DDM analysis using both effect and contrast coding of valence 

#| include: false
#first putting in some pre-made functions that will go into the ezDDM analysis: 

A. effect coding 

```{r}

normWS <- function(d ,s, dv, between = NULL) { #within subject normalization
  eval(substitute(d %>%
                    dplyr::group_by(s) %>%
                    dplyr::mutate(sAV = mean(dv, na.rm = TRUE)) %>%
                    dplyr::group_by_at(between) %>% #this is grouping by between subjects variables
                    dplyr::mutate(gAV = mean(dv, na.rm = TRUE)) %>%
                    dplyr::mutate(DV_n = dv - sAV + gAV), list(s = as.name(s), dv = as.name(dv))))
}


get_ci <- function(var, mean){
  sd <- sd(var, na.rm = TRUE)
  n <- length(var)
  se <- sd/sqrt(n)
  ci <- abs(qt(0.025, n-1, lower.tail = FALSE))*se
  return(c(mean + ci, mean - ci, sd, se, n))
}

convert_extremes <- function(value){
  
  if(value == 1){
    
    value = value - 1e-5
    
  } else if (value == 0 ){
    
    value = value + 1e-5
    
  }
  
  return(value)
  
}#making sure error is either .99 or .001 -- Q: is this because: This is typically used before a logit transformation (log(p / (1-p))), which breaks down at exactly 0 or 1 since log(0) and log(1/0) are undefined. By nudging the values slightly, the transformation stays mathematically valid.
```


## Aggregation and data processing

--hausekeep 

install.packages("cli")
packageVersion("cli") -- should show ≥ 3.6.5-- it is 3.6.5 
install.packages("devtools")
devtools::install_github("hauselin/hausekeep")
library(hausekeep)

```{r}
# library(devtools)
# library(rio)
# library(hausekeep)
# 
# 
# library(tidyverse)
d_analysis <- d_analysis %>%
  mutate(error = as.numeric(as.character(error)))

alt_cue_agg_ID_ddm <- d_analysis %>%
  mutate(RT_s = time/1000) %>%
  group_by(id, val_c_g, val_p_g, switch, cycle) %>%
  summarize(RT_s_m = mean(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            Error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>%
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  
  unnest(ezddm)



alt_cue_agg_ddm <- alt_cue_agg_ID_ddm %>%
  group_by(id, val_c_g, val_p_g, switch, cycle) %>%
  normWS(s = "id", dv = "a") %>%
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>%
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>%
  mutate(Ter = DV_n) %>%
  group_by(val_c_g, val_p_g, switch, cycle) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[1],
            a_ci_upper = get_ci(a, a_m)[2],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[1],
            v_ci_upper = get_ci(v, v_m)[2],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[1],
            Ter_ci_upper = get_ci(Ter, Ter_m)[2],)

#make a separate object that is averaging across the no-switch 2,3 and 4 average within those and then average within those variances
alt_cue_agg_ID_ddm_collapsed <- alt_cue_agg_ID_ddm %>% 
  filter(switch == 0, cycle %in% c(2, 3)) %>%
  group_by(id, val_c_g, val_p_g) %>% 
  summarize( # average the DDM parameters across cycles 2&3 
    a = mean(a, na.rm = TRUE), 
    v = mean(v, na.rm = TRUE), #average within those 
    Ter = mean(Ter, na.rm = TRUE), 
    a_var = mean(a^2, na.rm = TRUE), #average within those variances
    v_var = mean(v^2, na.rm = TRUE), 
    Ter_var = mean(Ter^2, na.rm = TRUE), 
    .groups = "drop" )

alt_cue_agg_ID_ddm_collapsed

alt_cue_agg_ID_ddm %>% filter(switch == 0, cycle %in% c(2,3)) %>% count(id, val_c_g, val_p_g)
```
## Statistical Models

### First prep data so that it's ignoring cycle

```{r}
# alt_cue_agg_ID_ddm_nocycle <- d_final_analysis %>%
#   mutate(RT_s = time/1000) %>%
#   group_by(id, valence_current_group, valence_previous_group, val_c_g_contrast, val_p_g_contrast, switch) %>%
#   summarize(RT_s_m = mean(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
#             RT_s_var = var(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
#             Error = mean(error, na.rm = TRUE),
#             N_trials = n()) %>%
#   rowwise() %>%
#   mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
#                             rtCorrectVariance_seconds = RT_s_var, 
#                             rtCorrectMean_seconds = RT_s_m, 
#                             nTrials = N_trials))) %>%
#   unnest(ezddm)


alt_cue_agg_ID_ddm_nocycle <- d_analysis %>%
  mutate(RT_s = time/1000) %>%
  group_by(id, valence_current_group, val_c_g, valence_previous_group, val_p_g, switch) %>%
  summarize(RT_s_m = mean(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            Error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>%
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  unnest(ezddm)


alt_cue_agg_ddm_nocycle <- alt_cue_agg_ID_ddm_nocycle %>%
  group_by(id, val_c_g, val_p_g, switch) %>%
  normWS(s = "id", dv = "a") %>%
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>%
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>%
  mutate(Ter = DV_n) %>%
  group_by(val_c_g, val_p_g, switch) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[1],
            a_ci_upper = get_ci(a, a_m)[2],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[1],
            v_ci_upper = get_ci(v, v_m)[2],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[1],
            Ter_ci_upper = get_ci(Ter, Ter_m)[2],)

```

### Plots

```{r}
#theme_set(apa_theming()[[1]])

alt_cue_agg_ddm$switch <- as.factor(alt_cue_agg_ddm$switch)
alt_cue_agg_ddm_nocycle$switch <- as.factor(alt_cue_agg_ddm_nocycle$switch)
alt_cue_agg_ddm_nocycle$val_c_g <- as.factor(alt_cue_agg_ddm_nocycle$val_c_g)
alt_cue_agg_ddm_nocycle$val_p_g <- as.factor(alt_cue_agg_ddm_nocycle$val_p_g)

plt_ddm_a <- ggplot(alt_cue_agg_ddm, aes(x = cycle, y = a_m, color = val_c_g, linetype = val_p_g, group = interaction(val_c_g, val_p_g)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper), width = 0.1, position = pos)+
theme_classic()

plt_ddm_v <- ggplot(alt_cue_agg_ddm, aes(x = cycle, y = v_m, color = val_c_g, linetype = val_p_g, group = interaction(val_c_g, val_p_g)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper), width = 0.1, position = pos)+
theme_classic()


plt_ddm_Ter <- ggplot(alt_cue_agg_ddm, aes(x = cycle, y = Ter_m, color = val_c_g, linetype = val_p_g, group = interaction(val_c_g, val_p_g)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper), width = 0.1, position = pos)+
theme_classic()

#########
plt_ddm_a_nocycle <- ggplot(alt_cue_agg_ddm_nocycle, aes(x = switch, y = a_m, color = val_c_g , linetype = val_p_g, group = interaction(val_c_g, val_p_g)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper), width = 0.1, position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
theme_classic()

plt_ddm_v_nocycle <- ggplot(alt_cue_agg_ddm_nocycle, aes(x = switch, y = v_m, color = val_c_g, linetype = val_p_g, group = interaction(val_c_g, val_p_g)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper), width = 0.1, position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
theme_classic()


plt_ddm_Ter_nocycle <- ggplot(alt_cue_agg_ddm_nocycle, aes(x = switch, y = Ter_m, color = val_c_g, linetype = val_p_g, group = interaction(val_c_g, val_p_g)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper), width = 0.1, position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
theme_classic()

ezddm_effect_plot<- ggpubr::ggarrange(plt_ddm_a, plt_ddm_a_nocycle,
                  plt_ddm_v, plt_ddm_v_nocycle,
                  plt_ddm_Ter, plt_ddm_Ter_nocycle, common.legend = TRUE, nrow = 3, ncol = 2)  

ezddm_effect_plot

#ggsave("RT_descriptive_plot.svg", RT_descriptive_plot, width = 10, height = 6)
ggsave("ezddm_effect_plot_apa.svg", ezddm_effect_plot, width = 10, height = 6)
```

B. contrast coding 

```{r}
# library(devtools)
# library(rio)
# library(hausekeep)
# 
# 
# library(tidyverse)
d_analysis <- d_analysis %>%
  mutate(error = as.numeric(as.character(error)))

alt_cue_agg_ID_ddm <- d_analysis %>%
  mutate(RT_s = time/1000) %>%
  group_by(id, val_c_g_contrast, val_p_g_contrast, switch, cycle) %>%
  summarize(RT_s_m = mean(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            Error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>%
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  
  unnest(ezddm)



alt_cue_agg_ddm <- alt_cue_agg_ID_ddm %>%
  group_by(id, val_c_g_contrast, val_p_g_contrast, switch, cycle) %>%
  normWS(s = "id", dv = "a") %>%
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>%
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>%
  mutate(Ter = DV_n) %>%
  group_by(val_c_g_contrast, val_p_g_contrast, switch, cycle) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[1],
            a_ci_upper = get_ci(a, a_m)[2],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[1],
            v_ci_upper = get_ci(v, v_m)[2],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[1],
            Ter_ci_upper = get_ci(Ter, Ter_m)[2],)

#make a separate object that is averaging across the no-switch 2,3 and 4 average within those and then average within those variances
alt_cue_agg_ID_ddm_collapsed <- alt_cue_agg_ID_ddm %>% 
  filter(switch == 0, cycle %in% c(2, 3)) %>%
  group_by(id, val_c_g_contrast, val_p_g_contrast) %>% 
  summarize( # average the DDM parameters across cycles 2&3 
    a = mean(a, na.rm = TRUE), 
    v = mean(v, na.rm = TRUE), #average within those 
    Ter = mean(Ter, na.rm = TRUE), 
    a_var = mean(a^2, na.rm = TRUE), #average within those variances
    v_var = mean(v^2, na.rm = TRUE), 
    Ter_var = mean(Ter^2, na.rm = TRUE), 
    .groups = "drop" )

alt_cue_agg_ID_ddm_collapsed

alt_cue_agg_ID_ddm %>% filter(switch == 0, cycle %in% c(2,3)) %>% count(id, val_c_g_contrast, val_p_g_contrast)
```
## Statistical Models

### First prep data so that it's ignoring cycle

```{r}
# alt_cue_agg_ID_ddm_nocycle <- d_final_analysis %>%
#   mutate(RT_s = time/1000) %>%
#   group_by(id, valence_current_group, valence_previous_group, val_c_g_contrast, val_p_g_contrast, switch) %>%
#   summarize(RT_s_m = mean(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
#             RT_s_var = var(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
#             Error = mean(error, na.rm = TRUE),
#             N_trials = n()) %>%
#   rowwise() %>%
#   mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
#                             rtCorrectVariance_seconds = RT_s_var, 
#                             rtCorrectMean_seconds = RT_s_m, 
#                             nTrials = N_trials))) %>%
#   unnest(ezddm)


alt_cue_agg_ID_ddm_nocycle <- d_analysis %>%
  mutate(RT_s = time/1000) %>%
  group_by(id, val_c_g, val_c_g_contrast, val_p_g, val_p_g_contrast, switch) %>%
  summarize(RT_s_m = mean(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            Error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>%
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  unnest(ezddm)


alt_cue_agg_ddm_nocycle <- alt_cue_agg_ID_ddm_nocycle %>%
  group_by(id, val_c_g_contrast, val_p_g_contrast, switch) %>%
  normWS(s = "id", dv = "a") %>%
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>%
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>%
  mutate(Ter = DV_n) %>%
  group_by(val_c_g_contrast, val_p_g_contrast, switch) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[1],
            a_ci_upper = get_ci(a, a_m)[2],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[1],
            v_ci_upper = get_ci(v, v_m)[2],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[1],
            Ter_ci_upper = get_ci(Ter, Ter_m)[2],)

```

### Plots

```{r}

# alt_cue_agg_ddm$val_p_g_contrast <- as.factor(alt_cue_agg_ddm$val_p_g_contrast)
# alt_cue_agg_ddm$val_c_g_contrast <- as.factor(alt_cue_agg_ddm$val_c_g_contrast)
# alt_cue_agg_ddm$switch <- as.factor(alt_cue_agg_ddm$switch)
# alt_cue_agg_ddm_nocycle$switch <- as.factor(alt_cue_agg_ddm_nocycle$switch)
# alt_cue_agg_ddm_nocycle$val_c_g_contrast <- as.factor(alt_cue_agg_ddm_nocycle$val_c_g_contrast)
# alt_cue_agg_ddm_nocycle$val_p_g_contrast <- as.factor(alt_cue_agg_ddm_nocycle$val_p_g_contrast)
# 
# plt_ddm_a <- ggplot(alt_cue_agg_ddm, aes(x = cycle, y = a_m, color = val_c_g_contrast, linetype = val_p_g_contrast, group = interaction(val_c_g_contrast, val_p_g_contrast)))+
#   geom_line(position = pos)+
#   geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper), width = 0.1, position = pos)+
# theme_set(apa_theming())
# 
# plt_ddm_v <- ggplot(alt_cue_agg_ddm, aes(x = cycle, y = v_m, color = val_c_g_contrast, linetype = val_p_g_contrast, group = interaction(val_c_g_contrast, val_p_g_contrast)))+
#   geom_line(position = pos)+
#   geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper), width = 0.1, position = pos)+
#  theme_set(apa_theming())
# 
# 
# plt_ddm_Ter <- ggplot(alt_cue_agg_ddm, aes(x = cycle, y = Ter_m, color = val_c_g_contrast, linetype = val_p_g_contrast, group = interaction(val_c_g_contrast, val_p_g_contrast)))+
#   geom_line(position = pos)+
#   geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper), width = 0.1, position = pos)+
# theme_set(apa_theming())
# 
# #########
# plt_ddm_a_nocycle <- ggplot(alt_cue_agg_ddm_nocycle, aes(x = switch, y = a_m, color = val_c_g_contrast , linetype = val_p_g_contrast, group = interaction(val_c_g_contrast, val_p_g_contrast)))+
#   geom_line(position = pos)+
#   geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper), width = 0.1, position = pos)+
#   scale_x_discrete(limits = c("1", "0"))+
# theme_set(apa_theming())
# 
# plt_ddm_v_nocycle <- ggplot(alt_cue_agg_ddm_nocycle, aes(x = switch, y = v_m, color = val_c_g_contrast, linetype = val_p_g_contrast, group = interaction(val_c_g_contrast, val_p_g_contrast)))+
#   geom_line(position = pos)+
#   geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper), width = 0.1, position = pos)+
#   scale_x_discrete(limits = c("1", "0"))+
# theme_set(apa_theming())
# 
# 
# plt_ddm_Ter_nocycle <- ggplot(alt_cue_agg_ddm_nocycle, aes(x = switch, y = Ter_m, color = val_c_g_contrast, linetype = val_p_g_contrast, group = interaction(val_c_g_contrast, val_p_g_contrast)))+
#   geom_line(position = pos)+
#   geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper), width = 0.1, position = pos)+
#   scale_x_discrete(limits = c("1", "0"))+
# theme_set(apa_theming())
# 
# ezddm_contrast_plot <- ggpubr::ggarrange(plt_ddm_a, plt_ddm_a_nocycle,
#                   plt_ddm_v, plt_ddm_v_nocycle,
#                   plt_ddm_Ter, plt_ddm_Ter_nocycle, common.legend = TRUE, nrow = 3, ncol = 2)  
# 
# ggsave("ezddm_contrast_plot_apa.svg", ezddm_contrast_plot, width = 10, height = 6)
```

### lmer models on ezDDM parameters for both effect and contrast coding  

```{r}

## note: look into why you cannot estimate Residual R^2 very well for lmer models 

alt_cue_a <- lmer(a ~ val_c_g * val_p_g * switch + (val_c_g + switch | id), alt_cue_agg_ID_ddm_nocycle)


summary(alt_cue_a)

tab_model(alt_cue_a)

alt_cue_v <- lmer(v ~  val_c_g * val_p_g * switch + (val_c_g + switch |id), 
     alt_cue_agg_ID_ddm_nocycle)

summary(alt_cue_v)

tab_model(alt_cue_v)


alt_cue_Ter <- lmer(Ter ~  val_c_g * val_p_g * switch + (val_c_g + switch |id), 
     alt_cue_agg_ID_ddm_nocycle)

summary(alt_cue_Ter)

tab_model(alt_cue_Ter)

#contrasts(alt_cue_agg_ID_ddm_nocycle$val_c_g)
#contrasts(alt_cue_agg_ID_ddm_nocycle$val_p_g)
```



2. contrast coding 

```{r}


alt_cue_a_contrast <- lmerTest::lmer(a ~ val_c_g_contrast * val_p_g_contrast * switch + (val_c_g_contrast + switch | id), alt_cue_agg_ID_ddm_nocycle)


summary(alt_cue_a_contrast)

tab_model(alt_cue_a_contrast, df.method = "satterthwaite" )

alt_cue_v_contrast <- lmer(v ~  val_c_g_contrast * val_p_g_contrast * switch + (val_c_g_contrast + switch |id), 
     alt_cue_agg_ID_ddm_nocycle)

summary(alt_cue_v_contrast)

tab_model(alt_cue_v_contrast, df.method = "satterthwaite")


alt_cue_Ter_contrast <- lmer(Ter ~  val_c_g_contrast * val_p_g_contrast * switch + (val_c_g_contrast + switch |id), 
     alt_cue_agg_ID_ddm_nocycle)

summary(alt_cue_Ter_contrast)

tab_model(alt_cue_Ter_contrast, df.method = "satterthwaite")
```


descriptive plots 

!!!!!!!!!!!!!!!!! wrong CI!! so do not use these sets of plots !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

1. rt: 
```{r}
# 
# 
# rt_plot_df <- d_analysis %>%
#   filter(filter_correct == 0 ) %>%
#   group_by(valence_current_group,
#            valence_previous_group,
#            switch) %>%
#   summarise(
#     mean_rt = mean(time, na.rm = TRUE),
#     se_rt   = sd(time, na.rm = TRUE)/sqrt(n()),
#     .groups = "drop"
#   )
# rt_plot_df <- rt_plot_df %>%
#   mutate(
#     switch = factor(switch, levels = c(0,1)),
#     valence_current_group = factor(valence_current_group,
#                                    labels = c("Current: Univalent",
#                                               "Current: Bivalent")),
#     valence_previous_group = factor(valence_previous_group,
#                                     labels = c("Previous: Univalent",
#                                                "Previous: Bivalent"))
#   )
# 
# rt_explevel_plot <- ggplot(rt_plot_df,
#        aes(x = switch,
#            y = mean_rt,
#            color = valence_current_group,
#            linetype = valence_previous_group,
#            group = interaction(valence_current_group,
#                                valence_previous_group))) +
#   
#   geom_line(size = 1) +
#   geom_point(size = 3) +
#   
#   geom_errorbar(aes(ymin = mean_rt - se_rt,
#                     ymax = mean_rt + se_rt),
#                 width = .1) +
#   
#   labs(
#     x = "Cycle",
#     y = "Mean RT (ms)",
#     color = "Current Group",
#     linetype = "Previous Group"
#   ) +
#   
#  theme_minimal()
# 
# ggsave("rt_explevel_plot.svg", rt_explevel_plot, width = 10, height = 6)
# 
# 
# ### apa_theming 
# 
# # --- PLOTTING ---
# 
# # 1. To set the global theme, extract just the first element of the list
# 
# 
# rt_explevel_plot <- ggplot(rt_plot_df,
#        aes(x = cycle,
#            y = mean_rt,
#            color = valence_current_group,
#            linetype = valence_previous_group,
#            group = interaction(valence_current_group,
#                                valence_previous_group))) +
#   
#   # Use linewidth instead of size for geom_line
#   geom_line(linewidth = 1) + 
#   geom_point(size = 3) +
#   
#   geom_errorbar(aes(ymin = mean_rt - se_rt,
#                     ymax = mean_rt + se_rt),
#                 width = .1) +
#   
#   labs(
#     x = "Cycle",
#     y = "Mean RT (ms)",
#     color = "Current Group",
#     linetype = "Previous Group"
#   ) +
#   # Use the function here to apply both the theme and the colors
#  theme_classic() 
# 
# ggsave("rt_explevel_plot_apa.svg", rt_explevel_plot, width = 10, height = 6)
# 
# rt_explevel_plot

```

1b. log rt 
```{r}
#theme_set(apa_theming()[[1]])

# log_rt_plot_df <- d_analysis %>%
#   filter(filter_correct == 0 ) %>%
#   group_by(valence_current_group,
#            valence_previous_group,
#            switch) %>%
#   summarise(
#     mean_rt = mean(log(time), na.rm = TRUE),
#     se_rt   = sd(log(time), na.rm = TRUE)/sqrt(n()),
#     .groups = "drop"
#   )
# log_rt_plot_df <- log_rt_plot_df %>%
#   mutate(
#     #switch = factor(switch, levels = c(0,1)),
#     switch = factor(switch),
#     valence_current_group = factor(valence_current_group,
#                                    labels = c("Current: Univalent",
#                                               "Current: Bivalent")),
#     valence_previous_group = factor(valence_previous_group,
#                                     labels = c("Previous: Univalent",
#                                                "Previous: Bivalent"))
#   )
# 
# logrt_explevel_plot<- ggplot(log_rt_plot_df,
#        aes(x = switch,
#            y = mean_rt,
#            color = valence_current_group,
#            linetype = valence_previous_group,
#            group = interaction(valence_current_group,
#                                valence_previous_group))) +
#   
#   geom_line(linewidth = 1) +
#   geom_point(size = 3) +
#   
#   geom_errorbar(aes(ymin = mean_rt - se_rt,
#                     ymax = mean_rt + se_rt),
#                 width = .1) +
#   
#   labs(
#     x = "Switch",
#     y = "Mean log RT (ms)",
#     color = "Current Group",
#     linetype = "Previous Group"
#   ) +
#   
#  
#   # Use the function here to apply both the theme and the colors
#   theme_classic() 
# 
# ggsave("logrt_explevel_plot_apa.svg", logrt_explevel_plot, width = 10, height = 6)
# 
# logrt_explevel_plot

```
2. error 

```{r}
# library(dplyr)
# library(ggplot2)

#theme_set(apa_theming()[[1]])
# 
# err_plot_df <- d_analysis %>%
#   group_by(valence_current_group,
#            valence_previous_group,
#            switch) %>%
#   summarise(
#     error_rate = mean(error, na.rm = TRUE),
#     se_error   = sd(error, na.rm = TRUE)/sqrt(n()),
#     .groups = "drop"
#   )
# err_plot_df <- err_plot_df %>%
#   mutate(
#     switch = factor(switch, levels = c(0,1)),
#     
#     valence_current_group = factor(
#       valence_current_group,
#       labels = c("Current: Univalent",
#                  "Current: Bivalent")
#     ),
#     
#     valence_previous_group = factor(
#       valence_previous_group,
#       labels = c("Previous: Univalent",
#                  "Previous: Bivalent")
#     )
#   )
# 
# error_explevel_plot <- ggplot(err_plot_df,
#        aes(x = switch,
#            y = error_rate,
#            color = valence_current_group,
#            linetype = valence_previous_group,
#            group = interaction(valence_current_group,
#                                valence_previous_group))) +
#   
#   geom_line(size = 1) +
#   geom_point(size = 3) +
#   
#   geom_errorbar(aes(ymin = error_rate - se_error,
#                     ymax = error_rate + se_error),
#                 width = .1) +
#   
#   labs(
#     x = "Cycle",
#     y = "Error Rate",
#     color = "Current Group",
#     linetype = "Previous Group"
#   ) +
#   
# theme_classic()
# 
# error_explevel_plot
# 
# ggsave("error_explevel_plot_apa.svg", error_explevel_plot, width = 10, height = 6)  


```

######################################################################################################

                            WITHIN SUBJECTS ANALYSIS 
                            
 #################################################################################################                           
```{r}

d_arrange <- d_analysis %>% 
  arrange(id, block, trial)

model_RT_trial <- lmer(log(time) ~ poly(trial_num, 2) + (poly(trial_num, 2)|id),  # poly function is for generating a polynomial and it gives two functions: one for linear and one for polynomial 
                       control = lmerControl(optimizer = "bobyqa"),
                       d_arrange %>%  filter(error == 0)) ## not filtering by prev_error == 0 


# model_RT_trial %>%
#   make_model_table()


tab_model(model_RT_trial)

summary(model_RT_trial)

d_arrange <- d_arrange %>%
  ungroup() %>%
  mutate(time_log_pred = predict(model_RT_trial, .)) #%>%
  
subs <- d_arrange$id %>% unique() %>% head(5) ## sanity check with just 5 subjects 


## checking for 5 subjects 
ggplot(d_arrange %>% filter(id %in% subs), aes(x = trial_num, y = log(time), color = block, group = interaction(id, block)))+
  geom_line(alpha = 0.5, lwd = 0.3)+
  geom_smooth(se = FALSE)+
  geom_line(aes(y = time_log_pred), color = "green")+
  facet_grid(~id)+
  theme_classic()+
  theme(legend.position = "none")


d_arrange$time_log_res <- NA
d_arrange$time_log_res[d_arrange$error == 0] <- residuals(model_RT_trial)


d_arrange <- d_arrange %>%
  group_by(id, block) %>%
  mutate(lag1_time_log_res = lag(time_log_res, 1))


length(d_arrange$time_log_res)
length(d_arrange$time_log_res[d_arrange$error == 0]) 
length(d_arrange$lag1_time_log_res)


d_arrange %>% 
  ungroup( ) %>% 
  filter(filter_correct ==0) %>% 
  summarize(x = sum(is.na(lag1_time_log_res)), n = n())
  

```
## step 2: helmert contrast 

a. create a new cycle variable (duplicate of cycle but with different name) and assign the coding of that version of the cycle variable 

```{r}

d_arrange <- d_arrange %>% 
  mutate(cycle_helmert = cycle)

names(d_arrange)

d_arrange <- d_arrange %>%
  mutate(cycle_helmert = factor(cycle))


```


b. 

```{r}
m <- contr.helmert(3) # 3 because cycle has 3 levels 

m[,1] <- rev(m[,1])
m[,2] <- rev(m[,2])

m

#m: 
#[,1] [,2]
#1    0    2
#2    1   -1
#3   -1   -1
```


c. naming the contrast levels: 

```{r}

colnames(m) <- c("cycle_2_v_3" , "cycle_1_v_23")

m
```

d. 


```{r}
contrasts(d_arrange$cycle_helmert) <- m  


```
e. RT residual analysis

-- now, adding the residual obtained from the previous model and will put that as an additional continuous predictor to our lmer model 

```{r}


# 
 d_arrange$val_c_g_contrast <- as.factor(d_arrange$val_c_g_contrast)
 d_arrange$val_p_g_contrast <- as.factor(d_arrange$val_p_g_contrast)
 d_arrange$cycle_helmert <- as.factor(d_arrange$cycle_helmert)



alt_cue_rt_log_resrt <- lmerTest::lmer(time_log_res ~ val_c_g_contrast * val_p_g_contrast * cycle_helmert * lag1_time_log_res + (val_c_g_contrast  + val_p_g_contrast + cycle_helmert + lag1_time_log_res |id), control = lmerControl(optimizer = "bobyqa"),
     d_arrange %>% 
       filter(filter_correct == 0)) #warning isSignular but the model converged 


alt_cue_rt_log_resrt_check <- lmerTest::lmer(time_log_res ~ val_c_g_contrast * val_p_g_contrast * cycle_helmert * lag1_time_log_res + (1 |id), control = lmerControl(optimizer = "bobyqa"),
     d_arrange %>% 
       filter(filter_correct == 0)) 

d_arrange_check <- d_arrange %>% 
  filter(filter_correct == 0)



tab_model(alt_cue_rt_log_resrt, df.method = "satterthwaite")

summary(alt_cue_rt_log_resrt_check)

# preds <- emmeans::emmeans(time, ~ val_c_g * val_p_g * switch * lag1_time_log_res, type = "response",
#                  at = list(val_c_g = c(-0.5, 0.5),
#                            val_p_g = c(-0.5, 0.5),
#                            switch = c(0, 1),
#                            lag1_time_log_res = c(6.5, 10.5))) %>% ## choosing random two values to denote a fast rt and a slow rt (can also use quantile function here to get it for three or more quantiles of)
  


  preds <- emmeans::emmeans(alt_cue_rt_log_resrt, ~ val_c_g_contrast * val_p_g_contrast * cycle_helmert * lag1_time_log_res, type = "response",
                 at = list(val_c_g_contrast = c(0, 1),
                           val_p_g_contrast = c(0, 1),
                          # switch = c(0, 1),
                          cycle_helmert = factor(c(1,2,3)),
                           lag1_time_log_res = c(-1.5, 1.5))) %>% ## choosing random two values to denote a fast rt and a slow rt (can also use quantile function here to get it for three or more quantiles of)
  
  
  as.data.frame() %>%
  mutate(prev_bivalent = case_when(val_p_g_contrast == 0 ~ 0, 
                                   val_p_g_contrast ==  1 ~ 1) %>% factor(),
         is_bivalent = case_when(val_c_g_contrast == 0 ~ 0,
                                   val_c_g_contrast ==  1 ~ 1) %>% factor(),
         switch = factor(cycle_helmert),
         speed = case_when(lag1_time_log_res == min(lag1_time_log_res) ~ "fast",
                           lag1_time_log_res == max(lag1_time_log_res) ~ "slow") %>% factor()) 
  
  summary(preds)

names(preds)

logrt_pred_cycle_helmert<- ggplot(preds, aes(x = cycle_helmert, y = emmean, color = is_bivalent, linetype = prev_bivalent, group = interaction(is_bivalent, prev_bivalent)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = pos)+
  #scale_x_discrete(limits = c("1", "0"))+
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast")))+
  labs(title = "Model predictions for log RTs",
       y = "log(RT) prediction")+
  theme_classic()

#ggsave("logrt_pred_cycle_helmert.svg", logrt_pred_cycle_helmert, width = 10, height = 6)

```
#################################################################################################################

putting the subject intercepts into the second model to combat issingualr 

```{r}

model_RT_trial <- lmer(log(time) ~ poly(trial_num, 2) + (poly(trial_num, 2)|id),  # poly function is for generating a polynomial and it gives two functions: one for linear and one for polynomial 
                       control = lmerControl(optimizer = "bobyqa"),
                       d_arrange %>%  filter(error == 0)) ## not filtering by prev_error == 0 

coefficients(model_RT_trial)

summary(model_RT_trial)

coefficents <- coefficients(model_RT_trial)
coefficents$id

intercept <- coefficients(model_RT_trial)$id %>% 
  as.data.frame() %>%
  rownames_to_column("id")

intercept


intercept$Intercept <- intercept$`(Intercept)`

d_arrange <- d_arrange %>% 
  left_join(intercept)

d_arrange <- d_arrange%>% 
  select(-`poly(trial_num, 2)1`)
  
d_arrange <- d_arrange%>% 
  select(- `poly(trial_num, 2)2`)
  
names(d_arrange)

```

```{r}


d_arrange <- d_arrange %>%
  #group_by(id, block) %>%
  mutate(lag1_time_log_res_inter = lag1_time_log_res + Intercept)


d_arrange <- d_arrange %>%
  #group_by(id, block) %>%
  mutate(time_log_res_inter = time_log_res + Intercept)


d_arrange


```


```{r}

# d_arrange <- d_arrange %>% 
#   mutate(time_log_res_z = scale(time_log_res)) 
# 
# d_arrange <- d_arrange %>% 
#   mutate(lag1_time_log_res_z = scale(lag1_time_log_res)) 


d_arrange <- d_arrange %>% 
  ungroup() %>% 
  mutate(time_log_res_c = time_log_res_inter - mean(time_log_res_inter, na.rm = TRUE) )

d_arrange <- d_arrange %>% 
  ungroup() %>% 
  mutate(lag1_time_log_res_c = lag1_time_log_res_inter - mean(lag1_time_log_res_inter, na.rm = TRUE) )



```

```{r}
d_arrange$val_c_g_contrast <- as.factor(d_arrange$val_c_g_contrast)
 d_arrange$val_p_g_contrast <- as.factor(d_arrange$val_p_g_contrast)
 d_arrange$cycle_helmert <- as.factor(d_arrange$cycle_helmert)



alt_cue_rt_log_resrt_2 <- lmerTest::lmer(time_log_res_c ~ val_c_g_contrast * val_p_g_contrast * cycle_helmert * lag1_time_log_res_c + (val_c_g_contrast + val_p_g_contrast + cycle_helmert + lag1_time_log_res_c |id), control = lmerControl(optimizer = "bobyqa"),
     d_arrange %>% 
       filter(filter_correct == 0)) #warning isSignular but the model converged 


summary(alt_cue_rt_log_resrt_2)
tab_model(alt_cue_rt_log_resrt_2, df.method = "satterthwaite")


```

```{r}

d_arrange <- d_arrange %>%
  mutate(
    val_c_g = factor(val_c_g),
    val_p_g = factor(val_p_g),
    switch   = factor(switch)
  )
```

by switch 

```{r}

alt_cue_rt_log_resrt_s <- lmerTest::lmer(time_log_res ~ val_c_g_contrast * val_p_g_contrast * switch * lag1_time_log_res + (val_c_g_contrast  +  switch + lag1_time_log_res |id), control = lmerControl(optimizer = "bobyqa"),
     d_arrange %>% 
       filter(filter_correct == 0))

summary(alt_cue_rt_log_resrt_s)

tab_model(alt_cue_rt_log_resrt_s, df.method = "satterthwaite")


alt_cue_rt_log_resrt_s_2 <- lmerTest::lmer(time_log_res_c ~ val_c_g * val_p_g * switch * lag1_time_log_res_c + (val_c_g + val_p_g+ switch + lag1_time_log_res_c |id), control = lmerControl(optimizer = "bobyqa"),
     d_arrange %>% 
       filter(filter_correct == 0))

summary(alt_cue_rt_log_resrt_s_2)

tab_model(alt_cue_rt_log_resrt_s_2, df.method = "satterthwaite")
```

```{r}

levels(d_arrange$val_c_g)

#d_arrange$switch <- as.factor(d_arrange$switch)

  preds_switch <- emmeans::emmeans(alt_cue_rt_log_resrt_s_2, ~ val_c_g * val_p_g * switch * lag1_time_log_res_c, type = "response",
                 at = list(val_c_g = factor(c(0, 1)),
                           val_p_g = factor(c(0, 1)),
                          switch =factor(c(0, 1)),
                         # cycle_helmert = factor(c(1,2,3)),
                           lag1_time_log_res_c = c(-1.5, 1.5))) %>% ## choosing random two values to denote a fast rt and a slow rt (can also use quantile function here to get it for three or more quantiles of)
  
  
  as.data.frame() %>%
  mutate(prev_bivalent = case_when(val_p_g == 0 ~ 0, 
                                  val_p_g ==  1 ~ 1) %>% factor(),
         is_bivalent = case_when(val_c_g == 0 ~ 0,
                                   val_c_g ==  1 ~ 1) %>% factor(),
         switch = factor(switch),
         speed = case_when(lag1_time_log_res_c == min(lag1_time_log_res_c) ~ "fast",
                           lag1_time_log_res_c == max(lag1_time_log_res_c) ~ "slow") %>% factor()) 
  
  summary(preds_switch)

names(preds_switch)

#theme_set(apa_theming()[[1]])
# 1. Define the dodge position
pos <- position_dodge(0.3) 

# 2. Plot with corrected column names for lmerTest results
logrt_pred_switch <- ggplot(preds_switch, 
       aes(x = switch, 
           y = emmean, 
           color = is_bivalent, 
           linetype = prev_bivalent, 
           group = interaction(is_bivalent, prev_bivalent))) +
  geom_line(position = pos) +
  geom_point(position = pos) + 
  # Use asymp.LCL and asymp.UCL which match your previous error output
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), width = 0.2, position = pos) + 
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast"))) +
  labs(title = "Model predictions for log RTs",
       y = "log(RT) Prediction",
       x = "Switch (0 = Repeat, 1 = Switch)") +
 theme_classic()

logrt_pred_switch

#ggsave("logrt_pred_switch_apa.svg", logrt_pred_switch, width = 10, height = 6)
```


```{r}
preds_switch <- emmeans::emmeans(alt_cue_rt_log_resrt_s_2, 
    ~ val_c_g * val_p_g * switch * lag1_time_log_res_c, 
    type = "response",
    at = list(
      val_c_g = c("-0.5", "0.5"),
      val_p_g = c("-0.5", "0.5"),
      switch   = c("0", "1"),
      lag1_time_log_res_c = c(-1.5, 1.5)
    )) %>%
  as.data.frame() %>%
  mutate(
    is_bivalent   = case_when(val_c_g == "-0.5" ~ "univalent",
                               val_c_g == "0.5"  ~ "bivalent") %>% 
                    factor(levels = c("univalent", "bivalent")),
    prev_bivalent = case_when(val_p_g == "-0.5" ~ "univalent",
                               val_p_g == "0.5"  ~ "bivalent") %>% 
                    factor(levels = c("univalent", "bivalent")),
    switch_factor = factor(switch, levels = c("0", "1"), 
                           labels = c("repeat", "switch")),
    speed         = case_when(lag1_time_log_res_c == -1.5 ~ "fast",
                               lag1_time_log_res_c ==  1.5 ~ "slow") %>% 
                    factor(levels = c("fast", "slow"))
  )

# 4. Define pos if not already defined
pos <- position_dodge(0.3)

# 5. Plot using the new column names
logrt_pred_switch <- ggplot(preds_switch, 
    aes(x = switch_factor, y = emmean, 
        color = is_bivalent, 
        linetype = prev_bivalent, 
        group = interaction(is_bivalent, prev_bivalent))) +
  geom_line(position = pos) +
  geom_point(position = pos) + # points help confirm data is there
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = pos, width = 0.2) +
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast"))) +
  labs(title = "Model predictions for log RTs",
       y = "log(RT) prediction",
       x = "Switch") +
  theme_classic()

logrt_pred_switch


#theme_set(apa_theming()[[1]])
# 1. Define the dodge position
pos <- position_dodge(0.3) 

# 2. Plot with corrected column names for lmerTest results
logrt_pred_switch <- ggplot(preds_switch, 
       aes(x = switch, 
           y = emmean, 
           color = is_bivalent, 
           linetype = prev_bivalent, 
           group = interaction(is_bivalent, prev_bivalent))) +
  geom_line(position = pos) +
  geom_point(position = pos) + 
  # Use asymp.LCL and asymp.UCL which match your previous error output
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), width = 0.2, position = pos) + 
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast"))) +
  labs(title = "Model predictions for log RTs",
       y = "log(RT) Prediction",
       x = "Switch (0 = Repeat, 1 = Switch)") +
 theme_classic()

logrt_pred_switch

#ggsave("logrt_pred_switch_apa.svg", logrt_pred_switch, width = 10, height = 6)
```


######################################################################################################




# Individual differences analysis

1. creating df compatible with indiv differences with pivot wider 

## checking for the number of non-decision times in the data 

```{r}

alt_cue_agg_ID_ddm_nocycle
any(alt_cue_agg_ID_ddm_nocycle$Ter < 0, na.rm = TRUE) # gives TRUE

sum(alt_cue_agg_ID_ddm_nocycle$Ter < 0, na.rm = TRUE) # 44 

alt_cue_agg_ID_ddm_nocycle %>%
  filter(Ter < 0) 

alt_cue_agg_ID_ddm_nocycle %>%
  filter(Ter < 0) %>%
  distinct(id) 


hist(alt_cue_agg_ID_ddm_nocycle$Ter)

alt_cue_agg_ID_ddm_nocycle_NA <- alt_cue_agg_ID_ddm_nocycle %>%
  mutate(Ter = if_else(Ter < 0, NA_real_, Ter))
```


```{r}


view(alt_cue_agg_ID_ddm_nocycle)
view(d_analysis)


rt_df <- d_analysis %>%
  group_by(id, valence_current_group, val_c_g,
           valence_previous_group, val_p_g, switch) %>%
  summarise(
    RT = mean(time[error == 0 & prev_error == 0], na.rm = TRUE),
    RT_log = mean(log(time[error == 0 & prev_error == 0]), na.rm = TRUE),
    .groups = "drop"
  )

alt_cue_agg_ID_ddm_nocycle <- alt_cue_agg_ID_ddm_nocycle %>%
  left_join(rt_df,
            by = c("id",

                   "val_c_g",

                   "val_p_g",
                   "switch"))


alt_cue_agg_ID_ddm_nocycle_NA <- alt_cue_agg_ID_ddm_nocycle_NA %>%
  left_join(rt_df,
            by = c("id",

                   "val_c_g",

                   "val_p_g",
                   "switch"))


names(alt_cue_agg_ID_ddm_nocycle_NA)

alt_cue_agg_ID_ddm_nocycle <- alt_cue_agg_ID_ddm_nocycle %>%
  select(-valence_current_group.y,
         -valence_previous_group.y,
         -RT.y) %>%
  rename(
    valence_current_group = valence_current_group.x,
    valence_previous_group = valence_previous_group.x,
    RT = RT.x
  )

alt_cue_agg_ID_ddm_nocycle_NA <- alt_cue_agg_ID_ddm_nocycle_NA %>%
  select(-valence_current_group.y,
         -valence_previous_group.y,
         -RT.y) %>%
  rename(
    valence_current_group = valence_current_group.x,
    valence_previous_group = valence_previous_group.x,
    RT = RT.x
  )

names(alt_cue_agg_ID_ddm_nocycle_NA)

alt_cue_indiv <- alt_cue_agg_ID_ddm_nocycle %>%
  pivot_wider(id_cols = id, names_from = c(val_c_g_contrast, val_p_g_contrast, switch),
              values_from = c(v, a, Ter, RT_log),
              names_glue = "{.value}_s{switch}_cbiv{val_c_g_contrast}_lbiv{val_p_g_contrast}") %>% ungroup()

# cbiv: current bivlent ; lbiv : lag bivalent

alt_cue_indiv


ggplot(alt_cue_indiv, aes(x = RT_log_s1_cbiv1_lbiv1, y = RT_log_s0_cbiv0_lbiv0))+
  geom_point()+
  geom_smooth(method = "lm")+
  theme_classic()

alt_cue_indiv_NA <- alt_cue_agg_ID_ddm_nocycle_NA %>%
  pivot_wider(id_cols = id, names_from = c(val_c_g_contrast, val_p_g_contrast, switch),
              values_from = c(v, a, Ter, RT_log),
              names_glue = "{.value}_s{switch}_cbiv{val_c_g_contrast}_lbiv{val_p_g_contrast}") %>% ungroup()
```


```{r}
alt_cue_indiv <- alt_cue_agg_ID_ddm_nocycle %>% 
  pivot_wider(id_cols = id, names_from = c(val_c_g_contrast, val_p_g_contrast, switch), 
              values_from = c(v, a, Ter, RT_log, Error), 
              names_glue = "{.value}_s{switch}_cbiv{val_c_g_contrast}_lbiv{val_p_g_contrast}") %>% 
  ungroup() %>%
  mutate(v_s0_cbiv0_lbiv0_NA = ifelse(Ter_s0_cbiv0_lbiv0 < 0, NA, v_s0_cbiv0_lbiv0),
         v_s0_cbiv0_lbiv1_NA = ifelse(Ter_s0_cbiv0_lbiv1 < 0, NA, v_s0_cbiv0_lbiv1),
         v_s0_cbiv1_lbiv0_NA = ifelse(Ter_s0_cbiv1_lbiv0 < 0, NA, v_s0_cbiv1_lbiv0),
         v_s0_cbiv1_lbiv1_NA = ifelse(Ter_s0_cbiv1_lbiv1 < 0, NA, v_s0_cbiv1_lbiv1),
         v_s1_cbiv0_lbiv0_NA = ifelse(Ter_s1_cbiv0_lbiv0 < 0, NA, v_s1_cbiv0_lbiv0),
         v_s1_cbiv0_lbiv1_NA = ifelse(Ter_s1_cbiv0_lbiv1 < 0, NA, v_s1_cbiv0_lbiv1),
         v_s1_cbiv1_lbiv0_NA = ifelse(Ter_s1_cbiv1_lbiv0 < 0, NA, v_s1_cbiv1_lbiv0),
         v_s1_cbiv1_lbiv1_NA = ifelse(Ter_s1_cbiv1_lbiv1 < 0, NA, v_s1_cbiv1_lbiv1))




# alt_cue_agg_ID_ddm_nocycle %>%
#   ggplot(aes(x = Ter))+
#   geom_histogram()+
#   geom_vline(xintercept = 0)+
#   theme_classic()
# 
# alt_cue_agg_ID_ddm_nocycle %>%
#   ungroup() %>%
#   summarize(N = n(),
#             neg_ter = sum(Ter < 0),
#             p_neg_Ter = neg_ter/N,
#             subjects_w_any_neg_Ter = length(unique(id[Ter < 0])))


alt_cue_indiv <- alt_cue_indiv %>%
  mutate(across(!id, ~ as.vector(scale(.x))))
```


2. linear regression models- my version. so do not use these sets of models. Use Dominik's code later on that has all the models per DV as a list 

Model 1A: lm(S[UU] ~ NS[UU]) 

Model 1B: lm(S[UU] ~ NS[UU]+ NS[BU]*) 

Model 1C: lm(S[UU] ~ NS[[UU]+ NS[BU] + NS[UB]*) 

Model 1D: lm(S[UU] ~ NS[UU]+ NS[BU] + NS[UB] + NS[BB]*) 

 

Model 2A: lm(S[BU] ~ NS[UU]) 

Model 2B: lm(S[BU] ~ NS[UU]+ NS[BU]*) 

Model 2C: lm(S[BU] ~ NS[[UU]+ NS[BU] + NS[UB]*) 

Model 2D: lm(S[BU] ~ NS[UU]+ NS[BU] + NS[UB] + NS[BB]*) 

 

Model 3A: lm(S[UB] ~ NS[UU]) 

Model 3B: lm(S[UB] ~ NS[UU]+ NS[BU]*) 

Model 3C: lm(S[UB] ~ NS[[UU]+ NS[BU] + NS[UB]*) 

Model 3D: lm(S[UB] ~ NS[UU]+ NS[BU] + NS[UB] + NS[BB]*) 

 

Model 4A: lm(S[BB] ~ NS[UU]) 

Model 4B: lm(S[BB] ~ NS[UU]+ NS[BU]*) 

Model 4C: lm(S[BB] ~ NS[[UU]+ NS[BU] + NS[UB]*) 

Model 4D: lm(S[BB] ~ NS[UU]+ NS[BU] + NS[UB] + NS[BB]*) 

 
(i) log RT

a. model 1 series 

```{r}

lm_1_a <- lm(RT_log_s1_cbiv0_lbiv0 ~ RT_log_s0_cbiv0_lbiv0,alt_cue_indiv_NA )  %>% summary()
lm_1_a

lm_1_b <- lm(RT_log_s1_cbiv0_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1,alt_cue_indiv_NA)  %>% summary()
lm_1_b


lm_1_c <- lm(RT_log_s1_cbiv0_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0,alt_cue_indiv_NA )  %>% summary()
lm_1_c


lm_1_d <- lm(RT_log_s1_cbiv0_lbiv0 ~ 
     RT_log_s0_cbiv0_lbiv0 + 
     RT_log_s0_cbiv0_lbiv1 +
     RT_log_s0_cbiv1_lbiv0 +
     RT_log_s0_cbiv1_lbiv1, 
   alt_cue_indiv_NA) %>% summary()
lm_1_d 

### no negative coefficients for model 1 
```

b. model 2 series

```{r}

lm_2_a <- lm(RT_log_s1_cbiv0_lbiv1 ~ RT_log_s0_cbiv0_lbiv0, alt_cue_indiv_NA )  %>% summary()
lm_2_a

lm_2_b <- lm(RT_log_s1_cbiv0_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1, alt_cue_indiv_NA)  %>% summary()
lm_2_b


lm_2_c <- lm(RT_log_s1_cbiv0_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0, alt_cue_indiv_NA )  %>% summary()
lm_2_c


lm_2_d <- lm(RT_log_s1_cbiv0_lbiv1 ~ 
     RT_log_s0_cbiv0_lbiv0 + 
     RT_log_s0_cbiv0_lbiv1 +
     RT_log_s0_cbiv1_lbiv0 +
     RT_log_s0_cbiv1_lbiv1, 
   alt_cue_indiv_NA) %>% summary()
lm_2_d 

## no negative coefficients for model 2 

```

c. model 3 series 

```{r}

lm_3_a <- lm(RT_log_s1_cbiv1_lbiv0 ~ RT_log_s0_cbiv0_lbiv0, alt_cue_indiv_NA )  %>% summary()
lm_3_a

lm_3_b <- lm(RT_log_s1_cbiv1_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1, alt_cue_indiv_NA)  %>% summary()
lm_3_b


lm_3_c <- lm(RT_log_s1_cbiv1_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0, alt_cue_indiv_NA )  %>% summary()
lm_3_c


lm_3_d <- lm(RT_log_s1_cbiv1_lbiv0 ~ 
     RT_log_s0_cbiv0_lbiv0 + 
     RT_log_s0_cbiv0_lbiv1 +
     RT_log_s0_cbiv1_lbiv0 +
     RT_log_s0_cbiv1_lbiv1, 
   alt_cue_indiv_NA) %>% summary()
lm_3_d 

## no negative coefficients for model 3

```

d. model 4 series 

```{r}
lm_4_a <- lm(RT_log_s1_cbiv1_lbiv1 ~ RT_log_s0_cbiv0_lbiv0,alt_cue_indiv_NA )  %>% summary()
lm_4_a

lm_4_b <- lm(RT_log_s1_cbiv1_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1,alt_cue_indiv_NA)  %>% summary()
lm_4_b


lm_4_c <- lm(RT_log_s1_cbiv1_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0,alt_cue_indiv_NA )  %>% summary()
lm_4_c


lm_4_d <- lm(RT_log_s1_cbiv1_lbiv1 ~ 
     RT_log_s0_cbiv0_lbiv0 + 
     RT_log_s0_cbiv0_lbiv1 +
     RT_log_s0_cbiv1_lbiv0 +
     RT_log_s0_cbiv1_lbiv1, 
   alt_cue_indiv) %>% summary()
lm_4_d 

lm_4_d_na <- lm(RT_log_s1_cbiv1_lbiv1 ~ 
     RT_log_s0_cbiv0_lbiv0 + 
     RT_log_s0_cbiv0_lbiv1 +
     RT_log_s0_cbiv1_lbiv0 +
     RT_log_s0_cbiv1_lbiv1, 
   alt_cue_indiv_NA) %>% summary()
lm_4_d_na

## no negative coefficients for model 4 
```


(ii) drift rate (v) 

a. model 1 series 

```{r}

lm_1_a <- lm(v_s1_cbiv0_lbiv0 ~ v_s0_cbiv0_lbiv0,alt_cue_indiv )  %>% summary()
lm_1_a

lm_1_b <- lm(v_s1_cbiv0_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1,alt_cue_indiv)  %>% summary()
lm_1_b


lm_1_c <- lm(v_s1_cbiv0_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0,alt_cue_indiv )  %>% summary()
lm_1_c


lm_1_d <- lm(v_s1_cbiv0_lbiv0 ~ 
     v_s0_cbiv0_lbiv0 + 
     v_s0_cbiv0_lbiv1 +
     v_s0_cbiv1_lbiv0 +
     v_s0_cbiv1_lbiv1, 
   alt_cue_indiv) %>% summary()
lm_1_d 

### no negative coefficients for model 1 
```

b. model 2 series

```{r}

lm_2_a <- lm(v_s1_cbiv0_lbiv1 ~ v_s0_cbiv0_lbiv0, alt_cue_indiv )  %>% summary()
lm_2_a

lm_2_b <- lm(v_s1_cbiv0_lbiv1 ~v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1, alt_cue_indiv)  %>% summary()
lm_2_b


lm_2_c <- lm(v_s1_cbiv0_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0, alt_cue_indiv )  %>% summary()
lm_2_c


lm_2_d <- lm(v_s1_cbiv0_lbiv1 ~ 
     v_s0_cbiv0_lbiv0 + 
     v_s0_cbiv0_lbiv1 +
     v_s0_cbiv1_lbiv0 +
    v_s0_cbiv1_lbiv1, 
   alt_cue_indiv) %>% summary()
lm_2_d 

## no negative coefficients for model 2 

```

c. model 3 series 

```{r}

lm_3_a <- lm(v_s1_cbiv1_lbiv0 ~ v_s0_cbiv0_lbiv0, alt_cue_indiv )  %>% summary()
lm_3_a

lm_3_b <- lm(v_s1_cbiv1_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1, alt_cue_indiv)  %>% summary()
lm_3_b


lm_3_c <- lm(v_s1_cbiv1_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0, alt_cue_indiv )  %>% summary()
lm_3_c


lm_3_d <- lm(v_s1_cbiv1_lbiv0 ~ 
     v_s0_cbiv0_lbiv0 + 
     v_s0_cbiv0_lbiv1 +
     v_s0_cbiv1_lbiv0 +
     v_s0_cbiv1_lbiv1, 
   alt_cue_indiv) %>% summary()
lm_3_d 

## no negative coefficients for model 3

```

d. model 4 series 

```{r}
lm_4_a <- lm(v_s1_cbiv1_lbiv1 ~ v_s0_cbiv0_lbiv0,alt_cue_indiv )  %>% summary()
lm_4_a

lm_4_b <- lm(v_s1_cbiv1_lbiv1 ~v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1,alt_cue_indiv)  %>% summary()
lm_4_b


lm_4_c <- lm(v_s1_cbiv1_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0,alt_cue_indiv )  %>% summary()
lm_4_c


lm_4_d <- lm(v_s1_cbiv1_lbiv1 ~ 
     v_s0_cbiv0_lbiv0 + 
     v_s0_cbiv0_lbiv1 +
     v_s0_cbiv1_lbiv0 +
     v_s0_cbiv1_lbiv1, 
   alt_cue_indiv) %>% summary()
lm_4_d

lm_4_d_na <- lm(v_s1_cbiv1_lbiv1 ~ 
     v_s0_cbiv0_lbiv0 + 
     v_s0_cbiv0_lbiv1 +
     v_s0_cbiv1_lbiv0 +
     v_s0_cbiv1_lbiv1, 
   alt_cue_indiv_NA) %>% summary()
lm_4_d_na


## no negative coefficients for model 4 
```

(iii) Error 


a. model 1 series 

```{r}

lm_1_a <- lm(Error_s1_cbiv0_lbiv0 ~ Error_s0_cbiv0_lbiv0,alt_cue_indiv )  %>% summary()
lm_1_a

lm_1_b <- lm(Error_s1_cbiv0_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1,alt_cue_indiv)  %>% summary()
lm_1_b


lm_1_c <- lm(Error_s1_cbiv0_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0,alt_cue_indiv )  %>% summary()
lm_1_c


lm_1_d <- lm(Error_s1_cbiv0_lbiv0 ~ 
     Error_s0_cbiv0_lbiv0 + 
     Error_s0_cbiv0_lbiv1 +
     Error_s0_cbiv1_lbiv0 +
     Error_s0_cbiv1_lbiv1, 
   alt_cue_indiv) %>% summary()
lm_1_d 

### no negative coefficients for model 1 
```

b. model 2 series

```{r}

lm_2_a <- lm(Error_s1_cbiv0_lbiv1 ~ Error_s0_cbiv0_lbiv0, alt_cue_indiv )  %>% summary()
lm_2_a

lm_2_b <- lm(Error_s1_cbiv0_lbiv1 ~Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1, alt_cue_indiv)  %>% summary()
lm_2_b


lm_2_c <- lm(Error_s1_cbiv0_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0, alt_cue_indiv )  %>% summary()
lm_2_c


lm_2_d <- lm(Error_s1_cbiv0_lbiv1 ~ 
     Error_s0_cbiv0_lbiv0 + 
     Error_s0_cbiv0_lbiv1 +
     Error_s0_cbiv1_lbiv0 +
    Error_s0_cbiv1_lbiv1, 
   alt_cue_indiv) %>% summary()
lm_2_d 

## no negative coefficients for model 2 

```

c. model 3 series 

```{r}

lm_3_a <- lm(Error_s1_cbiv1_lbiv0 ~ Error_s0_cbiv0_lbiv0, alt_cue_indiv )  %>% summary()
lm_3_a

lm_3_b <- lm(Error_s1_cbiv1_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1, alt_cue_indiv)  %>% summary()
lm_3_b


lm_3_c <- lm(Error_s1_cbiv1_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0, alt_cue_indiv )  %>% summary()
lm_3_c


lm_3_d <- lm(Error_s1_cbiv1_lbiv0 ~ 
     Error_s0_cbiv0_lbiv0 + 
     Error_s0_cbiv0_lbiv1 +
     Error_s0_cbiv1_lbiv0 +
     Error_s0_cbiv1_lbiv1, 
   alt_cue_indiv) %>% summary()
lm_3_d 

## no negative coefficients for model 3

```

d. model 4 series 

```{r}
lm_4_a <- lm(Error_s1_cbiv1_lbiv1 ~ Error_s0_cbiv0_lbiv0,alt_cue_indiv )  %>% summary()
lm_4_a

lm_4_b <- lm(Error_s1_cbiv1_lbiv1 ~Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1,alt_cue_indiv)  %>% summary()
lm_4_b


lm_4_c <- lm(Error_s1_cbiv1_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0,alt_cue_indiv )  %>% summary()
lm_4_c


lm_4_d <- lm(Error_s1_cbiv1_lbiv1 ~ 
     Error_s0_cbiv0_lbiv0 + 
     Error_s0_cbiv0_lbiv1 +
     Error_s0_cbiv1_lbiv0 +
     Error_s0_cbiv1_lbiv1, 
   alt_cue_indiv) %>% summary()
lm_4_d



## no negative coefficients for model 4 
```


(iv) drift rate NA (v - NA) 

a. model 1 series 

```{r}

lm_1_a <- lm(v_s1_cbiv0_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA, alt_cue_indiv )  %>% summary()
lm_1_a

lm_1_b <- lm(v_s1_cbiv0_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA ,alt_cue_indiv)  %>% summary()
lm_1_b


lm_1_c <- lm(v_s1_cbiv0_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA,alt_cue_indiv )  %>% summary()
lm_1_c


lm_1_d <- lm(v_s1_cbiv0_lbiv0_NA ~ 
     v_s0_cbiv0_lbiv0_NA + 
     v_s0_cbiv0_lbiv1_NA +
     v_s0_cbiv1_lbiv0_NA +
     v_s0_cbiv1_lbiv1_NA, 
   alt_cue_indiv) %>% summary()
lm_1_d 

### no negative coefficients for model 1 
```

b. model 2 series

```{r}

lm_2_a <- lm(v_s1_cbiv0_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA, alt_cue_indiv )  %>% summary()
lm_2_a

lm_2_b <- lm(v_s1_cbiv0_lbiv1_NA ~v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA, alt_cue_indiv)  %>% summary()
lm_2_b


lm_2_c <- lm(v_s1_cbiv0_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA, alt_cue_indiv )  %>% summary()
lm_2_c


lm_2_d <- lm(v_s1_cbiv0_lbiv1_NA ~ 
     v_s0_cbiv0_lbiv0_NA + 
     v_s0_cbiv0_lbiv1_NA +
     v_s0_cbiv1_lbiv0_NA +
    v_s0_cbiv1_lbiv1_NA, 
   alt_cue_indiv) %>% summary()
lm_2_d 

## no negative coefficients for model 2 

```

c. model 3 series 

```{r}

lm_3_a <- lm(v_s1_cbiv1_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA, alt_cue_indiv )  %>% summary()
lm_3_a

lm_3_b <- lm(v_s1_cbiv1_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA, alt_cue_indiv)  %>% summary()
lm_3_b


lm_3_c <- lm(v_s1_cbiv1_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA, alt_cue_indiv )  %>% summary()
lm_3_c


lm_3_d <- lm(v_s1_cbiv1_lbiv0_NA ~ 
     v_s0_cbiv0_lbiv0_NA + 
     v_s0_cbiv0_lbiv1_NA +
     v_s0_cbiv1_lbiv0_NA +
     v_s0_cbiv1_lbiv1_NA, 
   alt_cue_indiv) %>% summary()
lm_3_d 

## no negative coefficients for model 3

```

d. model 4 series 

```{r}
lm_4_a <- lm(v_s1_cbiv1_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA,alt_cue_indiv )  %>% summary()
lm_4_a

lm_4_b <- lm(v_s1_cbiv1_lbiv1_NA ~v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA,alt_cue_indiv)  %>% summary()
lm_4_b


lm_4_c <- lm(v_s1_cbiv1_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA,alt_cue_indiv )  %>% summary()
lm_4_c


lm_4_d <- lm(v_s1_cbiv1_lbiv1_NA ~ 
     v_s0_cbiv0_lbiv0_NA + 
     v_s0_cbiv0_lbiv1_NA +
     v_s0_cbiv1_lbiv0_NA +
     v_s0_cbiv1_lbiv1_NA, 
   alt_cue_indiv) %>% summary()
lm_4_d



## no negative coefficients for model 4 
```

### Model comp: univalent - univalent

## Models

```{r}
alt_cue_indiv_diff_models <- list(
  RT = list(uu1 = lm(RT_log_s1_cbiv0_lbiv0 ~ RT_log_s0_cbiv0_lbiv0, alt_cue_indiv),
            uu2 = lm(RT_log_s1_cbiv0_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1, alt_cue_indiv),
            uu3 = lm(RT_log_s1_cbiv0_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0, alt_cue_indiv),
            uu4 = lm(RT_log_s1_cbiv0_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0 + RT_log_s0_cbiv1_lbiv1, alt_cue_indiv),
            
            bu1 = lm(RT_log_s1_cbiv1_lbiv0 ~ RT_log_s0_cbiv0_lbiv0, alt_cue_indiv),
            bu2 = lm(RT_log_s1_cbiv1_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1, alt_cue_indiv),
            bu3 = lm(RT_log_s1_cbiv1_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0, alt_cue_indiv),
            bu4 = lm(RT_log_s1_cbiv1_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0 + RT_log_s0_cbiv1_lbiv1, alt_cue_indiv),
            
            ub1 = lm(RT_log_s1_cbiv0_lbiv1 ~ RT_log_s0_cbiv0_lbiv0, alt_cue_indiv),
            ub2 = lm(RT_log_s1_cbiv0_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1, alt_cue_indiv),
            ub3 = lm(RT_log_s1_cbiv0_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0, alt_cue_indiv),
            ub4 = lm(RT_log_s1_cbiv0_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0 + RT_log_s0_cbiv1_lbiv1, alt_cue_indiv),
            
            bb1 = lm(RT_log_s1_cbiv1_lbiv1 ~ RT_log_s0_cbiv0_lbiv0, alt_cue_indiv),
            bb2 = lm(RT_log_s1_cbiv1_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1, alt_cue_indiv),
            bb3 = lm(RT_log_s1_cbiv1_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0, alt_cue_indiv),
            bb4 = lm(RT_log_s1_cbiv1_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0 + RT_log_s0_cbiv1_lbiv1, alt_cue_indiv)
  ),
  
   Error = list(uu1 = lm(Error_s1_cbiv0_lbiv0 ~ Error_s0_cbiv0_lbiv0, alt_cue_indiv),
                uu2 = lm(Error_s1_cbiv0_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1, alt_cue_indiv),
                uu3 = lm(Error_s1_cbiv0_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0, alt_cue_indiv),
                uu4 = lm(Error_s1_cbiv0_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0 + Error_s0_cbiv1_lbiv1, alt_cue_indiv),
                
              bu1 = lm(Error_s1_cbiv1_lbiv0 ~ Error_s0_cbiv0_lbiv0, alt_cue_indiv),
               bu2 = lm(Error_s1_cbiv1_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1, alt_cue_indiv),
               bu3 = lm(Error_s1_cbiv1_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0, alt_cue_indiv),
               bu4 = lm(Error_s1_cbiv1_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0 + Error_s0_cbiv1_lbiv1, alt_cue_indiv),
               
            ub1 = lm(Error_s1_cbiv0_lbiv1 ~ Error_s0_cbiv0_lbiv0, alt_cue_indiv),
                ub2 = lm(Error_s1_cbiv0_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1, alt_cue_indiv),
                ub3 = lm(Error_s1_cbiv0_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0, alt_cue_indiv),
                ub4 = lm(Error_s1_cbiv0_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0 + Error_s0_cbiv1_lbiv1, alt_cue_indiv),
                
               bb1 = lm(Error_s1_cbiv1_lbiv1 ~ Error_s0_cbiv0_lbiv0, alt_cue_indiv),
               bb2 = lm(Error_s1_cbiv1_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1, alt_cue_indiv),
                bb3 = lm(Error_s1_cbiv1_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0, alt_cue_indiv),
                bb4 = lm(Error_s1_cbiv1_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0 + Error_s0_cbiv1_lbiv1, alt_cue_indiv)
   ),
   
  v = list(uu1 = lm(v_s1_cbiv0_lbiv0 ~ v_s0_cbiv0_lbiv0, alt_cue_indiv),
           uu2 = lm(v_s1_cbiv0_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1, alt_cue_indiv),
           uu3 = lm(v_s1_cbiv0_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0, alt_cue_indiv),
           uu4 = lm(v_s1_cbiv0_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0 + v_s0_cbiv1_lbiv1, alt_cue_indiv),
           
           bu1 = lm(v_s1_cbiv1_lbiv0 ~ v_s0_cbiv0_lbiv0, alt_cue_indiv),
           bu2 = lm(v_s1_cbiv1_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1, alt_cue_indiv),
           bu3 = lm(v_s1_cbiv1_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0, alt_cue_indiv),
           bu4 = lm(v_s1_cbiv1_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0 + v_s0_cbiv1_lbiv1, alt_cue_indiv),
           
           ub1 = lm(v_s1_cbiv0_lbiv1 ~ v_s0_cbiv0_lbiv0, alt_cue_indiv),
           ub2 = lm(v_s1_cbiv0_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1, alt_cue_indiv),
           ub3 = lm(v_s1_cbiv0_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0, alt_cue_indiv),
           ub4 = lm(v_s1_cbiv0_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0 + v_s0_cbiv1_lbiv1, alt_cue_indiv),
           
           bb1 = lm(v_s1_cbiv1_lbiv1 ~ v_s0_cbiv0_lbiv0, alt_cue_indiv),
           bb2 = lm(v_s1_cbiv1_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1, alt_cue_indiv),
           bb3 = lm(v_s1_cbiv1_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0, alt_cue_indiv),
           bb4 = lm(v_s1_cbiv1_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0 + v_s0_cbiv1_lbiv1, alt_cue_indiv)
  ),
  
   v_NA = list(uu1 = lm(v_s1_cbiv0_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA, alt_cue_indiv),
               uu2 = lm(v_s1_cbiv0_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA, alt_cue_indiv),
               uu3 = lm(v_s1_cbiv0_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA, alt_cue_indiv),
               uu4 = lm(v_s1_cbiv0_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA + v_s0_cbiv1_lbiv1_NA, alt_cue_indiv),
              
              bu1 = lm(v_s1_cbiv1_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA, alt_cue_indiv),
              bu2 = lm(v_s1_cbiv1_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA, alt_cue_indiv),
              bu3 = lm(v_s1_cbiv1_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA, alt_cue_indiv),
               bu4 = lm(v_s1_cbiv1_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA + v_s0_cbiv1_lbiv1_NA, alt_cue_indiv),
              
              ub1 = lm(v_s1_cbiv0_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA, alt_cue_indiv),
               ub2 = lm(v_s1_cbiv0_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA, alt_cue_indiv),
               ub3 = lm(v_s1_cbiv0_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA, alt_cue_indiv),
               ub4 = lm(v_s1_cbiv0_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA + v_s0_cbiv1_lbiv1_NA, alt_cue_indiv),
               
               bb1 = lm(v_s1_cbiv1_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA, alt_cue_indiv),
               bb2 = lm(v_s1_cbiv1_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA, alt_cue_indiv),
               bb3 = lm(v_s1_cbiv1_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA, alt_cue_indiv),
               bb4 = lm(v_s1_cbiv1_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA + v_s0_cbiv1_lbiv1_NA, alt_cue_indiv)
  )
 )


```



```{r}
compare_models <- function(model_list, dv){
  
  do.call(anova, unname(model_list[grepl(dv, names(model_list))]))
}
```

### Model comp: univalent - univalent

```{r}
compare_models(alt_cue_indiv_diff_models$v, "uu")
```
### Model comp: univalent - bivalent
```{r}
compare_models(alt_cue_indiv_diff_models$v, "ub")
```

### Model comp: bivalent - univalent

```{r}
compare_models(alt_cue_indiv_diff_models$v, "bu")
```

### Model comp: bivalent - bivalent


```{r}
compare_models(alt_cue_indiv_diff_models$v, "bb")
```


## the biggest positive effect actually occurs in bivalent bivalent, where you would expect the strongest tradeoff effect
standardize the betas for model comparisons 


#######################################################################################

    Determining which model versions to use by conducting anovas 

######################################################################################


Note: only for effect coded variables 

steps: first check if complete complex model with one bar converges. if not- then do the next steps 

A. Experimental level 

example:
 
 m_rt_effectBase<- lmer(log(time) ~  val_c_g * val_p_g * switch + (1 |  id),
                 data = d_analysis %>% filter(filter_correct == 0),
                  na.action = na.exclude,
              
               control = lmerControl(optimizer = "bobyqa"))

  summary(m_rt_effectBase)
  
  m_rt_effect1<- lmer(log(time) ~  val_c_g * val_p_g * switch + (1+ switch  |  id),
                 data = d_analysis %>% filter(filter_correct == 0),
                  na.action = na.exclude,
              
               control = lmerControl(optimizer = "bobyqa"))

  summary(m_rt_effect1)
  
  anova(m_rt_effect1,m_rt_effectBase)
 
 1. lmer + glmer effect coded 
  
```{r}

 m_rt_effect_check<- lmer(log(time) ~  val_c_g * val_p_g * switch + (1 + val_c_g + val_p_g + switch |  id),
                 data = d_analysis %>% filter(filter_correct == 0),
                  na.action = na.exclude,
              
               control = lmerControl(optimizer = "bobyqa"))

  summary(m_rt_effect_check)
  tab_model(m_rt_effect_check,show.est=T,auto.label=F,show.stat=T, df.method = "satterthwaite") ### converged + no is singular warning 
 # 
 # m_rt_effectBase<- lmer(log(time) ~  val_c_g * val_p_g * switch + (1 |  id),
 #                 data = d_analysis %>% filter(filter_correct == 0),
 #                  na.action = na.exclude,
 #              
 #               control = lmerControl(optimizer = "bobyqa"))
 # 
 #  summary(m_rt_effectBase)
 #  
 #  m_rt_effect1<- lmer(log(time) ~  val_c_g * val_p_g * switch + (1+switch  |  id),
 #                 data = d_analysis %>% filter(filter_correct == 0),
 #                  na.action = na.exclude,
 #              
 #               control = lmerControl(optimizer = "bobyqa"))
 # 
 #  summary(m_rt_effect1)
 #  
 #  
 #  
 # anova(m_rt_effect1,m_rt_effectBase)
 
 
 
#library(sjPlot)
# tab_model(m_rt_new,show.est=T,auto.label=F,show.stat=T)
# tab_model(m_rt_effect_try,show.est=T,auto.label=F,show.stat=T, df.method = "satterthwaite")
 


```
 
```{r}


d_analysis$error <- as.factor(d_analysis$error)
levels(d_analysis$error)

m_error_effect<- glmer(error ~  val_c_g * val_p_g * switch + ( val_c_g + val_p_g + switch| id),
                 data = d_analysis, 
                 family = "binomial",
                  na.action = na.exclude, 
                 control = glmerControl(optimizer = "bobyqa"))

 
 summary(m_error_effect)
 
 tab_model(m_error_effect,show.est=T,auto.label=F,show.stat=T) ## converged + no is singular warning 

```

2. ezDDM effect coded


```{r}

## note: look into why you cannot estimate Residual R^2 very well for lmer models 

alt_cue_a <- lmer(a ~ val_c_g * val_p_g * switch + (val_c_g + val_p_g + switch | id), alt_cue_agg_ID_ddm_nocycl, control = lmerControl(optimizer = "bobyqa")) # converged BUT is singualr warning 

## step 1: so, cuening baseline model 

alt_cue_a_b <- lmer(a ~ val_c_g * val_p_g * switch + (1 | id), alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa")) 

summary(alt_cue_a_b)

tab_model(alt_cue_a_b)


## step 2: adding one random slope to each model and conducting anovas with base model 

alt_cue_a_1 <- lmer(a ~ val_c_g * val_p_g * switch + (1 + val_c_g | id), alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa")) 

summary(alt_cue_a_1)

tab_model(alt_cue_a_1) # converged and is singular warning 

anova(alt_cue_a_b, alt_cue_a_1) ## but the anova shows that vak_c_g random slope is required 



alt_cue_a_2 <- lmer(a ~ val_c_g * val_p_g * switch + (1 + val_p_g | id), alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa")) 

summary(alt_cue_a_2)

tab_model(alt_cue_a_2) # converged but is singular warning 

anova(alt_cue_a_b, alt_cue_a_2) ## not significant 



alt_cue_a_3 <- lmer(a ~ val_c_g * val_p_g * switch + (1 + switch | id), alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa")) 

summary(alt_cue_a_3)

tab_model(alt_cue_a_3) # converged and NO is singualr warning 

anova(alt_cue_a_b, alt_cue_a_3) ## significant  


###### Compring different random intercepts model versions base moel and each other to get to the most complex model we can use (only comparing the models that converge and give no singular warnings)


alt_cue_a_4 <- lmer(a ~ val_c_g * val_p_g * switch + ( val_c_g + switch | id), alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa")) 

summary(alt_cue_a_4)

tab_model(alt_cue_a_4) # converged but is singular warning 


alt_cue_a_5 <- lmer(a ~ val_c_g * val_p_g * switch + (val_p_g + switch | id), alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa")) 

summary(alt_cue_a_5)

tab_model(alt_cue_a_5) # converged but is singular warning 


```

```{r}

alt_cue_v <- lmer(v ~  val_c_g * val_p_g * switch + (val_c_g + val_p_g + switch |id), 
     alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa"))

summary(alt_cue_v)

tab_model(alt_cue_v) ## did not converge + is singular warning 

alt_cue_v_b <- lmer(v ~  val_c_g * val_p_g * switch + (1 |id), 
     alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa"))

summary(alt_cue_v_b)

tab_model(alt_cue_v_b)


alt_cue_v_1 <- lmer(v ~  val_c_g * val_p_g * switch + (1 + val_c_g |id), 
     alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa"))

summary(alt_cue_v_1)

tab_model(alt_cue_v_1) # converged but is singular warning 

anova(alt_cue_v_b, alt_cue_v_1) # significant 


alt_cue_v_2 <- lmer(v ~  val_c_g * val_p_g * switch + (1 + val_p_g |id), 
     alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa"))

summary(alt_cue_v_2)

tab_model(alt_cue_v_2) # converged but is singular warning 

anova(alt_cue_v_b, alt_cue_v_2) # not significant 


alt_cue_v_3 <- lmer(v ~  val_c_g * val_p_g * switch + (1 + switch |id), 
     alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa"))

summary(alt_cue_v_3)

tab_model(alt_cue_v_3) # converged and no is singular warning 

anova(alt_cue_v_b, alt_cue_v_3) # significant 



###### Compring different random intercepts model versions base moel and each other to get to the most complex model we can use (only comparing the models that converge and give no singular warnings)

## cuening Sophia's best model version and comparing it to my best model version 

alt_cue_v_4 <- lmer(v ~  val_c_g * val_p_g * switch + (val_c_g + switch |id), 
     alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa"))

summary(alt_cue_v_4)

tab_model(alt_cue_v_4, df.method = "satterthwaite") # converged and NO is singular warning: so current valence by itself has is singular warning BUT with switch, does not have is signular anymore 

anova(alt_cue_v_3, alt_cue_v_4) # significant

anova(alt_cue_v_b, alt_cue_v_4) # significant 

alt_cue_v_5 <- lmer(v ~  val_c_g * val_p_g * switch + (val_p_g + switch |id), 
     alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa"))

summary(alt_cue_v_5)

tab_model(alt_cue_v_5) # did not converged and no is singular warning 



```

```{r}


alt_cue_Ter <- lmer(Ter ~  val_c_g * val_p_g * switch + (val_c_g + val_p_g + switch |id), 
     alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa"))

summary(alt_cue_Ter)

tab_model(alt_cue_Ter, df.method = "satterthwaite") # converged but is singular warning 


alt_cue_Ter_b <- lmer(Ter ~  val_c_g * val_p_g * switch + (1 |id), 
     alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa"))

summary(alt_cue_Ter_b)

tab_model(alt_cue_Ter_b) 


alt_cue_Ter_1 <- lmer(Ter ~  val_c_g * val_p_g * switch + (1 + val_c_g |id), 
     alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa"))

summary(alt_cue_Ter_1)

tab_model(alt_cue_Ter_1) # converged and NO is singular warning 

anova(alt_cue_Ter_b, alt_cue_Ter_1) # significant 


alt_cue_Ter_2 <- lmer(Ter ~  val_c_g * val_p_g * switch + (1 + val_p_g |id), 
     alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa"))

summary(alt_cue_Ter_2)

tab_model(alt_cue_Ter_2) # converged but is singular warning 

anova(alt_cue_Ter_b, alt_cue_Ter_2) # not significant 


alt_cue_Ter_3 <- lmer(Ter ~  val_c_g * val_p_g * switch + (1 + switch |id), 
     alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa"))

summary(alt_cue_Ter_3)

tab_model(alt_cue_Ter_3) # converged but is signgular warning! 


anova(alt_cue_Ter_b, alt_cue_Ter_3)# significant 


###### Compring different random intercepts model versions base moel and each other to get to the most complex model we can use (only comparing the models that converge and give no singular warnings)


alt_cue_Ter_4 <- lmer(Ter ~  val_c_g * val_p_g * switch + (val_c_g + switch |id), 
     alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa"))

summary(alt_cue_Ter_4)

tab_model(alt_cue_Ter_4) # converged but is signgular warning


alt_cue_Ter_5 <- lmer(Ter ~  val_c_g * val_p_g * switch + (val_p_g + switch |id), 
     alt_cue_agg_ID_ddm_nocycle, control = lmerControl(optimizer = "bobyqa"))

summary(alt_cue_Ter_5)

tab_model(alt_cue_Ter_5) # converged but is singular warning 



#contrasts(alt_cue_agg_ID_ddm_nocycle$val_c_g)
#contrasts(alt_cue_agg_ID_ddm_nocycle$val_p_g)
```

B. within-subjects level 


```{r}
alt_cue_rt_log_resrt <- lmer(time_log_res_c ~ val_c_g * val_p_g * switch * lag1_time_log_res_c + (val_c_g + val_p_g + switch + lag1_time_log_res_c |id), control = lmerControl(optimizer = "bobyqa"),
     d_arrange %>% 
       filter(filter_correct == 0))

summary(alt_cue_rt_log_resrt)

tab_model(alt_cue_rt_log_resrt, df.method = "satterthwaite") ## model failed to converge 


alt_cue_rt_log_resrt_b <- lmer(time_log_res_c ~ val_c_g * val_p_g * switch * lag1_time_log_res_c + (1+ lag1_time_log_res_c |id), control = lmerControl(optimizer = "bobyqa"),
     d_arrange %>% 
       filter(filter_correct == 0))

summary(alt_cue_rt_log_resrt_b)

tab_model(alt_cue_rt_log_resrt_b, df.method = "satterthwaite")  # base model converged + no is singular warning 

alt_cue_rt_log_resrt_1 <- lmer(time_log_res_c ~ val_c_g * val_p_g * switch * lag1_time_log_res_c + (val_c_g + lag1_time_log_res_c |id), control = lmerControl(optimizer = "bobyqa"),
     d_arrange %>% 
       filter(filter_correct == 0))

summary(alt_cue_rt_log_resrt_1)

tab_model(alt_cue_rt_log_resrt_1, df.method = "satterthwaite") # converged with no is singular warning 

anova(alt_cue_rt_log_resrt_b,alt_cue_rt_log_resrt_1 ) # significant 


alt_cue_rt_log_resrt_2 <- lmer(time_log_res_c ~ val_c_g * val_p_g * switch * lag1_time_log_res_c + (val_p_g + lag1_time_log_res_c |id), control = lmerControl(optimizer = "bobyqa"),
     d_arrange %>% 
       filter(filter_correct == 0))

summary(alt_cue_rt_log_resrt_2)

tab_model(alt_cue_rt_log_resrt_2, df.method = "satterthwaite") # not converged with is singular warning 

anova(alt_cue_rt_log_resrt_b,alt_cue_rt_log_resrt_2 ) # not significant 

alt_cue_rt_log_resrt_3 <- lmer(time_log_res_c ~ val_c_g * val_p_g * switch * lag1_time_log_res_c + (switch + lag1_time_log_res_c |id), control = lmerControl(optimizer = "bobyqa"),
     d_arrange %>% 
       filter(filter_correct == 0))

summary(alt_cue_rt_log_resrt_3)

tab_model(alt_cue_rt_log_resrt_3, df.method = "satterthwaite") # converged with no is singular warning 

anova(alt_cue_rt_log_resrt_b,alt_cue_rt_log_resrt_3 ) # significant 



alt_cue_rt_log_resrt_use <- lmer(time_log_res_c ~ val_c_g * val_p_g * switch * lag1_time_log_res_c + (val_c_g + switch+ lag1_time_log_res_c |id), control = lmerControl(optimizer = "bobyqa"),
     d_arrange %>% 
       filter(filter_correct == 0))

summary(alt_cue_rt_log_resrt_use)

tab_model(alt_cue_rt_log_resrt_use, df.method = "satterthwaite") # converged with no is singular warning 

print(alt_cue_rt_log_resrt_use, correlation = TRUE)


anova(alt_cue_rt_log_resrt_b,alt_cue_rt_log_resrt_use )

###### Compring different random intercepts model versions base moel and each other to get to the most complex model we can use (only comparing the models that converge and give no singular warnings)

alt_cue_rt_log_resrt_4 <- lmer(time_log_res_c ~ val_c_g * val_p_g * switch * lag1_time_log_res_c + (val_p_g + switch+ lag1_time_log_res_c |id), control = lmerControl(optimizer = "bobyqa"),
     d_arrange %>% 
       filter(filter_correct == 0))

summary(alt_cue_rt_log_resrt_4)

tab_model(alt_cue_rt_log_resrt_4, df.method = "satterthwaite") # did not converge + is singular warning 





```



############################################################################################

                      APA style figures 
                  
############################################################################################

experimental-level 

1b. log rt 
```{r}
log_rt_plot_df <- d_analysis %>%
  filter(filter_correct == 0) %>%
  group_by(id, valence_current_group, valence_previous_group, switch) %>%
  summarise(
    mean_rt = mean(log(time), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  normWS(s = "id", dv = "mean_rt") %>%
  mutate(mean_rt = DV_n) %>%
  group_by(valence_current_group, valence_previous_group, switch) %>%
  summarise(
    RT_m = mean(mean_rt, na.rm = TRUE),
    RT_ci_lower = get_ci(mean_rt, RT_m)[2],
    RT_ci_upper = get_ci(mean_rt, RT_m)[1],
    .groups = "drop"
  ) %>%
  mutate(
    switch = factor(switch, levels = c(1, 0), labels = c("Switch", "Repeat")),
    valence_current_group  = factor(valence_current_group,
                                    labels = c("Univalent", "Bivalent")),
    valence_previous_group = factor(valence_previous_group,
                                    labels = c("Univalent", "Bivalent"))
  )

log_rt_plot_df

logrt_explevel_plot <- ggplot(log_rt_plot_df,
    aes(x        = switch,
        y        = RT_m,
        color    = valence_current_group,
        linetype = valence_previous_group,
        group    = interaction(valence_previous_group,
                               valence_current_group))) +
  geom_line(linewidth = design$lines$linewidth, position = pos) +
  geom_errorbar(aes(ymin = RT_ci_lower,
                    ymax = RT_ci_upper),
                width     = design$errorbar$width,
                linewidth = design$errorbar$linewidth,
                position  = pos, 
                linetype = "solid") +
  scale_linetype_manual(
    name   = "Previous Group",
    values = c("Univalent" = design$prev_val$linetype$uni,
               "Bivalent"  = design$prev_val$linetype$bi)
  ) +
  scale_color_manual(
    name   = "Current Group",
    values = c("Univalent" = design$curr_val$color$uni,
               "Bivalent"  = design$curr_val$color$bi)
  ) +
  labs(
    x = NULL,
    y = "Mean log RT"
  )

logrt_explevel_plot

ggsave("AC_RTlog.svg", logrt_explevel_plot, width = 10, height = 6)
saveRDS(logrt_explevel_plot, "AC_RTlog.RDS")

log_rt_plot_df

```
adding the lower and upper limits of the confidence interval bars back into the d_analysis dataframe: 

```{r}

subject_rt <- d_analysis %>%
  filter(filter_correct == 0) %>%
  group_by(id, valence_current_group, valence_previous_group, switch) %>%
  summarise(
    mean_rt = mean(log(time), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  normWS(s = "id", dv = "mean_rt") %>%
  mutate(mean_rt_n = DV_n)

ci_df <- subject_rt %>%
  group_by(valence_current_group, valence_previous_group, switch) %>%
  summarise(
    RT_m        = mean(mean_rt_n, na.rm = TRUE),
    RT_ci_lower = get_ci(mean_rt_n, RT_m)[2],
    RT_ci_upper = get_ci(mean_rt_n, RT_m)[1],
    .groups = "drop"
  )

d_analysis <- d_analysis %>%
  left_join(ci_df, by = c("valence_current_group", "valence_previous_group", "switch"))
```


2. error 

```{r}
# library(dplyr)
# library(ggplot2)

names(err_plot_df)

err_plot_df <- d_analysis %>%
  group_by(id, valence_current_group, valence_previous_group, switch) %>%
  summarise(
    error_rate = mean(error, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  normWS(s = "id", dv = "error_rate") %>%
  mutate(error_rate = DV_n) %>%
  group_by(valence_current_group, valence_previous_group, switch) %>%
  summarise(
    Error_m = mean(error_rate, na.rm = TRUE),
    Error_ci_lower = get_ci(error_rate, Error_m)[2],
    Error_ci_upper = get_ci(error_rate, Error_m)[1],
    .groups = "drop"
  ) %>%
  mutate(
    switch = factor(switch, levels = c(1, 0), labels = c("Switch", "Repeat")),
    valence_current_group  = factor(valence_current_group,
                                    labels = c("Univalent", "Bivalent")),
    valence_previous_group = factor(valence_previous_group,
                                    labels = c("Univalent", "Bivalent"))
  )


error_explevel_plot <- ggplot(err_plot_df,
    aes(x        = switch,
        y        = Error_m,
        color    = valence_current_group,
        linetype = valence_previous_group,
        group    = interaction(valence_previous_group,
                               valence_current_group))) +
  geom_line(linewidth = design$lines$linewidth, position = pos) +
  geom_errorbar(aes(ymin = Error_ci_lower,
                    ymax = Error_ci_upper),
                width     = design$errorbar$width,
                linewidth = design$errorbar$linewidth,
                position  = pos, 
                linetype = "solid") +
  scale_linetype_manual(
    name   = "Previous Group Valence",
    values = c("Univalent" = design$prev_val$linetype$uni,
               "Bivalent"  = design$prev_val$linetype$bi)
  ) +
  scale_color_manual(
    name   = "Current Group Valence",
    values = c("Univalent" = design$curr_val$color$uni,
               "Bivalent"  = design$curr_val$color$bi)
  ) +
  labs(
    x = NULL,
    y = "Error Rate"
  )

error_explevel_plot

ggsave("AC_Errors.svg", error_explevel_plot, width = 10, height = 6)
saveRDS(error_explevel_plot, "AC_Errors.rds")

err_plot_df
```

adding the CIs into d_analysis 

```{r}

subject_err <- d_analysis %>%
  group_by(id, valence_current_group, valence_previous_group, switch) %>%
  summarise(
    error_rate = mean(error, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  normWS(s = "id", dv = "error_rate") %>%
  mutate(error_rate_n = DV_n)


ci_err_df <- subject_err %>%
  group_by(valence_current_group, valence_previous_group, switch) %>%
  summarise(
    Error_m        = mean(error_rate_n, na.rm = TRUE),
    Error_ci_lower = get_ci(error_rate_n, Error_m)[2],
    Error_ci_upper = get_ci(error_rate_n, Error_m)[1],
    .groups = "drop"
  )


d_analysis <- d_analysis %>%
  left_join(ci_err_df, by = c("valence_current_group", "valence_previous_group", "switch"))
```


```{r}
saveRDS( d_analysis, "d_analysis.RDS")
```


3. ezddm

```{r}

alt_cue_agg_ID_ddm_nocycle <- d_analysis %>%
  mutate(RT_s = time/1000) %>%
  group_by(id, valence_current_group, val_c_g, valence_previous_group, val_p_g, switch) %>%
  summarize(RT_s_m = mean(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            Error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>%
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  unnest(ezddm)


alt_cue_agg_ddm_nocycle <- alt_cue_agg_ID_ddm_nocycle %>%
  group_by(id, val_c_g, val_p_g, switch) %>%
  normWS(s = "id", dv = "a") %>%
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>%
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>%
  mutate(Ter = DV_n) %>%
  group_by(val_c_g, val_p_g, switch) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[2],
            a_ci_upper = get_ci(a, a_m)[1],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[2],
            v_ci_upper = get_ci(v, v_m)[1],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[2],
            Ter_ci_upper = get_ci(Ter, Ter_m)[1],)


alt_cue_agg_ddm$switch <- as.factor(alt_cue_agg_ddm$switch)
alt_cue_agg_ddm_nocycle$switch <- as.factor(alt_cue_agg_ddm_nocycle$switch)
alt_cue_agg_ddm_nocycle$val_c_g <- as.factor(alt_cue_agg_ddm_nocycle$val_c_g)
alt_cue_agg_ddm_nocycle$val_p_g <- as.factor(alt_cue_agg_ddm_nocycle$val_p_g)


# alt_cue_agg_ddm <- alt_cue_agg_ddm %>%
#   mutate(
#     val_c_g = factor(val_c_g, levels = c(-0.5, 0.5), labels = c("Univalent", "Bivalent")),
#     val_p_g = factor(val_p_g, levels = c(-0.5, 0.5), labels = c("Univalent", "Bivalent"))
#   )

alt_cue_agg_ddm_nocycle <- alt_cue_agg_ddm_nocycle %>%
  mutate(
    val_c_g = factor(val_c_g, levels = c(-0.5, 0.5), labels = c("Univalent", "Bivalent")),
    val_p_g = factor(val_p_g, levels = c(-0.5, 0.5), labels = c("Univalent", "Bivalent")),
    switch  = factor(switch, levels = c("1", "0"), labels = c("Switch", "Repeat"))
  )

# unique(alt_cue_agg_ddm_nocycle$val_c_g)
# unique(alt_cue_agg_ddm_nocycle$switch)
# names(alt_cue_agg_ddm_nocycle)
# levels(alt_cue_agg_ddm_nocycle$val_c_g) # -0.5, 0.5 
# shared scale calls to avoid repetition
ddm_scales <- list(
  scale_color_manual(
    name   = "Current Group",
    values = c("Univalent" = design$curr_val$color$uni,
               "Bivalent"  = design$curr_val$color$bi)
  ),
  scale_linetype_manual(
    name   = "Previous Group",
    values = c("Univalent" = design$prev_val$linetype$uni,
               "Bivalent"  = design$prev_val$linetype$bi)
  )
)

pos <- position_dodge(0.3)

# plt_ddm_a <- ggplot(alt_cue_agg_ddm,
#     aes(x = cycle, y = a_m,
#         color    = val_c_g,
#         linetype = val_p_g,
#         group    = interaction(val_p_g, val_c_g))) +
#   geom_line(linewidth = design$lines$linewidth, position = pos) +
#   geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper),
#                 width = design$errorbar$width, linewidth = design$errorbar$linewidth,
#                 position = pos) +
#   ddm_scales +
#   labs(y = "a")
# 
# plt_ddm_v <- ggplot(alt_cue_agg_ddm,
#     aes(x = cycle, y = v_m,
#         color    = val_c_g,
#         linetype = val_p_g,
#         group    = interaction(val_p_g, val_c_g))) +
#   geom_line(linewidth = design$lines$linewidth, position = pos) +
#   geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper),
#                 width = design$errorbar$width, linewidth = design$errorbar$linewidth,
#                 position = pos) +
#   ddm_scales +
#   labs(y = "v")
# 
# plt_ddm_Ter <- ggplot(alt_cue_agg_ddm,
#     aes(x = cycle, y = Ter_m,
#         color    = val_c_g,
#         linetype = val_p_g,
#         group    = interaction(val_p_g, val_c_g))) +
#   geom_line(linewidth = design$lines$linewidth, position = pos) +
#   geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper),
#                 width = design$errorbar$width, linewidth = design$errorbar$linewidth,
#                 position = pos) +
#   ddm_scales +
#   labs(y = "Ter")

plt_ddm_a_nocycle <- ggplot(alt_cue_agg_ddm_nocycle,
    aes(x = switch, y = a_m,
        color    = val_c_g,
        linetype = val_p_g,
        group    = interaction(val_p_g, val_c_g))) +
  geom_line(linewidth = design$lines$linewidth, position = pos) +
  geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper),
                width = design$errorbar$width, linewidth = design$errorbar$linewidth,
                position = pos, 
                linetype = "solid") +
scale_x_discrete(limits = c("Switch", "Repeat"))+
  ddm_scales +
  labs(x = NULL, y = "Boundary Separation")

plt_ddm_v_nocycle <- ggplot(alt_cue_agg_ddm_nocycle,
    aes(x = switch, y = v_m,
        color    = val_c_g,
        linetype = val_p_g,
        group    = interaction(val_p_g, val_c_g))) +
  geom_line(linewidth = design$lines$linewidth, position = pos) +
  geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper),
                width = design$errorbar$width, linewidth = design$errorbar$linewidth,
                position = pos, 
                linetype = "solid") +
  scale_x_discrete(limits = c("Switch", "Repeat")) +
  ddm_scales +
  labs(x = NULL, y = "Drift Rate")

plt_ddm_Ter_nocycle <- ggplot(alt_cue_agg_ddm_nocycle,
    aes(x = switch, y = Ter_m,
        color    = val_c_g,
        linetype = val_p_g,
        group    = interaction(val_p_g, val_c_g))) +
  geom_line(linewidth = design$lines$linewidth, position = pos) +
  geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper),
                width = design$errorbar$width, linewidth = design$errorbar$linewidth,
                position = pos, 
                linetype = "solid") +
  scale_x_discrete(limits = c("Switch", "Repeat")) +
  ddm_scales +
 labs(x = NULL, y = "Non-Decision Time")

ezddm_effect_plot <- ggpubr::ggarrange(
       plt_ddm_a_nocycle,
      plt_ddm_v_nocycle,
     plt_ddm_Ter_nocycle,
  common.legend = TRUE, nrow = 3
)



plt_ddm_a_nocycle
plt_ddm_v_nocycle
plt_ddm_Ter_nocycle
ezddm_effect_plot

#ggsave("RT_descriptive_plot.svg", RT_descriptive_plot, width = 10, height = 6)

 ggsave("AC_ddm_a.svg", plt_ddm_a_nocycle, width = 10, height = 6)
 ggsave("AC_ddm_v.svg", plt_ddm_v_nocycle, width = 10, height = 6)
 ggsave("AC_ddm_TER.svg", plt_ddm_Ter_nocycle, width = 10, height = 6)
 ggsave("ezddm_effect_plot_apa.svg", ezddm_effect_plot, width = 10, height = 6)
# 
# 
saveRDS( plt_ddm_a_nocycle, "AC_ddm_a.rds" )
saveRDS(plt_ddm_v_nocycle, "AC_ddm_v.rds" )
saveRDS( plt_ddm_Ter_nocycle, "AC_ddm_TER.rds")

alt_cue_agg_ddm_nocycle
```




within-subjects: 

```{r}
preds_switch <- emmeans::emmeans(alt_cue_rt_log_resrt_s_2, 
    ~ val_c_g * val_p_g * switch * lag1_time_log_res_c, 
    type = "response",
    at = list(
      val_c_g = c("-0.5", "0.5"),
      val_p_g = c("-0.5", "0.5"),
      switch   = c("0", "1"),
      lag1_time_log_res_c = c(-1.5, 1.5)
    )) %>%
  as.data.frame() %>%
  mutate(
    is_bivalent   = case_when(val_c_g == "-0.5" ~ "Univalent",
                               val_c_g == "0.5"  ~ "Bivalent") %>% 
                    factor(levels = c("Univalent", "Bivalent")),
    prev_bivalent = case_when(val_p_g == "-0.5" ~ "Univalent",
                               val_p_g == "0.5"  ~ "Bivalent") %>% 
                    factor(levels = c("Univalent", "Bivalent")),
    switch_factor = factor(switch, levels = c("1", "0"), 
                           labels = c("Switch", "Repeat")),
    speed         = case_when(lag1_time_log_res_c == -1.5 ~ "Fast",
                               lag1_time_log_res_c ==  1.5 ~ "Slow") %>% 
                    factor(levels = c("Fast", "Slow"))
  )


pos <- position_dodge(0.3)

logrt_pred_switch <- ggplot(preds_switch,
    aes(x        = switch_factor,
        y        = emmean,
        color    = is_bivalent,
        linetype = prev_bivalent,
        group    = interaction(prev_bivalent, is_bivalent))) +
  geom_line(linewidth = design$lines$linewidth, position = pos) +
  #geom_point(size = 3, position = pos) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL),
                width     = design$errorbar$width,
                linewidth = design$errorbar$linewidth,
                position  = pos) +
  facet_wrap(~speed, labeller = labeller(speed = c("Slow" = "Lag RT Slow",
                                                   "Fast" = "Lag RT Fast"))) +
 
  scale_linetype_manual(
    name   = "Previous Group Valence",
    values = c("Univalent" = design$prev_val$linetype$uni,
               "Bivalent"  = design$prev_val$linetype$bi)
  ) +
   scale_color_manual(
    name   = "Current Group Valnece",
    values = c("Univalent" = design$curr_val$color$uni,
               "Bivalent"  = design$curr_val$color$bi)
  ) +
  labs(
  #  title = "Model predictions for log RTs",
    x = NULL,
    y     = "log(RT) Prediction"
    #x     = "Switch Status"
  )


logrt_pred_switch

ggsave("AC_lagRT.svg", logrt_pred_switch, width = 10, height = 6)
saveRDS(logrt_pred_switch, "AC_lagRT.rds" )
```

3. between subjects (individual differences)

```{r}

alt_cue_v_NA_model_summary <- lapply(alt_cue_indiv_diff_models$v_NA, function(x){
  m_sum <- x %>% 
    summary() 
  
  m_sum %>% 
    coef() %>% 
    as.data.frame() %>%
    mutate(r_sq = m_sum$r.squared,
           r_sq_adj = m_sum$adj.r.squared)
  
}) %>% 
  bind_rows(.id = "model") %>% 
  rownames_to_column("coefficient") %>%
  janitor::clean_names() %>%
  mutate(coefficient = gsub("\\...[[:digit:]]+", "", coefficient),
         coefficient = gsub("v_", "", coefficient),
         coefficient = gsub("_NA", "", coefficient),
         outcome = gsub("[[:digit:]]", "", model),
         outcome = factor(outcome, levels = c("uu", "ub", "bu", "bb")),
         is_sig = ifelse(pr_t < 0.05, 1, 0),
         r_label = as.character(round(r_sq, 2)),
         r_label = gsub("^0.", ".", r_label),
         r_adj_label = as.character(round(r_sq_adj, 2)),
         r_adj_label = gsub("^0.", ".", r_adj_label),
         outcome = factor(outcome, levels = c("uu", "ub", "bu", "bb")))


ggplot(alt_cue_v_NA_model_summary, aes(x = coefficient, y = estimate, group = model, color = model))+ 
  geom_hline(yintercept = 0, linetype = "dotted")+
  geom_ribbon(aes(ymin = estimate - std_error,
                  ymax = estimate + std_error), alpha = 0.1, color = NA)+
  geom_line()+
  geom_text(data = alt_cue_v_NA_model_summary %>% group_by(model) %>% slice(n()),
            aes(label = r_adj_label), hjust = -0.3)+
  geom_point(data = alt_cue_v_NA_model_summary %>% filter(is_sig == 1), pch = "*", size = 10)+
  theme_classic()+
  facet_wrap(~outcome, labeller = labeller(outcome = c("uu" = "uni-uni",
                                                       "bu" = "bi-uni",
                                                       "ub" = "uni-bi",
                                                       "bb" = "bi-bi")),
            ncol = 1)+
  scale_x_discrete(labels = c("s0_cbiv0_lbiv1" = "NS\nL-bi\nC-uni",
                              "s0_cbiv1_lbiv1" = "NS\nL-bi\nC-bi",
                              "s0_cbiv0_lbiv0" = "NS\nL-uni\nC-uni",
                              "s0_cbiv1_lbiv0" = "NS\nL-uni\nC-bi",
                              "(Intercept)" = "Int"))+
  coord_cartesian(xlim = c(1, 5.5))+
  theme(legend.position = "none")



# compare_models(alt_cue_indiv_diff_models$v_NA, "uu")
# compare_models(alt_cue_indiv_diff_models$v_NA, "ub")
# compare_models(alt_cue_indiv_diff_models$v_NA, "bu")
# compare_models(alt_cue_indiv_diff_models$v_NA, "bb")

```


```{r}


alt_cue_v_NA_model_summary <- lapply(alt_cue_indiv_diff_models$v_NA, function(x){
  m_sum <- x %>% 
    summary() 
  
  m_sum %>% 
    coef() %>% 
    as.data.frame() %>%
    mutate(r_sq = m_sum$r.squared,
           r_sq_adj = m_sum$adj.r.squared)
  
}) %>% 
  bind_rows(.id = "model") %>% 
  rownames_to_column("coefficient") %>%
  janitor::clean_names() %>%
  mutate(coefficient = gsub("\\...[[:digit:]]+", "", coefficient),
         coefficient = gsub("v_", "", coefficient),
         coefficient = gsub("_NA", "", coefficient),
         outcome = gsub("[[:digit:]]", "", model),
         outcome = factor(outcome, levels = c("uu", "ub", "bu", "bb")),
         is_sig = ifelse(pr_t < 0.05, 1, 0),
         r_label = as.character(round(r_sq, 2)),
         r_label = gsub("^0.", ".", r_label),
         r_adj_label = as.character(round(r_sq_adj, 2)),
         r_adj_label = gsub("^0.", ".", r_adj_label),
         outcome = factor(outcome, levels = c("uu", "ub", "bu", "bb")),
         color = parse_number(model) %>% factor())


ggplot(alt_cue_v_NA_model_summary, aes(x = coefficient, y = estimate, group = model, color = model))+ 
  geom_hline(yintercept = 0, linetype = "dotted")+
  geom_ribbon(aes(ymin = estimate - std_error,
                  ymax = estimate + std_error), alpha = 0.1, color = NA)+
  geom_line()+
  geom_text(data = alt_cue_v_NA_model_summary %>% group_by(model) %>% slice(n()),
            aes(label = r_adj_label), hjust = -0.3)+
  geom_point(data = alt_cue_v_NA_model_summary %>% filter(is_sig == 1), pch = "*", size = 10)+
  theme_classic()+
  facet_wrap(~outcome, labeller = labeller(outcome = c("uu" = "uni-uni",
                                                       "ub" = "uni-bi",
                                                       "bu" = "bi-uni",
                                                       "bb" = "bi-bi")), nrow = 1)+
  scale_x_discrete(labels = c("s0_cbiv0_lbiv1" = "NS\nL-bi\nC-uni",
                              "s0_cbiv1_lbiv1" = "NS\nL-bi\nC-bi",
                              "s0_cbiv0_lbiv0" = "NS\nL-uni\nC-uni",
                              "s0_cbiv1_lbiv0" = "NS\nL-uni\nC-bi",
                              "(Intercept)" = "Int"))+
  coord_cartesian(xlim = c(1, 5.5))+
  theme(legend.position = "none")


```

## Models (just have this here pasted again as a reference)

```{r}
alt_cue_indiv_diff_models <- list(
  RT = list(
    uu0 = lm(RT_log_s1_cbiv0_lbiv0 ~ 1, alt_cue_indiv),
    uu1 = lm(RT_log_s1_cbiv0_lbiv0 ~ RT_log_s0_cbiv0_lbiv0, alt_cue_indiv),
    uu2 = lm(RT_log_s1_cbiv0_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1, alt_cue_indiv),
    uu3 = lm(RT_log_s1_cbiv0_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0, alt_cue_indiv),
    uu4 = lm(RT_log_s1_cbiv0_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0 + RT_log_s0_cbiv1_lbiv1, alt_cue_indiv),
    
    bu0 = lm(RT_log_s1_cbiv1_lbiv0 ~ 1, alt_cue_indiv),
    bu1 = lm(RT_log_s1_cbiv1_lbiv0 ~ RT_log_s0_cbiv0_lbiv0, alt_cue_indiv),
    bu2 = lm(RT_log_s1_cbiv1_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1, alt_cue_indiv),
    bu3 = lm(RT_log_s1_cbiv1_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0, alt_cue_indiv),
    bu4 = lm(RT_log_s1_cbiv1_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0 + RT_log_s0_cbiv1_lbiv1, alt_cue_indiv),
    
    ub0 = lm(RT_log_s1_cbiv0_lbiv1 ~ 1, alt_cue_indiv),
    ub1 = lm(RT_log_s1_cbiv0_lbiv1 ~ RT_log_s0_cbiv0_lbiv0, alt_cue_indiv),
    ub2 = lm(RT_log_s1_cbiv0_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1, alt_cue_indiv),
    ub3 = lm(RT_log_s1_cbiv0_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0, alt_cue_indiv),
    ub4 = lm(RT_log_s1_cbiv0_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0 + RT_log_s0_cbiv1_lbiv1, alt_cue_indiv),
    
    bb0 = lm(RT_log_s1_cbiv1_lbiv1 ~ 1, alt_cue_indiv),
    bb1 = lm(RT_log_s1_cbiv1_lbiv1 ~ RT_log_s0_cbiv0_lbiv0, alt_cue_indiv),
    bb2 = lm(RT_log_s1_cbiv1_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1, alt_cue_indiv),
    bb3 = lm(RT_log_s1_cbiv1_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0, alt_cue_indiv),
    bb4 = lm(RT_log_s1_cbiv1_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0 + RT_log_s0_cbiv1_lbiv1, alt_cue_indiv)
  ),
  
  
  Error = list(
    uu1 = lm(Error_s1_cbiv0_lbiv0 ~ 1, alt_cue_indiv),
    uu1 = lm(Error_s1_cbiv0_lbiv0 ~ Error_s0_cbiv0_lbiv0, alt_cue_indiv),
    uu2 = lm(Error_s1_cbiv0_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1, alt_cue_indiv),
    uu3 = lm(Error_s1_cbiv0_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0, alt_cue_indiv),
    uu4 = lm(Error_s1_cbiv0_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0 + Error_s0_cbiv1_lbiv1, alt_cue_indiv),
    
    bu0 = lm(Error_s1_cbiv1_lbiv0 ~ 1, alt_cue_indiv),
    bu1 = lm(Error_s1_cbiv1_lbiv0 ~ Error_s0_cbiv0_lbiv0, alt_cue_indiv),
    bu2 = lm(Error_s1_cbiv1_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1, alt_cue_indiv),
    bu3 = lm(Error_s1_cbiv1_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0, alt_cue_indiv),
    bu4 = lm(Error_s1_cbiv1_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0 + Error_s0_cbiv1_lbiv1, alt_cue_indiv),
    
    ub0 = lm(Error_s1_cbiv0_lbiv1 ~ 1, alt_cue_indiv),
    ub1 = lm(Error_s1_cbiv0_lbiv1 ~ Error_s0_cbiv0_lbiv0, alt_cue_indiv),
    ub2 = lm(Error_s1_cbiv0_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1, alt_cue_indiv),
    ub3 = lm(Error_s1_cbiv0_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0, alt_cue_indiv),
    ub4 = lm(Error_s1_cbiv0_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0 + Error_s0_cbiv1_lbiv1, alt_cue_indiv),
    
    bb0 = lm(Error_s1_cbiv1_lbiv1 ~ 1, alt_cue_indiv),
    bb1 = lm(Error_s1_cbiv1_lbiv1 ~ Error_s0_cbiv0_lbiv0, alt_cue_indiv),
    bb2 = lm(Error_s1_cbiv1_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1, alt_cue_indiv),
    bb3 = lm(Error_s1_cbiv1_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0, alt_cue_indiv),
    bb4 = lm(Error_s1_cbiv1_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0 + Error_s0_cbiv1_lbiv1, alt_cue_indiv)
  ),
  
  v = list(
    
    uu0 = lm(v_s1_cbiv0_lbiv0 ~ 1, alt_cue_indiv),
    uu1 = lm(v_s1_cbiv0_lbiv0 ~ v_s0_cbiv0_lbiv0, alt_cue_indiv),
    uu2 = lm(v_s1_cbiv0_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1, alt_cue_indiv),
    uu3 = lm(v_s1_cbiv0_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0, alt_cue_indiv),
    uu4 = lm(v_s1_cbiv0_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0 + v_s0_cbiv1_lbiv1, alt_cue_indiv),
    
    bu0 = lm(v_s1_cbiv1_lbiv0 ~ 1, alt_cue_indiv),
    bu1 = lm(v_s1_cbiv1_lbiv0 ~ v_s0_cbiv0_lbiv0, alt_cue_indiv),
    bu2 = lm(v_s1_cbiv1_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1, alt_cue_indiv),
    bu3 = lm(v_s1_cbiv1_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0, alt_cue_indiv),
    bu4 = lm(v_s1_cbiv1_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0 + v_s0_cbiv1_lbiv1, alt_cue_indiv),
    
    ub0 = lm(v_s1_cbiv0_lbiv1 ~ 1, alt_cue_indiv),
    ub1 = lm(v_s1_cbiv0_lbiv1 ~ v_s0_cbiv0_lbiv0, alt_cue_indiv),
    ub2 = lm(v_s1_cbiv0_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1, alt_cue_indiv),
    ub3 = lm(v_s1_cbiv0_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0, alt_cue_indiv),
    ub4 = lm(v_s1_cbiv0_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0 + v_s0_cbiv1_lbiv1, alt_cue_indiv),
    
    bb0 = lm(v_s1_cbiv1_lbiv1 ~ 1, alt_cue_indiv),
    bb1 = lm(v_s1_cbiv1_lbiv1 ~ v_s0_cbiv0_lbiv0, alt_cue_indiv),
    bb2 = lm(v_s1_cbiv1_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1, alt_cue_indiv),
    bb3 = lm(v_s1_cbiv1_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0, alt_cue_indiv),
    bb4 = lm(v_s1_cbiv1_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0 + v_s0_cbiv1_lbiv1, alt_cue_indiv)
  ),
  v_NA = list(
    
    uu0 = lm(v_s1_cbiv0_lbiv0_NA ~ 1, alt_cue_indiv),
    uu1 = lm(v_s1_cbiv0_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA, alt_cue_indiv),
    uu2 = lm(v_s1_cbiv0_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA, alt_cue_indiv),
    uu3 = lm(v_s1_cbiv0_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA, alt_cue_indiv),
    uu4 = lm(v_s1_cbiv0_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA + v_s0_cbiv1_lbiv1_NA, alt_cue_indiv),
    
    bu0 = lm(v_s1_cbiv1_lbiv0_NA ~ 1, alt_cue_indiv),
    bu1 = lm(v_s1_cbiv1_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA, alt_cue_indiv),
    bu2 = lm(v_s1_cbiv1_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA, alt_cue_indiv),
    bu3 = lm(v_s1_cbiv1_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA, alt_cue_indiv),
    bu4 = lm(v_s1_cbiv1_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA + v_s0_cbiv1_lbiv1_NA, alt_cue_indiv),
    
    ub0 = lm(v_s1_cbiv0_lbiv1_NA ~ 1, alt_cue_indiv),
    ub1 = lm(v_s1_cbiv0_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA, alt_cue_indiv),
    ub2 = lm(v_s1_cbiv0_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA, alt_cue_indiv),
    ub3 = lm(v_s1_cbiv0_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA, alt_cue_indiv),
    ub4 = lm(v_s1_cbiv0_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA + v_s0_cbiv1_lbiv1_NA, alt_cue_indiv),
    
    bb0 = lm(v_s1_cbiv1_lbiv1_NA ~ 1, alt_cue_indiv),
    bb1 = lm(v_s1_cbiv1_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA, alt_cue_indiv),
    bb2 = lm(v_s1_cbiv1_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA, alt_cue_indiv),
    bb3 = lm(v_s1_cbiv1_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA, alt_cue_indiv),
    bb4 = lm(v_s1_cbiv1_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA + v_s0_cbiv1_lbiv1_NA, alt_cue_indiv)
  )
)

summary(alt_cue_indiv_diff_models$RT$uu4)

```



```{r}

### USE THIS 

v_comparisons <- lapply(c("uu", "bu", "ub", "bb"), function(x){
  
  result <- compare_models(alt_cue_indiv_diff_models$v, x)
  
  data.frame(
    comparison = x,
    comparison_p = result[["Pr(>F)"]][!is.na(result[["Pr(>F)"]])]
  )
  
}) %>%
  bind_rows() %>%
  mutate(comparison_sig = ifelse(comparison_p < 0.05, 1, 0))

alt_cue_v_model_summary <- lapply(alt_cue_indiv_diff_models$v, function(x){
  m_sum <- x %>% 
    summary() 
  
  m_sum %>% 
    coef() %>% 
    as.data.frame() %>%
    mutate(r_sq = m_sum$r.squared,
           r_sq_adj = m_sum$adj.r.squared)
}) %>% 
  bind_rows(.id = "model") %>% 
  rownames_to_column("coefficient") %>%
  janitor::clean_names() %>%
  cross_join(v_comparisons) %>%
  filter(!grepl("(Intercept)", coefficient)) %>%
  mutate(coefficient = gsub("\\...[[:digit:]]+", "", coefficient),
         coefficient = gsub("v_", "", coefficient),
         outcome = gsub("[[:digit:]]", "", model),
         outcome = factor(outcome, levels = c("uu", "ub", "bu", "bb")),
         is_sig = ifelse(pr_t < 0.05, 1, 0),
         # r_label = as.character(round(r_sq, 2)),
         # r_label = gsub("^0.", ".", r_label),
         r_label = sprintf("%.2f", r_sq),
         r_label = case_when(comparison_sig == 1 ~ paste0(r_label, "*"), .default = r_label),
         r_adj_label = sprintf("%.2f", r_sq_adj),
         r_adj_label = case_when(comparison_sig == 1 ~ paste0(r_adj_label, "*"), .default = r_adj_label),
         color = parse_number(model) %>% factor())


ggplot(alt_cue_v_model_summary, aes(x = coefficient, y = estimate, group = model, color = model))+ 
  geom_hline(yintercept = 0, linetype = "dotted")+
  geom_ribbon(aes(ymin = estimate - std_error,
                  ymax = estimate + std_error), alpha = 0.1, color = NA)+
  geom_line()+
  geom_text(data = alt_cue_v_model_summary %>% group_by(model) %>% slice(n()),
            aes(label = r_adj_label), hjust = -0.3)+
  geom_point(data = alt_cue_v_model_summary %>% filter(is_sig == 1), pch = "*", size = 10)+
  theme_classic()+
  facet_wrap(~outcome, labeller = labeller(outcome = c("uu" = "Switch: Uni-Uni",
                                                       "ub" = "Switch: Uni-Bi",
                                                       "bu" = "Switch: Bi-Uni",
                                                       "bb" = "Switch: Bi-Bi")), ncol = 1)+
  scale_x_discrete(labels = c("v_s0_cbiv0_lbiv1" = "NS\nL-bi\nC-uni",
                              "v_s0_cbiv1_lbiv1" = "NS\nL-bi\nC-bi",
                              "v_s0_cbiv0_lbiv0" = "NS\nL-uni\nC-uni",
                              "v_s0_cbiv1_lbiv0" = "NS\nL-uni\nC-bi",
                              "(Intercept)" = "Int"))+
  coord_cartesian(xlim = c(1, 5.5))+
  theme(legend.position = "none")

plt_betw_v <- ggplot(alt_cue_v_model_summary, aes(x = coefficient, y = estimate, group = model, color = color))+ 
  geom_hline(yintercept = 0, linetype = "dotted")+
  geom_ribbon(aes(ymin = estimate - std_error,
                  ymax = estimate + std_error), alpha = 0.1, color = NA)+
  geom_line()+
  # geom_text(data = alt_cue_v_model_summary %>% group_by(model) %>% slice(n()),
  #           aes(label = r_adj_label), hjust = -0.3)+
  geom_label(data = alt_cue_v_model_summary %>% group_by(model) %>% slice(n()),
            aes(label = r_adj_label), hjust = -0.1, alpha = 0.8, linewidth = 0)+
  geom_point(data = alt_cue_v_model_summary %>% filter(is_sig == 1), pch = "*", size = 10)+
  labs(x = "",
       y = "")+
  facet_wrap(~outcome, labeller = labeller(outcome = c("uu" = "Switch: Uni-Uni",
                                                       "ub" = "Switch: Uni-Bi",
                                                       "bu" = "Switch: Bi-Uni",
                                                       "bb" = "Switch: Bi-Bi")), ncol = 1)+
  scale_color_manual(values = colorRampPalette(c("blue", "red"))(5))+
  scale_x_discrete(labels = c("s0_cbiv0_lbiv1" = "Bi-Uni",
                              "s0_cbiv1_lbiv1" = "Bi-Bi",
                              "s0_cbiv0_lbiv0" = "Uni-Uni",
                              "s0_cbiv1_lbiv0" = "Uni-Bi",
                              "(Intercept)" = "Int"))+
  coord_cartesian(xlim = c(1, 4.5))+
  theme(legend.position = "none", 
        strip.background = element_blank())

plt_betw_v

ggsave(plot = plt_betw_v, "AC_betw_v.svg", width = 4, height = 6, units = "in")
 saveRDS(plt_betw_v, "AC_betw_v.RDS")




```


```{r}
RT_comparisons <- lapply(c("uu", "bu", "ub", "bb"), function(x){
  
  result <- compare_models(alt_cue_indiv_diff_models$RT, x)
  
  data.frame(
    comparison = x,
    comparison_p = result[["Pr(>F)"]][!is.na(result[["Pr(>F)"]])]
  )
  
}) %>%
  bind_rows() %>%
  mutate(comparison_sig = ifelse(comparison_p < 0.05, 1, 0))

alt_cue_rt_model_summary <- lapply(alt_cue_indiv_diff_models$RT, function(x){
  m_sum <- x %>% 
    summary() 
  
  m_sum %>% 
    coef() %>% 
    as.data.frame() %>%
    mutate(r_sq = m_sum$r.squared,
           r_sq_adj = m_sum$adj.r.squared)
}) %>% 
  bind_rows(.id = "model") %>% 
  rownames_to_column("coefficient") %>%
  janitor::clean_names() %>%
  cross_join(RT_comparisons) %>%
  filter(!grepl("(Intercept)", coefficient)) %>%
  mutate(coefficient = gsub("\\...[[:digit:]]+", "", coefficient),
         coefficient = gsub("RT_log_", "", coefficient),
         outcome = gsub("[[:digit:]]", "", model),
         outcome = factor(outcome, levels = c("uu", "ub", "bu", "bb")),
         is_sig = ifelse(pr_t < 0.05, 1, 0),
         # r_label = as.character(round(r_sq, 2)),
         # r_label = gsub("^0.", ".", r_label),
         r_label = sprintf("%.2f", r_sq),
         r_label = case_when(comparison_sig == 1 ~ paste0(r_label, "*"), .default = r_label),
         r_adj_label = sprintf("%.2f", r_sq_adj),
         r_adj_label = case_when(comparison_sig == 1 ~ paste0(r_adj_label, "*"), .default = r_adj_label),
         color = parse_number(model) %>% factor())


ggplot(alt_cue_rt_model_summary, aes(x = coefficient, y = estimate, group = model, color = model))+ 
  geom_hline(yintercept = 0, linetype = "dotted")+
  geom_ribbon(aes(ymin = estimate - std_error,
                  ymax = estimate + std_error), alpha = 0.1, color = NA)+
  geom_line()+
  geom_text(data = alt_cue_rt_model_summary %>% group_by(model) %>% slice(n()),
            aes(label = r_adj_label), hjust = -0.3)+
  geom_point(data = alt_cue_rt_model_summary %>% filter(is_sig == 1), pch = "*", size = 10)+
  theme_classic()+
  facet_wrap(~outcome, labeller = labeller(outcome = c("uu" = "Switch: Uni-Uni",
                                                       "ub" = "Switch: Uni-Bi",
                                                       "bu" = "Switch: Bi-Uni",
                                                       "bb" = "Switch: Bi-Bi")), ncol = 1)+
  scale_x_discrete(labels = c("RT_log_s0_cbiv0_lbiv1" = "NS\nL-bi\nC-uni",
                              "RT_log_s0_cbiv1_lbiv1" = "NS\nL-bi\nC-bi",
                              "RT_log_s0_cbiv0_lbiv0" = "NS\nL-uni\nC-uni",
                              "RT_log_s0_cbiv1_lbiv0" = "NS\nL-uni\nC-bi",
                              "(Intercept)" = "Int"))+
  coord_cartesian(xlim = c(1, 5.5))+
  theme(legend.position = "none")

plt_betw_rt <- ggplot(alt_cue_rt_model_summary, aes(x = coefficient, y = estimate, group = model, color = color))+ 
  geom_hline(yintercept = 0, linetype = "dotted")+
  geom_ribbon(aes(ymin = estimate - std_error,
                  ymax = estimate + std_error), alpha = 0.1, color = NA)+
  geom_line()+
  # geom_text(data = alt_cue_v_model_summary %>% group_by(model) %>% slice(n()),
  #           aes(label = r_adj_label), hjust = -0.3)+
  geom_label(data = alt_cue_rt_model_summary %>% group_by(model) %>% slice(n()),
            aes(label = r_adj_label), hjust = -0.1, alpha = 0.8, linewidth = 0)+
  geom_point(data = alt_cue_rt_model_summary %>% filter(is_sig == 1), pch = "*", size = 10)+
  labs(x = "",
       y = "")+
  facet_wrap(~outcome, labeller = labeller(outcome = c("uu" = "Switch: Uni-Uni",
                                                       "ub" = "Switch: Uni-Bi",
                                                       "bu" = "Switch: Bi-Uni",
                                                       "bb" = "Switch: Bi-Bi")), ncol = 1)+
  scale_color_manual(values = colorRampPalette(c("blue", "red"))(4))+
  scale_x_discrete(labels = c("s0_cbiv0_lbiv1" = "Bi-Uni",
                              "s0_cbiv1_lbiv1" = "Bi-Bi",
                              "s0_cbiv0_lbiv0" = "Uni-Uni",
                              "s0_cbiv1_lbiv0" = "Uni-Bi",
                              "(Intercept)" = "Int"))+
  coord_cartesian(xlim = c(1, 4.5))+
  theme(legend.position = "none", 
        strip.background = element_blank())


plt_betw_rt

ggsave(plot = plt_betw_rt, "AC_betw_RT.svg", width = 4, height = 6, units = "in")
 saveRDS(plt_betw_rt, "AC_betw_RT.RDS")
```

```{r}


Error_comparisons <- lapply(c("uu", "bu", "ub", "bb"), function(x){
  
  result <- compare_models(alt_cue_indiv_diff_models$Error, x)
  
  data.frame(
    comparison = x,
    comparison_p = result[["Pr(>F)"]][!is.na(result[["Pr(>F)"]])]
  )
  
}) %>%
  bind_rows() %>%
  mutate(comparison_sig = ifelse(comparison_p < 0.05, 1, 0))

alt_cue_Error_model_summary <- lapply(alt_cue_indiv_diff_models$Error, function(x){
  m_sum <- x %>% 
    summary() 
  
  m_sum %>% 
    coef() %>% 
    as.data.frame() %>%
    mutate(r_sq = m_sum$r.squared,
           r_sq_adj = m_sum$adj.r.squared)
}) %>% 
  bind_rows(.id = "model") %>% 
  rownames_to_column("coefficient") %>%
  janitor::clean_names() %>%
  cross_join(Error_comparisons) %>%
  filter(!grepl("(Intercept)", coefficient)) %>%
  mutate(coefficient = gsub("\\...[[:digit:]]+", "", coefficient),
         coefficient = gsub("^Error_", "", coefficient),
         outcome = gsub("[[:digit:]]", "", model),
         outcome = factor(outcome, levels = c("uu", "ub", "bu", "bb")),
         is_sig = ifelse(pr_t < 0.05, 1, 0),
         # r_label = as.character(round(r_sq, 2)),
         # r_label = gsub("^0.", ".", r_label),
         r_label = sprintf("%.2f", r_sq),
         r_label = case_when(comparison_sig == 1 ~ paste0(r_label, "*"), .default = r_label),
         r_adj_label = sprintf("%.2f", r_sq_adj),
         r_adj_label = case_when(comparison_sig == 1 ~ paste0(r_adj_label, "*"), .default = r_adj_label),
         color = parse_number(model) %>% factor())


ggplot(alt_cue_Error_model_summary, aes(x = coefficient, y = estimate, group = model, color = model))+ 
  geom_hline(yintercept = 0, linetype = "dotted")+
  geom_ribbon(aes(ymin = estimate - std_error,
                  ymax = estimate + std_error), alpha = 0.1, color = NA)+
  geom_line()+
  geom_text(data = alt_cue_Error_model_summary %>% group_by(model) %>% slice(n()),
            aes(label = r_adj_label), hjust = -0.3)+
  geom_point(data = alt_cue_Error_model_summary %>% filter(is_sig == 1), pch = "*", size = 10)+
  theme_classic()+
  facet_wrap(~outcome, labeller = labeller(outcome = c("uu" = "Switch: Uni-Uni",
                                                       "ub" = "Switch: Uni-Bi",
                                                       "bu" = "Switch: Bi-Uni",
                                                       "bb" = "Switch: Bi-Bi")), ncol = 1)+
  scale_x_discrete(labels = c("Error_s0_cbiv0_lbiv1" = "NS\nL-bi\nC-uni",
                              "Error_s0_cbiv1_lbiv1" = "NS\nL-bi\nC-bi",
                              "Error_s0_cbiv0_lbiv0" = "NS\nL-uni\nC-uni",
                              "Error_s0_cbiv1_lbiv0" = "NS\nL-uni\nC-bi",
                              "(Intercept)" = "Int"))+
  coord_cartesian(xlim = c(1, 5.5))+
  theme(legend.position = "none")

plt_betw_Error <- ggplot(alt_cue_Error_model_summary, aes(x = coefficient, y = estimate, group = model, color = color))+ 
  geom_hline(yintercept = 0, linetype = "dotted")+
  geom_ribbon(aes(ymin = estimate - std_error,
                  ymax = estimate + std_error), alpha = 0.1, color = NA)+
  geom_line()+
  # geom_text(data = alt_cue_v_model_summary %>% group_by(model) %>% slice(n()),
  #           aes(label = r_adj_label), hjust = -0.3)+
  geom_label(data = alt_cue_Error_model_summary %>% group_by(model) %>% slice(n()),
            aes(label = r_adj_label), hjust = -0.1, alpha = 0.8, linewidth = 0)+
  geom_point(data = alt_cue_Error_model_summary %>% filter(is_sig == 1), pch = "*", size = 10)+
  labs(x = "",
       y = "")+
  facet_wrap(~outcome, labeller = labeller(outcome = c("uu" = "Switch: Uni-Uni",
                                                       "ub" = "Switch: Uni-Bi",
                                                       "bu" = "Switch: Bi-Uni",
                                                       "bb" = "Switch: Bi-Bi")), ncol = 1)+
  scale_color_manual(values = colorRampPalette(c("blue", "red"))(4))+
  scale_x_discrete(labels = c("s0_cbiv0_lbiv1" = "Bi-Uni",
                              "s0_cbiv1_lbiv1" = "Bi-Bi",
                              "s0_cbiv0_lbiv0" = "Uni-Uni",
                              "s0_cbiv1_lbiv0" = "Uni-Bi",
                              "(Intercept)" = "Int"))+
  coord_cartesian(xlim = c(1, 4.5))+
  theme(legend.position = "none", 
        strip.background = element_blank())


plt_betw_Error

ggsave(plot = plt_betw_Error, "AC_betw_Error.svg", width = 4, height = 6, units = "in")
 saveRDS(plt_betw_Error, "AC_betw_Error.RDS")

```

###############################################################################################

IQ and WM Tests 


```{r}
library(readr)
tests <- read_tsv("BigTestsToR.txt")

class(tests)

head(tests)

names(tests)

length(unique(tests$ID)) # 81 subjects 

```

```{r}
tests_clean <- tests %>%
  filter(!ID %in% c(901, 959, 201, 975, 902)) %>% 
  droplevels()


length(unique(tests_clean$ID)) ## 76 subjects 



sort(unique((d_clean$id))) # 3, 4, 5, 7 ,8, 9 , 10, 11, 12, 13, 14, 15, 16, 17, 99, 202 , 203    204, 401 , 402 , 403, 404, 405 , 406, 501,  502,  503, 504, 505, 701, 702, 703 , 704 ,705 ,706, 707, 708 , 752, 800, 903, 904, 905, 906, 907, 908, 909 , 910, 911, 912, 913, 914, 915, 916 ,   917 ,918, 919, 953, 954, 958, 962 ,963, 964 ,965 ,966 , 967 , 968 , 969 , 970,971, 974, 75033, 750445, 961422

sort(unique(tests_clean$ID)) #  3   4   5   7   9  10  11  12  13  14  15  17  99 202 203 204 301 403 404 405 406 501 502 503 504 505 701 702 703 704 705 706 707 708 751 752 800 903 904 905 906 907 908 909 910 911 912 913 914 915 916 917 918 919 951 952 953 954 956 957 958 960 961 962 963 964 965 966 967 968 969 970 971 972 973 974

## difference: tests has 301, d clean does not have it ; d_clean has 401 and 402. tests does not have it; tests has 751 and d clean does not; tests has 951, 952, 956, 957, 950, 960, 961 but d clean does not have it. tests does not have 75033, 750445, 961422


# # 1. Who is in df1 but NOT in df2? (The "Lost" subjects)
 missing_from_dclean <- setdiff(tests_clean$ID, d_clean$id)
 missing_from_dclean # 301 751 951 952 956 957 960 961 972 973
# 
# # 2. Who is in df2 but NOT in df1? (The "New" subjects)
 missing_from_test <- setdiff(d_clean$id, tests_clean$ID)
 missing_from_test # "16"     "8"      "401"    "402"    "750445" "75033"  "961422"
# 
# # 3. Who is in BOTH? (The "Overlap")
 common_ids <- intersect(tests_clean$ID, d_clean$id)
 sort(common_ids)  #  [1] "10"  "11"  "12"  "13"  "14"  "15"  "17"  "202" "203" "204" "3"   "4"   "403" "404" "405" "406" "5"   "501" "502" "503" "504" "505" "7"   "701" "702" "703" "704" "705" "706" "707" "708" "752" "800" "9"   "903" "904" "905" "906" "907" "908" "909" "910" "911" "912" "913" "914" "915" "916" "917" "918" "919" "953" "954" "958" "962" "963"  "964" "965" "966" "967" "968" "969" "970" "971" "974" "99" 
 
 length(common_ids) # 66 subjects 
```
 
 
 

#```{r}


id_4_clean <- d_clean %>%
  filter(id == 4) %>% 
  group_by(id, block, trial) %>%
  slice(1) %>%   # keep first occurrence
  ungroup() %>% 
  droplevels()
#```


#```{r}
data_clean <- d_clean %>%
  filter(id != 4) %>%   # keep everyone else untouched
  bind_rows(id_4_clean) %>% 
  droplevels()

#```

testing if traeoff itself is a function of cognitive capacity 

use g and slots
g: IQ
slots: WM 

add them as main effects predictors and allow them to interact with the other predictors 

WM is a pure measure of stability 
higher WM capacity would mean higher stability 



ungroup and then scale for within-subjects 



###########################################################################################




