---
title: "alternate_cues_analysis_updated"
author: "Neha"
date: "2026-02-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(readr)
#AlternateCues <- read_csv("~/Desktop/Mayr_lab/Data_analysis_project/AlternateCues/AlternateCues.csv")

AlternateCues <- read_csv("AlternateCues.csv")
View(AlternateCues)

library(tidyverse)
tibble_summary<- AlternateCues %>% 
  summary() %>% 
  tibble()
  


```

 have to remove practice blocks + the 5 unusable subjects (901, 959, 201, 975, 902) : 

Note: subject 4 can have duplicate trials removed 


```{r}

library(tidyverse)
d_use <- data %>%
  filter(!id %in% c(901, 959, 201, 975, 902)) %>% 
  droplevels()


unique(d_use$id) ## 73 subjects 

d_use <- d_use %>% 
  filter(block != 0) %>% 
  droplevels()

unique(d_use$block)

```


```{r}


id_4_clean <- d_use %>%
  filter(id == 4) %>% 
  group_by(id, block, trial) %>%
  slice(1) %>%   # keep first occurrence
  ungroup() %>% 
  droplevels()
```


```{r}
data_fixed <- d_use %>%
  filter(id != 4) %>%   # keep everyone else untouched
  bind_rows(id_4_clean) %>% 
  droplevels()

```

Sanity checks

After removing duplication-- should return back 0 for n>1

```{r}


data_fixed %>%
  count(id, block, trial) %>%
  filter(n > 1) %>% 
  droplevels()

unique(data_fixed$id) ## 73 subjects 

usable_subjects <- c(9  ,    12  ,   15  ,   10    , 11  ,   16    , 13  ,   17   ,  14 ,    8  ,    7 ,     3  ,    5  ,    99 ,    202  ,  203 ,   204  ,  401 ,   402 ,   403  ,  404,    405 ,   406 ,   501 ,   502 ,   503  ,  504 ,   505 ,   701  ,  702 ,   703  ,  704  ,  705 ,   706  ,  707  ,  708  ,  752 ,   750445, 75033,  800 ,   903,    904 ,   905 ,   906 ,   907 ,   908 ,   909 ,   910  ,  911  ,  912  ,  913 ,   914 ,   915,    916 ,   917  ,  918 ,   919  ,  953  ,  954 ,   958 ,   961422, 962,    963  ,  964,    965  ,  966,    967   , 968  ,  969 ,   970 ,   971  ,  974,    4    )
length(usable_subjects) # 73 subjects 


```

removing subjects below accuracy level of 80% 

```{r}


d_f <- data_fixed %>%
  mutate(error = as.numeric(as.character(error)))

str(d_f$error)

table(d_f$error) # 0 with 40814 trials and 1 with 2986 trials 

accuracy_per_subject <- d_f %>%
  group_by(id) %>%
  summarise(accuracy = 1 - mean(error, na.rm = TRUE))

# 2. See who falls below 80% accuracy:
accuracy_per_subject %>%
  filter(accuracy < 0.80) ## ids 202 and 914 have accuracy less than 80% 

# IDs below 80% accuracy
low_acc_ids <- accuracy_per_subject %>%
  filter(accuracy < 0.8) %>%
  pull(id)
low_acc_ids

d_final <- d_f %>% 
   filter(!id %in% c(202, 914)) %>% 
  droplevels()

unique(d_final$id) ## 71 subjects that are usable ## so overall- had to remove 8 subjects. 

```

###################################### Making new variables ############################################################################################################


A. making the valence of each group 

valence of current group has levels 1 and 2
valence of previous group has levels 1 and 2

- each group consists of three trials with the cycle variable as 1,2, and 3 (so first trials has cycle as 1 and the third trial has cycle as 3)
-valence of current group is 1 if dim 1 or dim 2 has the value of 4 
- valence of previous group is also 1 if dim 1 and dim 2 has the value of 4 
- if dim 1 and dim 2 have any values from 1-3, then the valence of current and previous group will be assigned as 2 

1- valence of current group


```{r}
library(dplyr)


d_final <- d_final %>%
  group_by(id, block) %>% 
  # valence of current group
  mutate(valence_current_group = if_else(dim1 == 4 | dim2 == 4, 1, 2)) # univalent is coded as 1 and bivalent is coded as 2 

names(d_final)
levels(d_final$valence_current_group) ## have to convert this to factor before analysis 

#unique(d_final$id)

```

2- valence_previous_group 
Lag by 3 trials within each subject (each group = 3 trials)

```{r}
d_final <- d_final %>%
  group_by(id, block) %>%       # only by subject
  #arrange(block, trial) %>%   
  mutate(valence_previous_group = lag(valence_current_group, 3)) %>%
  ungroup()


names(d_final)

# lag 1 
# turn all but first trial as NA
# fill will prapagate first value

```

3- switch variable 

```{r}

library(dplyr)

d_final <- d_final %>%
  group_by(id, block) %>%        
  mutate(
    switch = if_else(task != lag(task), 1, 0)  # 1 if task changed from previous trial
  ) %>%
  ungroup()

names(d_final)

```
I should also make prev_error variable before removing the first group of trials 

```{r}

library(tidyverse)

d_final <- d_final %>%
  group_by(id, block) %>%     # IMPORTANT
  mutate(prev_error = lag(error)) %>%
  ungroup()



```


have to first remove trials below the third trial of every block as they may not be in a group of three 

```{r}



d_final <- d_final %>%
  group_by(id, block) %>%          
  filter( trial>3) %>%   ## removes all the trials on each block that are less than the third trial 
  ungroup() %>%
  droplevels()


# trial != min(trial) &

##note: trial 4 of some blocks for some subjects (203,402,405,502,503,504) are being removed for d_final_analysis- is this due to trial != min(trial) & trial>3: because min trial is now 4??  so, removed trial != min(trial) and now i do have trial 4 for all the subjects. 
  
#   checking if all ids have trial 4: 

# num_id <- d_final_analysis %>% 
#  group_by(id, block) %>% 
#   filter( trial ==4)
# 
# unique(num_id$id) ## so all ids have trial == 4 for all blocks 

```


```{r}

# library(dplyr)
# 
# d_c <- data_use %>%
#   
#   # 2. Compute z-scores for reaction time
#   mutate(rt_z = scale(time)) %>%
#   
#   # 3. Remove extreme reaction times (|z| > 3)
#   filter(abs(rt_z) <= 3) %>% 
#   droplevels()




## remove first trial from eaxh bloxk after making the new variables cause it is only used for analysis 
## have not run this yet
# d_c_analysis <- data_c %>%
#   # 1. Remove the first trial of each block
#   group_by(id, block) %>%
#   filter(trial != min(trial, na.rm = TRUE)) %>%
#   ungroup() %>%


d_final_rt <- d_final

# d_final_rt %>%
#   group_by(subject) %>%   
#   filter(!(error == 1 | lead(error) == 1)) %>%
#   ungroup()

rt_estimation <- d_final_rt %>%
  filter(error == 0, prev_error == 0)

rt_stats <- rt_estimation %>%
  group_by(
    id,
    valence_current_group,
    valence_previous_group,
    cycle
  ) %>%
  summarise(
    mean_rt = mean(time, na.rm = TRUE),
    sd_rt   = sd(time, na.rm = TRUE),
    .groups = "drop"
  )

d_final_rt <- d_final_rt %>%
  left_join(
    rt_stats,
    by = c(
      "id",
      "valence_current_group",
      "valence_previous_group",
      "cycle"
    )
  )

d_final_rt <- d_final_rt %>%
  mutate(rt_z = (time - mean_rt) / sd_rt)

d_final_rt <- d_final_rt %>%
  filter(abs(rt_z) < 3)


## checking for NAs: 

sum(is.na(d_final_rt$rt_z)) # 0 

sum(is.na(d_final_rt$prev_error)) # 0 

d_final_analysis <- d_final_rt

```


No, after removing outlier trials based on rt cutoff, I have 40,454 observations of 23 variables 


```{r}

getwd()
write.csv(d_final_analysis, "/Users/nehanagarkar/Desktop/Mayr_lab/Data_analysis_project/AlternateCues/d_final_analysis.csv", row.names = FALSE)

```

######################################################################### Analysis #######################################################################

Note: 
(i)For the RT models, error trials, and trials before errors should also be removed
(ii) - using the Valence_current_group variable --> make new variable val_c_g with levels -0.5 for (Valence_current_group == 1) and + 0.5 for (Valence_current_group == 2) 
     - using the Valence_previous_group variable --> make new variable val_p_g with levels -0.5 for (Valence_previous_group == 1) and + 0.5 for Valence_previous_group == 2) 
     

Coding: 

- Switch (0 - no switch; 1 - switch) 

- Valence_current_group (-0.5 - univalent; 0.5 bivalent) - so make new variable with this 

- Valence_previous_group (-0.5 - univalent; 0.5 bivalent) - so make new variable with this 

Models: 

lmer(RT ~ Valence_current_group * Valence_previous_group*Switch + (Valence_current_group + Valence_previous_group + Switch|Subject)) 

glmer(Error ~ Valence_current_group * Valence_previous_group*Switch + (Valence_current_group + Valence_previous_group + Switch|Subject), family = “binomial”, control = glmerControl(optimizer = “bobyqa”)) 


A. New variables for valence of current and previous group according to -0.5 and +0.5 coding 


```{r}


class(d_final_analysis)

d_final_analysis$val_c_g <- ifelse(d_final_analysis$valence_current_group == 1, -0.5,
                     ifelse(d_final_analysis$valence_current_group == 2,  0.5, NA))

d_final_analysis$val_p_g <- ifelse(d_final_analysis$valence_previous_group == 1, -0.5,
                     ifelse(d_final_analysis$valence_previous_group == 2,  0.5, NA))




```

```{r}

df_models <- d_final_analysis

### DO NOT CONVERT VARIABLES THAT THE MODEL SHOULD TREAT AS FACTORS MANUALLY INTO AS FACTORS!! BECAUSE IT WILL TREAT THE VARIABLES AS DDUMMY CODING!!! 

# df_models$id <- factor(df_models$id)
# df_models$val_c_g <- factor(df_models$val_c_g)
# df_models$val_p_g <- factor(df_models$val_p_g)
# df_models$switch <- factor(df_models$switch)
# df_models$error <- factor(df_models$error)
# df_models$prev_error <- factor(df_models$prev_error)
# 
# 
# levels(df_models$id)
# levels(df_models$val_c_g)
# levels(df_models$val_p_g)
# levels(df_models$switch)
# levels(df_models$error)
# levels(df_models$prev_error)

```

c. Models 


1. lmer model

-For the RT models, error trials, and trials before errors should also be removed
Q: should it be block wise? or across all trials? 

remove  error == 0 and prev_error == 0 for the d_final_analysis inside lmer model filter()

```{r}

library(lme4)

df_models_rt <- df_models 

library(tidyverse)

df_models_rt <- df_models_rt %>%
  filter(error == 0, prev_error == 0)
  

  m_rt<- lmer(log(time) ~  val_c_g * val_p_g* switch + (val_c_g + val_p_g + switch ||  id),
                 data = df_models_rt,
                  na.action = na.exclude)
              
                # control = lmerControl(optimizer = "bobyqa"))


 
 summary(m_rt)
 
 
#library(sjPlot)
 tab_model(m_rt,show.est=T,auto.label=F,show.stat=T)
 
 
 names(df_models)
```


2. glmer model

```{r}


df_models$error <- as.factor(df_models$error)
levels(df_models$error)

  m_error<- glmer(error ~  val_c_g * val_p_g * switch + ( val_c_g +  val_p_g + switch| id),
                 data = df_models, 
                 family = "binomial",
                  na.action = na.exclude, 
                 control = glmerControl(optimizer = "bobyqa"))

 
 summary(m_error)
 
 tab_model(m_error,show.est=T,auto.label=F,show.stat=T)
```

################################################################################################################################
                                                   DDM 
#| include: false
#first putting in some pre-made functions that will go into the ezDDM analysis: 

```{r}

normWS <- function(d ,s, dv, between = NULL) { #within subject normalization
  eval(substitute(d %>%
                    dplyr::group_by(s) %>%
                    dplyr::mutate(sAV = mean(dv, na.rm = TRUE)) %>%
                    dplyr::group_by_at(between) %>% #this is grouping by between subjects variables
                    dplyr::mutate(gAV = mean(dv, na.rm = TRUE)) %>%
                    dplyr::mutate(DV_n = dv - sAV + gAV), list(s = as.name(s), dv = as.name(dv))))
}


get_ci <- function(var, mean){
  sd <- sd(var, na.rm = TRUE)
  n <- length(var)
  se <- sd/sqrt(n)
  ci <- abs(qt(0.025, n-1, lower.tail = FALSE))*se
  return(c(mean + ci, mean - ci, sd, se, n))
}

convert_extremes <- function(value){
  
  if(value == 1){
    
    value = value - 1e-5
    
  } else if (value == 0 ){
    
    value = value + 1e-5
    
  }
  
  return(value)
  
}#making sure error is either .99 or .001
```


## Aggregation and data processing

--hausekeep 

install.packages("cli")
packageVersion("cli") -- should show ≥ 3.6.5-- it is 3.6.5 
install.packages("devtools")
devtools::install_github("hauselin/hausekeep")
library(hausekeep)

```{r}
library(devtools)
library(rio)
library(hausekeep)


library(tidyverse)
alt_cue_agg_ID_ddm <- d_final_analysis %>%
  mutate(RT_s = time/1000) %>%
  group_by(id, val_c_g, val_p_g, switch, cycle) %>%
  summarize(RT_s_m = mean(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            Error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>%
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  
  unnest(ezddm)



alt_cue_agg_ddm <- alt_cue_agg_ID_ddm %>%
  group_by(id, val_c_g, val_p_g, switch, cycle) %>%
  normWS(s = "id", dv = "a") %>%
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>%
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>%
  mutate(Ter = DV_n) %>%
  group_by(val_c_g, val_p_g, switch, cycle) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[1],
            a_ci_upper = get_ci(a, a_m)[2],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[1],
            v_ci_upper = get_ci(v, v_m)[2],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[1],
            Ter_ci_upper = get_ci(Ter, Ter_m)[2],)

#make a separate object that is averaging across the no-switch 2,3 and 4 average within those and then average within those variances
alt_cue_agg_ID_ddm_collapsed <- alt_cue_agg_ID_ddm %>% 
  filter(switch == 0, cycle %in% c(2, 3)) %>%
  group_by(id, val_c_g, val_p_g) %>% 
  summarize( # average the DDM parameters across cycles 2&3 
    a = mean(a, na.rm = TRUE), 
    v = mean(v, na.rm = TRUE), #average within those 
    Ter = mean(Ter, na.rm = TRUE), 
    a_var = mean(a^2, na.rm = TRUE), #average within those variances
    v_var = mean(v^2, na.rm = TRUE), 
    Ter_var = mean(Ter^2, na.rm = TRUE), 
    .groups = "drop" )

alt_cue_agg_ID_ddm_collapsed

alt_cue_agg_ID_ddm %>% filter(switch == 0, cycle %in% c(2,3)) %>% count(id, val_c_g, val_p_g)
```



```{r}

# alt_cue_agg_ddm$is_bivalent <- ifelse(alt_cue_agg_ddm$valence_current_group == 1 , 1,
#                      ifelse(d_final_analysis$valence_current_group == 2,  2, NA))
# 
# alt_cue_agg_ddm$prev_bivalent <- ifelse(alt_cue_agg_ddm$valence_previous_group == 1, 1,
#                      ifelse(d_final_analysis$valence_previous_group == 2,  2, NA))
# 
# 
# alt_cue_agg_ID_ddm$is_bivalent <- ifelse(alt_cue_agg_ID_ddm$valence_current_group == 1 , 1,
#                      ifelse(d_final_analysis$valence_current_group == 2,  2, NA))
# 
# alt_cue_agg_ID_ddm$prev_bivalent <- ifelse(alt_cue_agg_ID_ddm$valence_previous_group == 1, 1,
#                      ifelse(d_final_analysis$valence_previous_group == 2,  2, NA))


```


## Plots

```{r}
pos <- position_dodge(width = 0.1)

alt_cue_agg_ddm$val_c_g <- as.factor(alt_cue_agg_ddm$val_c_g)
alt_cue_agg_ddm$val_p_g <- as.factor(alt_cue_agg_ddm$val_p_g)

plt_ddm_a <- ggplot(alt_cue_agg_ddm, aes(x = cycle, y = a_m, color = val_c_g, linetype = val_p_g, group = interaction(val_c_g, val_p_g)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper), width = 0.1, position = pos)+
  theme_classic()

plt_ddm_v <- ggplot(alt_cue_agg_ddm, aes(x = cycle, y = v_m, color = val_c_g, linetype = val_p_g, group = interaction(val_c_g, val_p_g)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper), width = 0.1, position = pos)+
  theme_classic()


plt_ddm_Ter <- ggplot(alt_cue_agg_ddm, aes(x = cycle, y = Ter_m, color = val_c_g, linetype = val_p_g, group = interaction(val_c_g, val_p_g)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper), width = 0.1, position = pos)+
  theme_classic()

ggpubr::ggarrange(plt_ddm_a, plt_ddm_v, plt_ddm_Ter, common.legend = TRUE, nrow = 1)  
  

```

## Statistical Models

### First prep data so that it's ignoring cycle

```{r}
alt_cue_agg_ID_ddm_nocycle <- d_final_analysis %>%
  mutate(RT_s = time/1000) %>%
  group_by(id, valence_current_group, valence_previous_group, val_c_g, val_p_g, switch) %>%
  summarize(RT_s_m = mean(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[error == 0 & prev_error == 0], na.rm = TRUE),
            Error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>%
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  unnest(ezddm)
```

### Models

```{r}

# library(sjPlot)
# library(lme4)


### all these models do not converge 


alt_cue_a <- lmer(a ~ val_c_g * val_p_g * switch + (val_c_g + val_p_g + switch|id), 
     alt_cue_agg_ID_ddm_nocycle)

#summary(alt_cue_a)
tab_model(alt_cue_a)

alt_cue_v <- lmer(v ~  val_c_g * val_p_g * switch + (val_c_g + val_p_g + switch|id), 
     alt_cue_agg_ID_ddm_nocycle)
#summary(alt_cue_v)
tab_model(alt_cue_v)


alt_cue_Ter <- lmer(Ter ~  val_c_g * val_p_g * switch + (val_c_g + val_p_g + switch|id), 
     alt_cue_agg_ID_ddm_nocycle)
#summary(alt_cue_Ter)
tab_model(alt_cue_Ter)
```




