---
title: "Alternate Runs Analysis"
author:
  - name: "Dominik Graetz"
    affiliation: "University of Oregon"
  - name: "Sophia Angleton"
    affiliation: "University of Oregon"
  - name: "Neha Nagarkar"
    affiliation: "University of Oregon"
  - name: "Ulrich Mayr"
    affiliation: "University of Oregon"
output: 
  html_document:
    code_folding: hide
    toc: true         # optional: adds a table of contents
    toc_float: true
    toc_depth: 6
    number_sections: true
date: "2026-02-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rerun_all <- 0
#https://osf.io/ywceb/overview
#https://osf.io/9bsf5/overview
library(tidyverse)
library(rio)
library(lmerTest)
library(hausekeep)
source(here::here("dominik/functions.R"))
source(here::here("theme.R"))
```

# Prep data


```{r}
#Alternate runs
alt_run <- import("data/AlternateRuns.csv")

# alt_run %>%
#   filter(id == 57) %>%
#   arrange(block, trial) %>% View()

exclude_subjects <- alt_run %>%
  filter(block != 0) %>%
  group_by(id) %>% 
  summarize(acc = mean(1-error),
            N = n())

exclude_subjects <- exclude_subjects %>%
  filter(acc < 0.8)

exclude_subjects <- c(exclude_subjects$id)


alt_run <- alt_run %>%
  group_by(id, block, trial) %>%
  slice(1) %>%
  filter(!id %in% exclude_subjects) %>%
  filter(!is.na(id)) %>%
  group_by(id, block) %>%
  mutate(cycle = ifelse(cycle > 4, cycle - 4, cycle), #transforming cycle variable to the range of 1-4
         trialgroup = ifelse(cycle == 1, 1, 0),
         trialgroup = cumsum(trialgroup),
         is_bivalent = ifelse(dim1 == 4 | dim2 == 4, 0, 1),
         is_conflict = ifelse(dim1 == dim2, 0, 1),
         prev_bivalent = lag(is_bivalent, 1),
         was_prev_error = lag(error, 1),
         prev_task = lag(task, 1),
         switch = ifelse(prev_task == task, 0, 1)) %>%
  group_by(id, block, trialgroup) %>%
  mutate(prev_bivalent = prev_bivalent[1]) %>%
  ungroup() %>%
  mutate(id = factor(id),
         prev_bivalent_contr = factor(prev_bivalent),
         prev_bivalent_eff = factor(prev_bivalent),
         is_bivalent_contr = factor(is_bivalent),
         is_bivalent_eff = factor(is_bivalent),
         cycle = factor(cycle),
         cycle_helmert = cycle,
         switch_contr = factor(switch),
         switch_eff = factor(switch)) %>%
  filter(trialgroup != 1, block != 0) %>%
  group_by(id) %>%
  mutate(trial_cont = seq(1, n()), .after = trial) %>%
  group_by(id, prev_bivalent, is_bivalent, cycle) %>%
  mutate(time_M = mean(time[error == 0 & was_prev_error == 0]),
         time_SD = sd(time[error == 0 & was_prev_error == 0]),
         time_z = (time - time_M)/time_SD,
         time_outlier = ifelse(abs(time_z) >= 3, 1, 0),
         filter_correct = ifelse(error == 1 | was_prev_error == 1, 1, 0),
         time_log = log(time))%>%
  filter(time_outlier == 0)

nrow(alt_run)
```


# Contrast coding

```{r}
contrasts(alt_run$prev_bivalent_eff) <- c(-0.5, 0.5)
contrasts(alt_run$is_bivalent_eff) <- c(-0.5, 0.5)
contrasts(alt_run$switch_eff) <- c(-0.5, 0.5) #we don't use that anywhere really
helmert <- contr.helmert(4)

helmert[,1] <- helmert[,1] %>% rev()
helmert[,2] <- helmert[,2] %>% rev()
helmert[,3] <- helmert[,3] %>% rev()

colnames(helmert) <- c("3_v_4", "2_v_34", "1_v_234")

contrasts(alt_run$cycle_helmert) <- helmert


```

```{r}

model_RT_trial <- lmer(time_log ~ poly(trial_cont, 2) + (poly(trial_cont, 2)|id), 
                       control = lmerControl(optimizer = "bobyqa"),
                       alt_run %>% 
                         filter(error == 0))

summary(model_RT_trial)

model_RT_trial %>%
  make_model_table()

alt_run <- alt_run %>%
  ungroup() %>%
  mutate(time_log_pred = predict(model_RT_trial, .)) #%>%


alt_run$time_log_res <- NA
alt_run$time_log_res[alt_run$error == 0] <- residuals(model_RT_trial)

#here i'm getting subject intercepts
model_RT_trial_ranef <- coefficients(model_RT_trial)$id %>% 
  as.data.frame() %>% 
  rownames_to_column("id") %>%
  select(id, "(Intercept)") %>%
  rename(poly_m_s_int = "(Intercept)")

alt_run <- alt_run %>%
  left_join(model_RT_trial_ranef) %>% #adding subject intercepts to the dataset to later add this
  group_by(id, block) %>%
  mutate(time_log_res_w_s_int = time_log_res + poly_m_s_int,
         lag1_time_log_res_w_s_int = lag(time_log_res_w_s_int, 1),
         lag1_time_log_res = lag(time_log_res, 1),
         lag1_time_log = lag(time_log, 1))

subs <- alt_run$id %>% unique() %>% head(5)

plt_rt_w_model <- ggplot(alt_run %>% filter(id %in% subs), aes(x = trial_cont, y = time_log, color = block, group = interaction(id, block)))+
  geom_line(alpha = 0.5, lwd = 0.3)+
  geom_smooth(se = FALSE)+
  geom_line(aes(y = time_log_pred), color = "green")+
  scale_color_viridis_c(end = 0.8)+
  facet_grid(~id)+
  labs(x = "Continuous Trial", y = "log(RT)", title = "log(RT) with trend model, by subject")+
  theme_classic()+
  theme(legend.position = "none")

plt_rt_residuals <- ggplot(alt_run %>% filter(id %in% subs), aes(x = trial_cont, y = time_log_res, color = block, group = interaction(id, block)))+
  geom_line(alpha = 0.5, lwd = 0.3)+
  geom_smooth(se = FALSE)+
  scale_color_viridis_c(end = 0.8)+
  facet_grid(~id)+
  labs(x = "Continuous Trial", y = "log(RT)", title = "Residual RTs, by subject")+
  theme_classic()+
  theme(legend.position = "none")

ggpubr::ggarrange(plt_rt_w_model, plt_rt_residuals, nrow = 2)

alt_run %>%
  group_by(id) %>%
  mutate(M_time_log_res = mean(time_log_res, na.rm = TRUE)) %>%
  ggplot()+
  geom_violin(aes(x = id, y = time_log_res))+
  geom_point(aes(x = id, y = M_time_log_res), size = 0.1)+
  theme_classic() +
  labs(x = "Subject ID",
       y = "Residual log(RT), without subject intecepts")

alt_run %>%
  group_by(id) %>%
  mutate(M_time_log_res_w_s_int = mean(time_log_res_w_s_int, na.rm = TRUE)) %>%
  ggplot()+
  geom_violin(aes(x = id, y = time_log_res_w_s_int))+
  geom_point(aes(x = id, y = M_time_log_res_w_s_int), size = 0.1)+
  theme_classic() +
  labs(x = "Subject ID",
       y = "Residual log(RT), *with* subject intecepts")

```


# Data Aggregation by cycle

```{r}
alt_run_agg_ID <- alt_run %>%
  group_by(id, is_bivalent_contr, prev_bivalent_contr, switch_contr, cycle) %>%
  summarize(RT = mean(time[filter_correct == 0], na.rm = TRUE),
            RT_log = mean(time_log[filter_correct == 0], na.rm = TRUE),
            Error = mean(error, na.rm = TRUE))

alt_run_agg <- alt_run_agg_ID %>%
  normWS(s = "id", dv = "RT") %>%
  mutate(RT = DV_n) %>%
  normWS(s = "id", dv = "RT_log") %>%
  mutate(RT_log = DV_n) %>%
  normWS(s = "id", dv = "Error") %>%
  mutate(Error = DV_n) %>%
  group_by(is_bivalent_contr, prev_bivalent_contr, switch_contr, cycle) %>%
  summarize(RT_m = mean(RT, na.rm = TRUE),
            RT_ci_lower = get_ci(RT, RT_m)[1],
            RT_ci_upper = get_ci(RT, RT_m)[2],
            RT_log_m = mean(RT_log, na.rm = TRUE),
            RT_log_ci_lower = get_ci(RT_log, RT_log_m)[1],
            RT_log_ci_upper = get_ci(RT_log, RT_log_m)[2],
            Error_m = mean(Error, na.rm = TRUE),
            Error_ci_lower = get_ci(Error, Error_m)[1],
            Error_ci_upper = get_ci(Error, Error_m)[2]
  )

alt_run_contr_agg_ID <- alt_run %>%
  group_by(id, is_bivalent_contr, prev_bivalent_contr, switch_contr) %>%
  summarize(RT = mean(time[filter_correct == 0], na.rm = TRUE),
            RT_log = mean(time_log[filter_correct == 0], na.rm = TRUE),
            Error = mean(error, na.rm = TRUE))

alt_run_contr_agg <- alt_run_agg_ID %>%
  normWS(s = "id", dv = "RT") %>%
  mutate(RT = DV_n) %>%
  normWS(s = "id", dv = "RT_log") %>%
  mutate(RT_log = DV_n) %>%
  normWS(s = "id", dv = "Error") %>%
  mutate(Error = DV_n) %>%
  group_by(is_bivalent_contr, prev_bivalent_contr, switch_contr) %>%
  summarize(RT_m = mean(RT, na.rm = TRUE),
            RT_ci_lower = get_ci(RT, RT_m)[1],
            RT_ci_upper = get_ci(RT, RT_m)[2],
            RT_log_m = mean(RT_log, na.rm = TRUE),
            RT_log_ci_lower = get_ci(RT_log, RT_log_m)[1],
            RT_log_ci_upper = get_ci(RT_log, RT_log_m)[2],
            Error_m = mean(Error, na.rm = TRUE),
            Error_ci_lower = get_ci(Error, Error_m)[1],
            Error_ci_upper = get_ci(Error, Error_m)[2]
  )



```


# Plots of correct RTs and Errors

```{r}
pos <- position_dodge(width = 0.3)

plt_rtlog_cycle <- ggplot(alt_run_agg, aes(x = cycle, y = RT_log_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = RT_log_ci_lower, ymax = RT_log_ci_upper), width = 0.1, position = pos)

plt_rt_cycle <- ggplot(alt_run_agg, aes(x = cycle, y = RT_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = RT_ci_lower, ymax = RT_ci_upper), width = 0.1, position = pos)


plt_error_cycle <- ggplot(alt_run_agg, aes(x = cycle, y = Error_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = Error_ci_lower, ymax = Error_ci_upper), width = 0.1, position = pos)

#########################

plt_rtlog_switch <- ggplot(alt_run_contr_agg, aes(x = switch_contr, y = RT_log_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = RT_log_ci_lower, ymax = RT_log_ci_upper), width = 0.1, position = pos)+
  scale_x_discrete(limits = c("1", "0"))
plt_rtlog_switch

plt_rt_switch <- ggplot(alt_run_contr_agg, aes(x = switch_contr, y = RT_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = RT_ci_lower, ymax = RT_ci_upper), width = 0.1, position = pos)+
  scale_x_discrete(limits = c("1", "0"))


plt_error_switch <- ggplot(alt_run_contr_agg, aes(x = switch_contr, y = Error_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = Error_ci_lower, ymax = Error_ci_upper), width = 0.1, position = pos)+
  scale_x_discrete(limits = c("1", "0"))


ggpubr::ggarrange(plt_rtlog_cycle, plt_rtlog_switch)
ggpubr::ggarrange(plt_rt_cycle, plt_rt_switch)
ggpubr::ggarrange(plt_error_cycle, plt_error_switch)




```

## Publication Figures

```{r}

plt_RT_log <- ggplot(alt_run_contr_agg, aes(x = switch_contr, y = RT_log_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(prev_bivalent_contr, is_bivalent_contr)))+
  geom_line(position = pos, linewidth = design$lines$linewidth)+
  geom_errorbar(aes(ymin = RT_log_ci_lower, ymax = RT_log_ci_upper), 
                width = design$errorbar$width, 
                position = pos, 
                linewidth = design$errorbar$linewidth,
                linetype = "solid")+
  scale_linetype_manual(name = "Previous Valence",
                       labels = c("0" = "Univalent",
                                  "1" = "Bivalent"),
                       values = c("0" = design$curr_val$linetype$uni,
                                 "1" = design$curr_val$linetype$bi))+
  scale_color_manual(name = "Current Valence",
                       labels = c("0" = "Univalent",
                                  "1" = "Bivalent"),
                       values = c("0" = design$curr_val$color$uni,
                                 "1" = design$curr_val$color$bi))+
  scale_x_discrete(limits = c("1", "0"), labels = c("1" = "Switch", "0" = "Repeat"))+
  labs(x = "", y = "log(RT)")+
  guides(
    linetype = guide_legend(order = 1),
    color    = guide_legend(order = 2)
  )

plt_RT_log
ggsave(plot = plt_RT_log, "figures/AR_RTlog.svg", width = 5, height = 5, units = "in")
saveRDS(plt_RT_log, "figures/AR_RTlog.RDS")

plt_Error <- ggplot(alt_run_contr_agg, aes(x = switch_contr, y = Error_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos, linewidth = design$lines$linewidth)+
  geom_errorbar(aes(ymin = Error_ci_lower, ymax = Error_ci_upper), 
                width = design$errorbar$width, 
                position = pos, 
                linewidth = design$errorbar$linewidth,
                linetype = "solid")+
  scale_color_manual(name = "Current Valence",
                       labels = c("0" = "Univalent",
                                  "1" = "Bivalent"),
                       values = c("0" = design$curr_val$color$uni,
                                 "1" = design$curr_val$color$bi))+
  scale_linetype_manual(name = "Previous Valence",
                       labels = c("0" = "Univalent",
                                  "1" = "Bivalent"),
                       values = c("0" = design$curr_val$linetype$uni,
                                 "1" = design$curr_val$linetype$bi))+
  scale_x_discrete(limits = c("1", "0"), labels = c("1" = "Switch", "0" = "Repeat"))+
  labs(x = "", y = "Errors")
plt_Error
ggsave(plot = plt_Error, "figures/AR_Errors.svg", width = 5, height = 5, units = "in")
saveRDS(plt_Error, "figures/AR_Errors.RDS")
```



# Stats: 

## RT

### Effect coded valence (-0.5, 0.5)

```{r}

alt_run_rt_log_eff <- lmer(time_log ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (is_bivalent_eff + prev_bivalent_eff + switch_contr|id), 
                           alt_run %>% 
                             filter(filter_correct == 0), 
                           control = lmerControl(optimizer = "bobyqa"))

make_model_table(alt_run_rt_log_eff)

```


### Contrast coded (0, 1)

https://stats.stackexchange.com/questions/381877/whether-to-use-factors-in-r-and-when-ordered-factors#:~:text=One%20of%20the%20categories%20is,does%20not%20cause%20any%20problem.

https://github.com/KennethEnevoldsen/Exp-Meth-III-Tutorials/issues/2

https://github.com/runehaubo/lmerTestR/issues/30

https://stats.stackexchange.com/questions/530804/sjplots-tab-model-and-summary-function-give-different-results-in-multilevel

https://stackoverflow.com/a/77664683

```{r}
alt_run_rt_log_contr <- lmer(time_log ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (is_bivalent_contr + prev_bivalent_contr + switch_contr|id), 
                             alt_run %>% 
                               filter(filter_correct == 0), 
                             control = lmerControl(optimizer = "bobyqa"))

make_model_table(alt_run_rt_log_contr)


```

## Errors

### Effect coded valence (-0.5, 0.5)

```{r}


alt_run_error_eff <- xfun::cache_rds({
  
  glmer(error ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (is_bivalent_eff + prev_bivalent_eff + switch_contr|id),
        family = "binomial",
        control = glmerControl(optimizer = "bobyqa"),
        alt_run)
}, dir = "dominik/models/", file = "alt_run_errors.RDS", rerun = rerun_all)

make_model_table(alt_run_error_eff)


```


Model figure:

```{r}
pos  = position_dodge(width = 0.3)
emmeans::emmeans(alt_run_error_eff, ~is_bivalent_eff * prev_bivalent_eff * switch_contr) %>%
  as.data.frame() %>%
  ggplot(aes(x = switch_contr, y = emmean, linetype = prev_bivalent_eff, color = is_bivalent_eff, group = interaction(prev_bivalent_eff, is_bivalent_eff)))+
  geom_line(position = pos)+
  geom_point(position = pos)+
  geom_errorbar(aes(ymin = asymp.LCL, max = asymp.UCL), position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
  theme_classic()

```



### Contrast coded (0, 1)

```{r}
alt_run_error_contr <- xfun::cache_rds({
  glmer(error ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (is_bivalent_contr + prev_bivalent_contr + switch_contr|id),
        family = "binomial",
        control = glmerControl(optimizer = "bobyqa"),
        alt_run)
  
}, dir = "dominik/models/", file = "alt_run_error_contr.RDS", rerun = rerun_all)

make_model_table(alt_run_error_contr)


```

# DDM analysis

## Aggregation and data processing


```{r}
alt_run_agg_ID_ddm <- alt_run %>%
  mutate(RT_s = time/1000) %>%
  group_by(id, is_bivalent_contr, prev_bivalent_contr, switch_contr, cycle) %>%
  summarize(RT_log =  mean(time_log[filter_correct == 0], na.rm = TRUE),
            RT_s_m = mean(RT_s[filter_correct == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[filter_correct == 0], na.rm = TRUE),
            Error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>%
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  unnest(ezddm)



alt_run_agg_ddm <- alt_run_agg_ID_ddm %>%
  group_by(id, is_bivalent_contr, prev_bivalent_contr, switch_contr, cycle) %>%
  normWS(s = "id", dv = "a") %>%
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>%
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>%
  mutate(Ter = DV_n) %>%
  group_by(is_bivalent_contr, prev_bivalent_contr, switch_contr, cycle) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[1],
            a_ci_upper = get_ci(a, a_m)[2],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[1],
            v_ci_upper = get_ci(v, v_m)[2],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[1],
            Ter_ci_upper = get_ci(Ter, Ter_m)[2],)
```



## Statistical Models

### First prep data so that it's ignoring cycle

```{r}
alt_run_agg_ID_ddm_nocycle <- alt_run %>%
  mutate(RT_s = time/1000) %>%
  group_by(id, is_bivalent_eff, is_bivalent_contr, prev_bivalent_eff, prev_bivalent_contr, switch_eff, switch_contr) %>%
  summarize(RT_log =  mean(time_log[filter_correct == 0], na.rm = TRUE),
            RT_s_m = mean(RT_s[filter_correct == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[filter_correct == 0], na.rm = TRUE),
            Error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>%
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-Error), 
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  unnest(ezddm)


alt_run_agg_ddm_nocycle <- alt_run_agg_ID_ddm_nocycle %>%
  group_by(id, is_bivalent_contr, prev_bivalent_contr, switch_contr) %>%
  normWS(s = "id", dv = "a") %>%
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>%
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>%
  mutate(Ter = DV_n) %>%
  group_by(is_bivalent_contr, prev_bivalent_contr, switch_contr) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[1],
            a_ci_upper = get_ci(a, a_m)[2],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[1],
            v_ci_upper = get_ci(v, v_m)[2],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[1],
            Ter_ci_upper = get_ci(Ter, Ter_m)[2],)


```

### Plots

```{r}
plt_ddm_a <- ggplot(alt_run_agg_ddm, aes(x = cycle, y = a_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper), width = 0.1, position = pos)+
  theme_classic()

plt_ddm_v <- ggplot(alt_run_agg_ddm, aes(x = cycle, y = v_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper), width = 0.1, position = pos)+
  theme_classic()


plt_ddm_Ter <- ggplot(alt_run_agg_ddm, aes(x = cycle, y = Ter_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper), width = 0.1, position = pos)+
  theme_classic()

#########
plt_ddm_a_nocycle <- ggplot(alt_run_agg_ddm_nocycle, aes(x = switch_contr, y = a_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper), width = 0.1, position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
  theme_classic()

plt_ddm_v_nocycle <- ggplot(alt_run_agg_ddm_nocycle, aes(x = switch_contr, y = v_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper), width = 0.1, position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
  theme_classic()


plt_ddm_Ter_nocycle <- ggplot(alt_run_agg_ddm_nocycle, aes(x = switch_contr, y = Ter_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper), width = 0.1, position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
  theme_classic()

ggpubr::ggarrange(plt_ddm_a, plt_ddm_a_nocycle,
                  plt_ddm_v, plt_ddm_v_nocycle,
                  plt_ddm_Ter, plt_ddm_Ter_nocycle, common.legend = TRUE, nrow = 3, ncol = 2)  


```

#### Publication Figures

```{r}
pos = position_dodge(0.3)
plt_ddm_a_nocycle <- ggplot(alt_run_agg_ddm_nocycle, aes(x = switch_contr, y = a_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(prev_bivalent_contr, is_bivalent_contr)))+
  geom_line(position = pos, linewidth = design$lines$linewidth)+
  geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper), 
                width = design$errorbar$width, 
                position = pos, 
                linewidth = design$errorbar$linewidth,
                linetype = "solid")+
  scale_color_manual(name = "Current Valence",
                     labels = c("0" = "Univalent",
                                "1" = "Bivalent"),
                     values = c("0" = design$curr_val$color$uni,
                                "1" = design$curr_val$color$bi))+
  scale_linetype_manual(name = "Previous Valence",
                        labels = c("0" = "Univalent",
                                   "1" = "Bivalent"),
                        values = c("0" = design$curr_val$linetype$uni,
                                   "1" = design$curr_val$linetype$bi))+
  scale_x_discrete(limits = c("1", "0"), labels = c("1" = "Switch", "0" = "Repeat"))+
  labs(x = "",
       y = "Boundary Separation\na") +
  guides(
    linetype = guide_legend(order = 1),  # appears first
    color    = guide_legend(order = 2)   # appears second
  )

plt_ddm_a_nocycle



plt_ddm_v_nocycle <- ggplot(alt_run_agg_ddm_nocycle, aes(x = switch_contr, y = v_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(prev_bivalent_contr, is_bivalent_contr)))+
  geom_line(position = pos, linewidth = design$lines$linewidth)+
  geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper), 
                width = design$errorbar$width, 
                position = pos, 
                linewidth = design$errorbar$linewidth,
                linetype = "solid")+
  scale_color_manual(name = "Current Valence",
                     labels = c("0" = "Univalent",
                                "1" = "Bivalent"),
                     values = c("0" = design$curr_val$color$uni,
                                "1" = design$curr_val$color$bi))+
  scale_linetype_manual(name = "Previous Valence",
                        labels = c("0" = "Univalent",
                                   "1" = "Bivalent"),
                        values = c("0" = design$curr_val$linetype$uni,
                                   "1" = design$curr_val$linetype$bi))+
  scale_x_discrete(limits = c("1", "0"), labels = c("1" = "Switch", "0" = "Repeat"))+
  labs(x = "",
       y = "Drift Rate\nv") +
  guides(
    linetype = guide_legend(order = 1),  # appears first
    color    = guide_legend(order = 2)   # appears second
  )
plt_ddm_v_nocycle


plt_ddm_Ter_nocycle <- ggplot(alt_run_agg_ddm_nocycle, aes(x = switch_contr, y = Ter_m, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(prev_bivalent_contr, is_bivalent_contr)))+
  geom_line(position = pos, linewidth = design$lines$linewidth)+
  geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper), 
                width = design$errorbar$width, 
                position = pos, 
                linewidth = design$errorbar$linewidth,
                linetype = "solid")+
  scale_color_manual(name = "Current Valence",
                     labels = c("0" = "Univalent",
                                "1" = "Bivalent"),
                     values = c("0" = design$curr_val$color$uni,
                                "1" = design$curr_val$color$bi))+
  scale_linetype_manual(name = "Previous Valence",
                        labels = c("0" = "Univalent",
                                   "1" = "Bivalent"),
                        values = c("0" = design$curr_val$linetype$uni,
                                   "1" = design$curr_val$linetype$bi))+
  scale_x_discrete(limits = c("1", "0"), labels = c("1" = "Switch", "0" = "Repeat")) +
  labs(x = "",
       y = "Non Reaction Time\nTer")+
  guides(
    linetype = guide_legend(order = 1),  # appears first
    color    = guide_legend(order = 2)   # appears second
  )


plt_ddm_Ter_nocycle


ggsave(plot = plt_ddm_Ter_nocycle, filename = "figures/AR_ddm_TER.svg", width = 5, height = 5, units = "in")
ggsave(plot = plt_ddm_v_nocycle, filename = "figures/AR_ddm_v.svg", width = 5, height = 5, units = "in")
ggsave(plot = plt_ddm_a_nocycle, filename = "figures/AR_ddm_a.svg", width = 5, height = 5, units = "in")

saveRDS(plt_ddm_Ter_nocycle,"figures/AR_ddm_TER.RDS")
saveRDS(plt_ddm_v_nocycle, "figures/AR_ddm_v.RDS")
saveRDS(plt_ddm_a_nocycle, "figures/AR_ddm_a.RDS")

```


### Models

#### Effect coded valence (-0.5, 0.5)

##### a

Only model that converges and is not singular is the intercept model.

```{r}
alt_run_a_eff <- lmer(a ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (prev_bivalent_eff + is_bivalent_eff + switch_contr|id),
                      control = lmerControl(optimizer = "bobyqa"),
                      alt_run_agg_ID_ddm_nocycle)

#summary(alt_run_a)
make_model_table(alt_run_a_eff)
```

This model is singular. Only the intercept only model is not singular.
```{r}

#BASELINE MODEL

alt_run_a_eff_baseline <- lmer(a ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (1|id),
                               control = lmerControl(optimizer = "bobyqa"),
                               alt_run_agg_ID_ddm_nocycle)


# MODELS WITH 1RE
alt_run_a_eff_prev_bivalent <- lmer(a ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (prev_bivalent_eff|id),
                                    control = lmerControl(optimizer = "bobyqa"),
                                    alt_run_agg_ID_ddm_nocycle)


alt_run_a_eff_is_bivalent <- lmer(a ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (is_bivalent_eff|id),
                                  control = lmerControl(optimizer = "bobyqa"),
                                  alt_run_agg_ID_ddm_nocycle)



alt_run_a_eff_switch <- lmer(a ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (switch_contr|id),
                             control = lmerControl(optimizer = "bobyqa"),
                             alt_run_agg_ID_ddm_nocycle)

# MODELS WITH 2 RE

alt_run_a_eff_switch_prev_bivalent <- lmer(a ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (switch_contr + prev_bivalent_eff|id),
                                    control = lmerControl(optimizer = "bobyqa"),
                                    alt_run_agg_ID_ddm_nocycle)


alt_run_a_eff_switch_is_bivalent <- lmer(a ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (switch_contr + is_bivalent_eff|id),
                                  control = lmerControl(optimizer = "bobyqa"),
                                  alt_run_agg_ID_ddm_nocycle)



alt_run_a_eff_is_bivalent_prev_bivalent <- lmer(a ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (prev_bivalent_eff + is_bivalent_eff|id),
                             control = lmerControl(optimizer = "bobyqa"),
                             alt_run_agg_ID_ddm_nocycle)


```

Final model:

```{r}
#final model
alt_run_a_eff_final <- alt_run_a_eff_baseline
make_model_table(alt_run_a_eff_final)
```

##### v

```{r}
alt_run_v_eff <- lmer(v ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (prev_bivalent_eff + is_bivalent_eff + switch_contr|id),
                      control = lmerControl(optimizer = "bobyqa"),
                      alt_run_agg_ID_ddm_nocycle)
#summary(alt_run_v)
make_model_table(alt_run_v_eff)
```

This model is singular. Let's check which random effects we can add.

```{r}

# BASELINE MODEL
alt_run_v_eff_baseline <- lmer(v ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (1|id),
                               control = lmerControl(optimizer = "bobyqa"),
                               alt_run_agg_ID_ddm_nocycle)


#MODELS WITH 1 RE
alt_run_v_eff_prev_bivalent <- lmer(v ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (prev_bivalent_eff|id),
                                    control = lmerControl(optimizer = "bobyqa"),
                                    alt_run_agg_ID_ddm_nocycle)


alt_run_v_eff_is_bivalent <- lmer(v ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (is_bivalent_eff|id),
                                  control = lmerControl(optimizer = "bobyqa"),
                                  alt_run_agg_ID_ddm_nocycle)

alt_run_v_eff_switch <- lmer(v ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (switch_contr|id), 
                             control = lmerControl(optimizer = "bobyqa"),
                             alt_run_agg_ID_ddm_nocycle)

# MODELS WITH 2 RE

alt_run_v_eff_switch_prev_bivalent <- lmer(v ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (switch_contr + prev_bivalent_eff|id),
                                    control = lmerControl(optimizer = "bobyqa"),
                                    alt_run_agg_ID_ddm_nocycle)


alt_run_v_eff_switch_is_bivalent <- lmer(v ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (switch_contr + is_bivalent_eff|id),
                                  control = lmerControl(optimizer = "bobyqa"),
                                  alt_run_agg_ID_ddm_nocycle)

alt_run_v_eff_prev_bivalent_is_bivalent <- lmer(v ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (prev_bivalent_eff + is_bivalent_eff|id), 
                             control = lmerControl(optimizer = "bobyqa"),
                             alt_run_agg_ID_ddm_nocycle)

AIC(alt_run_v_eff_switch_prev_bivalent, alt_run_v_eff_switch_is_bivalent)
BIC(alt_run_v_eff_switch_prev_bivalent, alt_run_v_eff_switch_is_bivalent)

```

Final model:

```{r}
alt_run_v_eff_final <- alt_run_v_eff_switch_is_bivalent

make_model_table(alt_run_v_eff_final)
```


The baseline model and the two competing 2 RE models show the same significance and direction of effects.


```{r}
emmeans::emmeans(alt_run_v_eff_final, ~ is_bivalent_eff * prev_bivalent_eff * switch_contr) %>%
  as.data.frame() %>%
  ggplot(aes(x = switch_contr, y = emmean, color = is_bivalent_eff, linetype = prev_bivalent_eff,
             group = interaction(is_bivalent_eff, prev_bivalent_eff)))+
  geom_line()


```


##### Ter

```{r}
alt_run_Ter_eff <- lmer(Ter ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (prev_bivalent_eff + is_bivalent_eff + switch_contr|id),
                        control = lmerControl(optimizer = "bobyqa"),
                        alt_run_agg_ID_ddm_nocycle)

#summary(alt_run_a)
make_model_table(alt_run_Ter_eff)

```

Ter model is singular. Adding slopes individually still results in singular models, so we stick with the intercept model.

```{r}

#BASELINE MODEL
alt_run_Ter_eff_baseline <- lmer(Ter ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (1|id),
                                 control = lmerControl(optimizer = "bobyqa"),
                                 alt_run_agg_ID_ddm_nocycle)
#MODELS WITH 1 RE

alt_run_Ter_eff_is_bivalent <- lmer(Ter ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (is_bivalent_eff|id),
                                    control = lmerControl(optimizer = "bobyqa"),
                                    alt_run_agg_ID_ddm_nocycle)

alt_run_Ter_eff_switch <- lmer(Ter ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (switch_contr|id),
                                    control = lmerControl(optimizer = "bobyqa"),
                                    alt_run_agg_ID_ddm_nocycle)

alt_run_Ter_eff_prev_bivalent <- lmer(Ter ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (prev_bivalent_eff|id),
                                    control = lmerControl(optimizer = "bobyqa"),
                                    alt_run_agg_ID_ddm_nocycle)

#MODELS WITH 2RE


alt_run_Ter_eff_switch_is_bivalent <- lmer(Ter ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (switch_contr + is_bivalent_eff|id),
                                    control = lmerControl(optimizer = "bobyqa"),
                                    alt_run_agg_ID_ddm_nocycle)

alt_run_Ter_eff_switch_prev_bivalent <- lmer(Ter ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (switch_contr + prev_bivalent_eff|id),
                                    control = lmerControl(optimizer = "bobyqa"),
                                    alt_run_agg_ID_ddm_nocycle)

alt_run_Ter_eff_prev_bivalent_is_bivalent <- lmer(Ter ~ is_bivalent_eff * prev_bivalent_eff * switch_contr + (prev_bivalent_eff + is_bivalent_eff|id),
                                    control = lmerControl(optimizer = "bobyqa"),
                                    alt_run_agg_ID_ddm_nocycle)


```

Final model: 

```{r}
alt_run_Ter_eff_final <- alt_run_Ter_eff_baseline

make_model_table(alt_run_Ter_eff_baseline)
```


#### Contrast coded (0, 1)

##### a

```{r}
alt_run_a_contr <- lmer(a ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (prev_bivalent_contr + is_bivalent_contr + switch_contr|id),
                        control = lmerControl(optimizer = "bobyqa"),
                        alt_run_agg_ID_ddm_nocycle)

make_model_table(alt_run_a_contr)
```

Singular. Let's test which random effects structure works. All of them are singular, so the intercept model wins.

```{r}

# BASELINE MODEL
alt_run_a_contr_baseline <- lmer(a ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (1|id),
                                 control = lmerControl(optimizer = "bobyqa"),
                                 alt_run_agg_ID_ddm_nocycle)

# MODELS WITH 1 RE
alt_run_a_contr_is_bivalent <- lmer(a ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (is_bivalent_contr|id),
                                    control = lmerControl(optimizer = "bobyqa"),
                                    alt_run_agg_ID_ddm_nocycle)

alt_run_a_contr_prev_bivalent <- lmer(a ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (prev_bivalent_contr|id),
                                      control = lmerControl(optimizer = "bobyqa"),
                                      alt_run_agg_ID_ddm_nocycle)


alt_run_a_contr_switch <- lmer(a ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (switch_contr|id),
                               control = lmerControl(optimizer = "bobyqa"),
                               alt_run_agg_ID_ddm_nocycle)

# MODELS 2 RE
alt_run_a_contr_switch_is_bivalent <- lmer(a ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (switch_contr + is_bivalent_contr|id),
                                    control = lmerControl(optimizer = "bobyqa"),
                                    alt_run_agg_ID_ddm_nocycle)

alt_run_a_contr_switch_prev_bivalent <- lmer(a ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (switch_contr + prev_bivalent_contr|id),
                                      control = lmerControl(optimizer = "bobyqa"),
                                      alt_run_agg_ID_ddm_nocycle)


alt_run_a_contr_is_bivalent_prev_bivalent <- lmer(a ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (is_bivalent_contr + prev_bivalent_contr|id),
                               control = lmerControl(optimizer = "bobyqa"),
                               alt_run_agg_ID_ddm_nocycle)

```

Final model: 

```{r}
alt_run_a_contr_final <- alt_run_a_contr_baseline 
make_model_table(alt_run_a_contr_final)
```

##### v

```{r}
alt_run_v_contr <- lmer(v ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (prev_bivalent_contr + is_bivalent_contr + switch_contr|id), 
                        control = lmerControl(optimizer = "bobyqa"),
                        alt_run_agg_ID_ddm_nocycle)
make_model_table(alt_run_v_contr)
```

Singular. Let's simplify.

```{r}


# BASELINE MODEL
alt_run_v_contr_baseline <- lmer(v ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (1|id), 
                                 control = lmerControl(optimizer = "bobyqa"),
                                 alt_run_agg_ID_ddm_nocycle)

# MODELS WITH 1 RE

alt_run_v_contr_is_bivalent <- lmer(v ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (is_bivalent_contr|id), 
                                    control = lmerControl(optimizer = "bobyqa"),
                                    alt_run_agg_ID_ddm_nocycle)


alt_run_v_contr_prev_bivalent <- lmer(v ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (prev_bivalent_contr|id), 
                                      control = lmerControl(optimizer = "bobyqa"),
                                      alt_run_agg_ID_ddm_nocycle)


alt_run_v_contr_switch <- lmer(v ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (switch_contr|id), 
                               control = lmerControl(optimizer = "bobyqa"),
                               alt_run_agg_ID_ddm_nocycle)


# MODELS WITH 2 RE

alt_run_v_contr_switch_is_bivalent <- lmer(v ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (switch_contr + is_bivalent_contr|id), 
                                    control = lmerControl(optimizer = "bobyqa"),
                                    alt_run_agg_ID_ddm_nocycle)


alt_run_v_contr_switch_prev_bivalent <- lmer(v ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (switch_contr + prev_bivalent_contr|id), 
                                      control = lmerControl(optimizer = "bobyqa"),
                                      alt_run_agg_ID_ddm_nocycle)


alt_run_v_contr_is_bivalent_prev_bivalent <- lmer(v ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (is_bivalent_contr + prev_bivalent_contr|id), 
                               control = lmerControl(optimizer = "bobyqa"),
                               alt_run_agg_ID_ddm_nocycle)

AIC(alt_run_v_contr_switch_is_bivalent, alt_run_v_contr_switch_prev_bivalent)
BIC(alt_run_v_contr_switch_is_bivalent, alt_run_v_contr_switch_prev_bivalent)

make_model_table(alt_run_v_contr_baseline)
make_model_table(alt_run_v_contr_switch_is_bivalent)
make_model_table(alt_run_v_contr_switch_prev_bivalent)
```


For the contrast coded version, the baseline model and the two converged/nonsingular models show different effects - the model with switch and current bivalence makes the previous bivalence X Switch interaction significant. 


Final model: 

```{r}
alt_run_v_contr_final <- alt_run_v_contr_switch_is_bivalent
make_model_table(alt_run_v_contr_final)
```

##### Ter

```{r}
alt_run_Ter_contr <- lmer(Ter ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (prev_bivalent_contr + is_bivalent_contr + switch_contr|id), 
                          control = lmerControl(optimizer = "bobyqa"),
                          alt_run_agg_ID_ddm_nocycle)
make_model_table(alt_run_Ter_contr)
```

Singular. Let's simplify. All random slope models are singular, so we go with the intercept model.


```{r}
#BASELINE MODEL
alt_run_Ter_contr_baseline <- lmer(Ter ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (1|id), 
                                   control = lmerControl(optimizer = "bobyqa"),
                                   alt_run_agg_ID_ddm_nocycle)

#MODELS WITH 1 RE
alt_run_Ter_contr_is_bivalent <- lmer(Ter ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (is_bivalent_contr|id), 
                                      control = lmerControl(optimizer = "bobyqa"),
                                      alt_run_agg_ID_ddm_nocycle)


alt_run_Ter_contr_prev_bivalent <- lmer(Ter ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (prev_bivalent_contr|id), 
                                        control = lmerControl(optimizer = "bobyqa"),
                                        alt_run_agg_ID_ddm_nocycle)

alt_run_Ter_contr_switch <- lmer(Ter ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (switch_contr|id), 
                                 control = lmerControl(optimizer = "bobyqa"),
                                 alt_run_agg_ID_ddm_nocycle)


#MODELS WITH 2 RE

alt_run_Ter_contr_switch_is_bivalent <- lmer(Ter ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (switch_contr + is_bivalent_contr|id), 
                                      control = lmerControl(optimizer = "bobyqa"),
                                      alt_run_agg_ID_ddm_nocycle)


alt_run_Ter_contr_switch_prev_bivalent <- lmer(Ter ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (switch_contr + prev_bivalent_contr|id), 
                                        control = lmerControl(optimizer = "bobyqa"),
                                        alt_run_agg_ID_ddm_nocycle)

alt_run_Ter_contr_is_bivalent_prev_bivalent <- lmer(Ter ~ is_bivalent_contr * prev_bivalent_contr * switch_contr + (is_bivalent_contr + prev_bivalent_contr|id), 
                                 control = lmerControl(optimizer = "bobyqa"),
                                 alt_run_agg_ID_ddm_nocycle)
```

Final model:

```{r}
alt_run_Ter_contr_final <- alt_run_Ter_contr_baseline
make_model_table(alt_run_Ter_contr_final)
```


# RT residual analysis

## Effect coded valence (-0.5, 0.5)

### Added subject intercepts

This model is singular.

```{r}
#For these analyses, we need to center the RTs:

alt_run <- alt_run %>%
  ungroup() %>%
  mutate(time_log_res_w_s_int_c = time_log_res_w_s_int - mean(time_log_res_w_s_int, na.rm = TRUE),
         lag1_time_log_res_w_s_int_c = lag1_time_log_res_w_s_int - mean(lag1_time_log_res_w_s_int, na.rm = TRUE))

alt_run_rt_log_resrt_eff_w_s_int <- xfun::cache_rds({
  lmer(time_log_res_w_s_int_c ~ is_bivalent_eff * prev_bivalent_eff * switch_contr * lag1_time_log_res_w_s_int_c + (is_bivalent_eff + switch_contr + prev_bivalent_eff + lag1_time_log_res_w_s_int_c | id), 
       control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_eff_w_s_int.RDS", rerun = rerun_all)

make_model_table(alt_run_rt_log_resrt_eff_w_s_int)
```

So let's check which random effects we can add.


```{r}
# BASELINE MODEL
alt_run_rt_log_resrt_eff_w_s_int_baseline <- xfun::cache_rds({
  lmer(time_log_res_w_s_int_c ~ is_bivalent_eff * prev_bivalent_eff * switch_contr * lag1_time_log_res_w_s_int_c + (lag1_time_log_res_w_s_int_c | id), 
       control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_eff_w_s_int_baseline.RDS", rerun = rerun_all)

sjPlot::tab_model(alt_run_rt_log_resrt_eff_w_s_int_baseline)

#MODELS WITH 1 RE
alt_run_rt_log_resrt_eff_w_s_int_switch <- xfun::cache_rds({
  lmer(time_log_res_w_s_int_c ~ is_bivalent_eff * prev_bivalent_eff * switch_contr * lag1_time_log_res_w_s_int_c + (lag1_time_log_res_w_s_int_c + switch_contr| id), 
       control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_eff_w_s_int_switch.RDS", rerun = rerun_all)

alt_run_rt_log_resrt_eff_w_s_int_prev_bivalent <- xfun::cache_rds({
  lmer(time_log_res_w_s_int_c ~ is_bivalent_eff * prev_bivalent_eff * switch_contr * lag1_time_log_res_w_s_int_c + (lag1_time_log_res_w_s_int_c + prev_bivalent_eff| id), 
       control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_eff_w_s_int_prev_bivalent.RDS", rerun = rerun_all)


alt_run_rt_log_resrt_eff_w_s_int_is_bivalent <- xfun::cache_rds({
  lmer(time_log_res_w_s_int_c ~ is_bivalent_eff * prev_bivalent_eff * switch_contr * lag1_time_log_res_w_s_int_c + (lag1_time_log_res_w_s_int_c + is_bivalent_eff| id), 
       control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_eff_w_s_int_is_bivalent.RDS", rerun = rerun_all)

#MODELS WITH 2 RE
alt_run_rt_log_resrt_eff_w_s_int_switch_prev_bivalent <- xfun::cache_rds({
  lmer(time_log_res_w_s_int_c ~ is_bivalent_eff * prev_bivalent_eff * switch_contr * lag1_time_log_res_w_s_int_c + 
         (lag1_time_log_res_w_s_int_c + switch_contr + prev_bivalent_eff| id), 
       control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_eff_w_s_int_switch_prev_bivalent.RDS", rerun = rerun_all)

alt_run_rt_log_resrt_eff_w_s_int_switch_is_bivalent <- xfun::cache_rds({
  lmer(time_log_res_w_s_int_c ~ is_bivalent_eff * prev_bivalent_eff * switch_contr * lag1_time_log_res_w_s_int_c + 
         (lag1_time_log_res_w_s_int_c + switch_contr + is_bivalent_eff| id), 
       control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_eff_w_s_int_switch_is_bivalent.RDS", rerun = rerun_all)


alt_run_rt_log_resrt_eff_w_s_int_prev_bivalent_is_bivalent <- xfun::cache_rds({
  lmer(time_log_res_w_s_int_c ~ is_bivalent_eff * prev_bivalent_eff * switch_contr * lag1_time_log_res_w_s_int_c + 
         (lag1_time_log_res_w_s_int_c + prev_bivalent_eff + is_bivalent_eff| id), 
       control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_eff_w_s_int_prev_bivalent_is_bivalent.RDS", rerun = rerun_all)

```


Final model: 

```{r}
alt_run_rt_log_resrt_eff_w_s_int_final <- alt_run_rt_log_resrt_eff_w_s_int_switch_prev_bivalent
make_model_table(alt_run_rt_log_resrt_eff_w_s_int_final)
```



```{r}
preds <- emmeans::emmeans(alt_run_rt_log_resrt_eff_w_s_int_final, ~ is_bivalent_eff * prev_bivalent_eff * switch_contr * lag1_time_log_res_w_s_int_c, type = "response",
                          at = list(is_bivalent_eff = factor(c(0, 1)),
                                    prev_bivalent_eff = factor(c(0, 1)),
                                    switch_contr = factor(c(0, 1)),
                                    lag1_time_log_res_w_s_int_c = c(-1.5, 1.5))) %>%
  as.data.frame() %>%
  mutate(speed = case_when(lag1_time_log_res_w_s_int_c == min(lag1_time_log_res_w_s_int_c) ~ "fast",
                           lag1_time_log_res_w_s_int_c == max(lag1_time_log_res_w_s_int_c) ~ "slow") %>% factor()) 



ggplot(preds, aes(x = switch_contr, y = emmean, color = is_bivalent_eff, linetype = prev_bivalent_eff, group = interaction(is_bivalent_eff, prev_bivalent_eff)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast")))+
  labs(title = "Model predictions for residual log RTs",
       y = "log(RT) prediction")+
  theme_classic()

```


## Contrast coded (0, 1)

### Removed subject intercepts - removed from output

```{r eval=FALSE}


alt_run_rt_log_resrt_contr <- xfun::cache_rds({
  lmer(time_log_res ~ is_bivalent_contr * prev_bivalent_contr * switch_contr * lag1_time_log_res + (is_bivalent_contr + prev_bivalent_contr + switch_contr + lag1_time_log_res |id), control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_contr.RDS", rerun = rerun_all)



make_model_table(alt_run_rt_log_resrt_contr)

preds <- emmeans::emmeans(alt_run_rt_log_resrt_contr, ~ is_bivalent_contr * prev_bivalent_contr * switch_contr * lag1_time_log_res, type = "response",
                          at = list(is_bivalent_contr = factor(c(0, 1)),
                                    prev_bivalent_contr = factor(c(0, 1)),
                                    switch_contr = factor(c(0, 1)),
                                    lag1_time_log_res = c(-1.5, 1.5))) %>%
  as.data.frame() %>%
  mutate(speed = case_when(lag1_time_log_res == min(lag1_time_log_res) ~ "fast",
                           lag1_time_log_res == max(lag1_time_log_res) ~ "slow") %>% factor()) 



ggplot(preds, aes(x = switch_contr, y = emmean, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast")))+
  labs(title = "Model predictions for residual log RTs",
       y = "log(RT) prediction")+
  theme_classic()

```



### Added subject intercepts

Convergence problems. Let's simplify!

```{r}

#BASELINE MODEL

alt_run_rt_log_resrt_contr_w_s_int <- xfun::cache_rds({
  lmer(time_log_res_w_s_int_c ~ is_bivalent_contr * prev_bivalent_contr * switch_contr * lag1_time_log_res_w_s_int_c + (lag1_time_log_res_w_s_int_c | id), 
       control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_contr_w_s_int.RDS", rerun = rerun_all)

make_model_table(alt_run_rt_log_resrt_contr_w_s_int)
```



```{r}

#this model is singular
alt_run_rt_log_resrt_contr_w_s_int_switch_is_bivalent <- xfun::cache_rds({
  lmer(time_log_res_w_s_int_c ~ is_bivalent_contr * prev_bivalent_contr * switch_contr * lag1_time_log_res_w_s_int_c + 
         (lag1_time_log_res_w_s_int_c + switch_contr + is_bivalent_contr| id), 
       control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_contr_w_s_int_switch_is_bivalent.RDS", rerun = rerun_all)


alt_run_rt_log_resrt_contr_w_s_int_switch_prev_bivalent <- xfun::cache_rds({
  lmer(time_log_res_w_s_int_c ~ is_bivalent_contr * prev_bivalent_contr * switch_contr * lag1_time_log_res_w_s_int_c + 
         (lag1_time_log_res_w_s_int_c + switch_contr + prev_bivalent_contr| id), 
       control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_contr_w_s_int_switch_prev_bivalent.RDS", rerun = rerun_all)


alt_run_rt_log_resrt_contr_w_s_int_prev_bivalent_is_bivalent <- xfun::cache_rds({
  lmer(time_log_res_w_s_int_c ~ is_bivalent_contr * prev_bivalent_contr * switch_contr * lag1_time_log_res_w_s_int_c + 
         (lag1_time_log_res_w_s_int_c + prev_bivalent_contr + is_bivalent_contr| id), 
       control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_contr_w_s_int_prev_bivalent_is_bivalent.RDS", rerun = rerun_all)



```



Final model: 

```{r}
alt_run_rt_log_resrt_contr_w_s_int_final <- alt_run_rt_log_resrt_contr_w_s_int_switch_prev_bivalent
make_model_table(alt_run_rt_log_resrt_contr_w_s_int_final)
```


```{r}
preds <- emmeans::emmeans(alt_run_rt_log_resrt_contr_w_s_int_final, ~ is_bivalent_contr * prev_bivalent_contr * switch_contr * lag1_time_log_res_w_s_int_c, type = "response",
                          at = list(is_bivalent_contr = factor(c(0, 1)),
                                    prev_bivalent_contr = factor(c(0, 1)),
                                    switch_contr = factor(c(0, 1)),
                                    lag1_time_log_res_w_s_int_c = c(-1.5, 1.5))) %>%
  as.data.frame() %>%
  mutate(speed = case_when(lag1_time_log_res_w_s_int_c == min(lag1_time_log_res_w_s_int_c) ~ "fast",
                           lag1_time_log_res_w_s_int_c == max(lag1_time_log_res_w_s_int_c) ~ "slow") %>% factor()) 



ggplot(preds, aes(x = switch_contr, y = emmean, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast")))+
  labs(title = "Model predictions for residual log RTs",
       y = "log(RT) prediction")+
  theme_classic()

```

#### Publication Figure

```{r}
 

plt_RTlog <- ggplot(preds, aes(x = switch_contr, y = emmean, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(prev_bivalent_contr, is_bivalent_contr)))+
  geom_line(position = pos, linewidth = design$lines$linewidth)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), 
                width = design$errorbar$width, 
                position = pos, 
                linewidth = design$errorbar$linewidth,
                linetype = "solid")+
  scale_color_manual(name = "Current Valence",
                     labels = c("0" = "Univalent",
                                "1" = "Bivalent"),
                     values = c("0" = design$curr_val$color$uni,
                                "1" = design$curr_val$color$bi))+
  scale_linetype_manual(name = "Previous Valence",
                        labels = c("0" = "Univalent",
                                   "1" = "Bivalent"),
                        values = c("0" = design$curr_val$linetype$uni,
                                   "1" = design$curr_val$linetype$bi))+
  scale_x_discrete(limits = c("1", "0"), labels = c("1" = "Switch", "0" = "Repeat"))+
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast")))+
  labs(x = "", y = "log(RT) prediction")+
  guides(
    linetype = guide_legend(order = 1),  # appears first
    color    = guide_legend(order = 2)   # appears second
  )

plt_RTlog
ggsave(plot = plt_RTlog, "figures/AR_lagRT.svg", height = 5, width = 7.5, units = "in")
saveRDS(plt_RTlog, "figures/AR_lagRT.RDS")
  
```


## Helmert-coded cycle variable (we decided to skip!)

### Effect coded valence (-0.5, 0.5)

#### Removed subject intercepts

```{r eval = FALSE}


alt_run_rt_log_resrt_prev_helmert_eff <- xfun::cache_rds({
  lmer(time_log_res ~ is_bivalent_eff * prev_bivalent_eff * lag1_time_log_res * cycle_helmert + (is_bivalent_eff + prev_bivalent_eff + lag1_time_log_res + cycle_helmert | id), control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_prev_helmert_eff.RDS", rerun = rerun_all)



make_model_table(alt_run_rt_log_resrt_prev_helmert_eff)

preds <- emmeans::emmeans(alt_run_rt_log_resrt_prev_helmert_eff, ~ is_bivalent_eff * prev_bivalent_eff * lag1_time_log_res * cycle_helmert, type = "response",
                          at = list(is_bivalent_eff = factor(c(0, 1)),
                                    prev_bivalent_eff = factor(c(0, 1)),
                                    cycle_helmert = factor(c(1, 2, 3)),
                                    lag1_time_log_res = c(-1.5, 1.5))) %>%
  as.data.frame() %>%
  mutate(speed = case_when(lag1_time_log_res == min(lag1_time_log_res) ~ "fast",
                           lag1_time_log_res == max(lag1_time_log_res) ~ "slow") %>% factor()) 



ggplot(preds, aes(x = cycle_helmert, y = emmean, color = is_bivalent_eff, linetype = prev_bivalent_eff, group = interaction(is_bivalent_eff, prev_bivalent_eff)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = pos)+
  #scale_x_discrete(limits = c("1", "0"))+
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast")))+
  labs(title = "Model predictions for residual log RTs",
       y = "log(RT) prediction")+
  theme_classic()



```


#### Added subject intercepts


```{r eval = FALSE}

alt_run_rt_log_resrt_prev_helmert_eff_w_s_int <- xfun::cache_rds({
  lmer(time_log_res_w_s_int_c ~ is_bivalent_eff * prev_bivalent_eff * lag1_time_log_res_w_s_int_c * cycle_helmert + (is_bivalent_eff + prev_bivalent_eff + lag1_time_log_res_w_s_int_c + cycle_helmert | id), control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_prev_helmert_eff_w_s_int.RDS", rerun = rerun_all)

make_model_table(alt_run_rt_log_resrt_prev_helmert_eff_w_s_int)

preds <- emmeans::emmeans(alt_run_rt_log_resrt_prev_helmert_eff_w_s_int, ~ is_bivalent_eff * prev_bivalent_eff * lag1_time_log_res_w_s_int_c * cycle_helmert, type = "response",
                          at = list(is_bivalent_eff = factor(c(0, 1)),
                                    prev_bivalent_eff = factor(c(0, 1)),
                                    cycle_helmert = factor(c(1, 2, 3)),
                                    lag1_time_log_res_w_s_int_c = c(-1.5, 1.5))) %>%
  as.data.frame() %>%
  mutate(speed = case_when(lag1_time_log_res_w_s_int_c == min(lag1_time_log_res_w_s_int_c) ~ "fast",
                           lag1_time_log_res_w_s_int_c == max(lag1_time_log_res_w_s_int_c) ~ "slow") %>% factor()) 



ggplot(preds, aes(x = cycle_helmert, y = emmean, color = is_bivalent_eff, linetype = prev_bivalent_eff, group = interaction(is_bivalent_eff, prev_bivalent_eff)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = pos)+
  #scale_x_discrete(limits = c("1", "0"))+
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast")))+
  labs(title = "Model predictions for residual log RTs",
       y = "log(RT) prediction")+
  theme_classic()



```


### contrast coded valence (0, 1)

#### Removed subject intercepts

```{r eval = FALSE}


alt_run_rt_log_resrt_prev_helmert_contr <- xfun::cache_rds({
  lmer(time_log_res ~ is_bivalent_contr * prev_bivalent_contr * lag1_time_log_res * cycle_helmert + (is_bivalent_contr + prev_bivalent_contr + lag1_time_log_res + cycle_helmert | id), control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
  
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_prev_helmert_contr.RDS", rerun = rerun_all)


make_model_table(alt_run_rt_log_resrt_prev_helmert_contr)



preds <- emmeans::emmeans(alt_run_rt_log_resrt_prev_helmert_contr, ~ is_bivalent_contr * prev_bivalent_contr * cycle_helmert * lag1_time_log_res, type = "response",
                          at = list(is_bivalent_contr = factor(c(0, 1)),
                                    prev_bivalent_contr = factor(c(0, 1)),
                                    cycle_helmert = factor(c(1, 2, 3)),
                                    lag1_time_log_res = c(-1.5, 1.5))) %>%
  as.data.frame() %>%
  mutate(speed = case_when(lag1_time_log_res == min(lag1_time_log_res) ~ "fast",
                           lag1_time_log_res == max(lag1_time_log_res) ~ "slow") %>% factor()) 



ggplot(preds, aes(x = cycle_helmert, y = emmean, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = pos)+
  #scale_x_discrete(limits = c("1", "0"))+
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast")))+
  labs(title = "Model predictions for residual log RTs",
       y = "log(RT) prediction")+
  theme_classic()



```


#### Added subject intercepts

```{r eval = FALSE}

alt_run_rt_log_resrt_prev_helmert_contr_w_s_int <- xfun::cache_rds({
  lmer(time_log_res_w_s_int_c ~ is_bivalent_contr * prev_bivalent_contr * lag1_time_log_res_w_s_int_c * cycle_helmert + (is_bivalent_contr + prev_bivalent_contr + lag1_time_log_res_w_s_int_c + cycle_helmert | id), control = lmerControl(optimizer = "bobyqa"),
       alt_run %>% 
         filter(filter_correct == 0))
}, dir = "dominik/models/", file = "alt_run_rt_log_resrt_prev_helmert_contr_w_s_int.RDS", rerun = rerun_all)


make_model_table(alt_run_rt_log_resrt_prev_helmert_contr_w_s_int)



preds <- emmeans::emmeans(alt_run_rt_log_resrt_prev_helmert_contr_w_s_int, ~ is_bivalent_contr * prev_bivalent_contr * cycle_helmert * lag1_time_log_res_w_s_int_c, type = "response",
                          at = list(is_bivalent_contr = factor(c(0, 1)),
                                    prev_bivalent_contr = factor(c(0, 1)),
                                    cycle_helmert = factor(c(1, 2, 3)),
                                    lag1_time_log_res_w_s_int_c = c(-1.5, 1.5))) %>%
  as.data.frame() %>%
  mutate(speed = case_when(lag1_time_log_res_w_s_int_c == min(lag1_time_log_res_w_s_int_c) ~ "fast",
                           lag1_time_log_res_w_s_int_c == max(lag1_time_log_res_w_s_int_c) ~ "slow") %>% factor()) 



ggplot(preds, aes(x = cycle_helmert, y = emmean, color = is_bivalent_contr, linetype = prev_bivalent_contr, group = interaction(is_bivalent_contr, prev_bivalent_contr)))+
  geom_line(position = pos)+
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = pos)+
  #scale_x_discrete(limits = c("1", "0"))+
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast")))+
  labs(title = "Model predictions for residual log RTs",
       y = "log(RT) prediction")+
  theme_classic()



```


# Individual differences analysis


```{r}
alt_run_indiv <- alt_run_agg_ID_ddm_nocycle %>% 
  pivot_wider(id_cols = id, names_from = c(is_bivalent_contr, prev_bivalent_contr, switch_contr), 
              values_from = c(v, a, Ter, RT_log, Error), 
              names_glue = "{.value}_s{switch_contr}_cbiv{is_bivalent_contr}_lbiv{prev_bivalent_contr}") %>% 
  ungroup() %>%
  mutate(v_s0_cbiv0_lbiv0_NA = ifelse(Ter_s0_cbiv0_lbiv0 < 0, NA, v_s0_cbiv0_lbiv0),
         v_s0_cbiv0_lbiv1_NA = ifelse(Ter_s0_cbiv0_lbiv1 < 0, NA, v_s0_cbiv0_lbiv1),
         v_s0_cbiv1_lbiv0_NA = ifelse(Ter_s0_cbiv1_lbiv0 < 0, NA, v_s0_cbiv1_lbiv0),
         v_s0_cbiv1_lbiv1_NA = ifelse(Ter_s0_cbiv1_lbiv1 < 0, NA, v_s0_cbiv1_lbiv1),
         v_s1_cbiv0_lbiv0_NA = ifelse(Ter_s1_cbiv0_lbiv0 < 0, NA, v_s1_cbiv0_lbiv0),
         v_s1_cbiv0_lbiv1_NA = ifelse(Ter_s1_cbiv0_lbiv1 < 0, NA, v_s1_cbiv0_lbiv1),
         v_s1_cbiv1_lbiv0_NA = ifelse(Ter_s1_cbiv1_lbiv0 < 0, NA, v_s1_cbiv1_lbiv0),
         v_s1_cbiv1_lbiv1_NA = ifelse(Ter_s1_cbiv1_lbiv1 < 0, NA, v_s1_cbiv1_lbiv1))



alt_run_agg_ID_ddm_nocycle %>%
  ggplot(aes(x = Ter))+
  geom_histogram()+
  geom_vline(xintercept = 0)+
  theme_classic()

alt_run_agg_ID_ddm_nocycle %>%
  ungroup() %>%
  summarize(N = n(),
            neg_ter = sum(Ter < 0),
            p_neg_Ter = neg_ter/N,
            subjects_w_any_neg_Ter = length(unique(id[Ter < 0])))


alt_run_indiv <- alt_run_indiv %>%
  mutate(across(!id, ~ as.vector(scale(.x))))
```


## Models

```{r}
alt_run_indiv_diff_models <- list(
  RT = list(
    uu0 = lm(RT_log_s1_cbiv0_lbiv0 ~ 1, alt_run_indiv),
    uu1 = lm(RT_log_s1_cbiv0_lbiv0 ~ RT_log_s0_cbiv0_lbiv0, alt_run_indiv),
    uu2 = lm(RT_log_s1_cbiv0_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1, alt_run_indiv),
    uu3 = lm(RT_log_s1_cbiv0_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0, alt_run_indiv),
    uu4 = lm(RT_log_s1_cbiv0_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0 + RT_log_s0_cbiv1_lbiv1, alt_run_indiv),
    
    bu0 = lm(RT_log_s1_cbiv1_lbiv0 ~ 1, alt_run_indiv),
    bu1 = lm(RT_log_s1_cbiv1_lbiv0 ~ RT_log_s0_cbiv0_lbiv0, alt_run_indiv),
    bu2 = lm(RT_log_s1_cbiv1_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1, alt_run_indiv),
    bu3 = lm(RT_log_s1_cbiv1_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0, alt_run_indiv),
    bu4 = lm(RT_log_s1_cbiv1_lbiv0 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0 + RT_log_s0_cbiv1_lbiv1, alt_run_indiv),
    
    ub0 = lm(RT_log_s1_cbiv0_lbiv1 ~ 1, alt_run_indiv),
    ub1 = lm(RT_log_s1_cbiv0_lbiv1 ~ RT_log_s0_cbiv0_lbiv0, alt_run_indiv),
    ub2 = lm(RT_log_s1_cbiv0_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1, alt_run_indiv),
    ub3 = lm(RT_log_s1_cbiv0_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0, alt_run_indiv),
    ub4 = lm(RT_log_s1_cbiv0_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0 + RT_log_s0_cbiv1_lbiv1, alt_run_indiv),
    
    bb0 = lm(RT_log_s1_cbiv1_lbiv1 ~ 1, alt_run_indiv),
    bb1 = lm(RT_log_s1_cbiv1_lbiv1 ~ RT_log_s0_cbiv0_lbiv0, alt_run_indiv),
    bb2 = lm(RT_log_s1_cbiv1_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1, alt_run_indiv),
    bb3 = lm(RT_log_s1_cbiv1_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0, alt_run_indiv),
    bb4 = lm(RT_log_s1_cbiv1_lbiv1 ~ RT_log_s0_cbiv0_lbiv0 + RT_log_s0_cbiv0_lbiv1 + RT_log_s0_cbiv1_lbiv0 + RT_log_s0_cbiv1_lbiv1, alt_run_indiv)
  ),
  
  
  Error = list(
    uu1 = lm(Error_s1_cbiv0_lbiv0 ~ 1, alt_run_indiv),
    uu1 = lm(Error_s1_cbiv0_lbiv0 ~ Error_s0_cbiv0_lbiv0, alt_run_indiv),
    uu2 = lm(Error_s1_cbiv0_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1, alt_run_indiv),
    uu3 = lm(Error_s1_cbiv0_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0, alt_run_indiv),
    uu4 = lm(Error_s1_cbiv0_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0 + Error_s0_cbiv1_lbiv1, alt_run_indiv),
    
    bu0 = lm(Error_s1_cbiv1_lbiv0 ~ 1, alt_run_indiv),
    bu1 = lm(Error_s1_cbiv1_lbiv0 ~ Error_s0_cbiv0_lbiv0, alt_run_indiv),
    bu2 = lm(Error_s1_cbiv1_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1, alt_run_indiv),
    bu3 = lm(Error_s1_cbiv1_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0, alt_run_indiv),
    bu4 = lm(Error_s1_cbiv1_lbiv0 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0 + Error_s0_cbiv1_lbiv1, alt_run_indiv),
    
    ub0 = lm(Error_s1_cbiv0_lbiv1 ~ 1, alt_run_indiv),
    ub1 = lm(Error_s1_cbiv0_lbiv1 ~ Error_s0_cbiv0_lbiv0, alt_run_indiv),
    ub2 = lm(Error_s1_cbiv0_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1, alt_run_indiv),
    ub3 = lm(Error_s1_cbiv0_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0, alt_run_indiv),
    ub4 = lm(Error_s1_cbiv0_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0 + Error_s0_cbiv1_lbiv1, alt_run_indiv),
    
    bb0 = lm(Error_s1_cbiv1_lbiv1 ~ 1, alt_run_indiv),
    bb1 = lm(Error_s1_cbiv1_lbiv1 ~ Error_s0_cbiv0_lbiv0, alt_run_indiv),
    bb2 = lm(Error_s1_cbiv1_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1, alt_run_indiv),
    bb3 = lm(Error_s1_cbiv1_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0, alt_run_indiv),
    bb4 = lm(Error_s1_cbiv1_lbiv1 ~ Error_s0_cbiv0_lbiv0 + Error_s0_cbiv0_lbiv1 + Error_s0_cbiv1_lbiv0 + Error_s0_cbiv1_lbiv1, alt_run_indiv)
  ),
  
  v = list(
    
    uu0 = lm(v_s1_cbiv0_lbiv0 ~ 1, alt_run_indiv),
    uu1 = lm(v_s1_cbiv0_lbiv0 ~ v_s0_cbiv0_lbiv0, alt_run_indiv),
    uu2 = lm(v_s1_cbiv0_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1, alt_run_indiv),
    uu3 = lm(v_s1_cbiv0_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0, alt_run_indiv),
    uu4 = lm(v_s1_cbiv0_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0 + v_s0_cbiv1_lbiv1, alt_run_indiv),
    
    bu0 = lm(v_s1_cbiv1_lbiv0 ~ 1, alt_run_indiv),
    bu1 = lm(v_s1_cbiv1_lbiv0 ~ v_s0_cbiv0_lbiv0, alt_run_indiv),
    bu2 = lm(v_s1_cbiv1_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1, alt_run_indiv),
    bu3 = lm(v_s1_cbiv1_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0, alt_run_indiv),
    bu4 = lm(v_s1_cbiv1_lbiv0 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0 + v_s0_cbiv1_lbiv1, alt_run_indiv),
    
    ub0 = lm(v_s1_cbiv0_lbiv1 ~ 1, alt_run_indiv),
    ub1 = lm(v_s1_cbiv0_lbiv1 ~ v_s0_cbiv0_lbiv0, alt_run_indiv),
    ub2 = lm(v_s1_cbiv0_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1, alt_run_indiv),
    ub3 = lm(v_s1_cbiv0_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0, alt_run_indiv),
    ub4 = lm(v_s1_cbiv0_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0 + v_s0_cbiv1_lbiv1, alt_run_indiv),
    
    bb0 = lm(v_s1_cbiv1_lbiv1 ~ 1, alt_run_indiv),
    bb1 = lm(v_s1_cbiv1_lbiv1 ~ v_s0_cbiv0_lbiv0, alt_run_indiv),
    bb2 = lm(v_s1_cbiv1_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1, alt_run_indiv),
    bb3 = lm(v_s1_cbiv1_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0, alt_run_indiv),
    bb4 = lm(v_s1_cbiv1_lbiv1 ~ v_s0_cbiv0_lbiv0 + v_s0_cbiv0_lbiv1 + v_s0_cbiv1_lbiv0 + v_s0_cbiv1_lbiv1, alt_run_indiv)
  ),
  v_NA = list(
    
    uu0 = lm(v_s1_cbiv0_lbiv0_NA ~ 1, alt_run_indiv),
    uu1 = lm(v_s1_cbiv0_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA, alt_run_indiv),
    uu2 = lm(v_s1_cbiv0_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA, alt_run_indiv),
    uu3 = lm(v_s1_cbiv0_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA, alt_run_indiv),
    uu4 = lm(v_s1_cbiv0_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA + v_s0_cbiv1_lbiv1_NA, alt_run_indiv),
    
    bu0 = lm(v_s1_cbiv1_lbiv0_NA ~ 1, alt_run_indiv),
    bu1 = lm(v_s1_cbiv1_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA, alt_run_indiv),
    bu2 = lm(v_s1_cbiv1_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA, alt_run_indiv),
    bu3 = lm(v_s1_cbiv1_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA, alt_run_indiv),
    bu4 = lm(v_s1_cbiv1_lbiv0_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA + v_s0_cbiv1_lbiv1_NA, alt_run_indiv),
    
    ub0 = lm(v_s1_cbiv0_lbiv1_NA ~ 1, alt_run_indiv),
    ub1 = lm(v_s1_cbiv0_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA, alt_run_indiv),
    ub2 = lm(v_s1_cbiv0_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA, alt_run_indiv),
    ub3 = lm(v_s1_cbiv0_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA, alt_run_indiv),
    ub4 = lm(v_s1_cbiv0_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA + v_s0_cbiv1_lbiv1_NA, alt_run_indiv),
    
    bb0 = lm(v_s1_cbiv1_lbiv1_NA ~ 1, alt_run_indiv),
    bb1 = lm(v_s1_cbiv1_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA, alt_run_indiv),
    bb2 = lm(v_s1_cbiv1_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA, alt_run_indiv),
    bb3 = lm(v_s1_cbiv1_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA, alt_run_indiv),
    bb4 = lm(v_s1_cbiv1_lbiv1_NA ~ v_s0_cbiv0_lbiv0_NA + v_s0_cbiv0_lbiv1_NA + v_s0_cbiv1_lbiv0_NA + v_s0_cbiv1_lbiv1_NA, alt_run_indiv)
  )
)

summary(alt_run_indiv_diff_models$RT$uu4)

```




## RT

```{r}

RT_comparisons <- lapply(c("uu", "bu", "ub", "bb"), function(x){
  
  data.frame(model = compare_models(alt_run_indiv_diff_models$RT, x)$model_names,
             comparison_p = compare_models(alt_run_indiv_diff_models$RT, x)$comparison$`Pr(>F)`)
  
}) %>%
  bind_rows() %>%
  mutate(comparison_sig = ifelse(comparison_p < 0.05, 1, 0))


alt_run_RT_model_summary <- lapply(alt_run_indiv_diff_models$RT, function(x){
  m_sum <- x %>% 
    summary() 
  
  m_sum %>% 
    coef() %>% 
    as.data.frame() %>%
    mutate(r_sq = m_sum$r.squared,
           r_sq_adj = m_sum$adj.r.squared)
  
  
}) %>% 
  bind_rows(.id = "model") %>% 
  rownames_to_column("coefficient") %>%
  janitor::clean_names() %>%
  left_join(RT_comparisons) %>%
  filter(!grepl("(Intercept)", coefficient)) %>%
  mutate(coefficient = gsub("\\...[[:digit:]]+", "", coefficient),
         coefficient = gsub("RT_log_", "", coefficient),
         outcome = gsub("[[:digit:]]", "", model),
         outcome = factor(outcome, levels = c("uu", "ub", "bu", "bb")),
         is_sig = ifelse(pr_t < 0.05, 1, 0),
         # r_label = as.character(round(r_sq, 2)),
         # r_label = gsub("^0.", ".", r_label),
         r_label = sprintf("%.2f", r_sq),
         r_label = case_when(comparison_sig == 1 ~ paste0(r_label, "*"), .default = r_label),
         r_adj_label = sprintf("%.2f", r_sq_adj),
         r_adj_label = case_when(comparison_sig == 1 ~ paste0(r_adj_label, "*"), .default = r_adj_label),
         color = parse_number(model) %>% factor())


n = 4
plt_betw_RT <- ggplot(alt_run_RT_model_summary, aes(x = coefficient, y = estimate, group = model, color = color))+ 
  geom_hline(yintercept = 0, linetype = "dotted")+
  geom_ribbon(aes(ymin = estimate - std_error,
                  ymax = estimate + std_error), alpha = 0.1, color = NA)+
  geom_line()+
  # geom_text(data = alt_run_RT_model_summary %>% group_by(model) %>% slice(n()),
  #           aes(label = r_adj_label), hjust = -0.3)+
  geom_label(data = alt_run_RT_model_summary %>% group_by(model) %>% slice(n()),
            aes(label = r_adj_label), hjust = -0.1, alpha = 0.8, label.size = 0)+
  geom_point(data = alt_run_RT_model_summary %>% filter(is_sig == 1), pch = "*", size = 10)+
   labs(x = "",
       y = "")+
  facet_wrap(~outcome, labeller = labeller(outcome = c("uu" = "Switch: Uni-Uni",
                                                       "ub" = "Switch: Uni-Bi",
                                                       "bu" = "Switch: Bi-Uni",
                                                       "bb" = "Switch: Bi-Bi")), ncol = 1)+
  scale_color_manual(values = colorRampPalette(c("blue", "red"))(n))+
  scale_x_discrete(labels = c("s0_cbiv0_lbiv1" = "Bi-Uni",
                              "s0_cbiv1_lbiv1" = "Bi-Bi",
                              "s0_cbiv0_lbiv0" = "Uni-Uni",
                              "s0_cbiv1_lbiv0" = "Uni-Bi",
                              "(Intercept)" = "Int"))+
  coord_cartesian(xlim = c(1, 4.5))+
  theme(legend.position = "none")

plt_betw_RT
ggsave(plot = plt_betw_RT, "figures/AR_betw_RT.svg", width = 4, height = 6, units = "in")
saveRDS(plt_betw_RT, file = "figures/AR_betw_RT.RDS")
```


### Model comp: univalent - univalent

```{r}
compare_models(alt_run_indiv_diff_models$RT, "uu")$comparison
```

### Model comp: univalent - bivalent


```{r}
compare_models(alt_run_indiv_diff_models$RT, "ub")$comparison
```

### Model comp: bivalent - univalent

```{r}
compare_models(alt_run_indiv_diff_models$RT, "bu")$comparison
```

### Model comp: bivalent - bivalent


```{r}
compare_models(alt_run_indiv_diff_models$RT, "bb")$comparison
```

## Error

```{r}


Error_comparisons <- lapply(c("uu", "bu", "ub", "bb"), function(x){
  
  data.frame(model = compare_models(alt_run_indiv_diff_models$Error, x)$model_names,
             comparison_p = compare_models(alt_run_indiv_diff_models$Error, x)$comparison$`Pr(>F)`)
  
}) %>%
  bind_rows() %>%
  mutate(comparison_sig = ifelse(comparison_p < 0.05, 1, 0))


alt_run_Error_model_summary <- lapply(alt_run_indiv_diff_models$Error, function(x){
  m_sum <- x %>% 
    summary() 
  
  m_sum %>% 
    coef() %>% 
    as.data.frame() %>%
    mutate(r_sq = m_sum$r.squared,
           r_sq_adj = m_sum$adj.r.squared)
}) %>% 
  bind_rows(.id = "model") %>% 
  rownames_to_column("coefficient") %>%
  janitor::clean_names() %>%
  left_join(Error_comparisons) %>%
  filter(!grepl("(Intercept)", coefficient)) %>%
  mutate(coefficient = gsub("\\...[[:digit:]]+", "", coefficient),
         coefficient = gsub("RT_log_", "", coefficient),
         outcome = gsub("[[:digit:]]", "", model),
         outcome = factor(outcome, levels = c("uu", "ub", "bu", "bb")),
         is_sig = ifelse(pr_t < 0.05, 1, 0),
         # r_label = as.character(round(r_sq, 2)),
         # r_label = gsub("^0.", ".", r_label),
         r_label = sprintf("%.2f", r_sq),
         r_label = case_when(comparison_sig == 1 ~ paste0(r_label, "*"), .default = r_label),
         r_adj_label = sprintf("%.2f", r_sq_adj),
         r_adj_label = case_when(comparison_sig == 1 ~ paste0(r_adj_label, "*"), .default = r_adj_label),
         color = parse_number(model) %>% factor())


ggplot(alt_run_Error_model_summary, aes(x = coefficient, y = estimate, group = model, color = model))+ 
  geom_hline(yintercept = 0, linetype = "dotted")+
  geom_ribbon(aes(ymin = estimate - std_error,
                  ymax = estimate + std_error), alpha = 0.1, color = NA)+
  geom_line()+
  geom_text(data = alt_run_Error_model_summary %>% group_by(model) %>% slice(n()),
            aes(label = r_adj_label), hjust = -0.3)+
  geom_point(data = alt_run_Error_model_summary %>% filter(is_sig == 1), pch = "*", size = 10)+
  theme_classic()+
  facet_wrap(~outcome, labeller = labeller(outcome = c("uu" = "uni-uni",
                                                       "ub" = "uni-bi",
                                                       "bu" = "bi-uni",
                                                       "bb" = "bi-bi")), ncol = 1)+
  scale_x_discrete(labels = c("Error_s0_cbiv0_lbiv1" = "NS\nL-bi\nC-uni",
                              "Error_s0_cbiv1_lbiv1" = "NS\nL-bi\nC-bi",
                              "Error_s0_cbiv0_lbiv0" = "NS\nL-uni\nC-uni",
                              "Error_s0_cbiv1_lbiv0" = "NS\nL-uni\nC-bi",
                              "(Intercept)" = "Int"))+
  coord_cartesian(xlim = c(1, 5.5))+
  theme(legend.position = "none")



plt_betw_Error <- ggplot(alt_run_Error_model_summary, aes(x = coefficient, y = estimate, group = model, color = color))+ 
  geom_hline(yintercept = 0, linetype = "dotted")+
  geom_ribbon(aes(ymin = estimate - std_error,
                  ymax = estimate + std_error), alpha = 0.1, color = NA)+
  geom_line()+
  # geom_text(data = alt_run_Error_model_summary %>% group_by(model) %>% slice(n()),
  #           aes(label = r_adj_label), hjust = -0.3)+
  geom_label(data = alt_run_Error_model_summary %>% group_by(model) %>% slice(n()),
            aes(label = r_adj_label), hjust = -0.1, alpha = 0.8, label.size = 0)+
  geom_point(data = alt_run_Error_model_summary %>% filter(is_sig == 1), pch = "*", size = 10)+
   labs(x = "",
       y = "")+
  facet_wrap(~outcome, labeller = labeller(outcome = c("uu" = "Switch: Uni-Uni",
                                                       "ub" = "Switch: Uni-Bi",
                                                       "bu" = "Switch: Bi-Uni",
                                                       "bb" = "Switch: Bi-Bi")), ncol = 1)+
  scale_color_manual(values = colorRampPalette(c("blue", "red"))(n))+
  scale_x_discrete(labels = c("Error_s0_cbiv0_lbiv1" = "Bi-Uni",
                              "Error_s0_cbiv1_lbiv1" = "Bi-Bi",
                              "Error_s0_cbiv0_lbiv0" = "Uni-Uni",
                              "Error_s0_cbiv1_lbiv0" = "Uni-Bi",
                              "(Intercept)" = "Int"))+
  coord_cartesian(xlim = c(1, 4.5))+
  theme(legend.position = "none")
plt_betw_Error

ggsave(plot= plt_betw_Error, "figures/AR_betw_Error.svg", width = 4, height = 6, units = "in")
saveRDS(plt_betw_Error, "figures/AR_betw_Error.RDS")

```


### Model comp: univalent - univalent

```{r}
compare_models(alt_run_indiv_diff_models$Error, "uu")$comparison
```

### Model comp: univalent - bivalent


```{r}
compare_models(alt_run_indiv_diff_models$Error, "ub")$comparison
```

### Model comp: bivalent - univalent

```{r}
compare_models(alt_run_indiv_diff_models$Error, "bu")$comparison
```

### Model comp: bivalent - bivalent


```{r}
compare_models(alt_run_indiv_diff_models$Error, "bb")$comparison
```



## v

```{r}

v_comparisons <- lapply(c("uu", "bu", "ub", "bb"), function(x){
  
  data.frame(model = compare_models(alt_run_indiv_diff_models$v, x)$model_names,
             comparison_p = compare_models(alt_run_indiv_diff_models$v, x)$comparison$`Pr(>F)`)
  
}) %>%
  bind_rows() %>%
  mutate(comparison_sig = ifelse(comparison_p < 0.05, 1, 0))



alt_run_v_model_summary <- lapply(alt_run_indiv_diff_models$v, function(x){
  m_sum <- x %>% 
    summary() 
  
  m_sum %>% 
    coef() %>% 
    as.data.frame() %>%
    mutate(r_sq = m_sum$r.squared,
           r_sq_adj = m_sum$adj.r.squared)
}) %>% 
  bind_rows(.id = "model") %>% 
  rownames_to_column("coefficient") %>%
  janitor::clean_names() %>%
  left_join(v_comparisons) %>%
  filter(!grepl("(Intercept)", coefficient)) %>%
  mutate(coefficient = gsub("\\...[[:digit:]]+", "", coefficient),
         coefficient = gsub("RT_log_", "", coefficient),
         outcome = gsub("[[:digit:]]", "", model),
         outcome = factor(outcome, levels = c("uu", "ub", "bu", "bb")),
         is_sig = ifelse(pr_t < 0.05, 1, 0),
         # r_label = as.character(round(r_sq, 2)),
         # r_label = gsub("^0.", ".", r_label),
         r_label = sprintf("%.2f", r_sq),
         r_label = case_when(comparison_sig == 1 ~ paste0(r_label, "*"), .default = r_label),
         r_adj_label = sprintf("%.2f", r_sq_adj),
         r_adj_label = case_when(comparison_sig == 1 ~ paste0(r_adj_label, "*"), .default = r_adj_label),
         color = parse_number(model) %>% factor())


ggplot(alt_run_v_model_summary, aes(x = coefficient, y = estimate, group = model, color = model))+ 
  geom_hline(yintercept = 0, linetype = "dotted")+
  geom_ribbon(aes(ymin = estimate - std_error,
                  ymax = estimate + std_error), alpha = 0.1, color = NA)+
  geom_line()+
  geom_text(data = alt_run_v_model_summary %>% group_by(model) %>% slice(n()),
            aes(label = r_adj_label), hjust = -0.3)+
  geom_point(data = alt_run_v_model_summary %>% filter(is_sig == 1), pch = "*", size = 10)+
  theme_classic()+
  facet_wrap(~outcome, labeller = labeller(outcome = c("uu" = "Switch: Uni-Uni",
                                                       "ub" = "Switch: Uni-Bi",
                                                       "bu" = "Switch: Bi-Uni",
                                                       "bb" = "Switch: Bi-Bi")), ncol = 1)+
  scale_x_discrete(labels = c("v_s0_cbiv0_lbiv1" = "NS\nL-bi\nC-uni",
                              "v_s0_cbiv1_lbiv1" = "NS\nL-bi\nC-bi",
                              "v_s0_cbiv0_lbiv0" = "NS\nL-uni\nC-uni",
                              "v_s0_cbiv1_lbiv0" = "NS\nL-uni\nC-bi",
                              "(Intercept)" = "Int"))+
  coord_cartesian(xlim = c(1, 5.5))+
  theme(legend.position = "none")

plt_betw_v <- ggplot(alt_run_v_model_summary, aes(x = coefficient, y = estimate, group = model, color = color))+ 
  geom_hline(yintercept = 0, linetype = "dotted")+
  geom_ribbon(aes(ymin = estimate - std_error,
                  ymax = estimate + std_error), alpha = 0.1, color = NA)+
  geom_line()+
  # geom_text(data = alt_run_v_model_summary %>% group_by(model) %>% slice(n()),
  #           aes(label = r_adj_label), hjust = -0.3)+
  geom_label(data = alt_run_v_model_summary %>% group_by(model) %>% slice(n()),
            aes(label = r_adj_label), hjust = -0.1, alpha = 0.8, label.size = 0)+
  geom_point(data = alt_run_v_model_summary %>% filter(is_sig == 1), pch = "*", size = 10)+
  labs(x = "",
       y = "")+
  facet_wrap(~outcome, labeller = labeller(outcome = c("uu" = "Switch: Uni-Uni",
                                                       "ub" = "Switch: Uni-Bi",
                                                       "bu" = "Switch: Bi-Uni",
                                                       "bb" = "Switch: Bi-Bi")), ncol = 1)+
  scale_color_manual(values = colorRampPalette(c("blue", "red"))(n))+
  scale_x_discrete(labels = c("v_s0_cbiv0_lbiv1" = "Bi-Uni",
                              "v_s0_cbiv1_lbiv1" = "Bi-Bi",
                              "v_s0_cbiv0_lbiv0" = "Uni-Uni",
                              "v_s0_cbiv1_lbiv0" = "Uni-Bi",
                              "(Intercept)" = "Int"))+
  coord_cartesian(xlim = c(1, 4.5))+
  theme(legend.position = "none")

plt_betw_v

ggsave(plot = plt_betw_v, "figures/AR_betw_v.svg", width = 4, height = 6, units = "in")
saveRDS(plt_betw_v, "figures/AR_betw_v.RDS")

```




### Model comp: univalent - univalent

```{r}
compare_models(alt_run_indiv_diff_models$v, "uu")$comparison
```

### Model comp: univalent - bivalent


```{r}
compare_models(alt_run_indiv_diff_models$v, "ub")$comparison
```

### Model comp: bivalent - univalent

```{r}
compare_models(alt_run_indiv_diff_models$v, "bu")$comparison
```

### Model comp: bivalent - bivalent


```{r}
compare_models(alt_run_indiv_diff_models$v, "bb")$comparison
```



## v NA

```{r}


alt_run_v_NA_model_summary <- lapply(alt_run_indiv_diff_models$v_NA, function(x){
  m_sum <- x %>% 
    summary() 
  
  m_sum %>% 
    coef() %>% 
    as.data.frame() %>%
    mutate(r_sq = m_sum$r.squared,
           r_sq_adj = m_sum$adj.r.squared)
  
}) %>% 
  bind_rows(.id = "model") %>% 
  rownames_to_column("coefficient") %>%
  janitor::clean_names() %>%
  mutate(coefficient = gsub("\\...[[:digit:]]+", "", coefficient),
         coefficient = gsub("v_", "", coefficient),
         coefficient = gsub("_NA", "", coefficient),
         outcome = gsub("[[:digit:]]", "", model),
         outcome = factor(outcome, levels = c("uu", "ub", "bu", "bb")),
         is_sig = ifelse(pr_t < 0.05, 1, 0),
         r_label = as.character(round(r_sq, 2)),
         r_label = gsub("^0.", ".", r_label),
         r_adj_label = as.character(round(r_sq_adj, 2)),
         r_adj_label = gsub("^0.", ".", r_adj_label),
         outcome = factor(outcome, levels = c("uu", "ub", "bu", "bb")),
         color = parse_number(model) %>% factor())


ggplot(alt_run_v_NA_model_summary, aes(x = coefficient, y = estimate, group = model, color = model))+ 
  geom_hline(yintercept = 0, linetype = "dotted")+
  geom_ribbon(aes(ymin = estimate - std_error,
                  ymax = estimate + std_error), alpha = 0.1, color = NA)+
  geom_line()+
  geom_text(data = alt_run_v_NA_model_summary %>% group_by(model) %>% slice(n()),
            aes(label = r_adj_label), hjust = -0.3)+
  geom_point(data = alt_run_v_NA_model_summary %>% filter(is_sig == 1), pch = "*", size = 10)+
  theme_classic()+
  facet_wrap(~outcome, labeller = labeller(outcome = c("uu" = "uni-uni",
                                                       "ub" = "uni-bi",
                                                       "bu" = "bi-uni",
                                                       "bb" = "bi-bi")), nrow = 1)+
  scale_x_discrete(labels = c("s0_cbiv0_lbiv1" = "NS\nL-bi\nC-uni",
                              "s0_cbiv1_lbiv1" = "NS\nL-bi\nC-bi",
                              "s0_cbiv0_lbiv0" = "NS\nL-uni\nC-uni",
                              "s0_cbiv1_lbiv0" = "NS\nL-uni\nC-bi",
                              "(Intercept)" = "Int"))+
  coord_cartesian(xlim = c(1, 5.5))+
  theme(legend.position = "none")




# compare_models(alt_run_indiv_diff_models$v_NA, "uu")
# compare_models(alt_run_indiv_diff_models$v_NA, "ub")
# compare_models(alt_run_indiv_diff_models$v_NA, "bu")
# compare_models(alt_run_indiv_diff_models$v_NA, "bb")

```

```{r}

```

