---
title: "SEM"
output: html_document
date: "2026-06-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(lmerTest)
library(tidyverse)
library(lavaan)
library(hausekeep)
library(semPlot)
library(tidySEM)
library(ggcorrplot)
```


```{r}
alt_cue <- readRDS("dominik/file_outputs/alt_cue_cleaned.RDS") 
alt_run <- readRDS("dominik/file_outputs/alt_run_cleaned.RDS")

alt_cue <- alt_cue %>%
  mutate(id = paste0("AC_", id),
         Experiment = "AC")

alt_run <- alt_run %>%
  mutate(id = paste0("AR_", id),
         Experiment = "AR")


```

# Prepping datasets

```{r}
set.seed(419)

alt_run <- alt_run %>%
  group_by(id, task) %>%
  mutate(N_total = n(),
         sem_group = sample(rep_len(c("A", "B", "C"), n())))

alt_cue <- alt_cue %>%
  group_by(id, task) %>%
  mutate(N_total = n(),
         sem_group = sample(rep_len(c("A", "B", "C"), n())))
 

```


# Calculating Stats and ddm parameters

```{r}
source("dominik/functions.R")
alt_run_ddm <- alt_run %>%
  mutate(RT_s = time/1000) %>%
  group_by(id, is_bivalent_contr, prev_bivalent_contr, switch_contr, sem_group) %>%
  summarize(RT_log = mean(time_log[filter_correct == 0], na.rm = TRUE),
            RT_s_m = mean(RT_s[filter_correct == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[filter_correct == 0], na.rm = TRUE),
            N_trials_total = n(),
            N_trials_forRT = sum(filter_correct == 0),
            Error = mean(error, na.rm = TRUE)) %>%
  rowwise() 


alt_cue_ddm <- alt_cue %>%
  mutate(RT_s = time/1000) %>%
  group_by(id, is_bivalent_contr, prev_bivalent_contr, switch_contr, sem_group) %>%
  summarize(RT_log = mean(time_log[filter_correct == 0], na.rm = TRUE),
            RT_s_m = mean(RT_s[filter_correct == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[filter_correct == 0], na.rm = TRUE),
            N_trials_total = n(),
            N_trials_forRT = sum(filter_correct == 0),
            Error = mean(error, na.rm = TRUE)) %>%
  rowwise() 


```


Let's just look at correlations between groups

```{r}
alt_run_ddm_wider <- alt_run_ddm %>%
  pivot_wider(names_from = sem_group, values_from = c(RT_log, RT_s_m, RT_s_var, Error, N_trials_total, N_trials_forRT))

alt_cue_ddm_wider <- alt_cue_ddm %>%
  pivot_wider(names_from = sem_group, values_from = c(RT_log, RT_s_m, RT_s_var, Error, N_trials_total, N_trials_forRT))

#correlations across "groups"
cor(alt_run_ddm_wider$RT_log_A, alt_run_ddm_wider$RT_log_B, use = "pairwise.complete.obs")
cor(alt_run_ddm_wider$RT_log_A, alt_run_ddm_wider$RT_log_C, use = "pairwise.complete.obs")
cor(alt_run_ddm_wider$RT_log_B, alt_run_ddm_wider$RT_log_C, use = "pairwise.complete.obs")

cor(alt_run_ddm_wider$RT_s_m_A, alt_run_ddm_wider$RT_s_m_B, use = "pairwise.complete.obs")
cor(alt_run_ddm_wider$RT_s_m_A, alt_run_ddm_wider$RT_s_m_C, use = "pairwise.complete.obs")
cor(alt_run_ddm_wider$RT_s_m_B, alt_run_ddm_wider$RT_s_m_C, use = "pairwise.complete.obs")

#cor(alt_run_ddm_wider$v_A, alt_run_ddm_wider$v_B, use = "pairwise.complete.obs")
#cor(alt_run_ddm_wider$v_A, alt_run_ddm_wider$v_C, use = "pairwise.complete.obs")
#cor(alt_run_ddm_wider$v_B, alt_run_ddm_wider$v_C, use = "pairwise.complete.obs")


# set dv here; can be RT_log, Error, v, a, Ter
dv <- as.name("RT_log")


#pivot to wide format
alt_run_sem <- alt_run_ddm %>%
  mutate(dv = !!dv) %>%
  select(id, sem_group, is_bivalent_contr, prev_bivalent_contr, switch_contr, dv) %>%
   pivot_wider(id_cols = id, names_from = c(sem_group, is_bivalent_contr, prev_bivalent_contr, switch_contr), 
              values_from = c(dv), 
              names_glue = "g{sem_group}_s{switch_contr}_lbi{prev_bivalent_contr}_cbi{is_bivalent_contr}")

colnames(alt_run_sem) <- case_when(grepl("gA_s0_lbi0_cbi0", colnames(alt_run_sem)) ~ "ARUU",
                                   grepl("gB_s0_lbi0_cbi0", colnames(alt_run_sem)) ~ "BRUU",
                                   grepl("gC_s0_lbi0_cbi0", colnames(alt_run_sem)) ~ "CRUU",
                                   grepl("gA_s0_lbi1_cbi0", colnames(alt_run_sem)) ~ "ARBU",
                                   grepl("gB_s0_lbi1_cbi0", colnames(alt_run_sem)) ~ "BRBU",
                                   grepl("gC_s0_lbi1_cbi0", colnames(alt_run_sem)) ~ "CRBU",
                                   grepl("gA_s0_lbi0_cbi1", colnames(alt_run_sem)) ~ "ARUB",
                                   grepl("gB_s0_lbi0_cbi1", colnames(alt_run_sem)) ~ "BRUB",
                                   grepl("gC_s0_lbi0_cbi1", colnames(alt_run_sem)) ~ "CRUB",
                                   grepl("gA_s0_lbi1_cbi1", colnames(alt_run_sem)) ~ "ARBB",
                                   grepl("gB_s0_lbi1_cbi1", colnames(alt_run_sem)) ~ "BRBB",
                                   grepl("gC_s0_lbi1_cbi1", colnames(alt_run_sem)) ~ "CRBB",
                                   grepl("gA_s1_lbi0_cbi0", colnames(alt_run_sem)) ~ "ASUU",
                                   grepl("gB_s1_lbi0_cbi0", colnames(alt_run_sem)) ~ "BSUU",
                                   grepl("gC_s1_lbi0_cbi0", colnames(alt_run_sem)) ~ "CSUU",
                                   grepl("gA_s1_lbi1_cbi0", colnames(alt_run_sem)) ~ "ASBU",
                                   grepl("gB_s1_lbi1_cbi0", colnames(alt_run_sem)) ~ "BSBU",
                                   grepl("gC_s1_lbi1_cbi0", colnames(alt_run_sem)) ~ "CSBU",
                                   grepl("gA_s1_lbi0_cbi1", colnames(alt_run_sem)) ~ "ASUB",
                                   grepl("gB_s1_lbi0_cbi1", colnames(alt_run_sem)) ~ "BSUB",
                                   grepl("gC_s1_lbi0_cbi1", colnames(alt_run_sem)) ~ "CSUB",
                                   grepl("gA_s1_lbi1_cbi1", colnames(alt_run_sem)) ~ "ASBB",
                                   grepl("gB_s1_lbi1_cbi1", colnames(alt_run_sem)) ~ "BSBB",
                                   grepl("gC_s1_lbi1_cbi1", colnames(alt_run_sem)) ~ "CSBB",
                                   .default = colnames(alt_run_sem))



alt_cue_sem <- alt_cue_ddm %>%
  mutate(dv = !!dv) %>%
  select(id, sem_group, is_bivalent_contr, prev_bivalent_contr, switch_contr, dv) %>%
   pivot_wider(id_cols = id, names_from = c(sem_group, is_bivalent_contr, prev_bivalent_contr, switch_contr), 
              values_from = c(dv), 
              names_glue = "g{sem_group}_s{switch_contr}_lbi{prev_bivalent_contr}_cbi{is_bivalent_contr}")

colnames(alt_cue_sem) <- case_when(grepl("gA_s0_lbi0_cbi0", colnames(alt_cue_sem)) ~ "ARUU",
                                   grepl("gB_s0_lbi0_cbi0", colnames(alt_cue_sem)) ~ "BRUU",
                                   grepl("gC_s0_lbi0_cbi0", colnames(alt_cue_sem)) ~ "CRUU",
                                   grepl("gA_s0_lbi1_cbi0", colnames(alt_cue_sem)) ~ "ARBU",
                                   grepl("gB_s0_lbi1_cbi0", colnames(alt_cue_sem)) ~ "BRBU",
                                   grepl("gC_s0_lbi1_cbi0", colnames(alt_cue_sem)) ~ "CRBU",
                                   grepl("gA_s0_lbi0_cbi1", colnames(alt_cue_sem)) ~ "ARUB",
                                   grepl("gB_s0_lbi0_cbi1", colnames(alt_cue_sem)) ~ "BRUB",
                                   grepl("gC_s0_lbi0_cbi1", colnames(alt_cue_sem)) ~ "CRUB",
                                   grepl("gA_s0_lbi1_cbi1", colnames(alt_cue_sem)) ~ "ARBB",
                                   grepl("gB_s0_lbi1_cbi1", colnames(alt_cue_sem)) ~ "BRBB",
                                   grepl("gC_s0_lbi1_cbi1", colnames(alt_cue_sem)) ~ "CRBB",
                                   grepl("gA_s1_lbi0_cbi0", colnames(alt_cue_sem)) ~ "ASUU",
                                   grepl("gB_s1_lbi0_cbi0", colnames(alt_cue_sem)) ~ "BSUU",
                                   grepl("gC_s1_lbi0_cbi0", colnames(alt_cue_sem)) ~ "CSUU",
                                   grepl("gA_s1_lbi1_cbi0", colnames(alt_cue_sem)) ~ "ASBU",
                                   grepl("gB_s1_lbi1_cbi0", colnames(alt_cue_sem)) ~ "BSBU",
                                   grepl("gC_s1_lbi1_cbi0", colnames(alt_cue_sem)) ~ "CSBU",
                                   grepl("gA_s1_lbi0_cbi1", colnames(alt_cue_sem)) ~ "ASUB",
                                   grepl("gB_s1_lbi0_cbi1", colnames(alt_cue_sem)) ~ "BSUB",
                                   grepl("gC_s1_lbi0_cbi1", colnames(alt_cue_sem)) ~ "CSUB",
                                   grepl("gA_s1_lbi1_cbi1", colnames(alt_cue_sem)) ~ "ASBB",
                                   grepl("gB_s1_lbi1_cbi1", colnames(alt_cue_sem)) ~ "BSBB",
                                   grepl("gC_s1_lbi1_cbi1", colnames(alt_cue_sem)) ~ "CSBB",
                                   .default = colnames(alt_cue_sem))
colnames(alt_cue_sem)
```

## Correlation matrices

```{r}
#this is the order for ggplot correlation matrices

my_order <- c("ARUU", "BRUU", "CRUU",
              "ARBU", "BRBU", "CRBU",
              "ARUB", "BRUB", "CRUB",
              "ARBB", "BRBB", "CRBB",
              "ASUU", "BSUU", "CSUU",
              "ASBU", "BSBU", "CSBU",
              "ASUB", "BSUB", "CSUB",
              "ASBB", "BSBB", "CSBB")



alt_run_cmat <- cor(alt_run_sem %>% 
                      ungroup() %>% 
                      select(-id),
                    use = "pairwise.complete.obs")
alt_run_cmat <- alt_run_cmat[my_order, my_order]

ggcorrplot(alt_run_cmat,
           type = "lower",
           lab  = TRUE, lab_size = 2.5,
           hc.order = F,
           colors = c("#2166AC", "white", "#B2182B"), show.diag = TRUE) + 
  theme_classic()+
  theme(axis.text.x = element_text(size = 7, angle = 35, hjust = 1),
        axis.title = element_blank())+
  labs(title = "Alt Run")

alt_cue_cmat <- cor(alt_cue_sem %>% 
                      ungroup() %>% 
                      select(-id),
                    use = "pairwise.complete.obs")
alt_cue_cmat <- alt_cue_cmat[my_order, my_order]

ggcorrplot(alt_cue_cmat,
           type = "lower",
           lab  = TRUE, lab_size = 2.5,
           hc.order = F,
           colors = c("#2166AC", "white", "#B2182B"), show.diag = TRUE) + 
  theme_classic()+
  theme(axis.text.x = element_text(size = 7, angle = 35, hjust = 1),
        axis.title = element_blank())+
  labs(title = "Alt Cue")

all_data_sem <- bind_rows(alt_run_sem, alt_cue_sem)



all_data_cmat <- cor(all_data_sem %>% 
                      ungroup() %>% 
                      select(-id),
                    use = "pairwise.complete.obs")
all_data_cmat <- all_data_cmat[my_order, my_order]

ggcorrplot(all_data_cmat,
           type = "lower",
           lab  = TRUE, lab_size = 2.5,
           hc.order = F,
           colors = c("#2166AC", "white", "#B2182B"), show.diag = TRUE) + 
  theme_classic()+
  theme(axis.text.x = element_text(size = 7, angle = 35, hjust = 1),
        axis.title = element_blank())+
  labs(title = "All Data")

```

# SEM



## Full model with separate nested factor both for repeat and switch. Shows that thes all can be established and that repeat and switch factors on the same level correlate positively with each other.  This could be due to shared conflict demand variance across repeat and switch, which is why we then also need to do common conflict demand factors across repeat and switch.

```{r}


rs_model <- '
Spd =~ a*ARUU + a*BRUU + a*CRUU + 
       a*ARUB + a*BRUB + a*CRUB +
       a*ARBU + a*BRBU + a*CRBU + 
       a*ARBB + a*BRBB + a*CRBB +
       a*ASUU + a*BSUU + a*CSUU + 
       a*ASUB + a*BSUB + a*CSUB +
       a*ASBU + a*BSBU + a*CSBU + 
       a*ASBB + a*BSBB + a*CSBB
       

S =~ b*ASUU + b*BSUU + b*CSUU + 
     b*ASUB + b*BSUB + b*CSUB +
     b*ASBU + b*BSBU + b*CSBU + 
     b*ASBB + b*BSBB + b*CSBB

RPC =~ c*ARBU + c*BRBU + c*CRBU +
       c*ARBB + c*BRBB + c*CRBB
       
RCC =~ d*ARUB + d*BRUB + d*CRUB + 
       d*ARBB + d*BRBB + d*CRBB
       
RPCC =~ ARBB + BRBB + CRBB

SPC =~ f*ASBU + f*BSBU + f*CSBU +
       f*ASBB + f*BSBB + f*CSBB
       
SCC =~g*ASUB + g*BSUB + g*CSUB +
       g*ASBB + g*BSBB + g*CSBB


SPCC =~ ASBB + BSBB + CSBB 

Spd ~~ S + 0*RPC + 0*RCC + 0*RPCC + 0*SPC + 0*SCC + 0*SPCC
S ~~ + 0*RPC + 0*RCC + 0*RPCC + 0*SPC + 0*SCC + 0*SPCC
RPC ~~ 0*RCC + 0*RPCC
RCC ~~ 0*RPCC
SPC ~~ 0*SCC + 0*SPCC
SCC ~~ 0*SPCC

SPC ~~ RPC + 0*RCC + 0*RPCC
SCC ~~ 0*RPC + RCC + 0*RPCC
SPCC ~~ 0*RPC + 0*RCC + RPCC



'


cfa_full_model2 <- cfa(rs_model, data = alt_run_sem, estimator = "MLM", std.lv = TRUE)
summary(cfa_full_model2, standardized=TRUE, fit.measures=TRUE, rsquare=TRUE)

anova(cfa_full_model, cfa_full_model2)


layout <- matrix(NA, ncol = 24, nrow = 8)
layout[1, 1] <- "R"
layout[2, 3] <- "RPC"
layout[1, 9] <- "RCC"
layout[2, 11] <- "RPCC"
layout[4, 1:12] <- c("ARUU",
                     "BRUU",
                     "CRUU",
                     "ARBU",
                     "BRBU",
                     "CRBU",
                     "BRUB",
                     "CRUB",
                     "ARUB",
                     "ARBB",
                     "BRBB",
                     "CRBB")
layout[8, 4] <- "Spd"

layout[2, 15] <- "S"
layout[3, 20] <- "SPC"
layout[4, 22] <- "SCC"
layout[5, 24] <- "SPCC"
layout[6, 11:22] <- c("ASUU",
                      "BSUU",
                      "CSUU",
                      "ASBU",
                      "BSBU",
                      "CSBU",
                      "BSUB",
                      "CSUB",
                      "ASUB",
                      "ASBB",
                      "BSBB",
                      "CSBB")


graph_data <- prepare_graph(cfa_full_model2, layout = layout)
plot(graph_data)

edges(graph_data) <- edges(graph_data) %>% 
  mutate(label = est_sig_std,
         label = gsub("0\\.", ".", label),
         label = gsub("\\*", "", label),
         show = ifelse(est == "0.00", FALSE, show),
         #show = ifelse(est == "1.00", FALSE, show),
         connect_from = ifelse(from %in% c("R", "RPC", "RCC", "RPCC", "S", "SPC", "SCC", "SPCC") & to %in% colnames(alt_run_sem), "bottom", connect_from),
         connect_to   = ifelse(from %in% c("R", "RPC", "RCC", "RPCC", "S", "SPC", "SCC", "SPCC") & to %in% colnames(alt_run_sem), "top", connect_to),
         connect_from = ifelse(from %in% c("R", "RPC", "RCC", "RPCC", "S", "SPC", "SCC", "SPCC") & from == to, "top", connect_from),
         connect_to   = ifelse(from %in% c("R", "RPC", "RCC", "RPCC", "S", "SPC", "SCC", "SPCC") & from == to, "top", connect_to),
         connect_from = ifelse(from %in% c("Spd") & from == to, "bottom", connect_from),
         connect_to   = ifelse(from %in% c("Spd") & from == to, "bottom", connect_to),
         connect_from = ifelse(from %in% c("Spd") & to %in% colnames(alt_run_sem), "top", connect_from),
         connect_to   = ifelse(from %in% c("Spd") & to %in% colnames(alt_run_sem), "bottom", connect_to),
         connect_from = ifelse(from %in% colnames(alt_run_sem) & to %in% colnames(alt_run_sem), "bottom", connect_from),
         connect_to = ifelse(from %in% colnames(alt_run_sem) & to %in% colnames(alt_run_sem), "bottom", connect_to))

plot(graph_data)
ggsave("dominik/d_figs/sem.svg", width = 60, height = 30, units = "cm")



```




## Full model with common nested factors:  testing for fixed loadings across repeat and switch.  This first tests whether common factors can be estahished, but does not yet include nested switch factors.
```{r}


rs_model <- '
Spd =~ a*ARUU + a*BRUU + a*CRUU + 
       a*ARUB + a*BRUB + a*CRUB +
       a*ARBU + a*BRBU + a*CRBU + 
       a*ARBB + a*BRBB + a*CRBB +
       a*ASUU + a*BSUU + a*CSUU + 
       a*ASUB + a*BSUB + a*CSUB +
       a*ASBU + a*BSBU + a*CSBU + 
       a*ASBB + a*BSBB + a*CSBB
       

S =~ b*ASUU + b*BSUU + b*CSUU + 
     b*ASUB + b*BSUB + b*CSUB +
     b*ASBU + b*BSBU + b*CSBU + 
     b*ASBB + b*BSBB + b*CSBB

RPC =~ c*ARBU + c*BRBU + c*CRBU +
       c*ARBB + c*BRBB + c*CRBB +
       c*ASBU + c*BSBU + c*CSBU +
       c*ASBB + c*BSBB + c*CSBB
       
RCC =~ d*ARUB + d*BRUB + d*CRUB + 
       d*ARBB + d*BRBB + d*CRBB +
       d*ASUB + d*BSUB + d*CSUB +
       d*ASBB + d*BSBB + d*CSBB
       
RPCC =~ h*ARBB + h*BRBB + h*CRBB +
        h2*ASBB + h2*BSBB + h2*CSBB 



Spd ~~ S + 0*RPC + 0*RCC + 0*RPCC 
S ~~   0*RPC + 0*RCC + 0*RPCC 
RPC ~~ 0*RCC + 0*RPCC
RCC ~~ 0*RPCC



'


cfa_full_model2 <- cfa(rs_model, data = alt_run_sem, estimator = "MLM", std.lv = TRUE)
summary(cfa_full_model2, standardized=TRUE, fit.measures=TRUE, rsquare=TRUE)

anova(cfa_full_model1,cfa_full_model2)


```



## Where we add the nested switch factors (all except the most complex one exist.)

```{r}


rs_model <- '
Spd =~ a*ARUU + a*BRUU + a*CRUU + 
       a*ARUB + a*BRUB + a*CRUB +
       a*ARBU + a*BRBU + a*CRBU + 
       a*ARBB + a*BRBB + a*CRBB +
       a*ASUU + a*BSUU + a*CSUU + 
       a*ASUB + a*BSUB + a*CSUB +
       a*ASBU + a*BSBU + a*CSBU + 
       a*ASBB + a*BSBB + a*CSBB
       

S =~ b*ASUU + b*BSUU + b*CSUU + 
     b*ASUB + b*BSUB + b*CSUB +
     b*ASBU + b*BSBU + b*CSBU + 
     b*ASBB + b*BSBB + b*CSBB

RPC =~ c*ARBU + c*BRBU + c*CRBU +
       c*ARBB + c*BRBB + c*CRBB +
       c*ASBU + c*BSBU + c*CSBU +
       c*ASBB + c*BSBB + c*CSBB
       
RCC =~ d*ARUB + d*BRUB + d*CRUB + 
       d*ARBB + d*BRBB + d*CRBB +
       d*ASUB + d*BSUB + d*CSUB +
       d*ASBB + d*BSBB + d*CSBB
       
RPCC =~ h*ARBB + h*BRBB + h*CRBB +
        h*ASBB + h*BSBB + h*CSBB 


SPC =~ASBU + BSBU + CSBU +
       ASBB + BSBB + CSBB
       
SCC =~ASUB + BSUB + CSUB +ASBB + BSBB + CSBB


#SPCC =~ ASBB + BSBB + CSBB 

Spd ~~ S + 0*RPC + 0*RCC + 0*RPCC + 0*SPC + 0*SCC #+ 0*SPCC
S ~~   0*RPC + 0*RCC + 0*RPCC + 0*SPC +0*SCC #+ 0*SPCC
RPC ~~ 0*RCC + 0*RPCC
RCC ~~ 0*RPCC
SPC ~~ 0*SCC #+ 0*SPCC
#SCC ~~ 0*SPCC

SPC ~~ RPC + 0*RCC + 0*RPCC
SCC ~~ 0*RPC + RCC + 0*RPCC
#SPCC ~~ 0*RPC + 0*RCC + RPCC



'


cfa_full_model2 <- cfa(rs_model, data = alt_run_sem, estimator = "MLM", std.lv = TRUE)
summary(cfa_full_model2, standardized=TRUE, fit.measures=TRUE, rsquare=TRUE)

anova(cfa_full_model, cfa_full_model2)


layout <- matrix(NA, ncol = 24, nrow = 8)
layout[1, 1] <- "R"
layout[2, 3] <- "RPC"
layout[1, 9] <- "RCC"
layout[2, 11] <- "RPCC"
layout[4, 1:12] <- c("ARUU",
                     "BRUU",
                     "CRUU",
                     "ARBU",
                     "BRBU",
                     "CRBU",
                     "BRUB",
                     "CRUB",
                     "ARUB",
                     "ARBB",
                     "BRBB",
                     "CRBB")
layout[8, 4] <- "Spd"

layout[2, 15] <- "S"
layout[3, 20] <- "SPC"
layout[4, 22] <- "SCC"
layout[5, 24] <- "SPCC"
layout[6, 11:22] <- c("ASUU",
                      "BSUU",
                      "CSUU",
                      "ASBU",
                      "BSBU",
                      "CSBU",
                      "BSUB",
                      "CSUB",
                      "ASUB",
                      "ASBB",
                      "BSBB",
                      "CSBB")


graph_data <- prepare_graph(cfa_full_model2, layout = layout)
plot(graph_data)

edges(graph_data) <- edges(graph_data) %>% 
  mutate(label = est_sig_std,
         label = gsub("0\\.", ".", label),
         label = gsub("\\*", "", label),
         show = ifelse(est == "0.00", FALSE, show),
         #show = ifelse(est == "1.00", FALSE, show),
         connect_from = ifelse(from %in% c("R", "RPC", "RCC", "RPCC", "S", "SPC", "SCC", "SPCC") & to %in% colnames(alt_run_sem), "bottom", connect_from),
         connect_to   = ifelse(from %in% c("R", "RPC", "RCC", "RPCC", "S", "SPC", "SCC", "SPCC") & to %in% colnames(alt_run_sem), "top", connect_to),
         connect_from = ifelse(from %in% c("R", "RPC", "RCC", "RPCC", "S", "SPC", "SCC", "SPCC") & from == to, "top", connect_from),
         connect_to   = ifelse(from %in% c("R", "RPC", "RCC", "RPCC", "S", "SPC", "SCC", "SPCC") & from == to, "top", connect_to),
         connect_from = ifelse(from %in% c("Spd") & from == to, "bottom", connect_from),
         connect_to   = ifelse(from %in% c("Spd") & from == to, "bottom", connect_to),
         connect_from = ifelse(from %in% c("Spd") & to %in% colnames(alt_run_sem), "top", connect_from),
         connect_to   = ifelse(from %in% c("Spd") & to %in% colnames(alt_run_sem), "bottom", connect_to),
         connect_from = ifelse(from %in% colnames(alt_run_sem) & to %in% colnames(alt_run_sem), "bottom", connect_from),
         connect_to = ifelse(from %in% colnames(alt_run_sem) & to %in% colnames(alt_run_sem), "bottom", connect_to))

plot(graph_data)
ggsave("dominik/d_figs/sem.svg", width = 60, height = 30, units = "cm")



```




## Model discussed on 06/08/2026

```{r}
rs_model <- '
Spd =~ a*ARUU + a*BRUU + a*CRUU + 
       a*ARUB + a*BRUB + a*CRUB +
       a*ARBU + a*BRBU + a*CRBU + 
       a*ARBB + a*BRBB + a*CRBB +
       a*ASUU + a*BSUU + a*CSUU + 
       a*ASUB + a*BSUB + a*CSUB +
       a*ASBU + a*BSBU + a*CSBU + 
       a*ASBB + a*BSBB + a*CSBB
       

S =~ ASUU + BSUU + CSUU + 
     ASUB + BSUB + CSUB +
     ASBU + BSBU + CSBU + 
     ASBB + BSBB + CSBB


RCC =~ b*ARUB + b*BRUB + b*CRUB + 
       b*ARBB + b*BRBB + b*CRBB +
       b*ASUB + b*BSUB + b*CSUB + 
       b*ASBB + b*BSBB + b*CSBB 
       
      

SCC =~ ASUB + BSUB + CSUB + 
       ASBB + BSBB + CSBB

Spd ~~ S + 0*SCC + 0*RCC
SCC ~~ RCC + 0*S
S ~~ 0*RCC

'

cfa_full_model <- cfa(rs_model, data = alt_run_sem, estimator = "MLM", std.lv = TRUE)
summary(cfa_full_model, standardized=TRUE, fit.measures=TRUE, rsquare=TRUE)





layout <- matrix(NA, ncol = 24, nrow = 8)
layout[1, 1] <- "R"
layout[2, 3] <- "RPC"
layout[1, 9] <- "RCC"
layout[2, 11] <- "RPCC"
layout[4, 1:12] <- c("ARUU",
                     "BRUU",
                     "CRUU",
                     "ARBU",
                     "BRBU",
                     "CRBU",
                     "BRUB",
                     "CRUB",
                     "ARUB",
                     "ARBB",
                     "BRBB",
                     "CRBB")
layout[8, 4] <- "Spd"

layout[2, 15] <- "S"
layout[3, 20] <- "SPC"
layout[4, 22] <- "SCC"
layout[5, 24] <- "SPCC"
layout[6, 11:22] <- c("ASUU",
                      "BSUU",
                      "CSUU",
                      "ASBU",
                      "BSBU",
                      "CSBU",
                      "BSUB",
                      "CSUB",
                      "ASUB",
                      "ASBB",
                      "BSBB",
                      "CSBB")


graph_data <- prepare_graph(cfa_full_model, layout = layout)
plot(graph_data)

edges(graph_data) <- edges(graph_data) %>% 
  mutate(label = est_sig_std,
         label = gsub("0\\.", ".", label),
         label = gsub("\\*", "", label),
         show = ifelse(est == "0.00", FALSE, show),
         #show = ifelse(est == "1.00", FALSE, show),
         connect_from = ifelse(from %in% c("R", "RPC", "RCC", "RPCC", "S", "SPC", "SCC", "SPCC") & to %in% colnames(alt_run_sem), "bottom", connect_from),
         connect_to   = ifelse(from %in% c("R", "RPC", "RCC", "RPCC", "S", "SPC", "SCC", "SPCC") & to %in% colnames(alt_run_sem), "top", connect_to),
         connect_from = ifelse(from %in% c("R", "RPC", "RCC", "RPCC", "S", "SPC", "SCC", "SPCC") & from == to, "top", connect_from),
         connect_to   = ifelse(from %in% c("R", "RPC", "RCC", "RPCC", "S", "SPC", "SCC", "SPCC") & from == to, "top", connect_to),
         connect_from = ifelse(from %in% c("Spd") & from == to, "bottom", connect_from),
         connect_to   = ifelse(from %in% c("Spd") & from == to, "bottom", connect_to),
         connect_from = ifelse(from %in% c("Spd") & to %in% colnames(alt_run_sem), "top", connect_from),
         connect_to   = ifelse(from %in% c("Spd") & to %in% colnames(alt_run_sem), "bottom", connect_to),
         connect_from = ifelse(from %in% colnames(alt_run_sem) & to %in% colnames(alt_run_sem), "bottom", connect_from),
         connect_to = ifelse(from %in% colnames(alt_run_sem) & to %in% colnames(alt_run_sem), "bottom", connect_to))

plot(graph_data)
ggsave("dominik/d_figs/sem.svg", width = 60, height = 30, units = "cm")







```


