---
title: "AlternateRunsAnalysis"
author: "Sophia Angleton"
format: html
editor: visual
---

## Multilevel Test of Stability-Flexibility

This script cleans and analyses the AlternateRuns Dataset.

**Variables** - block: 0 for practice, there are a total of 8 blocks per part and each block consists of 112 trials. So 896 trials per participant over all 7 blocks (not counting practice)

-   bal: counterbalancing of conditions across blocks

-   x, y, c2: irrelevant (already taken out)

-   cycle: counting within full alternating cycle (8), switch at 1 and 5

-   task: 1=shape, 2=color

-   dimshape=specific shapes--4=neutral

-   dimcolor=specific color--4=neutral

-   correct: correct response (i.e., value of the currently relevant task dimension)

-   error: 0 = no error, 1 = yes error

-   response: actual response

-   RT: or response time

```{r}
#| include: false
library(tidyverse)
library(janitor)
library(readr)
library(rio)
library(psych) 
library(stats)
library(lmerTest)
library(sjPlot)
library(hausekeep)
library(hlmer)

#import dataset
AlternateRuns <- read_csv("AlternateRuns.csv")
#view(AlternateRuns) 

#make lmer models lmertests
```

## Data Cleaning

Rename variables for clarity, remove practice blocks and subjects with \> 80% accuracy, compute z-scores and create switch + valence + lag variables.

```{r}

#rename columns to understand better
alt_run <- AlternateRuns %>% 
  rename(dimshape = dim1, dimcolor = dim2, rt = time) %>% #remane variables 
  filter(block != 0) #filter practice trials out

alt_run <- alt_run %>% group_by(id, block, trial) %>% #remove sub 57 showing up 3 times
slice(1)

#determine 80% acc

#crit # need at least 179 out of 896 trials to be correct, denoted by 0 in error col
sum_er <- alt_run %>% 
  group_by(id) %>% 
summarize(acc = mean(1-error), 
          N = n())
sum_er

sum_er <- sum_er %>% 
  filter(acc < .8) 

alt_run <- alt_run %>% 
  filter(!id %in% sum_er$id) #removing those outliers here 

#Making new variables
alt_run <- alt_run %>% 
 # arrange(id, trial) %>% 
  group_by(id, block) %>%
  mutate(
    switch = if_else(cycle %in% c(1,5), 1, 0),
    cycle2 = ifelse(cycle > 4, cycle - 4, cycle),
    group = ifelse(cycle2 == 1, 1, 0),
    group = cumsum(group),
    lerror = lag(error, 1), 
    ltrial = lag(trial, 1), 
    lrt = lag(rt, 1),
    valence = if_else(dimshape == 4 | dimcolor == 4, 1, 2),  # 1 = uni, 2 = bi
    lvalence = lag(valence, 1), 
    conflict = if_else(dimshape != dimcolor & dimshape !=4 & dimcolor != 4, 1,0), 
    lconflict = lag(conflict), 
  ) %>%
  group_by(id, block, group) %>%
  mutate(lvalence = lvalence[1]) %>%                         # constant within 4‑trial group
  ungroup() %>% 
  mutate(
    cycle_helmert = cycle2
  )


alt_run <- alt_run %>% #making contrasts outlined in prereg
  group_by(id, block, group) %>% 
  mutate(
    lvalence_contr = case_when(lvalence == 1 ~ -0.5, lvalence == 2 ~ 0.5),
    valence_contr = case_when(valence == 1 ~ -0.5, valence == 2 ~ 0.5)
    )



#compute z-score on trial level 
alt_run <- alt_run %>% 
  group_by(id, cycle2, valence, lvalence) %>% #cycle or cycle2
  mutate(
    z = (rt - mean(rt[error == 0 & lerror == 0])) / sd(rt[error == 0 & lerror == 0])) %>% 
  ungroup()

# Overall count 
overall_outliers <- alt_run_z %>% summarize(n_outliers = sum(abs(z) > 3, na.rm = TRUE)) #overall_outliers

# Per participant 
outliers_by_id <- alt_run_z %>% 
  group_by(id) %>%
  summarize(n_outliers = sum(abs(z) > 3, na.rm = TRUE))
#outliers_by_id




#last filtering then adding a continuous trials variable
alt_run <- alt_run %>%
           filter(group != 1) %>% 
mutate(rt_log = (log(rt)), 
       filter_correct = ifelse(error == 1 | lerror == 1, 1, 0)
       )
alt_run <- alt_run %>% 
  mutate( valence= factor(valence), 
    lvalence = factor(lvalence),
    cycle2 = factor(cycle2),
    id = factor(id),
  switch = factor(switch)) %>% 
      group_by(id) %>% 
  mutate(conttrials = 1:n())
alt_run
#Remove z‑score outliers
alt_run <- alt_run %>%
  filter(abs(z) <= 3 | is.na(z)) 
alt_run
#for the within-sub analysis
#create a new variable in initial data with trial numbers that continue adding person 
#new model to take the residuals from, this needs to include block trial and sub, need to add poly function within the model (doing just conttrials instead)
set.seed(123)
polymodel <- lmer(
  rt_log ~ poly(conttrials, 2)* (poly(conttrials, 2) | id), control = lmerControl(optimizer = 'bobyqa'),#poly(x,2) is specifications for linear and quadratic
  data = alt_run %>% filter(error == 0)#filers out cur er 
)
summary(polymodel)
#looking for 1 is linear 2 is quadratic
#residuals for this new model 

tab_model(polymodel, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')

#create a new column in the dataframe using residuals() 
alt_run$logresidual <- NA
alt_run$logresidual[alt_run$error == 0] <- residuals(polymodel)

view(alt_run)

alt_run %>% 
  ungroup() %>% 
  summarise(m= mean(conttrials, na.rm = F), sd = sd(conttrials, na.rm = F))

alt_run %>% 
  ungroup() %>% 
  summarise(m= mean(rt_log, na.rm = F), sd = sd(rt_log, na.rm = F))
```
Aggragation experimental level analysis

```{r}
#function for CI

norm_for_errorbars <- function(dv,ID){
  dat <- tibble(dv = dv,ID=ID)
  dat2 <- dat %>%
    mutate(grand_mean = mean(dv,na.rm=T)) %>%
    group_by(ID) %>%
    mutate(submean = mean(dv,na.rm=T)) %>%
    ungroup() %>%
    mutate(normdv = dv - submean + grand_mean)
  return(dat2$normdv)
}
```

```{r}

alt_run <- alt_run %>% #norm on trial level
  group_by(id) %>%
  mutate(
    rt_norm       = norm_for_errorbars(rt, id),
    rt_log_norm   = norm_for_errorbars(rt_log, id),
    error_norm    = norm_for_errorbars(error, id)
  ) %>%
  ungroup()


allagg <- alt_run %>%
  group_by(id, cycle2, switch, valence, lvalence) %>% #first agg
  summarize(
    rt_mean          = mean(rt[filter_correct == 0], na.rm = TRUE),
    rt_log_mean      = mean(rt_log[filter_correct == 0], na.rm = TRUE),
    error_mean       = mean(error, na.rm = TRUE),

    rt_norm_mean     = mean(rt_norm[filter_correct == 0], na.rm = TRUE),
    rt_log_norm_mean = mean(rt_log_norm[filter_correct == 0], na.rm = TRUE),
    error_norm_mean  = mean(error_norm, na.rm = TRUE),

    .groups = "drop"
  )


allagg_ci <- allagg %>% #group level CIs
  group_by(cycle2, switch, valence, lvalence) %>%
  summarize(
    n = n(),

    rt_mean      = mean(rt_mean),    # grand means
    rt_log_mean  = mean(rt_log_mean),
    error_mean   = mean(error_mean),

    rt_se        = sd(rt_norm_mean) / sqrt(n),    # SEs using normalized participant means
    rt_log_se    = sd(rt_log_norm_mean) / sqrt(n),
    error_se     = sd(error_norm_mean) / sqrt(n),

    rt_ci_low        = rt_mean - 1.96 * rt_se,    # 95% 
    rt_ci_high       = rt_mean + 1.96 * rt_se,
    rt_log_ci_low    = rt_log_mean - 1.96 * rt_log_se,
    rt_log_ci_high   = rt_log_mean + 1.96 * rt_log_se,
    error_ci_low     = error_mean - 1.96 * error_se,
    error_ci_high    = error_mean + 1.96 * error_se,

    .groups = "drop"
  ) %>%
  mutate(
    valence = factor(valence, #make it nice for plot
                     levels = c(1, 2),
                     labels = c("Univalent", "Bivalent")),
    lvalence = factor(lvalence,
                      levels = c(1, 2),
                      labels = c("Univalent", "Bivalent")),
    cycle2 = factor(cycle2)
  )

```

## Visualizations
also make figures with averages of no-switch by cycle

By logged RT
```{r}

rtlogplot <- ggplot(
  allagg_ci,
  aes(
    x = cycle2,
    y = rt_log_mean,
    color = valence,
    linetype = lvalence,
    group = interaction(valence, lvalence)
  )
) +
  geom_line(position = position_dodge(width = 0.25)) +
  geom_point(position = position_dodge(width = 0.25)) +
  geom_errorbar(
    aes(ymin = rt_log_ci_low, ymax = rt_log_ci_high),
    width = 0.15,
    position =position_dodge(width = 0.25),
    linewidth = 0.8
  ) +
  theme_classic()

rtlogplot


```
By Error
```{r}


erplot <- ggplot(allagg_ci,
  aes(
    x = cycle2,
    y = error_mean,
    color = valence,
    linetype = lvalence,
    group = interaction(valence, lvalence)
  )
) +
  geom_line(position = position_dodge(width = 0.25)) +
  geom_point(position = position_dodge(width = 0.25)) +
  geom_errorbar(
    aes(ymin = error_ci_low, ymax = error_ci_high),
    width = 0.15,
    position =position_dodge(width = 0.25),
    linewidth = 0.8
  ) +
  theme_classic()

erplot
```
by reg rt
```{r}

rtplot <- ggplot(
  allagg_ci,
  aes(
    x = cycle2,
    y = rt_mean,
    color = valence,
    linetype = lvalence,
    group = interaction(valence, lvalence)
  )
) +
  geom_line(position = position_dodge(width = 0.25)) +
  geom_point(position = position_dodge(width = 0.25)) +
  geom_errorbar(
    aes(ymin = rt_ci_low, ymax = rt_ci_high),
    width = 0.15,
    position =position_dodge(width = 0.25),
    linewidth = 0.8
  ) +
  theme_classic()

rtplot
```

## Experimental Level Analysis

Here we test whether experimental manipulations of previous and current trial control demands interact with the switch contrast in a manner that is consistent with a flexibility/stability tradeoff model.

### by RT

By valence contrasts
```{r}

model_lmer <- lmer(
  rt ~ valence_contr * lvalence_contr * switch +
    (valence_contr + lvalence_contr + switch | id),
  data = alt_run %>% filter(filter_correct == 0)
)

summary(model_lmer)

tab_model(model_lmer, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

checking for conflict effects by adding it into the model
```{r}
model_conflictcheck <- lmer(
  rt_log ~ valence_contr * lvalence_contr * switch +(valence_contr + lvalence_contr + switch || id), control = lmerControl(optimizer = 'bobyqa'),
  data = alt_run %>% filter(filter_correct == 0, conflict == 0, lconflict == 0)
)

summary(model_conflictcheck)

tab_model(model_conflictcheck, show.est = T, auto.label = F, show.stat = T , df.method = 'satterthwaite') #this does change the significance of two way interactions with switch
```
by rt log with valence contrasts

```{r}
model_lmer_log_c <- lmer(
  rt_log ~ valence_contr * lvalence_contr * switch +
    (valence_contr + lvalence_contr + switch || id), #double bar bc does not converge with single, is less complex w double 
  control = lmerControl(optimizer = 'bobyqa'),
  data = alt_run %>% filter(filter_correct == 0)
)

summary(model_lmer_log_c)


tab_model(model_lmer_log_c, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')

 
```

rt log by valence not coded as a contrast

```{r}
model_lmer <- lmer(
  rt_log ~ valence * lvalence * switch +
    (valence + lvalence + switch 
     | id),
  control = lmerControl(optimizer = 'bobyqa'),
  data = alt_run %>% filter(filter_correct == 0)
)

summary(model_lmer)

tab_model(model_lmer, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```
adding conflict as a fixed effect into the rt_log

```{r}
model_lmer_log_conflict <- lmer(
  rt_log ~ valence_contr * lvalence_contr * conflict * lconflict *switch +
    (valence_contr + lvalence_contr + switch + conflict + lconflict | id), #double bar bc does not converge with single, is less complex w double ONLY when effects are numeric not factor
  data = alt_run %>% filter(filter_correct == 0)
)

summary(model_lmer_log_conflict)


tab_model(model_lmer_log_conflict, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')

```
### by Error
by error with valence contrasts
```{r}
model_glmer_c <- glmer(
  error ~ valence_contr * lvalence_contr*switch + (valence_contr + lvalence_contr + switch|id), family = 'binomial', control = glmerControl(optimizer = 'bobyqa'), data = alt_run
)

summary(model_glmer_c)

tab_model(model_glmer_c, show.est = T, auto.label = F, show.stat = T)
```

by error without valence contrasts
```{r}
model_glmer <- glmer(
  error ~ valence * lvalence*switch + (valence + lvalence + switch|id), family = 'binomial', control = glmerControl(optimizer = 'bobyqa'), data = alt_run
)

summary(model_glmer)

tab_model(model_glmer, show.est = T, auto.label = F, show.stat = T)
```

by error with conflict included
```{r}
model_glmer_conflictcheck <- glmer(
  error ~ valence_contr * lvalence_contr*switch + (valence_contr + lvalence_contr + switch|id), family = 'binomial', control = glmerControl(optimizer = 'bobyqa'), data = alt_run %>% filter(conflict == 0, lconflict == 0)
)

summary(model_glmer_conflictcheck)

tab_model(model_glmer_conflictcheck, show.est = T, auto.label = F, show.stat = T)
```

## ezDDM Analysis 
```{r}
#| include: false
#first putting in some pre-made functions that will go into the ezDDM analysis: 

normWS <- function(d ,s, dv, between = NULL) { #within subject normalization
  eval(substitute(d %>%
                    dplyr::group_by(s) %>%
                    dplyr::mutate(sAV = mean(dv, na.rm = TRUE)) %>%
                    dplyr::group_by_at(between) %>% #this is grouping by between subjects variables
                    dplyr::mutate(gAV = mean(dv, na.rm = TRUE)) %>%
                    dplyr::mutate(DV_n = dv - sAV + gAV), list(s = as.name(s), dv = as.name(dv))))
}


get_ci <- function(var, mean){
  sd <- sd(var, na.rm = TRUE)
  n <- length(var)
  se <- sd/sqrt(n)
  ci <- abs(qt(0.025, n-1, lower.tail = FALSE))*se
  return(c(mean + ci, mean - ci, sd, se, n))
}

convert_extremes <- function(value){
  
  if(value == 1){
    
    value = value - 1e-5
    
  } else if (value == 0 ){
    
    value = value + 1e-5
    
  }
  
  return(value)
  
}#making sure error is either .99 or .001
```

### DDM aggregation
```{r}

alt_run_agg_ID_ddm <- alt_run %>%
  mutate(RT_s = rt/1000) %>% #convert rt to seconds
  group_by(id, valence, lvalence, switch, cycle2) %>%
  summarize(RT_s_m = mean(RT_s[filter_correct == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[filter_correct == 0], na.rm = TRUE),
            error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>% #this is looking at everything in one row, have to agg data like this for DDM becuase it does not compute vectors but rows
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-error), #were essentially making a dataframe that shows up as an extra cell next to each part
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  unnest(ezddm) #this extracts the newly created dataframe per column into its own separate columns 

alt_run_agg_ddm <- alt_run_agg_ID_ddm %>%
  group_by(id, valence,lvalence, switch, cycle2) %>%
  normWS(s = "id", dv = "a") %>% #boundary separation. this is starting value
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>% #drift rate
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>% #non-decision time
  mutate(Ter = DV_n) %>%
  group_by(valence,lvalence, switch, cycle2) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[1],
            a_ci_upper = get_ci(a, a_m)[2],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[1],
            v_ci_upper = get_ci(v, v_m)[2],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[1],
            Ter_ci_upper = get_ci(Ter, Ter_m)[2],)

#make a separate object that is averaging across the no-switch 2,3 and 4 average within those and then average within those variances. 
#this agg is the one we use for he lmer models

alt_run_agg_ID_ddm_collapsed <- alt_run  %>% #doing this a different way, if we groupby everything but cycle, the switch v no-switch will auto treat 2,3,4 as averaged i think
  mutate(RT_s = rt/1000) %>% #convert rt to seconds
  group_by(id, valence,valence_contr, lvalence, lvalence_contr, switch) %>%
  summarize(RT_s_m = mean(RT_s[filter_correct == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[filter_correct == 0], na.rm = TRUE),
            error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>% #this is looking at everything in one row, have to agg data like this for DDM becuase it does not compute vectors but rows
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-error), #were essentially making a dataframe that shows up as an extra cell next to each part
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  unnest(ezddm) #this extracts the newly created dataframe per column into its own separate columns 

alt_run_agg_ddm_collapsed <- alt_run_agg_ID_ddm_collapsed %>%
  group_by(id, valence,valence_contr, lvalence, lvalence_contr, switch) %>%
  normWS(s = "id", dv = "a") %>% #boundary separation. this is starting value
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>% #drift rate
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>% #non-decision time
  mutate(Ter = DV_n) %>%
  group_by(id, valence,valence_contr, lvalence, lvalence_contr, switch) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[1],
            a_ci_upper = get_ci(a, a_m)[2],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[1],
            v_ci_upper = get_ci(v, v_m)[2],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[1],
            Ter_ci_upper = get_ci(Ter, Ter_m)[2],)

```
### DDM vis
```{r}
plt_ddm_a <- ggplot(alt_run_agg_ddm, aes(x = cycle2, y = a_m, color = valence, linetype = lvalence, group = interaction(valence,lvalence )))+
  geom_line(position = position_dodge(width = 0.25))+
  geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper), width = 0.1, position = position_dodge(width = 0.25))+
  theme_classic()

plt_ddm_v <- ggplot(alt_run_agg_ddm, aes(x = cycle2, y = v_m, color = valence, linetype = lvalence, group = interaction(valence,lvalence )))+
  geom_line(position = position_dodge(width = 0.25))+
  geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper), width = 0.1, position = position_dodge(width = 0.25))+
  theme_classic()


plt_ddm_Ter <- ggplot(alt_run_agg_ddm, aes(x = cycle2, y = Ter_m, color = valence, linetype = lvalence, group = interaction(valence,lvalence )))+
  geom_line(position = position_dodge(width = 0.25))+
  geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper), width = 0.1, position = position_dodge(width = 0.25))+
  theme_classic()

ggpubr::ggarrange(plt_ddm_a, plt_ddm_v, plt_ddm_Ter, common.legend = TRUE, nrow = 1)  

#ok this works but idk how to interpret
```
plotting with the aggregation averaging between no-switch cycles
```{r}

plt_ddm_a <- ggplot(alt_run_agg_ddm_collapsed, aes(x = switch, y = a_m, color = valence, linetype = lvalence, group = interaction(valence,lvalence)))+
  geom_line(position = position_dodge(width = 0.25))+
  geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper), width = 0.1, position = position_dodge(width = 0.25))+
  theme_classic()

plt_ddm_v <- ggplot(alt_run_agg_ddm_collapsed, aes(x = switch, y = v_m, color = valence, linetype = lvalence, group = interaction(valence,lvalence)))+
  geom_line(position = position_dodge(width = 0.25))+
  geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper), width = 0.1, position = position_dodge(width = 0.25))+
  theme_classic()


plt_ddm_Ter <- ggplot(alt_run_agg_ddm_collapsed, aes(x = switch, y = Ter_m, color = valence, linetype = lvalence, group = interaction(valence,lvalence)))+
  geom_line(position = position_dodge(width = 0.25))+
  geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper), width = 0.1, position = position_dodge(width = 0.25))+
  theme_classic()

ggpubr::ggarrange(plt_ddm_a, plt_ddm_v, plt_ddm_Ter, common.legend = TRUE, nrow = 1) 
```
### DDM Models 

with valence contrasts

```{r}
model_a_c <- lmer(a ~ valence_contr * lvalence_contr *switch + (valence_contr+lvalence_contr+switch || id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)

summary(model_a_c)

tab_model(model_a_c, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```


```{r}
model_v_c<- lmer(v ~ valence_contr * lvalence_contr *switch + (valence_contr+lvalence_contr+switch || id), control = lmerControl(optimizer = "bobyqa"),data = alt_run_agg_ID_ddm_collapsed)

summary(model_v_c)

tab_model(model_v_c, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

```{r}
model_Ter_c <- lmer(Ter ~ valence_contr * lvalence_contr *switch + (valence_contr+lvalence_contr+switch || id), control = lmerControl(optimizer = "bobyqa"),data = alt_run_agg_ID_ddm_collapsed)

summary(model_Ter_c)

tab_model(model_Ter_c, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

without valence contrasts

```{r}
model_a <- lmer(a ~ valence * lvalence *switch + (valence+lvalence+switch | id), control = lmerControl(optimizer = "bobyqa"),data = alt_run_agg_ID_ddm_collapsed)

summary(model_a)

tab_model(model_a, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```


```{r}
model_v <- lmer(v ~ valence * lvalence *switch + (valence+lvalence+switch | id), control = lmerControl(optimizer = "bobyqa"),data = alt_run_agg_ID_ddm_collapsed)

summary(model_v)

tab_model(model_v, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

```{r}
model_Ter <- lmer(Ter ~ valence * lvalence *switch + (valence+lvalence+switch | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)

summary(model_Ter)

tab_model(model_Ter, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

## Within subject analysis
(although altruns does show a speed accuracy relationship)

not only residualize the general trends but by task (bc task is assymetric) 

add in helmert contrast (3 for runs, 2 for cues) 

visualization for models 

to fix singularity, can run a model comparisons to see what fixed effects to keep, can do this by running an ANOVA

### Reverse Helmert Contrasts

```{r}

# for reference
# alt_run$logresidual <- NA
# alt_run$logresidual[alt_run$filter_correct == 0] <- residuals(polymodel)

m <- contr.helmert(4) #this is the matrix genereated that we will place onto our cycle variable

m[,1] <- rev(m[,1])

m[,2] <- rev(m[,2])
m[,3] <- rev(m[,3])
#reverse helmert
colnames(m) <- c('3vr','2vr','1vr')

alt_run <- alt_run %>% 
  mutate(cycle_helmert = cycle2
           )
contrasts(alt_run$cycle_helmert) <- m

contrasts(alt_run$cycle_helmert) 

head(alt_run)
```
# auto correlations lag rt and rt
the way we are calculating residual rt's makes it so that there is little variance between subjects (I still need to understand this more)

```{r}
alt_run <- alt_run %>%
  group_by(id, block) %>%
  mutate(lrt_logres = lag(logresidual, 1),
         lrt_log = lag(rt_log, 1))

```

by valence contrast
```{r}
autocor_model_c <- lmer(logresidual ~ valence_contr * lvalence_contr * cycle_helmert * lmeanlogres_noswitch + (valence_contr + lvalence_contr + cycle_helmert + lmeanlogres_noswitch||id), control = lmerControl(optimizer = "bobyqa"),
     alt_run %>% filter(filter_correct==0))

summary(autocor_model_c)

tab_model(autocor_model_c, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')

```

no valence contrast
this does not converge and takes forever to run
```{r}
autocor_model <- lmer(logresidual ~ valence * lvalence * cycle_helmert * lrt_logres + (valence + lvalence + cycle_helmert + lrt_logres|id), control = lmerControl(optimizer = "bobyqa"),
     alt_run %>% 
       filter(filter_correct == 0))

summary(autocor_model)

tab_model(autocor_model, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```
visualize residual rt_log in slow and fast responses
this doesnt work for me, pulled from doms code
```{r}
preds <- emmeans::emmeans(autocor_model, ~ valence * lvalence * switch * lmeanlogres_noswitch, type = "response",
                          at = list(valence = factor(c(0, 1)),
                                    lvalence = factor(c(0, 1)),
                                    switch = factor(c(0, 1)),
                                    lmeanlogres_noswitch = c(-1.5, 1.5))) %>%
  as.data.frame() %>%
  mutate(speed = case_when(lmeanlogres_noswitch == min(lmeanlogres_noswitch) ~ "fast",
                           lmeanlogres_noswitch == max(lmeanlogres_noswitch) ~ "slow") %>% factor()) 


preds


ggplot(preds, aes(x = switch, y = emmean, color = valence, linetype = lvalence, group = interaction(valence, lvalence)))+
 geom_line(position = position_dodge(width = 0.25)) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = pos)+
  scale_x_discrete(limits = c("1", "0"))+
  facet_wrap(~speed, labeller = labeller(speed = c("slow" = "lag RT slow",
                                                   "fast" = "lag RT fast")))+
  labs(title = "Model predictions for residual log RTs",
       y = "log(RT) prediction")+
  theme_classic()
```


