---
title: "AlternateRunsAnalysis"
author: "Sophia Angleton"
format: html
editor: visual
---

## Multilevel Test of Stability-Flexibility

This script cleans and analyses the AlternateRuns Dataset.

**Variables** - block: 0 for practice, there are a total of 8 blocks per part and each block consists of 112 trials. So 896 trials per participant over all 7 blocks (not counting practice)

-   bal: counterbalancing of conditions across blocks

-   x, y, c2: irrelevant (already taken out)

-   cycle: counting within full alternating cycle (8), switch at 1 and 5

-   task: 1=shape, 2=color

-   dimshape=specific shapes--4=neutral

-   dimcolor=specific color--4=neutral

-   correct: correct response (i.e., value of the currently relevant task dimension)

-   error: 0 = no error, 1 = yes error

-   response: actual response

-   RT: or response time

```{r}
#| include: false
library(tidyverse)
library(janitor)
library(readr)
library(rio)
library(psych) 
library(lme4)
library(sjPlot)
library(hausekeep)
#import dataset
AlternateRuns <- read_csv("AlternateRuns.csv")
#view(AlternateRuns) 

#sub 57 has 2352 trials check this 
```

## Data Cleaning

Rename variables for clarity, remove practice blocks and subjects with \> 80% accuracy, compute z-scores and create switch + valence + lag variables.

```{r}


#rename columns to understand better
alt_run <- AlternateRuns %>% 
  rename(dimshape = dim1, dimcolor = dim2, rt = time) %>% #remane variables also need to remove sub 57 showing up 3 times
  filter(block != 0) #filter practice trials out

#determine 80% acc

#crit # need at least 179 out of 896 trials to be correct, denoted by 0 in error col
sum_er <- alt_run %>% 
  group_by(id) %>% 
summarize(acc = mean(1-error), 
          N = n())
sum_er

sum_er <- sum_er %>% 
  filter(acc < .8) 

alt_run <- alt_run %>% 
  filter(!id %in% sum_er$id) #removing those outliers here 

#Making new variables
alt_run <- alt_run %>% 
  group_by(id, block) %>%
  mutate(
    switch = if_else(cycle %in% c(1,5), 1, 0),
    cycle2 = ifelse(cycle > 4, cycle - 4, cycle), # i didnt want to overwrite cycle, but this is breaking the cycle of 8 into 1-4 
    group = ifelse(cycle2 == 1,1,0),
    group = cumsum(group),
    lerror = lag(error, 1), 
    ltrial = lag(trial, 1), 
    lrt = lag(rt, 1),
    valence = if_else(dimshape == 4 | dimcolor == 4,1,2),#univalent = 1, bivalalent = 2
    lvalence = lag(valence, 4))#lvalence l = 1 group so for me 4 ... is this right? 

alt_run <- alt_run %>% #making contrasts outlined in prereg
  group_by(id, block, group) %>% 
  mutate(
    lvalence_contr = case_when(lvalence == 1 ~ -0.5, lvalence == 2 ~ 0.5),
    valence_contr = case_when(valence == 1 ~ -0.5, valence == 2 ~ 0.5)
    )

#compute z-score on trial level 
alt_run_z <- alt_run %>% 
  group_by(id, cycle2, valence, lvalence) %>% #cycle or cycle2
  mutate(
    z = (rt - mean(rt[error == 0 & lerror == 0])) / sd(rt[error == 0 & lerror == 0])) %>% 
  ungroup()

# Overall count 
overall_outliers <- alt_run_z %>% summarize(n_outliers = sum(abs(z) > 3, na.rm = TRUE)) #overall_outliers

# Per participant 
outliers_by_id <- alt_run_z %>% 
  group_by(id) %>%
  summarize(n_outliers = sum(abs(z) > 3, na.rm = TRUE))
#outliers_by_id

#Remove z‑score outliers
alt_run <- alt_run_z %>%
  filter(abs(z) <= 3 | is.na(z)) 


# Final summary dataset
z_score_inspect <- alt_run %>%
  group_by(id, cycle2, valence, lvalence) %>%
  summarize( 
    z_score_mean = mean(z, na.rm = TRUE), 
    z_score_sd = sd(z, na.rm = TRUE), 
    response_time_mean = mean(rt, na.rm = TRUE),
    response_time_sd = sd(rt, na.rm = TRUE) 
    )
z_score_inspect

alt_run <- alt_run %>%
           filter(group != 1) %>% 
mutate(rt_log = (log(rt)), 
       filter_correct = ifelse(error == 1 | lerror == 1, 1, 0)
       )
#I think somewhere in here I need to filter out first trials but I dont know where I should put this in my workflow
view(alt_run)
```

**Analysis On The Experimental Level:** Here we test whether experimental manipulations of previous and current trial control demands interact with the switch contrast in a manner that is consistent with a flexibility/stability tradeoff model.

```{r}

model_lmer <- lmer(
  rt ~ valence_contr * lvalence_contr * switch +
    (valence_contr + lvalence_contr + switch | id),
  data = alt_run %>% filter(filter_correct == 0)
)

summary(model_lmer)

tab_model(model_lmer, show.est = T, auto.label = F, show.stat = T)
```

```{r}
model_lmer_log <- lmer(
  rt_log ~ valence_contr * lvalence_contr * switch +
    (valence_contr + lvalence_contr + switch || id),
  data = alt_run %>% filter(filter_correct == 0)
)

summary(model_lmer_log)

tab_model(model_lmer_log, show.est = T, auto.label = F, show.stat = T)
```

```{r}
set.seed(10)
model_glmer <- glmer(
  error ~ valence_contr * lvalence_contr*switch + (valence_contr + lvalence_contr + switch|id), family = 'binomial', control = glmerControl(optimizer = 'bobyqa'), data = alt_run
)

summary(model_glmer)

tab_model(model_glmer, show.est = T, auto.label = F, show.stat = T)
```

## ezDDM Analysis
```{r}
normWS <- function(d ,s, dv, between = NULL) {
  eval(substitute(d %>%
                    dplyr::group_by(s) %>%
                    dplyr::mutate(sAV = mean(dv, na.rm = TRUE)) %>%
                    dplyr::group_by_at(between) %>% #this is grouping by between subjects variables
                    dplyr::mutate(gAV = mean(dv, na.rm = TRUE)) %>%
                    dplyr::mutate(DV_n = dv - sAV + gAV), list(s = as.name(s), dv = as.name(dv))))
}


get_ci <- function(var, mean){
  sd <- sd(var, na.rm = TRUE)
  n <- length(var)
  se <- sd/sqrt(n)
  ci <- abs(qt(0.025, n-1, lower.tail = FALSE))*se
  return(c(mean + ci, mean - ci, sd, se, n))
}

convert_extremes <- function(value){
  
  if(value == 1){
    
    value = value - 1e-5
    
  } else if (value == 0 ){
    
    value = value + 1e-5
    
  }
  
  return(value)
  
}#making sure error is either .99 or .001
```


```{r}


alt_run_agg_ID_ddm <- alt_run %>%
  mutate(RT_s = rt/1000) %>%
  group_by(id, valence, lvalence, switch, cycle2) %>%
  summarize(RT_s_m = mean(RT_s[filter_correct == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[filter_correct == 0], na.rm = TRUE),
            error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>% #this is looking at everything in one row, have to agg data like this for DDM becuase it does not compute vectors but rows
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-error), #were essentially making a dataframe that shows up as an extra cell next to each part
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  unnest(ezddm) #this extracts the newly created dataframe per column into its own separate columns 

#make a separate object that is averaging across the no-switch 2,3 and 4 average within those and then average within those variances 

alt_run_agg_ddm <- alt_run_agg_ID_ddm %>%
  group_by(id, valence,lvalence, switch, cycle2) %>%
  normWS(s = "id", dv = "a") %>%
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>%
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>%
  mutate(Ter = DV_n) %>%
  group_by(valence,lvalence, switch, cycle2) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[1],
            a_ci_upper = get_ci(a, a_m)[2],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[1],
            v_ci_upper = get_ci(v, v_m)[2],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[1],
            Ter_ci_upper = get_ci(Ter, Ter_m)[2],)
```
