---
title: "AlternateRunsAnalysis"
author: "Sophia Angleton"
format: html
editor: visual
---

# Multilevel Test of Stability-Flexibility

This script cleans and analyses the AlternateRuns Dataset.

**Variables** - block: 0 for practice, there are a total of 8 blocks per part and each block consists of 112 trials. So 896 trials per participant over all 7 blocks (not counting practice)

-   bal: counterbalancing of conditions across blocks

-   x, y, c2: irrelevant (already taken out)

-   cycle: counting within full alternating cycle (8), switch at 1 and 5

-   task: 1=shape, 2=color

-   dimshape=specific shapes--4=neutral

-   dimcolor=specific color--4=neutral

-   correct: correct response (i.e., value of the currently relevant task dimension)

-   error: 0 = no error, 1 = yes error

-   response: actual response

-   RT: or response time

**Note** With most complex models (all random effects included):

-   experimental level: everything converges, singularity issues arise across all ezDDM. using outlined preregistration contrasts (.5,-.5 val lval, 0,1 switch).

-   within-sub level: does not converge and is singular

```{r}
#| include: false
library(tidyverse)
library(janitor)
library(readr)
library(rio)
library(psych) 
library(stats)
library(lmerTest)
library(sjPlot)
library(hausekeep)
library(hlmer)

#import dataset
AlternateRuns <- read_csv("AlternateRuns.csv")
#view(AlternateRuns) 

iqTest <- read_csv("tests.csv")

view(iqTest)

#make lmer models lmertests
rerun_all <- 0

library(grateful)
cite_packages(
output = "file",          # saves a file
out.format = "tex-document",  # LaTeX document
out.dir = getwd(),        # directory to save files
bib.file = "my-packages.bib"  # BibTeX file name
)

```

## Data Cleaning

Rename variables for clarity, remove practice blocks and subjects with \> 80% accuracy, compute z-scores and create switch + valence + lag variables.

```{r}

#rename columns to understand better
alt_run <- AlternateRuns %>% 
  rename(dimshape = dim1, dimcolor = dim2, rt = time) %>% #remane variables 
  filter(block != 0) #filter practice trials out

alt_run <- alt_run %>% group_by(id, block, trial) %>% #remove sub 57 showing up 3 times
slice(1)

#determine 80% acc

#crit # need at least 179 out of 896 trials to be correct, denoted by 0 in error col
sum_er <- alt_run %>% 
  group_by(id) %>% 
summarize(acc = mean(1-error), 
          N = n())
sum_er

sum_er <- sum_er %>% 
  filter(acc < .8) 

sum_er

alt_run <- alt_run %>% 
  filter(!id %in% sum_er$id) #removing those outliers here 

#Making new variables
alt_run <- alt_run %>% 
 # arrange(id, trial) %>% 
  group_by(id, block) %>%
  mutate(
    switch = if_else(cycle %in% c(1,5), 1, 0),
    cycle2 = ifelse(cycle > 4, cycle - 4, cycle),
    group = ifelse(cycle2 == 1, 1, 0),
    group = cumsum(group),
    lerror = lag(error, 1), 
    ltrial = lag(trial, 1), 
    lrt = lag(rt, 1),
    valence = if_else(dimshape == 4 | dimcolor == 4, 1, 2),  # 1 = uni, 2 = bi
    lvalence = lag(valence, 1), 
    conflict = if_else(dimshape != dimcolor & dimshape !=4 & dimcolor != 4, 1,0), 
    lconflict = lag(conflict), 
  ) %>%
  group_by(id, block, group) %>%
  mutate(lvalence = lvalence[1]) %>%                         # constant within 4‑trial group
  ungroup() %>% 
  mutate(
    cycle_helmert = cycle2
  )


alt_run <- alt_run %>% #making contrasts outlined in prereg
  group_by(id, block, group) %>% 
  mutate(
    lvalence_contr = case_when(lvalence == 1 ~ -0.5, lvalence == 2 ~ 0.5),
    valence_contr = case_when(valence == 1 ~ -0.5, valence == 2 ~ 0.5)
    )



#compute z-score on trial level 
alt_run <- alt_run %>% 
  group_by(id, cycle2, valence, lvalence) %>% #cycle or cycle2
  mutate(
    z = (rt - mean(rt[error == 0 & lerror == 0])) / sd(rt[error == 0 & lerror == 0])) %>% 
  ungroup()

# # Overall count 
# overall_outliers <- alt_run %>% summarize(n_outliers = sum(abs(z) > 3, na.rm = TRUE)) #overall_outliers
# 
# # Per participant 
# outliers_by_id <- alt_run %>% 
#   group_by(id) %>%
#   summarize(n_outliers = sum(abs(z) > 3, na.rm = TRUE))
# #outliers_by_id
# 



#last filtering then adding a continuous trials variable
alt_run <- alt_run %>%
           filter(group != 1) %>% 
mutate(rt_log = (log(rt)), 
       filter_correct = ifelse(error == 1 | lerror == 1, 1, 0)
       )
alt_run <- alt_run %>% 
  mutate( valence= factor(valence), 
    lvalence = factor(lvalence),
    cycle2 = factor(cycle2),
    id = factor(id),
  switch = factor(switch), 
 lvalence_contr= factor(lvalence_contr),
 valence_contr = factor(valence_contr)) %>% 
      group_by(id) %>% 
  mutate(conttrials = 1:n())

contrasts(alt_run$lvalence_contr) <- c(-0.5, 0.5)
contrasts(alt_run$valence_contr) <- c(-0.5, 0.5)

contrasts(alt_run$valence_contr) #looks gouda
contrasts(alt_run$lvalence_contr)

#Remove z‑score outliers
alt_run <- alt_run %>%
  filter(abs(z) <= 3 | is.na(z)) 

#for the within-sub analysis
#create a new variable in initial data with trial numbers that continue adding person 
#new model to take the residuals from, this needs to include block trial and sub, need to add poly function within the model (doing just conttrials instead)
set.seed(123)
polymodel <- lmer(
  rt_log ~ poly(conttrials, 2)* (poly(conttrials, 2) | id), control = lmerControl(optimizer = 'bobyqa'),#poly(x,2) is specifications for linear and quadratic
  data = alt_run %>% filter(error == 0)#filers out cur er 
)
#summary(polymodel)

#looking for 1 is linear 2 is quadratic
#residuals for this new model 

#tab_model(polymodel, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')

#create a new column in the dataframe using residuals() 
alt_run$logresidual <- NA
alt_run$logresidual[alt_run$error == 0] <- residuals(polymodel)

#adding back in the subject intercepts into the residual variable. better for modeling 
residualintercept <- coefficients(polymodel)$id %>% 
  as.data.frame() %>% 
  rownames_to_column("id") %>%
  select(id, "(Intercept)") %>%
  rename(polymodel_int = "(Intercept)")

alt_run <- alt_run %>% #leftjoining togther to add back in the intercepts to altrun. will use in residual within-subject modeling (second level)
  left_join(residualintercept) %>% 
  group_by(id, block) %>%
  mutate(rt_log_res_w_s_int = logresidual + polymodel_int,
         lrt_log_res_w_s_int = lag(rt_log_res_w_s_int, 1),
         lrt_logres = lag(logresidual, 1),
         lrt_log = lag(rt_log, 1))

### Reverse Helmert Contrasts

m <- contr.helmert(4) #this is the matrix genereated that we will place onto our cycle variable

m[,1] <- rev(m[,1])

m[,2] <- rev(m[,2])
m[,3] <- rev(m[,3])
#reverse helmert
colnames(m) <- c('3vr','2vr','1vr')

alt_run <- alt_run %>% 
  mutate(cycle_helmert = cycle2
           )
contrasts(alt_run$cycle_helmert) <- m

contrasts(alt_run$cycle_helmert) 

#view(alt_run)
```
IQ test 
```{r}
length(unique(iqTest$id)) #n=100

iqTest <- iqTest %>%
  filter(!id %in% c(19,70,87)) %>% 
  droplevels()
iqTest #same as alt_runs


iqTest <- iqTest %>% 
  mutate(
    z_raven = (raven - mean(raven, na.rm = TRUE)) / sd(raven, na.rm = TRUE),
    z_cfit  = (cfit  - mean(cfit,  na.rm = TRUE)) / sd(cfit,  na.rm = TRUE)
  )

iqTest <- iqTest %>% 
  mutate(
    g = (z_raven + z_cfit) / 2, 
    g_c = scale(g, center = TRUE, scale = FALSE)
  )

iqTest

alt_run <- alt_run %>% mutate(id = as.character(id))
iqTest  <- iqTest  %>% mutate(id = as.character(id))

alt_run <- alt_run %>%
  left_join(
    iqTest %>% select(id, g_c),
    by = "id"
  )

view(alt_run)


```


Aggregation experimental level analysis

```{r}
#function for CI

norm_for_errorbars <- function(dv,ID){
  dat <- tibble(dv = dv,ID=ID)
  dat2 <- dat %>%
    mutate(grand_mean = mean(dv,na.rm=T)) %>%
    group_by(ID) %>%
    mutate(submean = mean(dv,na.rm=T)) %>%
    ungroup() %>%
    mutate(normdv = dv - submean + grand_mean)
  return(dat2$normdv)
}
```

```{r}

alt_run <- alt_run %>% #norm on trial level
  group_by(id) %>%
  mutate(
    rt_norm       = norm_for_errorbars(rt, id),
    rt_log_norm   = norm_for_errorbars(rt_log, id),
    error_norm    = norm_for_errorbars(error, id)
  ) %>%
  ungroup()


allagg <- alt_run %>%
  group_by(id, cycle2, switch, valence, lvalence) %>% #first agg
  summarize(
    rt_mean          = mean(rt[filter_correct == 0], na.rm = TRUE),
    rt_log_mean      = mean(rt_log[filter_correct == 0], na.rm = TRUE),
    error_mean       = mean(error, na.rm = TRUE),

    rt_norm_mean     = mean(rt_norm[filter_correct == 0], na.rm = TRUE),
    rt_log_norm_mean = mean(rt_log_norm[filter_correct == 0], na.rm = TRUE),
    error_norm_mean  = mean(error_norm, na.rm = TRUE),

    .groups = "drop"
  )


allagg_ci <- allagg %>% #group level CIs
  group_by(cycle2, switch, valence, lvalence) %>%
  summarize(
    n = n(),

    rt_mean      = mean(rt_mean),    # grand means
    rt_log_mean  = mean(rt_log_mean),
    error_mean   = mean(error_mean),

    rt_se        = sd(rt_norm_mean) / sqrt(n),    # SEs using normalized participant means
    rt_log_se    = sd(rt_log_norm_mean) / sqrt(n),
    error_se     = sd(error_norm_mean) / sqrt(n),

    rt_ci_low        = rt_mean - 1.96 * rt_se,    # 95% 
    rt_ci_high       = rt_mean + 1.96 * rt_se,
    rt_log_ci_low    = rt_log_mean - 1.96 * rt_log_se,
    rt_log_ci_high   = rt_log_mean + 1.96 * rt_log_se,
    error_ci_low     = error_mean - 1.96 * error_se,
    error_ci_high    = error_mean + 1.96 * error_se,

    .groups = "drop"
  ) %>%
  mutate(
    valence = factor(valence, #make it nice for plot
                     levels = c(1, 2),
                     labels = c("Univalent", "Bivalent")),
    lvalence = factor(lvalence,
                      levels = c(1, 2),
                      labels = c("Univalent", "Bivalent")),
    cycle2 = factor(cycle2)
  )

```

### Visualizations

also make figures with averages of no-switch by cycle

By logged RT

```{r}
apa_theming <- function(base_size = 12,
                        base_family = "sans",
                        blue = "#56B4E9",
                        orange = "#E69F00") {

  list(
    # based off how others strucutre their apa figure themes but adding the specifications we talked about
    theme_bw(base_size = base_size, base_family = base_family) %+replace%
      theme(
        text = element_text(family = base_family, color = "black"),
        plot.title = element_text(size = base_size * 1.4, face = "bold"),
        plot.subtitle = element_text(size = base_size * 1.1),
        plot.caption = element_text(size = base_size * 0.9),

        axis.title = element_text(size = base_size * 1.1),
        axis.text = element_text(size = base_size),
        axis.line = element_line(color = "black", linewidth = 0.5),
        axis.ticks = element_line(color = "black"),

        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),

        legend.position = "right",
        legend.title = element_text(size = base_size * 1.1),
        legend.text = element_text(size = base_size),

        strip.background = element_rect(fill = "gray90", color = "black"),
        strip.text = element_text(size = base_size * 1.1, face = "bold")
      ),

    #assigning colors specified in specfifc order
    scale_color_manual(values = c(blue, orange))
  )
}





rtlogplot <- ggplot(
  allagg_ci,
  aes(
    x = cycle2,
    y = rt_log_mean,
    color = valence,
    linetype = lvalence,
    group = interaction(valence, lvalence)
  )
) +
  geom_line(position = position_dodge(width = 0.25)) +
  geom_point(position = position_dodge(width = 0.25)) +
  geom_errorbar(
    aes(ymin = rt_log_ci_low, ymax = rt_log_ci_high),
    width = 0.15,
    position =position_dodge(width = 0.25),
    linewidth = 0.8
  ) +
  apa_theming()

rtlogplot


```

By Error

```{r}


erplot <- ggplot(allagg_ci,
  aes(
    x = cycle2,
    y = error_mean,
    color = valence,
    linetype = lvalence,
    group = interaction(valence, lvalence)
  )
) +
  geom_line(position = position_dodge(width = 0.25)) +
  geom_point(position = position_dodge(width = 0.25)) +
  geom_errorbar(
    aes(ymin = error_ci_low, ymax = error_ci_high),
    width = 0.15,
    position =position_dodge(width = 0.25),
    linewidth = 0.8
  ) +
  apa_theming()

erplot
```

by reg rt

```{r}

rtplot <- ggplot(
  allagg_ci,
  aes(
    x = cycle2,
    y = rt_mean,
    color = valence,
    linetype = lvalence,
    group = interaction(valence, lvalence)
  )
) +
  geom_line(position = position_dodge(width = 0.25)) +
  geom_point(position = position_dodge(width = 0.25)) +
  geom_errorbar(
    aes(ymin = rt_ci_low, ymax = rt_ci_high),
    width = 0.15,
    position =position_dodge(width = 0.25),
    linewidth = 0.8
  ) +
  apa_theming()

rtplot
```

## Experimental Level Analysis

Here we test whether experimental manipulations of previous and current trial control demands interact with the switch contrast in a manner that is consistent with a flexibility/stability tradeoff model.

### by RT

By valence contrasts

```{r}
# 
# model_lmer <- lmer(
#   rt ~ valence_contr * lvalence_contr * cycle_helmert +
#     (valence_contr + lvalence_contr + cycle_helmert | id),
#   data = alt_run %>% filter(filter_correct == 0)
# )
# 
# summary(model_lmer)
# 
# tab_model(model_lmer, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

checking for conflict effects by adding it into the model

```{r}
# model_conflictcheck <- lmer(
#   rt_log ~ valence_contr * lvalence_contr * cycle_helmert +(valence_contr + lvalence_contr + cycle_helmert || id), control = lmerControl(optimizer = 'bobyqa'),
#   data = alt_run %>% filter(filter_correct == 0, conflict == 0, lconflict == 0)
# )
# 
# summary(model_conflictcheck)
# 
# tab_model(model_conflictcheck, show.est = T, auto.label = F, show.stat = T , df.method = 'satterthwaite') #this does change the significance of two way interactions with switch
```

by rt log with valence contrasts

```{r}
model_lmer_log_c <- xfun::cache_rds({
  lmer(rt_log ~ valence_contr * lvalence_contr * switch * g_c +
    (valence_contr + lvalence_contr + switch| id), 
  control = lmerControl(optimizer = 'bobyqa'),
  data = alt_run %>% filter(filter_correct == 0)
)
}, dir = "sophia/output/", file = "model_lmer_log_c.rds", rerun = rerun_all)
summary(model_lmer_log_c)


tab_model(model_lmer_log_c, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')


 
```

rt log by valence not coded as a contrast

```{r}
# model_lmer <- xfun::cache_rds({
#   lmer(
#   rt_log ~ valence * lvalence * switch +
#     (valence + lvalence + switch 
#      | id),
#   control = lmerControl(optimizer = 'bobyqa'),
#   data = alt_run %>% filter(filter_correct == 0)
# )
# }, dir = "sophia/output/", file = "model_lmer.rds", rerun = rerun_all)
# summary(model_lmer)
# 
# tab_model(model_lmer, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')

```

adding conflict as a fixed effect into the rt_log

```{r}
# model_lmer_log_conflict <- lmer(
#   rt_log ~ valence_contr * lvalence_contr * conflict * lconflict *cycle_helmert +
#     (valence_contr + lvalence_contr + cycle_helmert+ conflict + lconflict | id), #double bar bc does not converge with single, is less complex w double ONLY when effects are numeric not factor
#   data = alt_run %>% filter(filter_correct == 0)
# )
# 
# summary(model_lmer_log_conflict)
# 
# 
# tab_model(model_lmer_log_conflict, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')

```

### by Error

by error with valence contrasts

```{r}
model_glmer_c <- xfun::cache_rds({
  glmer(
  error ~ valence_contr * lvalence_contr*switch*g_c + (valence_contr + lvalence_contr + switch|id), family = 'binomial', control = glmerControl(optimizer = 'bobyqa'), data = alt_run
)
}, dir = "sophia/output/", file = "model_glmer_c.rds", rerun = rerun_all)
summary(model_glmer_c)

tab_model(model_glmer_c, show.est = T, auto.label = F, show.stat = T)

```

by error without valence contrasts

```{r}
# model_glmer <- xfun::cache_rds({
#   glmer(
#   error ~ valence * lvalence*switch+ (valence + lvalence + switch|id), family = 'binomial', control = glmerControl(optimizer = 'bobyqa'), data = alt_run
# )
# }, dir = "sophia/output/", file = "model_glmer.rds", rerun = rerun_all)
# summary(model_glmer)
# 
# tab_model(model_glmer, show.est = T, auto.label = F, show.stat = T)

```

by error with conflict included

```{r}
# model_glmer_conflictcheck <- glmer(
#   error ~ valence_contr * lvalence_contr*cycle_helmert + (valence_contr + lvalence_contr + cycle_helmert|id), family = 'binomial', control = glmerControl(optimizer = 'bobyqa'), data = alt_run %>% filter(conflict == 0, lconflict == 0)
# )
# 
# summary(model_glmer_conflictcheck)
# 
# tab_model(model_glmer_conflictcheck, show.est = T, auto.label = F, show.stat = T)
```

## ezDDM Analysis

```{r}
#| include: false
#first putting in some pre-made functions that will go into the ezDDM analysis: 

normWS <- function(d ,s, dv, between = NULL) { #within subject normalization
  eval(substitute(d %>%
                    dplyr::group_by(s) %>%
                    dplyr::mutate(sAV = mean(dv, na.rm = TRUE)) %>%
                    dplyr::group_by_at(between) %>% #this is grouping by between subjects variables
                    dplyr::mutate(gAV = mean(dv, na.rm = TRUE)) %>%
                    dplyr::mutate(DV_n = dv - sAV + gAV), list(s = as.name(s), dv = as.name(dv))))
}


get_ci <- function(var, mean){
  sd <- sd(var, na.rm = TRUE)
  n <- length(var)
  se <- sd/sqrt(n)
  ci <- abs(qt(0.025, n-1, lower.tail = FALSE))*se
  return(c(mean + ci, mean - ci, sd, se, n))
}

convert_extremes <- function(value){
  
  if(value == 1){
    
    value = value - 1e-5
    
  } else if (value == 0 ){
    
    value = value + 1e-5
    
  }
  
  return(value)
  
}#making sure error is either .99 or .001
```

DDM aggregation

```{r}

alt_run_agg_ID_ddm <- alt_run %>%
  mutate(RT_s = rt/1000) %>% #convert rt to seconds
  group_by(id, valence, lvalence, switch, cycle2) %>%
  summarize(RT_s_m = mean(RT_s[filter_correct == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[filter_correct == 0], na.rm = TRUE),
            error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>% #this is looking at everything in one row, have to agg data like this for DDM becuase it does not compute vectors but rows
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-error), #were essentially making a dataframe that shows up as an extra cell next to each part
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  unnest(ezddm) #this extracts the newly created dataframe per column into its own separate columns 

alt_run_agg_ddm <- alt_run_agg_ID_ddm %>%
  group_by(id, valence,lvalence, switch, cycle2) %>%
  normWS(s = "id", dv = "a") %>% #boundary separation. this is starting value
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>% #drift rate
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>% #non-decision time
  mutate(Ter = DV_n) %>%
  group_by(valence,lvalence, switch, cycle2) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[1],
            a_ci_upper = get_ci(a, a_m)[2],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[1],
            v_ci_upper = get_ci(v, v_m)[2],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[1],
            Ter_ci_upper = get_ci(Ter, Ter_m)[2],)

#make a separate object that is averaging across the no-switch 2,3 and 4 average within those and then average within those variances. 
#this agg is the one we use for he lmer models

alt_run_agg_ID_ddm_collapsed <- alt_run  %>% #doing this a different way, if we groupby everything but cycle, the switch v no-switch will auto treat 2,3,4 as averaged i think
  mutate(RT_s = rt/1000) %>% #convert rt to seconds
  group_by(id, valence,valence_contr, lvalence, lvalence_contr, switch, g_c) %>%
  summarize(rt_log =  mean(rt_log[filter_correct == 0], na.rm = TRUE),
            RT_s_m = mean(RT_s[filter_correct == 0], na.rm = TRUE),
            RT_s_var = var(RT_s[filter_correct == 0], na.rm = TRUE),
            error = mean(error, na.rm = TRUE),
            N_trials = n()) %>%
  rowwise() %>% #this is looking at everything in one row, have to agg data like this for DDM becuase it does not compute vectors but rows
  mutate(ezddm = list(ezddm(propCorrect = convert_extremes(1-error), #were essentially making a dataframe that shows up as an extra cell next to each part
                            rtCorrectVariance_seconds = RT_s_var, 
                            rtCorrectMean_seconds = RT_s_m, 
                            nTrials = N_trials))) %>%
  unnest(ezddm) #this extracts the newly created dataframe per column into its own separate columns 

alt_run_agg_ddm_collapsed <- alt_run_agg_ID_ddm_collapsed %>%
  group_by(id, valence,valence_contr, lvalence, lvalence_contr, switch, g_c) %>%
  normWS(s = "id", dv = "a") %>% #boundary separation. this is starting value
  mutate(a = DV_n) %>%
  normWS(s = "id", dv = "v") %>% #drift rate
  mutate(v = DV_n) %>%
  normWS(s = "id", dv = "Ter") %>% #non-decision time
  mutate(Ter = DV_n) %>%
  group_by(id, valence,valence_contr, lvalence, lvalence_contr, switch) %>%
  summarize(a_m = mean(a, na.rm = TRUE),
            a_ci_lower = get_ci(a, a_m)[1],
            a_ci_upper = get_ci(a, a_m)[2],
            v_m = mean(v, na.rm = TRUE),
            v_ci_lower = get_ci(v, v_m)[1],
            v_ci_upper = get_ci(v, v_m)[2],
            Ter_m = mean(Ter, na.rm = TRUE),
            Ter_ci_lower = get_ci(Ter, Ter_m)[1],
            Ter_ci_upper = get_ci(Ter, Ter_m)[2],)



```

### DDM vis

```{r}
plt_ddm_a <- ggplot(alt_run_agg_ddm, aes(x = cycle2, y = a_m, color = valence, linetype = lvalence, group = interaction(valence,lvalence )))+
  geom_line(position = position_dodge(width = 0.25))+
  geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper), width = 0.1, position = position_dodge(width = 0.25))+
  apa_theming()

plt_ddm_v <- ggplot(alt_run_agg_ddm, aes(x = cycle2, y = v_m, color = valence, linetype = lvalence, group = interaction(valence,lvalence )))+
  geom_line(position = position_dodge(width = 0.25))+
  geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper), width = 0.1, position = position_dodge(width = 0.25))+
  apa_theming()


plt_ddm_Ter <- ggplot(alt_run_agg_ddm, aes(x = cycle2, y = Ter_m, color = valence, linetype = lvalence, group = interaction(valence,lvalence )))+
  geom_line(position = position_dodge(width = 0.25))+
  geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper), width = 0.1, position = position_dodge(width = 0.25))+
  apa_theming()

ggpubr::ggarrange(plt_ddm_a, plt_ddm_v, plt_ddm_Ter, common.legend = TRUE, nrow = 1)  

#ok this works but idk how to interpret
```

plotting with the aggregation averaging between no-switch cycles

```{r}

plt_ddm_a <- ggplot(alt_run_agg_ddm_collapsed, aes(x = switch, y = a_m, color = valence, linetype = lvalence, group = interaction(valence,lvalence)))+
  geom_line(position = position_dodge(width = 0.25))+
  geom_errorbar(aes(ymin = a_ci_lower, ymax = a_ci_upper), width = 0.1, position = position_dodge(width = 0.25))+
  theme_classic()

plt_ddm_v <- ggplot(alt_run_agg_ddm_collapsed, aes(x = switch, y = v_m, color = valence, linetype = lvalence, group = interaction(valence,lvalence)))+
  geom_line(position = position_dodge(width = 0.25))+
  geom_errorbar(aes(ymin = v_ci_lower, ymax = v_ci_upper), width = 0.1, position = position_dodge(width = 0.25))+
  theme_classic()


plt_ddm_Ter <- ggplot(alt_run_agg_ddm_collapsed, aes(x = switch, y = Ter_m, color = valence, linetype = lvalence, group = interaction(valence,lvalence)))+
  geom_line(position = position_dodge(width = 0.25))+
  geom_errorbar(aes(ymin = Ter_ci_lower, ymax = Ter_ci_upper), width = 0.1, position = position_dodge(width = 0.25))+
  theme_classic()

ggpubr::ggarrange(plt_ddm_a, plt_ddm_v, plt_ddm_Ter, common.legend = TRUE, nrow = 1) 
```

### DDM Models

with valence contrasts

```{r}
model_a_c <- xfun::cache_rds({
  lmer(a ~ valence_contr * lvalence_contr *switch + (valence_contr+lvalence_contr+switch | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
}, dir = "sophia/output/", file = "model_a_c.rds", rerun = rerun_all)
summary(model_a_c)

tab_model(model_a_c, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')

#baseline model comparisions
model_a_int <- 
  lmer(a ~ valence_contr * lvalence_contr *switch + (1|id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)

summary(model_a_int)

tab_model(model_a_int, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

for one variable
```{r}
#this creates singularity issues so running model with only 1 random intercept included and then running anova to compare them together

 a_val<-  lmer(a ~ valence_contr * lvalence_contr *switch + (valence_contr | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(a_val)

anova(model_a_int, a_val) #not sig

 a_lval<-  lmer(a ~ valence_contr * lvalence_contr *switch + (lvalence_contr | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(a_lval)

anova(model_a_int, a_lval) #sig

 a_switch<-  lmer(a ~ valence_contr * lvalence_contr *switch + (switch | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(a_switch)

anova(model_a_int, a_switch) # sig

```

for two values all singular
```{r}
 a_val_lval<-  lmer(a ~ valence_contr * lvalence_contr *switch + (valence_contr+lvalence_contr | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(a_val_lval)

anova(model_a_int, a_val_lval) #not sig

 a_lval_switch<-  lmer(a ~ valence_contr * lvalence_contr *switch + (lvalence_contr +switch | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(a_lval_switch)

anova(model_a_int, a_lval_switch) #sig

 a_switch_val<-  lmer(a ~ valence_contr * lvalence_contr *switch + (switch +valence_contr | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(a_switch_val)

anova(model_a_int, a_switch_val) # sig
```

Model A that converges, intercept only model

```{r}
model_a_simple <- xfun::cache_rds({
  lmer(a ~ valence_contr * lvalence_contr *switch + (1|id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
}, dir = "sophia/output/", file = "model_a_c.rds", rerun = rerun_all)
summary(model_a_simple)

tab_model(model_a_simple, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
 
 
```

anovas all sig but none are singular + dont converge

```{r}
model_v_c<- xfun::cache_rds({
  lmer(v ~ valence_contr * lvalence_contr *switch + (valence_contr+lvalence_contr+switch | id), control = lmerControl(optimizer = "bobyqa"),data = alt_run_agg_ID_ddm_collapsed)
}, dir = "sophia/output/", file = "model_v_c.rds", rerun = rerun_all)
#summary(model_v_c)

tab_model(model_v_c, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

for one value
```{r}
model_v_int<-  lmer(v ~ valence_contr * lvalence_contr *switch + (1 | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(model_v_int)

 v_val<-  lmer(v ~ valence_contr * lvalence_contr *switch + (valence_contr | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(v_val)

anova(model_v_int, v_val) #sig

 v_lval<-  lmer(v ~ valence_contr * lvalence_contr *switch + (lvalence_contr | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(v_lval)

anova(model_v_int, v_lval) #not sig

 v_switch<-  lmer(v ~ valence_contr * lvalence_contr *switch + (switch | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(v_switch)

anova(model_v_int, v_switch) #sig
```
two random effect
```{r}
 v_val_lval<-  lmer(v ~ valence_contr * lvalence_contr *switch + (valence_contr+lvalence_contr | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(v_val_lval) #singular

anova(model_v_int, v_val_lval) # sig

 v_lval_switch<-  lmer(v ~ valence_contr * lvalence_contr *switch + (lvalence_contr +switch | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(v_lval_switch) #agood

anova(model_v_int, v_lval_switch) #sig

 v_switch_val<-  lmer(v ~ valence_contr * lvalence_contr *switch + (switch +valence_contr | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(v_switch_val) #good 

anova(model_v_int, v_switch_val) # sig

AIC(v_lval_switch, v_switch_val)
BIC(v_lval_switch, v_switch_val)
```


final model with val and switch random int
```{r}
model_final_v <- xfun::cache_rds({
  lmer(v ~ valence_contr * lvalence_contr *switch + (valence_contr+switch | id), control = lmerControl(optimizer = "bobyqa"),data = alt_run_agg_ID_ddm_collapsed)
}, dir = "sophia/output/", file = "model_final_v.rds", rerun = rerun_all)
summary(model_final_v)
tab_model(model_final_v, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')

anova(model_final_v, v_switch) #sig

model_final2_v <- xfun::cache_rds({
  lmer(v ~ valence_contr * lvalence_contr *switch*g_c + (switch +valence_contr | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
}, dir = "sophia/output/", file = "model_final2_v.rds", rerun = rerun_all)
summary(model_final2_v) #good 
tab_model(model_final2_v, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')

#evidence for an antitradeoff, the more pos here the more of an antitradeoff pattern 
```

```{r}
model_Ter_c <- xfun::cache_rds({
  lmer(Ter ~ valence_contr * lvalence_contr *switch + (valence_contr+lvalence_contr+switch | id), control = lmerControl(optimizer = "bobyqa"),data = alt_run_agg_ID_ddm_collapsed)
}, dir = "sophia/output/", file = "model_Ter_c.rds", rerun = rerun_all)
summary(model_Ter_c)

tab_model(model_Ter_c, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

for one value
```{r}
model_Ter_int <-
  lmer(Ter ~ valence_contr * lvalence_contr *switch + (1 | id), control = lmerControl(optimizer = "bobyqa"),data = alt_run_agg_ID_ddm_collapsed)

summary(model_Ter_int)

 ter_val<-  lmer(Ter ~ valence_contr * lvalence_contr *switch + (valence_contr | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(ter_val)

#anova(model_Ter_int, ter_val) #not sig

 ter_lval<-  lmer(Ter ~ valence_contr * lvalence_contr *switch + (lvalence_contr | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(ter_lval)

#anova(model_Ter_int, ter_lval) #sig

 ter_switch<-  lmer(Ter ~ valence_contr * lvalence_contr *switch + (switch | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(ter_switch)

#anova(model_Ter_int, ter_switch) #sig
```
for two values
```{r}
 ter_val_lval<-  lmer(Ter ~ valence_contr * lvalence_contr *switch + (valence_contr+lvalence_contr | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(ter_val_lval) #singular

anova(model_Ter_int, ter_val_lval) # sig

 ter_lval_switch<-  lmer(Ter ~ valence_contr * lvalence_contr *switch + (lvalence_contr +switch | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(ter_lval_switch) #singular

anova(model_Ter_int, ter_lval_switch) #sig

 ter_switch_val<-  lmer(Ter ~ valence_contr * lvalence_contr *switch + (switch +valence_contr | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
 
summary(ter_switch_val) #singualr

anova(model_Ter_int, ter_switch_val) # sig
```

ter simplest model int only

```{r}
model_Ter_simple <- xfun::cache_rds({
  lmer(Ter ~ valence_contr * lvalence_contr *switch + (1 | id), control = lmerControl(optimizer = "bobyqa"),data = alt_run_agg_ID_ddm_collapsed)
}, dir = "sophia/output/", file = "model_Ter_c.rds", rerun = rerun_all)
summary(model_Ter_simple)

tab_model(model_Ter_simple, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

without valence contrasts

```{r}
# model_a <-xfun::cache_rds({
#   lmer(a ~ valence * lvalence *switch + (valence+lvalence+switch | id), control = lmerControl(optimizer = "bobyqa"),data = alt_run_agg_ID_ddm_collapsed)
# }, dir = "sophia/output/", file = "model_a.rds", rerun = rerun_all)
# summary(model_a)
# 
# tab_model(model_a, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

```{r}
# model_v <- xfun::cache_rds({
#   lmer(v ~ valence * lvalence *switch + (valence+lvalence+switch | id), control = lmerControl(optimizer = "bobyqa"),data = alt_run_agg_ID_ddm_collapsed)
# }, dir = "sophia/output/", file = "model_v.rds", rerun = rerun_all)
# summary(model_v)
# 
# tab_model(model_v, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

```{r}
# model_Ter <- xfun::cache_rds({
#   lmer(Ter ~ valence * lvalence *switch + (valence+lvalence+switch | id), control = lmerControl(optimizer = "bobyqa"), data = alt_run_agg_ID_ddm_collapsed)
# }, dir = "sophia/output/", file = "model_Ter.rds", rerun = rerun_all)
# summary(model_Ter)
# 
# tab_model(model_Ter, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

## Within subject analysis

(although altruns does show a speed accuracy relationship)

not only residualize the general trends but by task (bc task is assymetric)

add in helmert contrast (3 for runs, 2 for cues)

visualization for models

to fix singularity, can run a model comparisons to see what fixed effects to keep, can do this by running an ANOVA

auto correlations lag rt_log and rt_log

These models using the residual are both run with subject intercepts added back in, this is done at the datacleaning stage at the beginning

```{r}
#c here means centered not contrast
alt_run <- alt_run %>%
  ungroup() %>%
  mutate(rt_log_res_w_s_int_c = rt_log_res_w_s_int - mean(rt_log_res_w_s_int, na.rm = TRUE),
         lrt_log_res_w_s_int_c = lrt_log_res_w_s_int - mean(lrt_log_res_w_s_int, na.rm = TRUE))
```

by valence contrast with cycle helmert

```{r}
# autocor_model_c_helmert <- xfun::cache_rds({
#   
#   lmer(rt_log_res_w_s_int_c ~ valence_contr * lvalence_contr * cycle_helmert * lrt_log_res_w_s_int_c + (valence_contr + lvalence_contr + cycle_helmert + lrt_log_res_w_s_int_c|id), control = lmerControl(optimizer = "bobyqa"),
#      alt_run %>% filter(filter_correct==0))
# }, dir = "sophia/output/", file = "autocor_model_c_helmert.rds", rerun = rerun_all)
# summary(autocor_model_c_helmert)
# 
# tab_model(autocor_model_c_helmert, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
# 
# #need to use function coeficents(autocor_model_c) to get the averages from the model and put it back into the dataframe to get indivusual subject averages back into the data. need to create a new dataframe with this information left_join into dataframe 
# 
# 


```

no valence contrast with cycle helmert

```{r}
# autocor_model_helmert <- xfun::cache_rds({
#   lmer(rt_log_res_w_s_int_c  ~ valence * lvalence * cycle_helmert * lrt_log_res_w_s_int_c + (valence + lvalence + cycle_helmert + lrt_log_res_w_s_int_c|id), control = lmerControl(optimizer = "bobyqa"),
#      alt_run %>% 
#        filter(filter_correct == 0))
# }, dir = "sophia/output/", file = "autocor_model_helmert.rds", rerun = rerun_all)
# summary(autocor_model_helmert)
# 
# tab_model(autocor_model_helmert, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

valence contrast with switch

```{r}
autocor_model_c <- xfun::cache_rds({
  
  lmer(rt_log_res_w_s_int_c ~ valence_contr * lvalence_contr * switch * lrt_log_res_w_s_int_c + (valence_contr + lvalence_contr + switch + lrt_log_res_w_s_int_c|id), control = lmerControl(optimizer = "bobyqa"),
     alt_run %>% filter(filter_correct==0))
}, dir = "sophia/output/", file = "autocor_model_c.rds", rerun = rerun_all)
summary(autocor_model_c)

tab_model(autocor_model_c, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

```{r}
autocor_model_lrt <- 
  
  lmer(rt_log_res_w_s_int_c ~ valence_contr * lvalence_contr * switch * lrt_log_res_w_s_int_c + (lrt_log_res_w_s_int_c|id), control = lmerControl(optimizer = "bobyqa"),
     alt_run %>% filter(filter_correct==0))
summary(autocor_model_lrt)
tab_model(autocor_model_lrt, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')

#val

autocor_model_val <- 
  
  lmer(rt_log_res_w_s_int_c ~ valence_contr * lvalence_contr * switch * lrt_log_res_w_s_int_c + (lrt_log_res_w_s_int_c+valence_contr|id), control = lmerControl(optimizer = "bobyqa"),
     alt_run %>% filter(filter_correct==0))
summary(autocor_model_val)

anova(autocor_model_lrt, autocor_model_val) #doesnt converge 
#lval

autocor_model_lval <- 
  
  lmer(rt_log_res_w_s_int_c ~ valence_contr * lvalence_contr * switch * lrt_log_res_w_s_int_c + (lrt_log_res_w_s_int_c+lvalence_contr|id), control = lmerControl(optimizer = "bobyqa"),
     alt_run %>% filter(filter_correct==0))
summary(autocor_model_lval)

anova(autocor_model_lrt, autocor_model_lval) #sig and converges 
#switch

autocor_model_switch <- 
  
  lmer(rt_log_res_w_s_int_c ~ valence_contr * lvalence_contr * switch * lrt_log_res_w_s_int_c + (lrt_log_res_w_s_int_c+switch|id), control = lmerControl(optimizer = "bobyqa"),
     alt_run %>% filter(filter_correct==0))
summary(autocor_model_switch)

anova(autocor_model_lrt, autocor_model_switch) #sig and converges
```
two values 
```{r}
autocor_model_val_lval <- 
  
  lmer(rt_log_res_w_s_int_c ~ valence_contr * lvalence_contr * switch * lrt_log_res_w_s_int_c + (lrt_log_res_w_s_int_c+valence_contr+lvalence_contr|id), control = lmerControl(optimizer = "bobyqa"),
     alt_run %>% filter(filter_correct==0))
summary(autocor_model_val_lval) #singular

anova(autocor_model_lrt, autocor_model_val_lval)  
#lval

autocor_model_switch_val <- 
  
  lmer(rt_log_res_w_s_int_c ~ valence_contr * lvalence_contr * switch * lrt_log_res_w_s_int_c + (lrt_log_res_w_s_int_c+switch+valence_contr|id), control = lmerControl(optimizer = "bobyqa"),
     alt_run %>% filter(filter_correct==0))
summary(autocor_model_switch_val) #singular

anova(autocor_model_lrt, autocor_model_switch_val) #sig
```


```{r}
#final model, converges and is not singular anova sig

autocor_model_switch_lval <- xfun::cache_rds({
  
  lmer(rt_log_res_w_s_int_c ~ valence_contr * lvalence_contr * switch * lrt_log_res_w_s_int_c + (lrt_log_res_w_s_int_c+lvalence_contr+switch|id), control = lmerControl(optimizer = "bobyqa"),
     alt_run %>% filter(filter_correct==0))
}, dir = "sophia/output/", file = "autocor_model_switch_lval.rds", rerun = rerun_all)

summary(autocor_model_switch_lval)
print(autocor_model_switch_lval, correlation = TRUE)
tab_model(autocor_model_switch_lval, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')

```


no valence contrast with switch

```{r}
# autocor_model <- xfun::cache_rds({
#   lmer(rt_log_res_w_s_int_c  ~ valence * lvalence * switch * lrt_log_res_w_s_int_c + (valence + lvalence + switch + lrt_log_res_w_s_int_c|id), control = lmerControl(optimizer = "bobyqa"),
#      alt_run %>% 
#        filter(filter_correct == 0))
# }, dir = "sophia/output/", file = "autocor_model.rds", rerun = rerun_all)
# summary(autocor_model)
# 
# tab_model(autocor_model, show.est = T, auto.label = F, show.stat = T, df.method = 'satterthwaite')
```

## psychometric differences

```{r}
#first from the long format calculate the drift rate then when you pivot wider add in drift rate did this earlier 

#reorg using pivot wider, each subject is a row and have a column for every possible combination of valence
indif <- alt_run_agg_ID_ddm_collapsed %>% 
  pivot_wider(id_cols = id, names_from = c(valence, lvalence, switch), 
              values_from = c(v, a, Ter, rt_log, error), 
              names_glue = "{.value}_s{switch}_cbiv{valence}_lbiv{lvalence}") %>% 
  ungroup()
indif
```

### by drift rate

```{r}
#first from the long format calculate the drift rate then when you pivot wider add in drift rate

#building up model 1 
lm(v_s1_cbiv1_lbiv1 ~ 
     v_s0_cbiv1_lbiv1,
      data = indif ) %>% 
  summary()

lm(v_s1_cbiv1_lbiv1 ~ 
     v_s0_cbiv1_lbiv1 + 
     v_s0_cbiv2_lbiv1,
      data = indif ) %>% 
  summary()

lm(v_s1_cbiv1_lbiv1 ~ 
     v_s0_cbiv1_lbiv1 + 
     v_s0_cbiv2_lbiv1 +
     v_s0_cbiv1_lbiv2,
      data = indif ) %>% 
  summary()

lm(v_s1_cbiv1_lbiv1 ~ 
     v_s0_cbiv1_lbiv1 + 
     v_s0_cbiv2_lbiv1 +
     v_s0_cbiv1_lbiv2 +
     v_s0_cbiv2_lbiv2,
   data = indif ) %>% 
  summary()
```

```{r}
#model 2
lm(v_s1_cbiv2_lbiv1 ~ 
     v_s0_cbiv1_lbiv1,
      data = indif ) %>% 
  summary()

lm(v_s1_cbiv2_lbiv1 ~ 
     v_s0_cbiv1_lbiv1 + 
     v_s0_cbiv2_lbiv1,
      data = indif ) %>% 
  summary()

lm(v_s1_cbiv2_lbiv1 ~ 
     v_s0_cbiv1_lbiv1 + 
     v_s0_cbiv2_lbiv1 +
     v_s0_cbiv1_lbiv2,
      data = indif ) %>% 
  summary()

lm(v_s1_cbiv2_lbiv1 ~ 
     v_s0_cbiv1_lbiv1 + 
     v_s0_cbiv2_lbiv1 +
     v_s0_cbiv1_lbiv2 +
     v_s0_cbiv2_lbiv2,
   data = indif ) %>% 
  summary()


```

```{r}
#model 3 
lm(v_s1_cbiv1_lbiv2 ~ 
     v_s0_cbiv1_lbiv1,
 data = indif ) %>% 
  summary()

lm(v_s1_cbiv1_lbiv2 ~ 
     v_s0_cbiv1_lbiv1 + 
     v_s0_cbiv2_lbiv1,
 data = indif ) %>% 
  summary()

lm(v_s1_cbiv1_lbiv2 ~ 
     v_s0_cbiv1_lbiv1 + 
     v_s0_cbiv2_lbiv1 +
     v_s0_cbiv1_lbiv2,
 data = indif ) %>% 
  summary()

lm(v_s1_cbiv1_lbiv2 ~ 
     v_s0_cbiv1_lbiv1 + 
     v_s0_cbiv2_lbiv1 +
     v_s0_cbiv1_lbiv2 +
     v_s0_cbiv2_lbiv2,
   data = indif ) %>% 
  summary()
```

```{r}
#model 4
lm(v_s1_cbiv2_lbiv2 ~ 
     v_s0_cbiv1_lbiv1,
   data = indif ) %>% 
  summary()

lm(v_s1_cbiv2_lbiv2 ~ 
     v_s0_cbiv1_lbiv1 + 
     v_s0_cbiv2_lbiv1,
   data = indif ) %>% 
  summary()

lm(v_s1_cbiv2_lbiv2 ~ 
     v_s0_cbiv1_lbiv1 + 
     v_s0_cbiv2_lbiv1 +
     v_s0_cbiv1_lbiv2,
   data = indif ) %>% 
  summary()

lm(v_s1_cbiv2_lbiv2 ~ 
     v_s0_cbiv1_lbiv1 + 
     v_s0_cbiv2_lbiv1 +
     v_s0_cbiv1_lbiv2 +
     v_s0_cbiv2_lbiv2,
   data = indif ) %>% 
  summary()
```

### by rt log

```{r}
#model 1
lm(rt_log_s1_cbiv1_lbiv1 ~ 
     rt_log_s0_cbiv1_lbiv1,
    data = indif ) %>% 
  summary()

lm(rt_log_s1_cbiv1_lbiv1 ~ 
     rt_log_s0_cbiv1_lbiv1 + 
     rt_log_s0_cbiv2_lbiv1,
    data = indif ) %>% 
  summary()

lm(rt_log_s1_cbiv1_lbiv1 ~ 
     rt_log_s0_cbiv1_lbiv1 + 
     rt_log_s0_cbiv2_lbiv1 +
     rt_log_s0_cbiv1_lbiv2,
 data = indif ) %>% 
  summary()

lm(rt_log_s1_cbiv1_lbiv1 ~ 
     rt_log_s0_cbiv1_lbiv1 + 
     rt_log_s0_cbiv2_lbiv1 +
     rt_log_s0_cbiv1_lbiv2 +
     rt_log_s0_cbiv2_lbiv2,
   data = indif ) %>% 
  summary()

```

```{r}
#model 2

lm(rt_log_s1_cbiv2_lbiv1 ~ 
     rt_log_s0_cbiv1_lbiv1,
    data = indif ) %>% 
  summary()

lm(rt_log_s1_cbiv2_lbiv1 ~ 
     rt_log_s0_cbiv1_lbiv1 + 
     rt_log_s0_cbiv2_lbiv1,
    data = indif ) %>% 
  summary()

lm(rt_log_s1_cbiv2_lbiv1 ~ 
     rt_log_s0_cbiv1_lbiv1 + 
     rt_log_s0_cbiv2_lbiv1 +
     rt_log_s0_cbiv1_lbiv2,
 data = indif ) %>% 
  summary()

lm(rt_log_s1_cbiv2_lbiv1 ~ 
     rt_log_s0_cbiv1_lbiv1 + 
     rt_log_s0_cbiv2_lbiv1 +
     rt_log_s0_cbiv1_lbiv2 +
     rt_log_s0_cbiv2_lbiv2,
   data = indif ) %>% 
  summary()
```

```{r}
#model 3

lm(rt_log_s1_cbiv1_lbiv2 ~ 
     rt_log_s0_cbiv1_lbiv1,
    data = indif ) %>% 
  summary()

lm(rt_log_s1_cbiv1_lbiv2 ~ 
     rt_log_s0_cbiv1_lbiv1 + 
     rt_log_s0_cbiv2_lbiv1,
    data = indif ) %>% 
  summary()

lm(rt_log_s1_cbiv1_lbiv2 ~ 
     rt_log_s0_cbiv1_lbiv1 + 
     rt_log_s0_cbiv2_lbiv1 +
     rt_log_s0_cbiv1_lbiv2,
 data = indif ) %>% 
  summary()

lm(rt_log_s1_cbiv1_lbiv2 ~ 
     rt_log_s0_cbiv1_lbiv1 + 
     rt_log_s0_cbiv2_lbiv1 +
     rt_log_s0_cbiv1_lbiv2 +
     rt_log_s0_cbiv2_lbiv2,
   data = indif ) %>% 
  summary()
```

```{r}
#model 4

lm(rt_log_s1_cbiv1_lbiv2 ~ 
     rt_log_s0_cbiv1_lbiv1,
    data = indif ) %>% 
  summary()

lm(rt_log_s1_cbiv2_lbiv2 ~ 
     rt_log_s0_cbiv1_lbiv1 + 
     rt_log_s0_cbiv2_lbiv1,
    data = indif ) %>% 
  summary()

lm(rt_log_s1_cbiv2_lbiv2 ~ 
     rt_log_s0_cbiv1_lbiv1 + 
     rt_log_s0_cbiv2_lbiv1 +
     rt_log_s0_cbiv1_lbiv2,
 data = indif ) %>% 
  summary()

lm(rt_log_s1_cbiv2_lbiv2 ~ 
     rt_log_s0_cbiv1_lbiv1 + 
     rt_log_s0_cbiv2_lbiv1 +
     rt_log_s0_cbiv1_lbiv2 +
     rt_log_s0_cbiv2_lbiv2,
   data = indif ) %>% 
  summary()
```

### by error

```{r}
#model 1
lm(error_s1_cbiv1_lbiv1 ~ 
     error_s0_cbiv1_lbiv1,
    data = indif ) %>% 
  summary()

lm(error_s1_cbiv1_lbiv1 ~ 
     error_s0_cbiv1_lbiv1 + 
     error_s0_cbiv2_lbiv1,
    data = indif ) %>% 
  summary()

lm(error_s1_cbiv1_lbiv1 ~ 
     error_s0_cbiv1_lbiv1 + 
     error_s0_cbiv2_lbiv1 +
     error_s0_cbiv1_lbiv2,
 data = indif ) %>% 
  summary()

lm(error_s1_cbiv1_lbiv1 ~ 
     error_s0_cbiv1_lbiv1 + 
     error_s0_cbiv2_lbiv1 +
     error_s0_cbiv1_lbiv2 +
     error_s0_cbiv2_lbiv2,
   data = indif ) %>% 
  summary()
```

```{r}
#model 2 
lm(error_s1_cbiv2_lbiv1 ~ 
     error_s0_cbiv1_lbiv1,
    data = indif ) %>% 
  summary()

lm(error_s1_cbiv2_lbiv1 ~ 
     error_s0_cbiv1_lbiv1 + 
     error_s0_cbiv2_lbiv1,
    data = indif ) %>% 
  summary()

lm(error_s1_cbiv2_lbiv1 ~ 
     error_s0_cbiv1_lbiv1 + 
     error_s0_cbiv2_lbiv1 +
     error_s0_cbiv1_lbiv2,
 data = indif ) %>% 
  summary()

lm(error_s1_cbiv2_lbiv1 ~ 
     error_s0_cbiv1_lbiv1 + 
     error_s0_cbiv2_lbiv1 +
     error_s0_cbiv1_lbiv2 +
     error_s0_cbiv2_lbiv2,
   data = indif ) %>% 
  summary()
```

```{r}
# model 3
lm(error_s1_cbiv1_lbiv2 ~ 
     error_s0_cbiv1_lbiv1,
    data = indif ) %>% 
  summary()

lm(error_s1_cbiv1_lbiv2 ~ 
     error_s0_cbiv1_lbiv1 + 
     error_s0_cbiv2_lbiv1,
    data = indif ) %>% 
  summary()

lm(error_s1_cbiv1_lbiv2 ~ 
     error_s0_cbiv1_lbiv1 + 
     error_s0_cbiv2_lbiv1 +
     error_s0_cbiv1_lbiv2,
 data = indif ) %>% 
  summary()

lm(error_s1_cbiv1_lbiv2 ~ 
     error_s0_cbiv1_lbiv1 + 
     error_s0_cbiv2_lbiv1 +
     error_s0_cbiv1_lbiv2 +
     error_s0_cbiv2_lbiv2,
   data = indif ) %>% 
  summary()
```

```{r}
#model 4
lm(error_s1_cbiv2_lbiv2 ~ 
     error_s0_cbiv1_lbiv1,
    data = indif ) %>% 
  summary()

lm(error_s1_cbiv2_lbiv2 ~ 
     error_s0_cbiv1_lbiv1 + 
     error_s0_cbiv2_lbiv1,
    data = indif ) %>% 
  summary()

lm(error_s1_cbiv2_lbiv2 ~ 
     error_s0_cbiv1_lbiv1 + 
     error_s0_cbiv2_lbiv1 +
     error_s0_cbiv1_lbiv2,
 data = indif ) %>% 
  summary()

lm(error_s1_cbiv2_lbiv2 ~ 
     error_s0_cbiv1_lbiv1 + 
     error_s0_cbiv2_lbiv1 +
     error_s0_cbiv1_lbiv2 +
     error_s0_cbiv2_lbiv2,
   data = indif ) %>% 
  summary()
```
